### 2021-06-03 paper.tex
Initial commit; copied images and text from thesis chapter on fluting instabilities

\documentclass[12pt]{article}
\usepackage[T1]{fontenc} % modern encoding
\usepackage[utf8]{inputenc}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scaled=0.95]{inconsolata}
\usepackage[margin=0.5in]{geometry}

\usepackage{graphicx}  % standard package for importing graphics files

%% --- user packages ---

\usepackage{csquotes}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{grffile}
\usepackage{overpic}
\usepackage{float}
\usepackage{enumitem}
\usepackage{amsfonts}
\usepackage{easy-todo}
\usepackage{listings}

\usepackage[
backend=biber,
style=numeric,
firstinits,
url=false,
isbn=false,
eprint=false
]{biblatex}
\renewbibmacro{in:}{}
%\AtEveryBibitem{\clearfield{pages}} 
\DeclareFieldFormat{date}{%
  \thefield{year}}
\DeclareFieldFormat{issue}{\bfseries{#1}}

\addbibresource{bib.bib}

\usepackage{lineno}
\usepackage[citecolor=blue]{hyperref}
%\modulolinenumbers[5]

% Url style
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\urlstyle{same}

\newdimen\figrasterwd
\figrasterwd\textwidth

% For editing
\usepackage{color}
\newcommand{\rr}[1]{\textcolor{red}{#1}}
\newcommand{\bb}[1]{\textcolor{blue}{#1}}
\newcommand{\rs}[1]{\textcolor{blue}{#1}}
%\newcommand{\rr}[1]{#1}
%\newcommand{\bb}[1]{#1}
%\newcommand{\rs}[1]{#1}

%\newcommand\todo[1]{\textcolor{red}{#1}}

%% --- user commands ---

% Make tensors and vectors bold
\newcommand{\ten}[1]{{\bm #1}}
\renewcommand{\vec}[1]{{\bm #1}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\mycaption}[2]{\caption[#1]{\emph{#1} #2}}

%% --- end user commands ---

\begin{document}
\lstset{
  language=[90]Fortran,
  basicstyle=\ttfamily,
  keywordstyle=\color{red},
  commentstyle=\color{green},
  frame=single
}

Kink and fluting instabilities in a dynamically twisted flux tube

\graphicspath{{images/kink_instability_straight/}}

\section{Introduction}

\todo{add switching function}

The helical kink instability is a form of ideal MHD instability which occurs in highly twisted magnetic flux tubes such as those making up much of the solar corona~\cite{realeCoronalLoopsObservations2014} and has been well studied in the coronal context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003c,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020a}. Given its energetic nonlinear development, it is considered a potential mechanism for heating the solar corona through the theory of nanoflares~\cite{klimchukSolvingCoronalHeating2006a,browningMechanismsSolarCoronal1991} and a key mechanism in the production of solar flares~\cite{hoodKinkInstabilitySolar1979}. Previous work by the same authors has investigated a twisted magnetic flux tube already linearly unstable to the helical kink instability, investigating particularly the effect of anisotropic viscosity on the nonlinear dynamics~\cite{quinnEffectAnisotropicViscosity2020a}. In~\cite{quinnEffectAnisotropicViscosity2020a} and most other investigations of the kink instability, a perturbation is applied to an already significantly twisted flux tube. An alternative way to excite the instability is to start with an initially straight field and apply twisting motions at the boundaries to form a twisted flux tube which eventually becomes unstable. This kind of dynamic excitation of the kink instability is useful in that it represents more closely the real development of a magnetic flux tube and associated instabilities in the solar corona. The dynamic twisting of the flux tube reveals an additional instability, the fluting instability, which has been theorised (for example, in~\cite{priestMagnetohydrodynamicsSuna}) but not yet observed in coronal simulations or observations, to our knowledge.

The fluting instability arises in magnetised plasmas where the plasma pressure gradient is directed in the same direction as the field line curvature, that is the pressure and magnetic tension forces compete. This is similar to the competition between pressure and gravitational forces which gives rise to the Rayleigh-Taylor instability (RTI). In MHD, the RTI is a typical example of an ideal interchange instability, where magnetic field lines are minimally bent and are, instead, exchanged during the evolution of the instability. The ideal fluting instability is another example of an ideal interchange instability, but confined to a cylindrical geometry, the name ``fluting instability'' referring to its likeness to a fluted column. In a twisted flux tube like a coronal loop, the magnetic curvature is always directed towards the axis so the tube may be unstable to fluting when the pressure decreases outwards from a high-pressure core. Such a pressure distribution is found in the flux tubes studied here. The appearance of the fluting instability is illustrated by, for example, the pressure contours in figure~\ref{fig:kink_field_line_plots}, where the perturbations follow the pitch of the twisted field.

In other solar contexts, interchange instabilities can be found in the form of ballooning modes in arcades~\cite{hoodBallooningInstabilitiesSolar1986}, as the instability which forms tubes of specific size in the photosphere~\cite{bunteInterchangeInstabilitySolar1993} and in the buoyancy of flux tubes~\cite{schuesslerInterchangeInstabilitySmall1984}. However, the instability is more commonly studied in fusion contexts.

While the stability of both the ideal and resistive fluting instabilities has been studied extensively in fusion research~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}, the focus is generally on understanding how a particular plasma device may be stabilised to the instability in particular geometries such as that of the mirror machine~\cite{jungwirthTheoryFluteInstability1965} or in toroidal geometries such as the tokomak~\cite{shafranovFluteInstabilityCurrentcarrying1968}. The resistive fluting instability (also known as the resistive interchange instability) can be excited even when the ideal fluting instability is stabilised. As a result, this has been given significantly more attention~\cite{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}. While this body of research is useful and applicable in solar contexts, it is mostly limited to the stability and linear development of the fluting instability. More detailed investigations of its nonlinear development is required to understand its importance in the context of coronal dynamics and coronal heating. The development of the fluting instability and its interaction with the simultaneously growing kink instability is the focus of this work and the experiments described here represent an initial exploration into the nonlinear fluting instability in the solar corona.

\subsection{The fluting instability}

In general, the stability of a cylindrical twisted magnetic flux tube is analysed using perturbations of the form
\begin{equation}
  \label{eq:kink_perturbation}
\xi(r, \theta, z) = \xi(r) e^{i(m\theta + kz)},
\end{equation}
where $m$ and $k$ are the wavenumbers in the $\theta$ and $z$ directions, respectively. The helical kink instability occurs for perturbations where $m=1, k\ne0$ and is the only instability of this form which is a body instability, that is it moves the entire body of the flux tube. Perturbations where $m>1$ are termed fluting or interchange instabilities.

When the magnetic field is sheared, as in a twisted magnetic flux tube, an interchange instability (such as the fluting instability) is confined to a surface where the peaks and troughs follow the shear of the field. That is, the instability is confined to the surface where the perturbation wavevector $(0, m/r, k)$ is perpendicular to the direction of the field which, in an axisymmetric, twisted flux tube, is located at a radius $r$ given by
\begin{equation}
  \label{eq:resonant_surface}
\frac{m}{r} B_{\theta}(r) + kB_z(r) \approx 0.
\end{equation}

The stability of an infinite cylindrical flux tube to perturbations of the form~\eqref{eq:kink_perturbation} is given by the classical Suydam's criterion
\begin{equation}
  \label{eq:suydams_criterion}
\frac{B_z^2 S^2}{4} + 2 r p' > 0,
\end{equation}
where $S = r q'/q$ is a measure of the shear, $q = 2\pi r B_z / L B_{\theta}$ is the safety factor for a flux tube of length $L$ and a dash denotes differentiation with respect to $r$~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998}. This applies to both fluting and kink instabilities although many additional effects such as line-tying are not incorporated into the corresponding linear analysis. The effect of line-tying on the kink instability can be found in~\cite{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion} is not satisfied, the flux tube may be unstable to perturbations of the form~\eqref{eq:kink_perturbation}. When $m>1$, the perturbations remain local to resonant surfaces given by~\eqref{eq:resonant_surface}.

When Suydam's criterion is satisfied and the flux tube is linearly stable, it may still be unstable to non-local perturbations, where the shear and pressure are small enough that interchange perturbations do not need to satisfy~\eqref{eq:resonant_surface}. Additionally, the inclusion of resistivity generally reduces the stabilising effect of the shear, permitting growth of a resistive interchange mode, albeit at a slower rate than that of the ideal instability~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998}. It will be found that the ideal linear analysis of~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998} is sufficient for understanding the fluting instabilities investigated here since the associated flux tubes adequately fail the criterion~\eqref{eq:suydams_criterion}.

While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal fluting instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\cite{goldstonIntroductionPlasmaPhysics2020}) and is given by
\begin{equation}
  \label{eq:fluting_growth_rate}
\gamma^2 = \frac{2|\nabla p|}{\rho R_c},
\end{equation}
where $R_c$ is the radius of curvature of the magnetic field. This equation only applies when the pressure gradient and radius of curvature vector are in the same direction, that is the plasma is constrained by a concave magnetic field such that the pressure forces and magnetic tension forces are in competition. In a cylindrical, twisted flux tube, the field is always concave towards the central axis of the tube, so any inwardly directed pressure gradient is potentially unstable to fluting.

Throughout this chapter, the twisted flux tube generated by the drivers has a pressure profile which is approximately axisymmetric, and independent of $z$ away from the boundaries at $z=\pm2$, and has a negative gradient, hence $|\nabla p|$ may be written as $-d p/ dr$. Similarly, away from the boundaries, the magnetic field has a negligible $r$ component and little dependence on $\theta$ and $z$, allowing the field to be approximated as $\vec{B} = (0, B_{\theta}(r), B_z(r))^{\text{T}}$, in cylindrical coordinates $(r, \theta, z)$. For a twisted field of this form, the radius of curvature is given by 
\begin{equation}
  \label{eq:radius_of_curvature}
  R_c = \frac{1}{|(\vec{b}\cdot\nabla) \vec{b}|} = \frac{r}{b_{\theta}^2},
\end{equation}
where $\vec{b} = \vec{B}/|\vec{B}|$ is the unit vector in the direction of the magnetic field and $b_{\theta}$ is the component of $\vec{b}$ in the azimuthal direction. These approximations allows the growth rate to be written as
\begin{equation}
  \label{eq:fluting_growth_rate2}
\gamma_{ideal}^2 = \frac{-2p'}{\rho R_c}.
\end{equation}
This growth rate remains applicable while the flux tube remains relatively axisymmetric, that is while the kink instability remains in its linear phase.

In contrast to the precise form of the equilibrium state and perturbation studied in~\cite{quinnEffectAnisotropicViscosity2020a}, this is an experiment where a system is driven and instabilities occur organically as a result of noise providing a random perturbation. As a result of the driving, the flux tube is not in static equilibrium. Consequently, the stability criterion and linear growth rate presented previously are useful only as a guide and for approximate comparison.

\section{Numerical setup}

The non-dimensionalisation scheme and values are identical to those used in~\cite{quinnEffectAnisotropicViscosity2020a}. The magnetic field is prescribed as initially straight and uniform,
\begin{equation}
\vec{B} = (0, 0, 1)^{\text{T}},
\end{equation}
in a cube of dimension $[-2,2]^3$. The velocity is set everywhere to $\vec{u} = \vec{0}$, the density to $\rho = 1$, the internal energy to $\varepsilon = 8.67\times 10^{-4}$ (corresponding to a temperature of $10^6$ K). At the boundaries, the magnetic field, density, and energy are fixed to their initial values and the velocity to zero except at the upper and lower boundary where the twisting driver, described below, is prescribed. The spatial derivatives of these variables are also set to zero at the boundaries. The resolution is $512$ grid points per dimension, comparable to the highest resolution kink instability studies of~\cite{hoodCoronalHeatingMagnetic2009} or medium resolution studies of~\cite{barefordShockHeatingNumerical2015}. The switching function employed is the von Mises function~\eqref{eq:switching_function} and the switching parameter is chosen to be $a_0 = 150$, a value sufficiently large to ensure the viscosity is anisotropic throughout the entire domain.

\begin{figure}[t]
  \centering
  \begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{u_r.pdf}
  \caption{Radial dependence of driver}
  \label{fig:kink_radial_driver}
  \end{subfigure}
  \begin{subfigure}{.49\textwidth}
  \centering
  \includegraphics[width=1.0\linewidth]{u_t.pdf}
  \caption{Acceleration of driver}
  \label{fig:kink_driver_accel}
  \end{subfigure}

  \mycaption{Radial velocity profile $u_r(r)$ and acceleration profile $u_t(t)$ of the driver for parameters $u_0 = 0.15$, $r_d = 5$ and $t_r = 2$.}{}
  \label{fig:kink_driver}
\end{figure}

The flux rope is formed by prescribing a slowly accelerating, rotating flow at the upper $z$-boundary as
\begin{equation}
  \label{eq:null_twisting_profile}
  \vec{u} = u_0 u_r(r) u_t(t) (-y, x, 0)^T,
\end{equation}
where $u_r(r)$ describes the radial profile of the twisting motion in terms of the radius $r^2 = x^2 + y^2$,
\begin{equation}
  \label{eq:radial_twisting_function}
  u_r(r) = u_{r0}(1 + \tanh(1 - r_d r^2)),
\end{equation}
where $r_d$ controls the radial extent of the driver, $u_{r0}$ is a normalising factor, and $u_t(t)$ describes the imposed acceleration of the twisting motion,
\begin{equation}
  \label{eq:ramping_up_function}
  u_t(t) = \tanh^2(t/t_r),
\end{equation}
where the parameter $t_r$ controls the time taken to reach the final driver velocity $u_0$. The functions $u_r(r)$ and $u_t(t)$ are plotted in figure~\ref{fig:kink_driver}. At the lower boundary, the flow is in the opposite direction.

This form of driver allows the system to be accelerated slowly enough that the production of disruptive shocks and fast waves is minimal. It is unavoidable that some waves are produced during the boundary acceleration, however these usefully provide one source of noise which eventually forms a perturbation.

The driver velocity is set to $u_0 = 0.15$, the normalising factor is $u_{r0} = 2.08$, and setting $r_d = 5$ corresponds to a driver constrained to $r<1$ and with a peak velocity at $r\approx 0.38$. The ramping time is set to $t_r = 2$, resulting in an acceleration from $0$ to $u_0$ over approximately $5$ Alfv\'en times. These driver parameters correspond to a peak rotational period of $T_R = 15.92$, the length of time taken for one full turn to be injected by a single driver. Both drivers result in twist being added at a rate of $2\pi$ every $7.96$ Alfv\'en times. The twist profile across the entire flux tube develops in such a way that it is qualitatively similar to that studied in chapter~\cite{quinnEffectAnisotropicViscosity2020a} by $t\approx 20$, however the length of the flux tubes differs significantly. This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the fluting instability and the helical kink instability.

Two pairs of simulations were performed, one pair where the background resistivity is set to $\eta=10^{-3}$ and another where $\eta=10^{-4}$. As in chapter~\cite{quinnEffectAnisotropicViscosity2020a}, only background resistivity is used. Each simulation pair consists of one simulation using isotropic viscosity and another using the switching model~\eqref{eq:switching_model_simple} with the von Mises switching function~\eqref{eq:switching_function}. The value of viscosity is set to $\nu = 10^{-4}$ in all cases.

\section{Results}

The overall development of both instabilities is broadly similar for the two values of resistivity and is described initially. Focus is then placed on the development of the $\eta=10^{-4}$ cases, comparing the results of the two viscosity models. These cases illustrate the development of the instabilities while showcasing the effect of the viscosity models. Then the differences apparent in the $\eta=10^{-3}$ cases are summarised without a full exploration of the (qualitatively similar) results.

\subsection{Overview of instability development}

\begin{figure}[t]
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{current_profiles.pdf}
      \caption{Current}
      \label{fig:current_profiles}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{ohmic_heating_profiles.pdf}
      \caption{Ohmic heating}
      \label{fig:kink_straight_ohmic_heating_profile}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{pressure_profiles.pdf}
      \caption{Pressure}
      \label{fig:pressure_profiles}
    \end{subfigure}
  \mycaption{Gradients in the current density generate pressure gradients through Ohmic heating.}{All plots are from switching cases when $t=20$ through the plane $z=0$. Note the sign of the axial current density $j_z$ has been flipped for comparison and the Ohmic heating is given by $Q_{\eta} = \eta j^2$. The pressure profile of an additional test-case where $\eta=0$ is also shown.}%
  \label{fig:pressure_and_heating}
\end{figure}

In all cases, the initial reaction to the twisting at the upper and lower boundaries is two torsional Alfv\'en waves which travel along the tube from the upper and lower boundaries to the opposite boundary. The interaction between these waves produces an oscillating pattern in the kinetic energy with a period of approximately $4$ Alfv\'en times, equal to the time taken for an Alfv\'en wave to travel the entire length of the domain (visible early in figure~\ref{fig:kink_ke-4}).

As the field continues to be twisted, currents form due to the local shear in the magnetic field which heat the plasma through Ohmic heating. Due to the radial form of the driver, the magnitude of the current density is greatest at the axis of the tube, then decreases radially outwards (figure~\ref{fig:current_profiles}). The orientation of the twisting produces a current directed in the negative $z$-direction for $r\lessapprox0.5$. At $r \approx 0.5$ (corresponding to the radius of peak driving velocity) the current switches direction and is in the positive $z$-direction in a shell where $0.5\lessapprox r \lessapprox 0.8$. This form of twisted field with an inner core of current in one direction surrounded by an oppositely-directed current shell is similar to the prescribed field in chapter~\cite{quinnEffectAnisotropicViscosity2020a}.

This current profile is reflected in the radial Ohmic heating profile (figure~\ref{fig:kink_straight_ohmic_heating_profile}) and, consequently, in the radial pressure profile (figure~\ref{fig:pressure_profiles}). The highly pressurised core extends to $r\approx 0.2$--$0.4$ (depending on the value of $\eta$) before increasing slightly around $r\approx 0.7$. The secondary bump in pressure is due to the outer shell of current. The pressure gradient near the axis provides the outwardly directed pressure force which competes against the binding action of the magnetic tension to (potentially) result in the fluting instability.  The magnitude of the pressure gradient depends strongly on the value of $\eta$, with lower values producing shallower gradients which (as shall be seen) are more stable to the fluting instability. Indeed, when $\eta=0$, the radial pressure profile is nearly flat and the tube stable to the fluting instability.

In all cases unstable to the fluting instability, it occurs some time between $t=20$ and $t=30$. During this time, the continued driving at the boundaries eventually injects enough twist that the tube also becomes unstable to the kink instability. This initially develops linearly alongside the fluting instability and then erupts during the kink's nonlinear phase, dominating the dynamics and disrupting the fluting instability. The development of the two instabilities is strongly affected by the value of $\eta$ and the viscosity model used.

\subsection{Development where $\eta=10^{-4}$}

\begin{figure}[t]
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-4_pressure_13.pdf}
      \caption{$t=26$}
      \label{fig:swi-4_pressure_13}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-4_pressure_14.pdf}
      \caption{$t=28$}
      \label{fig:swi-4_pressure_14}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-4_pressure_15.pdf}
      \caption{$t=30$}
      \label{fig:swi-4_pressure_15}
    \end{subfigure}
\mycaption{Pressure profiles during the development of the fluting and kink instabilities.}{Shown are slices of pressure through $z=0$ where $\eta = 10^{-4}$ and the viscosity model is switching. Note the difference in colour scale in figure~\ref{fig:swi-4_pressure_15}. The development in the isotropic case is similar.}
\label{fig:kink_pressure_slices-4}%
\end{figure}

Figure~\ref{fig:kink_pressure_slices-4} shows the pressure profile through $z=0$ where $\eta=10^{-4}$ and the viscosity model is switching for times $t=26$, $28$ and $30$. At $t=26$ the tube becomes unstable to the $m=4$ fluting instability, when the plasma begins to (slightly) bulge out diagonally from the high-pressure core (figure~\ref{fig:swi-4_pressure_13}). As the bulges move radially outwards into lower pressure regions they expand and accelerate, resulting in the entire pressure structure appearing clover-shaped (figure~\ref{fig:swi-4_pressure_14}). By $t=30$ the kink instability has disrupted the fluting instability and is developing nonlinearly (figure~\ref{fig:swi-4_pressure_15}). As is typical of nonlinear kink development, the tube continues to release its stored potential energy as kinetic energy and heat and the contained plasma becomes highly mixed. In the unseen isotropic case, the fluting instability is present but damped, and the kink instability quickly dominates the dynamics.

\begin{figure}[t]
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{field_line_plots/cropped/v-4r-4-isotropic_0014_cropped.png}
      \caption{Isotropic}
      \label{fig:field_line_plots_iso}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{field_line_plots/cropped/v-4r-4-switching_0014_cropped.png}
      \caption{Switching}
      \label{fig:field_line_plots_swi}
    \end{subfigure}
\mycaption{Simultaneous development of fluting and kink instabilities in the isotropic and switching cases as field lines and pressure contours.}{Field lines and contours of pressure (where $p=0.3$) are plotted at $t=28$. Also shown is the velocity driver as a slice. The fluting instability grows in both cases, though faster in the switching case. The initial stages of the kink instability can also be observed in the field lines of the isotropic case in subfigure~\ref{fig:field_line_plots_iso}.}
\label{fig:kink_field_line_plots}%
\end{figure}

Figure~\ref{fig:kink_field_line_plots} shows the effect the viscosity models have on the initial stages of the fluting and kink instabilities in 3D. While the fluting instability is observed in both cases, it is damped in the isotropic case and grows faster in the switching case. In the latter case, the extended development of the fluting instability appears to disrupt the inner core of field lines and (as shall be seen) slows the growth of the kink instability. In the isotropic case, the fluting instability has been damped to the extent that the kink instability grows uninhibited and quickly disrupts the fluting.

\begin{figure}[t]
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-4}
    \end{subfigure}
  \mycaption{Kinetic energy as a function of time showing the development and measured growth rates of the fluting and kink instabilities.}{Both plots are from results where $\eta=10^{-4}$.}
\label{fig:kink_str8_ke-4}%
\end{figure}

Despite the fluting instability appearing in the isotropic case (figure~\ref{fig:field_line_plots_iso}) only in the switching case can the onset of both the fluting and kink instabilities be seen in the kinetic energy profile (figure~\ref{fig:kink_ke_log-4}), where the nonlinear growth rates of the two instabilities are found to be $\gamma = 0.69$ for the fluting and $\sigma = 2.55$ for the kink. The onset times are approximately $t=27$ for the fluting instability and $t=28$ for the kink. In the isotropic case, the growth rate of the kink, $\sigma = 2.97$, is larger than in the switching case, although the onset times appear similar, and the kinetic energy profile shows no evidence of the growth of the fluting instability.

The faster growth of the kink compared to, say, that of chapter~\cite{quinnEffectAnisotropicViscosity2020a} is due to the relative aspect ratios of the flux tubes. The tube prescribed in chapter~\cite{quinnEffectAnisotropicViscosity2020a} has an aspect ratio of approximately $20$ compared to the tube studied here which has an aspect ratio of approximately $4$. While the total twist is similar in both tubes (after the drivers have injected twist up to $t\approx20$) the small aspect ratio results in more turns per unit length, resulting in a faster growing instability.

\begin{figure}[t]
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{suydam_condition_4.pdf}
      \caption{Suydam condition}
      \label{fig:suydam_condition_4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{growth_rate_4.pdf}
      \caption{Linear growth rate}
      \label{fig:growth_rate_4}
    \end{subfigure}
\mycaption{Stability and linear growth rate of the fluting instability.}{In~\ref{fig:suydam_condition_4}, Suydam's stability criterion and contributing terms (LHS of~\eqref{eq:suydams_criterion})  are plotted and in~\ref{fig:growth_rate_4} the predicted linear growth rate~\eqref{eq:fluting_growth_rate2} is plotted. Both plots are produced at $t=20$ for $\eta=10^{-4}$ and using the switching model. The location of the peak linear growth rate is also shown.}
\label{fig:stability_and_growth}%
\end{figure}

Prior to the onset of either instability, the flux tube is found to be linearly unstable to perturbations of the form~\eqref{eq:kink_perturbation} at $t=20$ via Suydam's criterion~\eqref{eq:suydams_criterion} (figure~\ref{fig:suydam_condition_4}). The criterion represents a balance between destabilising pressure gradients and stabilising magnetic shear and in this case, the shear is so small and the pressure gradient so large that the tube is unstable over a wide range of radii, for $ 0.02 \lessapprox r \lessapprox 0.29$. The measure of linear fluting growth rate $\gamma$ is plotted as a function of $r$ at the same time (figure~\ref{fig:growth_rate_4}). While the magnitude of the peak linear growth rate predicts the observed rate reasonably well, the location of the peak growth matches nearly exactly the location of the resonant surface where the observed perturbation grows (figure~\ref{fig:swi-4_pressure_13}).

\begin{figure}[t]
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{perturbations_4.pdf}
      \caption{Perturbations}
      \label{fig:pressure_pert_4}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{resonant_surface_4.pdf}
      \caption{Resonance function}
      \label{fig:resonant_surface_4}
    \end{subfigure}
\mycaption{Perturbations corresponding to the fluting and kink instabilities and the spatial radial distribution of the associated resonance function.}{Pressure and velocity perturbations in $z$ (corresponding to the fluting and kink instabilities, respectively) and of the resonance function $m B_{\theta}(r)/r + kB_z(r)$ as a function of $r$ using the observed fluting perturbation wavenumbers. All plots are from snapshots at $t=26$ where $\eta=10^{-4}$ and the viscosity model is switching.}
\label{fig:k_and_resonance}%
\end{figure}

Figure~\ref{fig:pressure_pert_4} plots the observed perturbations corresponding to the fluting and kink instabilities at $t=26$. The fluting perturbation is observed in the pressure and is plotted as a function of $z$ following a line through the point $(r, \theta) = (0.101, 0)$. The kink instability is observed in the $x$-velocity (a proxy for the radial velocity) through the axis. Comparing the magnitudes of the perturbations at this time suggests the fluting instability is close to transitioning to its nonlinear phase while the kink instability is still very much in its linear phase.

The value of $k$ for each perturbation is calculated as $k = 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the perturbation, measured as the difference between the two peaks closest to $z=0$ (thus minimising the influence of line-tying on the measurement). This gives a value of $k_{flute}=23.61$ and $k_{kink}=4.57$ for both viscosity models. Hence, the observed most unstable fluting perturbation is that of the form~\eqref{eq:kink_perturbation} where $m=4$ and $k=23.61$ and the observed kink instability is that where $m=1$ and $k=4.57$. Using these values, it is observed that the fluting perturbation exactly resonates with the field, that is $m B_{\theta}(r)/r + kB_z(r) = 0$, at $r=0.125$ (figure~\ref{fig:resonant_surface_4}). This is precisely the predicted radius of peak linear growth (figure~\ref{fig:growth_rate_4}). At this time the perturbation is close to resonance, that is $m B_{\theta}(r)/r + kB_z(r) \approx 0$, over a range of radii from $r=0.125$ to $0.2$.

Comparing the effect of the viscous models on the perturbations, in the isotropic case, the fluting perturbation is damped, while in the switching case the kink perturbation is diminished, explaining why the fluting instability appears more readily in the switching case (figure~\ref{fig:kink_ke-4}).

\subsection{Development where $\eta=10^{-3}$}

\begin{figure}[t]
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-3_pressure_12.pdf}
      \caption{$t=24$}
      \label{fig:swi-3_pressure_12}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-3_pressure_14.pdf}
      \caption{$t=28$}
      \label{fig:swi-3_pressure_14}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-3_pressure_15.pdf}
      \caption{$t=30$}
      \label{fig:swi-3_pressure_15}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-3_pressure_16.pdf}
      \caption{$t=32$}
      \label{fig:swi-3_pressure_16}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-3_pressure_17.pdf}
      \caption{$t=34$}
      \label{fig:swi-3_pressure_17}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{swi-3_pressure_18.pdf}
      \caption{$t=36$}
      \label{fig:swi-3_pressure_18}
    \end{subfigure}
\mycaption{Pressure profiles through $z=0$ during the development of the fluting and kink instabilities in the higher resistivity switching case.}{The viscosity model is switching and $\eta = 10^{-3}$. In contrast to the case of $\eta=10^{-4}$, the nonlinear development of the fluting instability has time to mix the interior of the flux tube before the onset of the kink instability, the growth of which is affected by the mixed plasma.}
\label{fig:kink_pressure_slices-3}%
\end{figure}

Figures~\ref{fig:kink_pressure_slices-3} show the prolonged development of the fluting instability and the slow nonlinear development of the kink. Due to the enhanced Ohmic heating when $\eta=10^{-3}$, the pressure gradient is substantially stronger than when $\eta=10^{-4}$ and the fluting instability is excited much earlier. Compared to the $\eta=10^{-4}$ cases, the instability occurs further from the axis, at $r\approx0.16$, and the larger pressure gradient drives the bulges further from the axis in the nonlinear phase (figure~\ref{fig:swi-3_pressure_12}). These bulges continue to extend outwards and mix the plasma as they develop. The kink instability can be observed moving the axis of the tube diagonally upwards and to the right in figure~\ref{fig:swi-3_pressure_15}. At this time in the $\eta=10^{-4}$ cases, the nonlinear development of the kink was further along (figure~\ref{fig:swi-4_pressure_15}). The development of the kink then proceeds slowly as it moves the axis of the tube through the mixed region to eventually begin the reconnection process with the outer region of field that is typical of the instability in this kind of flux tube (as was observed in chapter~\cite{quinnEffectAnisotropicViscosity2020a}).

\begin{figure}[t]
  \centering
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.49\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
\mycaption{Kinetic energy as a function of time in the cases where $\eta=10^{-3}$.}{The results from both viscosity models are shown. The fluting instability appears earlier than where $\eta=10^{-4}$ and the growth rate of the kink instability is decreased.}
\label{fig:kink_str8_ke-3}%
\end{figure}

It is evident from the kinetic energy profile that the fluting instability develops much earlier than in the $\eta=10^{-4}$ cases and grows at an increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}). The kink instability grows at a rate of $\sigma \approx 0.15$, much slower than that observed in the $\eta=10^{-4}$ cases, and much lower than the fluting instability. One key observation is that, despite the early and disruptive growth of the fluting instability, the kink instability still generates the bulk of the kinetic energy (figure~\ref{fig:kink_ke-3}).

Due to the influence of the drivers on the kinetic energy, the fluting growth rate is difficult to estimate from the kinetic energy profile as accurately as in the $\eta=10^{-4}$ cases. Since the kink instability occurs after the development of the fluting, its growth rate is similarly difficult to gauge. Nevertheless, it is clear that the fluting instability grows at a rate of the same order as that in the $\eta=10^{-4}$ cases. It is also apparent that the kink instability grows much slower in the $\eta=10^{-3}$ cases.

\begin{table}[]
\centering
\begin{tabular}{ccc}
&
$\eta=10^{-4}$ &
$\eta=10^{-3}$ \\
\midrule
Predicted linear $\gamma$ & 1.43 & 2.72  \\
Observed nonlinear $\gamma$ & 0.69 & 1.06  \\
Observed $\sigma$ & 2.55 & 0.15\\
\midrule
Radius of peak $\gamma$ & 0.125 & 0.163 \\
Observed $r_s$ & 0.125 & 0.163 \\
\midrule
Observed $k_{flute}$ & 23.61 & 16.05 \\
Observed $k_{kink}$ & 4.57 & 4.53 \\
\end{tabular}
\caption{Quantitative differences in the observed perturbations between results for both values of $\eta$. See text for details of measurements times.}
\label{tab:kink_fluting_params}
\end{table}

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences between the results for the two values of $\eta$. All values are calculated from simulations using the switching model with the exception of $k_{kink}$ which is measured from isotropic results due to noise in the switching case (the value of $k_{kink}$ appears similar, however). The results of the isotropic cases are qualitatively similar. The radius of peak $\gamma$ is calculated at time $t=20$. The fluting wavenumber $k$ and observed $r_s$ are measured at times just prior to the nonlinear development of the fluting instability, that is at $t=22$ when $\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$. The kink wavenumber is measured at $t=26$ in both cases. These times allow fair comparison between measurements.

The longitudinal wavenumber $k_{kink}$ of the observed kink perturbation remains similar in both cases since the instability is essentially governed by the twist injected by the driver which remains the same in both cases. In contrast, the longitudinal wavenumber $k_{flute}$ of the observed fluting perturbation is lower in the $\eta=10^{-3}$ cases. This is due to the different resonant surface within which the perturbation grows, the location being dictated by the peak of the linear growth rate. Note that the location of this peak again matches well the location of the observed resonant surface, as in the $\eta=10^{-4}$ cases. Similar to the $\eta=10^{-4}$ cases, the peak growth rate predicted by the linear analysis is the same order of magnitude as the observed growth rate.

\section{Discussion}

Due to the perturbations arising from numerical noise, it is likely that the $m=4$ perturbation is excited due to influences from the boundaries in the Cartesian box, for example through the interaction of reflected fast waves generated in part by the driver. Performing a similar experiment in a cylindrical numerical domain, or prescribing a variety of perturbations in the Cartesian domain may reveal other, faster growing modes. The modes may also be influenced by nonlinear coupling between the $m>1$ and $m=1$ modes, as is found in the study of kink and fluting oscillations~\cite{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017a}.

This set of experiments has shown that the mixing as a result of the nonlinear fluting instability appears to slow the growth of the kink instability. In the linear regime it seems unlikely that the linear perturbations of either the fluting or kink are able to directly couple, given that the kink instability generally presents at the axis of a flux tube and the fluting at some resonant surface away from the axis. Further investigation of the nonlinear interaction between the two instabilities is required.

Since the main driver of the fluting instability is the pressure gradient generated through Ohmic heating, it is prudent to ask if the same pressure gradient could be generated using physical coronal values of the resistivity (of approximately $\eta=10^{-8}$~\cite{craigAnisotropicViscousDissipation2009a}) which are much smaller than those studied here. Additionally, the simulations presented here do not incorporate radiation or thermal conductivity, two processes which would remove energy (and thus pressure) from high-pressure regions in a coronal loop and thus could remove the required conditions for the growth of a fluting instability. Where $\eta=10^{-4}$, the fluting instability was quickly dominated by the kink instability and appeared to have little impact on the resultant dynamics, which mirror those of other kink instability studies (such as~\cite{hoodCoronalHeatingMagnetic2009}). This suggests that even lower values of resistivity would result in flux tubes without any significant fluting instability, at least for this form of driver and mechanism of pressure generation. Regardless, coronal loops with strong radial pressure gradients have been observed~\cite{foukalTemperatureStructurePressure1975} and such loops may be unstable to the fluting instability. Modelling of a prescribed fluting-unstable flux tube (as opposed to the dynamically stressed loop investigated here) would provide a useful comparison to observations, however it may be difficult to prescribe a tube which is not also susceptible to kinking. Linear stability analyses of this kind of flux tube (a dynamically created zero total axial current tube) focus on the kink instability~\cite{browningSolarCoronalHeating2003c} so do not provide much insight into the potential for fluting without a kink.

These results show that a flux tube can be unstable to the fluting instability and yet the faster growing kink instability can quickly dominate when the pressure gradient is small enough. However, the opposite case is also observed, where a faster growing fluting instability appears to slow the growth of the kink instability although, importantly, it does not fully disrupt the development of the kink. Understanding the balance between the nonlinear growth rates of the two instabilities is important in understanding whether the fluting instability may be found at all in the real solar corona, or whether a realistic growth rate is too slow compared to that of the kink instability.

\section{Conclusion}

This chapter details the nonlinear development of two ideal instabilities, the kink and fluting instabilities, both of which develop naturally in the course of twisting an initially straight magnetic flux tube. This provides a different approach to that employed in the simulations performed in chapter~\cite{quinnEffectAnisotropicViscosity2020a} in that the instabilities are not excited by any prescribed perturbations but, instead, the field is dynamically driven into an unstable state and the perturbations provided by noise in the system. Not only is the kink instability excited due to the twist in the field, a pressure-driven fluting instability can also be excited in unstable pressure gradients generated by Ohmic heating. Simulations were run over two values of resistivity, $\eta=10^{-3}$ and $10^{-4}$, and for two forms of viscosity, isotropic and switching, providing an initial and important first step into the simulation of nonlinear fluting instabilities in the solar corona.

It has been shown that the fluting instability can be quickly dominated by the kink instability if the kink grows substantially faster than the fluting. However, if the fluting has time to develop nonlinearly, it mixes the plasma within the flux tube, generating small scale current sheets and releasing some magnetic energy. The overall effect of this mixing is to slow the growth of the kink instability. The slowed growth of the kink does not appear to significantly impact the kinetic energy released during its evolution, only the time over which it is released.

The form of viscosity has been found to significantly affect the growth of the fluting instability. Importantly, isotropic viscosity is found to damp the growth of the fluting instability to the degree that it is unable to grow appreciably before the onset of the faster growing nonlinear kink instability. Overall, the switching model permits greater release of kinetic energy. Similar to chapter~\cite{quinnEffectAnisotropicViscosity2020a}, isotropic viscous heating is found to be significantly lower than anisotropic (switching) viscous heating, by approximately two orders of magnitude.

These numerical experiments have provided evidence that the fluting instability can occur in twisted magnetic flux ropes and grow at similar rates to the kink instability. Further estimation of the relative growth rates in more realistic coronal loop setups is required to fully understand if the fluting instability plays a pertinent role in coronal loop physics.

\printbibliography

\end{document}

### 2021-06-05 paper.tex
Add lots of introductory material

@@
 
-\todo{add switching function}
-
-The helical kink instability is a form of ideal MHD instability which occurs in highly twisted magnetic flux tubes such as those making up much of the solar corona~\cite{realeCoronalLoopsObservations2014} and has been well studied in the coronal context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003c,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020a}.
+The helical kink instability is a form of ideal magnetohydrodynamic (MHD) instability which occurs in highly twisted magnetic flux tubes such as those making up much of the solar corona~\cite{realeCoronalLoopsObservations2014} and has been well studied in the coronal context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003c,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020a}.
 Given its energetic nonlinear development, it is considered a potential mechanism for heating the solar corona through the theory of nanoflares~\cite{klimchukSolvingCoronalHeating2006a,browningMechanismsSolarCoronal1991} and a key mechanism in the production of solar flares~\cite{hoodKinkInstabilitySolar1979}.
@@
 In~\cite{quinnEffectAnisotropicViscosity2020a} and most other investigations of the kink instability, a perturbation is applied to an already significantly twisted flux tube.
-An alternative way to excite the instability is to start with an initially straight field and apply twisting motions at the boundaries to form a twisted flux tube which eventually becomes unstable.
+An alternative way to excite the instability (and the way employed here) is to start with an initially straight field and apply twisting motions at the boundaries to form a twisted flux tube which eventually becomes unstable.
 This kind of dynamic excitation of the kink instability is useful in that it represents more closely the real development of a magnetic flux tube and associated instabilities in the solar corona.
@@
 In MHD, the RTI is a typical example of an ideal interchange instability, where magnetic field lines are minimally bent and are, instead, exchanged during the evolution of the instability.
-The ideal fluting instability is another example of an ideal interchange instability, but confined to a cylindrical geometry, the name ``fluting instability'' referring to its likeness to a fluted column.
-In a twisted flux tube like a coronal loop, the magnetic curvature is always directed towards the axis so the tube may be unstable to fluting when the pressure decreases outwards from a high-pressure core.
-Such a pressure distribution is found in the flux tubes studied here.
+The ideal fluting instability is another example of an ideal interchange instability but confined to a cylindrical geometry, the name ``fluting instability'' referring to its likeness to a fluted column.
+In a twisted flux tube like a simple, unbraided coronal loop, the magnetic curvature is always directed towards the axis so the tube may be unstable to fluting when the pressure decreases outwards from a high-pressure core.
+Such a pressure distribution is generated in the flux tubes studied here as a result of the driving.
 The appearance of the fluting instability is illustrated by, for example, the pressure contours in figure~\ref{fig:kink_field_line_plots}, where the perturbations follow the pitch of the twisted field.
@@
 In other solar contexts, interchange instabilities can be found in the form of ballooning modes in arcades~\cite{hoodBallooningInstabilitiesSolar1986}, as the instability which forms tubes of specific size in the photosphere~\cite{bunteInterchangeInstabilitySolar1993} and in the buoyancy of flux tubes~\cite{schuesslerInterchangeInstabilitySmall1984}.
-However, the instability is more commonly studied in fusion contexts.
-
-While the stability of both the ideal and resistive fluting instabilities has been studied extensively in fusion research~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}, the focus is generally on understanding how a particular plasma device may be stabilised to the instability in particular geometries such as that of the mirror machine~\cite{jungwirthTheoryFluteInstability1965} or in toroidal geometries such as the tokomak~\cite{shafranovFluteInstabilityCurrentcarrying1968}.
+However, the fluting instability specifically is more commonly studied in fusion contexts~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}.
+In fusion, the focus is generally on understanding how a particular plasma device may be stabilised to the instability in particular geometries such as that of the mirror machine~\cite{jungwirthTheoryFluteInstability1965} or in toroidal geometries such as the tokomak~\cite{shafranovFluteInstabilityCurrentcarrying1968}.
 The resistive fluting instability (also known as the resistive interchange instability) can be excited even when the ideal fluting instability is stabilised.
 As a result, this has been given significantly more attention~\cite{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}.
-While this body of research is useful and applicable in solar contexts, it is mostly limited to the stability and linear development of the fluting instability.
+While this body of research is useful and applicable in solar contexts, it is mostly limited to the study of the stability and linear development of the fluting instability, the nonlinear development being of secondary importance to the functioning of fusion devices.
 More detailed investigations of its nonlinear development is required to understand its importance in the context of coronal dynamics and coronal heating.
 The development of the fluting instability and its interaction with the simultaneously growing kink instability is the focus of this work and the experiments described here represent an initial exploration into the nonlinear fluting instability in the solar corona.
+Of particular interest is the effect of anisotropic viscosity, which is found to strongly affect the growth of the fluting instability.
+
+It is well known that viscosity in magnetised plasmas (such as that which makes up the solar corona) is anisotropic and strongly dependent on the strength and direction of the local magnetic field~\cite{hollwegViscosityChewGoldbergerLowEquations1986a,hollwegViscosityMagnetizedPlasma1985,Braginskii1965}.
+The development of the switching model~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} and implementation in Lare3d has allowed the investigation of the effect of anisotropic viscosity on solar phenomena.
+We find the stability of Lare3d without (the more commonly employed) isotropic or shock viscosity to be sufficient for at least the study of kink instabilities in coronal loops~\cite{quinnEffectAnisotropicViscosity2020a}.
+The interest in anisotropic viscosity stems from the unanswered question of which heating mechanism (viscous or Ohmic) is dominant in the solar corona~\cite{klimchukSolvingCoronalHeating2006a}, an important facet of solving the coronal heating problem.
+Using scaling laws, it has been suggested that viscous heating (generated through anisotropic viscosity) can dwarf that of Ohmic heating~\cite{craigAnisotropicViscousDissipation2009a,litvinenkoViscousEnergyDissipation2005}.
+However, due to computational and observational limitations, this cannot be directly tested, and so the influence of other factors such as small scale instabilities and turbulence is relatively unknown~\cite{klimchukSolvingCoronalHeating2006a}.
+In addition to directly heating the plasma, viscosity plays a part in the damping of instabilities and waves~\cite{rudermanSlowSurfaceWave2000a}.
+It is this effect we are most interested in here, and it shall be found that the use of anisotropic viscosity permits the growth of the fluting instability, which is otherwise strongly damped by isotropic viscosity.
 
@@
 
-The non-dimensionalisation scheme and values are identical to those used in~\cite{quinnEffectAnisotropicViscosity2020a}. The magnetic field is prescribed as initially straight and uniform,
+Lare3d numerically solves the MHD equations for the density $\rho$, plasma velocity $\vec{u}$, pressure $p$, magnetic field $\vec{B}$ and internal energy $\varepsilon$,
+\begin{gather}
+%\begin{equation}
+\label{eq:mhda}
+\frac{D\rho}{Dt} = - \rho \vec{\nabla} \cdot \vec{u},\\
+%\end{equation}
+%\begin{equation}
+\rho\frac{D\vec{u}}{Dt} = -\vec{\nabla} p + \vec{\jmath} \times \vec{B} + \vec{\nabla} \cdot \ten{\sigma},\\
+%\end{equation}
+%\begin{equation}
+\frac{D\vec{B}}{Dt} = (\vec{B} \cdot \vec{\nabla})\vec{u} - (\vec{\nabla} \cdot \vec{u})\vec{B} + \eta \nabla^2 \vec{B},\\
+%\end{equation}
+%\begin{equation}
+\rho\frac{D\varepsilon}{Dt} = -p \vec{\nabla} \cdot \vec{u} + {Q}_{\nu} + {Q}_{\eta},%\\
+\label{eq:energy}
+%\end{equation}
+\end{gather}
+where $\eta$ is the non-dimensionalised resistivity, $\jmath = \nabla \times \vec{B}$ is the current density and $\ten{\sigma}$ is the viscous stress tensor (described below).
+The terms ${Q}_{\nu} = \ten{\sigma} : \vec{\nabla}\vec{u}$ and ${Q}_{\eta} = \eta | \vec{\jmath} |^2$ are viscous heating and Ohmic heating, respectively.
+The system is closed by the inclusion of the equation of state for an ideal gas
+\begin{equation}
+\varepsilon = \frac{p}{\rho(\gamma - 1)},
+\end{equation}
+where the specific heat ratio is given by $\gamma = 5/3$.
+
+The isotropic (or Newtonian) viscosity stress tensor is given by
+\begin{equation}
+  \label{eq:isotropic_viscous_tensor}
+  \ten{\sigma} = \nu \ten{W},
+\end{equation}
+where $\nu$ is the viscous transport parameter, generally referred to as the viscosity,
+\begin{equation}
+  \label{eq:rate_of_strain}
+  \ten{W} = \nabla\vec{u} + (\nabla\vec{u})^T - \tfrac{2}{3}(\nabla \cdot \vec{u})\ten{I},
+\end{equation}
+is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$ identity matrix.
+We use an identical model of anisotropic viscosity as that used in previous work~\cite{quinnEffectAnisotropicViscosity2020a}, the switching model, first presented in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}.
+While this model is intended to revert to an isotropic model in the vicinity of magnetic null points, we effectively only make use of the anisotropic component, since there are no null points present in the simulations at any point.
+To this end, we set the switching parameter (which controls the degree of viscous anisotropy) to $a_0 = 150$ in Lare3d's control, a value sufficiently large that the anisotropic viscous stress tensor is given by
+\begin{equation}
+  \label{eq:switching_model}
+\ten{\sigma}_{\text{swi}} = \nu \left[\frac{3}{2}(\ten{W}\vec{b}\cdot\vec{b}) \left( \vec{b} \otimes \vec{b} - \frac{1}{3}\ten{I} \right)\right],
+\end{equation}
+where $\vec{b}$ is the unit vector in the direction of the magnetic field.
+This tensor is identical to the strong field approximation of Braginskii~\cite{braginskiiTransportProcessesPlasma1965}.
+Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020a}\todo{ref KHI paper}.
+
+The non-dimensionalisation scheme and values align with the scheme used by Lare3d~\cite{arberStaggeredGridLagrangian2001} and are identical to those used in~\cite{quinnEffectAnisotropicViscosity2020a}.
+The magnetic field is prescribed as initially straight and uniform,
 \begin{equation}
@@
 The velocity is set everywhere to $\vec{u} = \vec{0}$, the density to $\rho = 1$, the internal energy to $\varepsilon = 8.67\times 10^{-4}$ (corresponding to a temperature of $10^6$ K).
-At the boundaries, the magnetic field, density, and energy are fixed to their initial values and the velocity to zero except at the upper and lower boundary where the twisting driver, described below, is prescribed.
+\todo{what's the plasma beta?} At the boundaries, the magnetic field, density, and energy are fixed to their initial values and the velocity to zero except at the boundaries where the twisting driver, described below, is prescribed.
 The spatial derivatives of these variables are also set to zero at the boundaries.
 The resolution is $512$ grid points per dimension, comparable to the highest resolution kink instability studies of~\cite{hoodCoronalHeatingMagnetic2009} or medium resolution studies of~\cite{barefordShockHeatingNumerical2015}.
-The switching function employed is the von Mises function~\eqref{eq:switching_function} and the switching parameter is chosen to be $a_0 = 150$, a value sufficiently large to ensure the viscosity is anisotropic throughout the entire domain.
 
@@
 At the lower boundary, the flow is in the opposite direction.
-
 This form of driver allows the system to be accelerated slowly enough that the production of disruptive shocks and fast waves is minimal.
@@
 Both drivers result in twist being added at a rate of $2\pi$ every $7.96$ Alfv\'en times.
-The twist profile across the entire flux tube develops in such a way that it is qualitatively similar to that studied in chapter~\cite{quinnEffectAnisotropicViscosity2020a} by $t\approx 20$, however the length of the flux tubes differs significantly.
+The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\cite{quinnEffectAnisotropicViscosity2020a,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
 This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the fluting instability and the helical kink instability.
@@
 Two pairs of simulations were performed, one pair where the background resistivity is set to $\eta=10^{-3}$ and another where $\eta=10^{-4}$.
-As in chapter~\cite{quinnEffectAnisotropicViscosity2020a}, only background resistivity is used.
-Each simulation pair consists of one simulation using isotropic viscosity and another using the switching model~\eqref{eq:switching_model_simple} with the von Mises switching function~\eqref{eq:switching_function}.
+As in~\cite{quinnEffectAnisotropicViscosity2020a}, only background resistivity is used.
+Each simulation pair consists of one simulation using isotropic viscosity~\eqref{eq:isotropic_viscous_tensor} and another using the switching model~\eqref{eq:switching_model}.
 The value of viscosity is set to $\nu = 10^{-4}$ in all cases.

### 2021-06-05 paper.tex
Minor typos

@@
 
-It is well known that viscosity in magnetised plasmas (such as that which makes up the solar corona) is anisotropic and strongly dependent on the strength and direction of the local magnetic field~\cite{hollwegViscosityChewGoldbergerLowEquations1986a,hollwegViscosityMagnetizedPlasma1985,Braginskii1965}.
+It is well known that viscosity in magnetised plasmas (such as that which makes up the solar corona) is anisotropic and strongly dependent on the strength and direction of the local magnetic field~\cite{hollwegViscosityChewGoldbergerLowEquations1986a,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
 The development of the switching model~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} and implementation in Lare3d has allowed the investigation of the effect of anisotropic viscosity on solar phenomena.
@@
   \label{eq:isotropic_viscous_tensor}
-  \ten{\sigma} = \nu \ten{W},
+  \ten{\sigma}_{iso} = \nu \ten{W},
 \end{equation}

### 2021-09-24 paper.tex
Add Rado's changes

--- 2021-06-05 paper.tex
@@
 \documentclass[12pt]{article}
-\usepackage[T1]{fontenc} % modern encoding
-\usepackage[utf8]{inputenc}
-\usepackage{libertine}
-\usepackage[libertine]{newtxmath}
-\usepackage[scaled=0.95]{inconsolata}
+%\usepackage[T1]{fontenc} % modern encoding
+%\usepackage[utf8]{inputenc}
+%\usepackage{libertine}
+%\usepackage[libertine]{newtxmath}
+%\usepackage[scaled=0.95]{inconsolata}
 \usepackage[margin=0.5in]{geometry}
@@
 %% --- user packages ---
-
+\usepackage{amssymb}
 \usepackage{csquotes}
@@
 \newcommand{\bb}[1]{\textcolor{blue}{#1}}
-\newcommand{\rs}[1]{\textcolor{blue}{#1}}
+\newcommand{\rs}[2]{\textcolor{red}{#2}}
 %\newcommand{\rr}[1]{#1}
@@
 
-Kink and fluting instabilities in a dynamically twisted flux tube
+\title{\rs{Kink and fluting instabilities in a dynamically twisted
+    flux tube}{Flute and kink instabilities in a dynamically twisted
+    flux tube with anisotropic plasma viscosity}}
+\author{\rs{}{James J.~Quinn$^{1,\ast}$, Radostin D.~Simitev$^2$}}
+\date{\small
+  $^1$ Research Software Development Group, University College London, Gower Street, London WC1E 6BT, UK.\\
+  e-mail:
+  \href{mailto:jamiejquinn@jamiejquinn.com}{jamiejquinn@jamiejquinn.com}. $^\ast$
+  Corresponding author\\
+  $^2$ School of Mathematics and Statistics, University of Glasgow,
+  Glasgow G12 8QQ,
+  UK. \\ \href{https://orcid.org/0000-0002-2207-5789}{orcid.org/0000-0002-2207-5789}\\
+\vspace{5mm}
+  Version: \today}
+\maketitle
 
@@
 
+\begin{abstract}
+  \rs{}{NEEDS ABSTRACT}
+\end{abstract}
+
 \section{Introduction}
 
-The helical kink instability is a form of ideal magnetohydrodynamic (MHD) instability which occurs in highly twisted magnetic flux tubes such as those making up much of the solar corona~\cite{realeCoronalLoopsObservations2014} and has been well studied in the coronal context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003c,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020a}.
-Given its energetic nonlinear development, it is considered a potential mechanism for heating the solar corona through the theory of nanoflares~\cite{klimchukSolvingCoronalHeating2006a,browningMechanismsSolarCoronal1991} and a key mechanism in the production of solar flares~\cite{hoodKinkInstabilitySolar1979}.
-Previous work by the same authors has investigated a twisted magnetic flux tube already linearly unstable to the helical kink instability, investigating particularly the effect of anisotropic viscosity on the nonlinear dynamics~\cite{quinnEffectAnisotropicViscosity2020a}.
-In~\cite{quinnEffectAnisotropicViscosity2020a} and most other investigations of the kink instability, a perturbation is applied to an already significantly twisted flux tube.
-An alternative way to excite the instability (and the way employed here) is to start with an initially straight field and apply twisting motions at the boundaries to form a twisted flux tube which eventually becomes unstable.
-This kind of dynamic excitation of the kink instability is useful in that it represents more closely the real development of a magnetic flux tube and associated instabilities in the solar corona.
-The dynamic twisting of the flux tube reveals an additional instability, the fluting instability, which has been theorised (for example, in~\cite{priestMagnetohydrodynamicsSuna}) but not yet observed in coronal simulations or observations, to our knowledge.
+The helical kink instability is a form of ideal magnetohydrodynamic
+(MHD) instability which occurs in highly twisted magnetic flux tubes
+such as those making up much of the solar
+corona~\cite{realeCoronalLoopsObservations2014} and has been well
+studied in the coronal
+context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003c,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020a}. Given
+its energetic nonlinear development, it is considered a potential
+mechanism for heating the solar corona through the theory of
+nanoflares~\cite{klimchukSolvingCoronalHeating2006a,browningMechanismsSolarCoronal1991}
+and a key mechanism in the production of solar
+flares~\cite{hoodKinkInstabilitySolar1979}. Previous work by the same
+authors has investigated a twisted magnetic flux tube already linearly
+unstable to the helical kink instability, \rs{investigating particularly}{focussing specifically on}
+the effect of anisotropic viscosity on the nonlinear
+dynamics~\cite{quinnEffectAnisotropicViscosity2020a}. In~\cite{quinnEffectAnisotropicViscosity2020a}
+and most other investigations of the kink instability
+\rs{}{e.g. \cite{hoodCoronalHeatingMagnetic2009}}, a perturbation 
+is applied to an already significantly twisted flux tube. An
+alternative way to excite the instability (and the way employed here)
+is to start with an initially straight field and apply twisting
+motions at the boundaries to form a twisted flux tube which eventually
+becomes unstable. This kind of dynamic excitation of the kink
+instability is useful in that it represents more closely \rs{the real
+development of a magnetic flux tube and associated}{actual evolution
+  of magnetic flux tubes and the associated} instabilities in 
+the solar corona. \rs{The}{In our simulations, the}
+dynamic twisting of the flux tube reveals an additional instability,
+the \rs{fluting}{flute} instability, which has been theorised (for example,
+in~\cite{priestMagnetohydrodynamicsSuna}) but not yet observed in
+coronal simulations or observations, to our knowledge. \rs{}{RADO: NOT
+  YET OBSERVED? 
+  WHAT ABOUT \cite{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017a}??!!]}
 
-The fluting instability arises in magnetised plasmas where the plasma pressure gradient is directed in the same direction as the field line curvature, that is the pressure and magnetic tension forces compete.
-This is similar to the competition between pressure and gravitational forces which gives rise to the Rayleigh-Taylor instability (RTI).
-In MHD, the RTI is a typical example of an ideal interchange instability, where magnetic field lines are minimally bent and are, instead, exchanged during the evolution of the instability.
-The ideal fluting instability is another example of an ideal interchange instability but confined to a cylindrical geometry, the name ``fluting instability'' referring to its likeness to a fluted column.
-In a twisted flux tube like a simple, unbraided coronal loop, the magnetic curvature is always directed towards the axis so the tube may be unstable to fluting when the pressure decreases outwards from a high-pressure core.
-Such a pressure distribution is generated in the flux tubes studied here as a result of the driving.
-The appearance of the fluting instability is illustrated by, for example, the pressure contours in figure~\ref{fig:kink_field_line_plots}, where the perturbations follow the pitch of the twisted field.
+The \rs{fluting}{flute} instability arises in magnetised plasmas where
+the plasma pressure gradient is \rs{directed}{oriented} in the same direction as the
+field line curvature, that is the pressure and magnetic tension forces
+compete. This is similar to the competition between pressure and
+gravitational forces which gives rise to the Rayleigh-Taylor
+instability (RTI). In \rs{MHD}{magnetohydrodynamic terminology}, the RTI is a typical example of an ideal
+interchange instability, where magnetic field lines are minimally bent
+and are, instead, exchanged during the evolution of the
+instability. The ideal \rs{fluting}{flute} instability is another example of an
+ideal interchange instability but confined to a cylindrical geometry,
+the name \rs{``fluting instability''}{``flute instability''} referring to its likeness to a fluted
+column. In a twisted flux tube like a simple, unbraided coronal loop,
+the magnetic curvature is always directed towards the axis so the tube
+may be unstable to fluting when the pressure decreases outwards from a
+high-pressure core. Such a pressure distribution is generated in the
+flux tubes studied here as a result of the driving. The appearance of
+the \rs{fluting}{flute} instability is illustrated by, for example, the pressure
+contours in figure~\ref{fig:kink_field_line_plots}, where the
+perturbations follow the pitch of the twisted field.
 
-In other solar contexts, interchange instabilities can be found in the form of ballooning modes in arcades~\cite{hoodBallooningInstabilitiesSolar1986}, as the instability which forms tubes of specific size in the photosphere~\cite{bunteInterchangeInstabilitySolar1993} and in the buoyancy of flux tubes~\cite{schuesslerInterchangeInstabilitySmall1984}.
-However, the fluting instability specifically is more commonly studied in fusion contexts~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}.
-In fusion, the focus is generally on understanding how a particular plasma device may be stabilised to the instability in particular geometries such as that of the mirror machine~\cite{jungwirthTheoryFluteInstability1965} or in toroidal geometries such as the tokomak~\cite{shafranovFluteInstabilityCurrentcarrying1968}.
-The resistive fluting instability (also known as the resistive interchange instability) can be excited even when the ideal fluting instability is stabilised.
-As a result, this has been given significantly more attention~\cite{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}.
-While this body of research is useful and applicable in solar contexts, it is mostly limited to the study of the stability and linear development of the fluting instability, the nonlinear development being of secondary importance to the functioning of fusion devices.
-More detailed investigations of its nonlinear development is required to understand its importance in the context of coronal dynamics and coronal heating.
-The development of the fluting instability and its interaction with the simultaneously growing kink instability is the focus of this work and the experiments described here represent an initial exploration into the nonlinear fluting instability in the solar corona.
-Of particular interest is the effect of anisotropic viscosity, which is found to strongly affect the growth of the fluting instability.
+In other solar contexts, interchange instabilities can be found in the
+form of ballooning modes in
+arcades~\cite{hoodBallooningInstabilitiesSolar1986}, as the
+instability which forms tubes of specific size in the
+photosphere~\cite{bunteInterchangeInstabilitySolar1993} and in the
+buoyancy of flux
+tubes~\cite{schuesslerInterchangeInstabilitySmall1984}. However, the
+\rs{fluting}{flute} instability specifically is more commonly studied in fusion
+contexts~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}. In
+fusion, the focus is generally on understanding how a particular
+plasma device may be stabilised to the instability in particular
+geometries such as that of the mirror
+machine~\cite{jungwirthTheoryFluteInstability1965} or in toroidal
+geometries such as the
+tokomak~\cite{shafranovFluteInstabilityCurrentcarrying1968}. The
+resistive \rs{fluting}{flute} instability (also known as the resistive interchange
+instability) can be excited even when the ideal \rs{fluting}{flute} instability is
+stabilised. As a result, this has been given significantly more
+attention~\cite{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}. While
+this body of research is useful and applicable in solar contexts, it
+is mostly limited to the study of the stability and linear development
+of the \rs{fluting}{flute} instability, the nonlinear development being of
+secondary importance to the functioning of fusion devices. More
+detailed investigations of its nonlinear development is required to
+understand its importance in the context of coronal dynamics and
+coronal heating. The development of the \rs{fluting}{flute} instability and its
+interaction with the simultaneously growing kink instability is the
+\rs{}{main} focus of this work and the experiments described here represent an
+initial exploration into the nonlinear \rs{fluting}{flute} instability in the
+solar corona. \rs{Of particular interest is the effect of anisotropic
+viscosity, which is found to strongly affect the growth of the \rs{fluting}{flute}
+instability.}{}
 
-It is well known that viscosity in magnetised plasmas (such as that which makes up the solar corona) is anisotropic and strongly dependent on the strength and direction of the local magnetic field~\cite{hollwegViscosityChewGoldbergerLowEquations1986a,hollwegViscosityMagnetizedPlasma1985,Braginskii1965}.
-The development of the switching model~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} and implementation in Lare3d has allowed the investigation of the effect of anisotropic viscosity on solar phenomena.
-We find the stability of Lare3d without (the more commonly employed) isotropic or shock viscosity to be sufficient for at least the study of kink instabilities in coronal loops~\cite{quinnEffectAnisotropicViscosity2020a}.
-The interest in anisotropic viscosity stems from the unanswered question of which heating mechanism (viscous or Ohmic) is dominant in the solar corona~\cite{klimchukSolvingCoronalHeating2006a}, an important facet of solving the coronal heating problem.
-Using scaling laws, it has been suggested that viscous heating (generated through anisotropic viscosity) can dwarf that of Ohmic heating~\cite{craigAnisotropicViscousDissipation2009a,litvinenkoViscousEnergyDissipation2005}.
-However, due to computational and observational limitations, this cannot be directly tested, and so the influence of other factors such as small scale instabilities and turbulence is relatively unknown~\cite{klimchukSolvingCoronalHeating2006a}.
-In addition to directly heating the plasma, viscosity plays a part in the damping of instabilities and waves~\cite{rudermanSlowSurfaceWave2000a}.
-It is this effect we are most interested in here, and it shall be found that the use of anisotropic viscosity permits the growth of the fluting instability, which is otherwise strongly damped by isotropic viscosity.
+\rs{}{In addition to our main goal, of particular interest here is
+also the effect of anisotropic plasma viscosity, which in the following is found to
+strongly influence the growth of the \rs{fluting}{flute} instability.}
+It is well known that viscosity in magnetised plasmas (such as
+\rs{that which makes up}{those which make up} the solar corona) is
+anisotropic and strongly dependent on the strength and direction of
+the local magnetic
+field~\cite{hollwegViscosityChewGoldbergerLowEquations1986a,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
+\rs{The development of the switching
+model~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}
+and implementation in Lare3d has allowed the investigation of
+the effect of anisotropic viscosity on solar phenomena.
+We find the stability of Lare3d without (the more commonly employed)
+isotropic or shock viscosity to be sufficient for at least the study
+of kink instabilities in coronal loops~\cite{quinnEffectAnisotropicViscosity2020a}.
+}{To take this into account, in \cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017},
+we developed a phenomenological model of anisotropic viscosity that
+captures the main physics of viscosity in the 
+solar corona as outlined in the analysis of
+\cite{braginskiiTransportProcessesPlasma1965}, namely parallel
+viscosity in regions of strong field  strength and isotropic viscosity
+in regions of very weak or zero field strength. For brevity, we will
+refer to this model of viscosity as ``the switching model''. In
+\cite{quinnEffectAnisotropicViscosity2020a,Quinn2021} we implemented
+the switching model as a module for the widely-used general MHD code
+Lare3d \cite{arberStaggeredGridLagrangian2001}, and demonstrated
+significant effects of anisotropic viscosity on the 
+development of the nonlinear MHD kink instability and the
+Kelvin-Helmholtz instability.} \rs{The}{More generally, the} interest in
+anisotropic viscosity stems from the \rs{unanswered}{open} question of
+which heating mechanism (viscous or Ohmic) is dominant in the solar
+corona~\cite{klimchukSolvingCoronalHeating2006a}, an important facet
+of solving the coronal heating problem. Using scaling laws, it has
+been suggested that viscous heating (generated through anisotropic
+viscosity) can dwarf that of Ohmic
+heating~\cite{craigAnisotropicViscousDissipation2009a,litvinenkoViscousEnergyDissipation2005}.
+However,
+due to computational and observational limitations, this cannot be
+directly tested, and so the influence of other factors such as small
+scale instabilities and turbulence is relatively
+unknown~\cite{klimchukSolvingCoronalHeating2006a}. In addition to
+directly heating the plasma, viscosity plays a part in the damping of
+instabilities and waves~\cite{rudermanSlowSurfaceWave2000a}. It is
+this effect we are most interested in here, and it shall be \rs{found}{reported} that
+the use of anisotropic viscosity permits the growth of the
+\rs{fluting}{flute} instability, which is otherwise strongly damped by
+isotropic viscosity.
 
-\subsection{The fluting instability}
+\rs{}{ADD A BRIEF NEW ``CONTENTS PARAGRAPH'':
+This paper is organized as follows. Section 1 ..., Section 2...}
+
+\subsection{The \rs{fluting}{flute} instability}
 
@@
 \end{equation}
-where $m$ and $k$ are the wavenumbers in the $\theta$ and $z$ directions, respectively.
+where $m$ and $k$ are the wavenumbers \rs{in the $\theta$ and $z$
+  directions, respectively}{in the azimuthal and axial directions,
+  $\theta$ and $z$, respectively and $r$ is the radial coordinate in
+  cylindrical polars}. 
 The helical kink instability occurs for perturbations where $m=1, k\ne0$ and is the only instability of this form which is a body instability, that is it moves the entire body of the flux tube.
-Perturbations where $m>1$ are termed fluting or interchange instabilities.
+Perturbations where $m>1$ are termed \rs{fluting}{flute} or interchange instabilities.
 
-When the magnetic field is sheared, as in a twisted magnetic flux tube, an interchange instability (such as the fluting instability) is confined to a surface where the peaks and troughs follow the shear of the field.
-That is, the instability is confined to the surface where the perturbation wavevector $(0, m/r, k)$ is perpendicular to the direction of the field which, in an axisymmetric, twisted flux tube, is located at a radius $r$ given by
+When the magnetic field is sheared, as in a twisted magnetic flux
+tube, an interchange instability (such as the \rs{fluting}{flute}
+instability) is confined to a surface where the peaks and troughs
+follow the shear of the field. That is, the instability is confined to
+the surface where the perturbation wavevector $(0, m/r, k)$ is
+perpendicular to the direction of the field, \rs{}{known as the
+  ``resonance surface''}. \rs{which in}{In} an axisymmetric twisted
+flux tube \rs{}{the resonance surface} is located at a radius $r$
+given by
 \begin{equation}
@@
 
-The stability of an infinite cylindrical flux tube to perturbations of the form~\eqref{eq:kink_perturbation} is given by the classical Suydam's criterion
+The stability of an infinite cylindrical flux tube to perturbations of
+the form~\eqref{eq:kink_perturbation} is given by the classical
+\rs{}{Suydam's criterion \cite{Suydam1959}}
 \begin{equation}
@@
 \end{equation}
-where $S = r q'/q$ is a measure of the shear, $q = 2\pi r B_z / L B_{\theta}$ is the safety factor for a flux tube of length $L$ and a dash denotes differentiation with respect to $r$~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998}.
-This applies to both fluting and kink instabilities although many additional effects such as line-tying are not incorporated into the corresponding linear analysis.
-The effect of line-tying on the kink instability can be found in~\cite{hoodKinkInstabilitySolar1979}.
-Where~\eqref{eq:suydams_criterion} is not satisfied, the flux tube may be unstable to perturbations of the form~\eqref{eq:kink_perturbation}.
-When $m>1$, the perturbations remain local to resonant surfaces given by~\eqref{eq:resonant_surface}.
+where $S = r q'/q$ is a measure of the shear, $q = 2\pi r B_z / L
+B_{\theta}$ is the safety factor for a flux tube of length $L$ and a
+\rs{dash}{prime} denotes differentiation with respect to
+$r$~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998}. This applies
+to both \rs{fluting}{flute} and kink instabilities although many
+additional effects such as line-tying are not incorporated into the
+corresponding linear analysis. The effect of line-tying on the kink
+instability \rs{can be found}{is investigated}
+in~\cite{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion}
+is not satisfied, the flux tube may be unstable to perturbations of
+the form~\eqref{eq:kink_perturbation}. When $m>1$, the perturbations
+remain local to resonant surfaces given
+by~\eqref{eq:resonant_surface}. 
+\rs{}{When} Suydam's criterion is satisfied and the flux tube is linearly stable, it may still be unstable to non-local perturbations, where the shear and pressure are small enough that interchange perturbations do not need to satisfy~\eqref{eq:resonant_surface}.
+Additionally, the inclusion of resistivity generally reduces the stabilising effect of the shear, permitting growth of a resistive interchange mode, albeit at a slower rate than that of the ideal instability~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998}.
+It will be found that the ideal linear analysis of~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998} is sufficient for understanding the \rs{fluting}{flute} instabilities investigated here since the associated flux tubes adequately fail the criterion~\eqref{eq:suydams_criterion}.
 
-When Suydam's criterion is satisfied and the flux tube is linearly stable, it may still be unstable to non-local perturbations, where the shear and pressure are small enough that interchange perturbations do not need to satisfy~\eqref{eq:resonant_surface}.
-Additionally, the inclusion of resistivity generally reduces the stabilising effect of the shear, permitting growth of a resistive interchange mode, albeit at a slower rate than that of the ideal instability~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998}.
-It will be found that the ideal linear analysis of~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998} is sufficient for understanding the fluting instabilities investigated here since the associated flux tubes adequately fail the criterion~\eqref{eq:suydams_criterion}.
-
-While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal fluting instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\cite{goldstonIntroductionPlasmaPhysics2020}) and is given by
+While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal \rs{fluting}{flute} instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\cite{goldstonIntroductionPlasmaPhysics2020}) and is given by
 \begin{equation}
@@
 
-Throughout this chapter, the twisted flux tube generated by the drivers has a pressure profile which is approximately axisymmetric, and independent of $z$ away from the boundaries at $z=\pm2$, and has a negative gradient, hence $|\nabla p|$ may be written as $-d p/ dr$.
+Throughout this \rs{chapter}{paper}, the twisted flux tube generated by the drivers has a pressure profile which is approximately axisymmetric, and independent of $z$ away from the boundaries at $z=\pm2$, and has a negative gradient, hence $|\nabla p|$ may be written as $-d p/ dr$.
 Similarly, away from the boundaries, the magnetic field has a negligible $r$ component and little dependence on $\theta$ and $z$, allowing the field to be approximated as $\vec{B} = (0, B_{\theta}(r), B_z(r))^{\text{T}}$, in cylindrical coordinates $(r, \theta, z)$.
@@
   \label{eq:fluting_growth_rate2}
-\gamma_{ideal}^2 = \frac{-2p'}{\rho R_c}.
+\gamma_{\rs{{ideal}}{\text{ideal}}}^2 = \frac{-2p'}{\rho R_c}.
 \end{equation}
-This growth rate remains applicable while the flux tube remains relatively axisymmetric, that is while the kink instability remains in its linear phase.
+This \rs{growth rate remains applicable}{approximation for the growth rate continues to hold} while the flux tube remains relatively axisymmetric, that is while the kink instability remains in its linear phase.
 
-In contrast to the precise form of the equilibrium state and perturbation studied in~\cite{quinnEffectAnisotropicViscosity2020a}, this is an experiment where a system is driven and instabilities occur organically as a result of noise providing a random perturbation.
-As a result of the driving, the flux tube is not in static equilibrium.
-Consequently, the stability criterion and linear growth rate presented previously are useful only as a guide and for approximate comparison.
+\rs{In contrast to the precise form of the equilibrium state and
+  perturbation studied in~\cite{quinnEffectAnisotropicViscosity2020a},
+  this is an experiment where a system is driven and instabilities
+  occur organically as a result of noise providing a random
+  perturbation. As a result of the driving, the flux tube is not in
+  static equilibrium. Consequently, the stability criterion and linear
+  growth rate presented previously are useful only as a guide and for
+  approximate comparison.}{The stability criterion
+  \eqref{eq:suydams_criterion} and the linear
+  growth rate approximation \eqref{eq:fluting_growth_rate2} are useful
+  only as a guide and for 
+  approximate analysis of the numerical simulations presented in this
+  work.  The precise form of the equilibrium state and the
+  perturbations needed for the validity of
+  \eqref{eq:suydams_criterion} and \eqref{eq:fluting_growth_rate2}
+  were used in~\cite{quinnEffectAnisotropicViscosity2020a}.
+  In contrast, in the experiments reported in the following the system
+  is driven and instabilities occur spontaneously due to random
+  perturbation. As a result of the driving, the flux tube is also not
+  in static equilibrium initially. }
 
-\section{Numerical setup}
+\section{\rs{Numerical setup}{Mathematical formulation and numerical setup}}
 
-Lare3d numerically solves the MHD equations for the density $\rho$, plasma velocity $\vec{u}$, pressure $p$, magnetic field $\vec{B}$ and internal energy $\varepsilon$,
+\rs{Lare3d numerically solves}{We consider} the
+\rs{MHD}{magnetohydrodynamic} equations for the density $\rho$, plasma
+velocity $\vec{u}$, pressure $p$, magnetic field $\vec{B}$ and
+internal energy $\varepsilon$, \rs{}{in their non-dimensionalised
+  visco-resistive form}
+\begin{subequations}
+  \label{eq:MHD}
   \begin{gather}
@@
 \rho\frac{D\varepsilon}{Dt} = -p \vec{\nabla} \cdot \vec{u} + {Q}_{\nu} + {Q}_{\eta},%\\
-\label{eq:energy}
+%\label{eq:energy}
 %\end{equation}
     \end{gather}
-where $\eta$ is the non-dimensionalised resistivity, $\jmath = \nabla \times \vec{B}$ is the current density and $\ten{\sigma}$ is the viscous stress tensor (described below).
-The terms ${Q}_{\nu} = \ten{\sigma} : \vec{\nabla}\vec{u}$ and ${Q}_{\eta} = \eta | \vec{\jmath} |^2$ are viscous heating and Ohmic heating, respectively.
-The system is closed by the inclusion of the equation of state for an ideal gas
+\end{subequations}
+where $\eta$ is the non-dimensionalised resistivity,
+$\rs{\jmath}{\vec{\jmath}} = \nabla \times \vec{B}$ is the current
+density and \rs{$\ten{\sigma}$ is the viscous stress tensor (described
+  below). The}{the} terms ${Q}_{\nu} = \ten{\sigma} : \vec{\nabla}\vec{u}$
+  and ${Q}_{\eta} = \eta | \vec{\jmath} |^2$ are viscous heating and
+  Ohmic heating, respectively. The system is closed by the inclusion
+  of the equation of state for an ideal gas 
 \begin{equation}
@@
 \end{equation}
-where the specific heat ratio is given by $\gamma = 5/3$.
+\rs{where}{with} the specific heat ratio is given by $\gamma = 5/3$.
 
-The isotropic (or Newtonian) viscosity stress tensor is given by
+\rs{The isotropic (or Newtonian) viscosity stress tensor is given by
 \begin{equation}
   \label{eq:isotropic_viscous_tensor}
-  \ten{\sigma} = \nu \ten{W},
+  \ten{\sigma}_{\rs{{iso}}{\text{iso}}} = \nu \ten{W},
 \end{equation}
@@
 \end{equation}
-is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$ identity matrix.
-We use an identical model of anisotropic viscosity as that used in previous work~\cite{quinnEffectAnisotropicViscosity2020a}, the switching model, first presented in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}.
-While this model is intended to revert to an isotropic model in the vicinity of magnetic null points, we effectively only make use of the anisotropic component, since there are no null points present in the simulations at any point.
-To this end, we set the switching parameter (which controls the degree of viscous anisotropy) to $a_0 = 150$ in Lare3d's control, a value sufficiently large that the anisotropic viscous stress tensor is given by
+is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$
+identity matrix. We use an identical model of anisotropic viscosity \rs{as}{to}
+that used in
+\rs{our previous work~\cite{quinnEffectAnisotropicViscosity2020a}}{previous work~\cite{quinnEffectAnisotropicViscosity2020a,Quinn2021}},
+ the switching model, first presented
+ in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}. While
+ this model is intended to revert to an isotropic model in the
+ vicinity of magnetic null points, we effectively only make use of the
+ anisotropic component, since there are no null points present in the
+ \rs{simulations}{simulations reported here} at any point. To this
+ end, we set the switching parameter (which controls the degree of
+ viscous anisotropy) to $a_0 = 150$ in Lare3d's control, a value
+ sufficiently large \rs{}{so} that the anisotropic viscous stress tensor is given by
 \begin{equation}
@@
 Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020a}\todo{ref KHI paper}.
+}{}
+\rs{}{Two different models for the viscosity stress tensor $\ten{\sigma}$
+will be compared and contrasted in this study. The first model is the
+conventional} isotropic (or Newtonian) viscosity stress tensor \rs{}{used in
+the vast majority of the existing literature, so that,} 
+\begin{equation}
+  \label{eq:isotropic_viscous_tensor}
+\rs{}{\ten{\sigma} = }\ten{\sigma}_{\rs{{iso}}{\text{iso}}} = \nu \ten{W},
+\end{equation}
+where $\nu$ is the viscous transport parameter, generally referred to as the viscosity,
+\begin{equation}
+  \label{eq:rate_of_strain}
+  \ten{W} = \nabla\vec{u} + (\nabla\vec{u})^T - \tfrac{2}{3}(\nabla \cdot \vec{u})\ten{I},
+\end{equation}
+is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$
+identity \rs{}{tensor. The second model, which is the one of actual interest, is the} anisotropic viscosity stress
+tensor given by
+\begin{equation}
+  \label{eq:switching_model}
+\rs{}{\ten{\sigma} = \ten{\sigma}_\text{aniso}} = \nu \left[\frac{3}{2}(\ten{W}\vec{b}\cdot\vec{b}) \left( \vec{b} \otimes \vec{b} - \frac{1}{3}\ten{I} \right)\right],
+\end{equation}
+where $\vec{b}$ is the unit vector in the direction of the magnetic
+field.
+\rs{}{
+Expression \eqref{eq:switching_model} is identical to the strong field approximation of the
+general anisotropic viscosity tensor derived by Braginskii~\cite{braginskiiTransportProcessesPlasma1965}.
+Expressions \eqref{eq:isotropic_viscous_tensor} and \eqref{eq:switching_model} arise as asymptotic limits of the
+more general switching model used in our earlier works 
+\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020a,Quinn2021}
+which, includes both isotropic and anisotropic contributions and can
+switch gradually between them depending on the strength of the
+magnetic field at a given spacio-temporal location. For example, in
+the vicinity of a null point where the magnetic field becomes weak the
+isotropic viscosity contribution becomes dominant in the switching
+model. Switching between the two limit cases is not relevant in the
+present study where the variations in the magnetic field are not
+significantly large.}
 
-The non-dimensionalisation scheme and values align with the scheme used by Lare3d~\cite{arberStaggeredGridLagrangian2001} and are identical to those used in~\cite{quinnEffectAnisotropicViscosity2020a}.
+\rs{The non-dimensionalisation scheme and values align with the scheme
+used by Lare3d~\cite{arberStaggeredGridLagrangian2001} and are
+identical to those used
+in~\cite{quinnEffectAnisotropicViscosity2020a}.}
+   {
+The non-dimensionalisation of equations \eqref{eq:MHD} is identical to that used in
+our earlier works
+\cite{quinnEffectAnisotropicViscosity2020a,Quinn2021} and in reference
+\cite{arberStaggeredGridLagrangian2001} that describes the code Lare3d
+we use for numerical solution, see further below. A typical magnetic
+field strength $B_0$, density $\rho_0$ and length scale $L_0$ are
+chosen and the other variables non-dimensionalised
+appropriately. Velocity and time are non-dimensionalised using the
+Alfv\'en speed $u_A = B_0 / \sqrt{\rho_0 \mu_0}$ and Alfv\'en crossing 
+time $t_A = L_0/u_A$, respectively. Temperature is non-dimensionalised
+via $T_0 = u_A^2 \bar{m} / k_B$, where $k_B$ is the Boltzmann constant
+and $\bar{m}$ is the average mass of ions, here taken to be $\bar{m} =
+1.2m_p$ (a mass typical for the solar corona) where $m_p$ is the
+proton mass. Dimensional quantities can be recovered by multiplying
+the non-dimensional variables by their respective reference value
+(e.g. $\vec{B}_{\dim} = B_0 \vec{B}$). The reference values used here
+are $B_0 = 5 \times 10^{-3}$ T, $L_0 = 1$ Mm and $\rho_0 = 1.67 \times
+10^{-12} \ \text{kg m}^{-3}$, giving reference values for the Alfv\'en
+speed $u_A = 3.45\ \text{Mm s}^{-1}$, Alfv\'en time $t_A =
+0.29\ \text{s}$ and temperature $T_0 = 1.73 \times 10^{9}\ K$.      
+   }
+
+\rs{}{The following initial and boundary conditions are used to form a
+magnetic flux tube and excite instabilities by dynamic twisting.} 
 The magnetic field is prescribed as initially straight and uniform,
@@
 \end{equation}
-in a cube of dimension $[-2,2]^3$.
-The velocity is set everywhere to $\vec{u} = \vec{0}$, the density to $\rho = 1$, the internal energy to $\varepsilon = 8.67\times 10^{-4}$ (corresponding to a temperature of $10^6$ K).
-\todo{what's the plasma beta?} At the boundaries, the magnetic field, density, and energy are fixed to their initial values and the velocity to zero except at the boundaries where the twisting driver, described below, is prescribed.
-The spatial derivatives of these variables are also set to zero at the boundaries.
-The resolution is $512$ grid points per dimension, comparable to the highest resolution kink instability studies of~\cite{hoodCoronalHeatingMagnetic2009} or medium resolution studies of~\cite{barefordShockHeatingNumerical2015}.
+in a cube of \rs{dimension}{size} $[-2,2]^3$. \rs{The}{Initially, the} velocity is set
+everywhere to $\vec{u} = \vec{0}$, the density to $\rho = 1$,
+\rs{}{and} the
+internal energy to $\varepsilon = 8.67\times 10^{-4}$ (corresponding
+to a temperature of $10^6$ K). \todo{what's the plasma beta?} At the
+boundaries, the magnetic field, \rs{}{velocity,} density, and energy are fixed to their
+initial values \rs{}{and their derivatives normal to the
+boundaries are set to zero} \rs{and the velocity to zero}{} except
+\rs{the boundaries}{where twisting velocity ``driver''}, described
+below, is prescribed.
+\rs{The spatial
+derivatives of these variables are also set to zero at the
+boundaries.}{} \rs{The resolution is $512$ grid points per dimension,
+comparable to the highest resolution kink instability studies
+of~\cite{hoodCoronalHeatingMagnetic2009} or medium resolution studies
+of~\cite{barefordShockHeatingNumerical2015}.}{}
 
@@
   \end{subfigure}
-
-  \mycaption{Radial velocity profile $u_r(r)$ and acceleration profile $u_t(t)$ of the driver for parameters $u_0 = 0.15$, $r_d = 5$ and $t_r = 2$.}{}
+  \mycaption{Radial velocity profile $u_r(r)$ and acceleration profile
+    $u_t(t)$ of the driver \rs{}{\eqref{eq:null_twisting_profile}} for
+    parameters $u_0 = 0.15$, $r_d = 5$ and $t_r = 2$.}{} 
   \label{fig:kink_driver}
@@
 This form of driver allows the system to be accelerated slowly enough that the production of disruptive shocks and fast waves is minimal.
-It is unavoidable that some waves are produced during the boundary acceleration, however these usefully provide one source of noise which eventually forms a perturbation.
-
-The driver velocity is set to $u_0 = 0.15$, the normalising factor is $u_{r0} = 2.08$, and setting $r_d = 5$ corresponds to a driver constrained to $r<1$ and with a peak velocity at $r\approx 0.38$.
+It is unavoidable that some waves are produced during the boundary acceleration, however these usefully provide \rs{one}{a} source of noise which eventually forms a perturbation.
+\rs{}{
+The driver} velocity is set to $u_0 = 0.15$, the normalising factor is $u_{r0} = 2.08$, and setting $r_d = 5$ corresponds to a driver constrained to $r<1$ and with a peak velocity at $r\approx 0.38$.
 The ramping time is set to $t_r = 2$, resulting in an acceleration from $0$ to $u_0$ over approximately $5$ Alfv\'en times.
@@
 The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\cite{quinnEffectAnisotropicViscosity2020a,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
-This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the fluting instability and the helical kink instability.
+This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the \rs{fluting}{flute} instability and the helical kink instability.
 
-Two pairs of simulations were performed, one pair where the background resistivity is set to $\eta=10^{-3}$ and another where $\eta=10^{-4}$.
-As in~\cite{quinnEffectAnisotropicViscosity2020a}, only background resistivity is used.
-Each simulation pair consists of one simulation using isotropic viscosity~\eqref{eq:isotropic_viscous_tensor} and another using the switching model~\eqref{eq:switching_model}.
-The value of viscosity is set to $\nu = 10^{-4}$ in all cases.
+\rs{}{The problem formulated above is solved numerically using the
+  staggered-grid, Lagrangian–Eulerian remap code for 3D MHD
+  simulations Lare3D of \cite{arberStaggeredGridLagrangian2001} where
+  a  new module for anisotropic viscosity has been
+  included as detailed in \cite{Quinn2021}.} The resolution used in the
+current work is  $512$ grid points per dimension, comparable to the
+highest resolution kink instability studies
+of~\cite{hoodCoronalHeatingMagnetic2009} or medium resolution studies
+of~\cite{barefordShockHeatingNumerical2015}.
 
@@
 
-The overall development of both instabilities is broadly similar for the two values of resistivity and is described initially.
-Focus is then placed on the development of the $\eta=10^{-4}$ cases, comparing the results of the two viscosity models.
-These cases illustrate the development of the instabilities while showcasing the effect of the viscosity models.
-Then the differences apparent in the $\eta=10^{-3}$ cases are summarised without a full exploration of the (qualitatively similar) results.
+\rs{Two pairs of simulations were performed,}{We focus the attention
+on two selected pairs of  
+simulations, one pair where the background resistivity is set to
+$\eta=10^{-3}$ and another where $\eta=10^{-4}$. As
+in~\cite{quinnEffectAnisotropicViscosity2020a}, only background
+resistivity is used. Each pair consists of one simulation
+using isotropic viscosity~\eqref{eq:isotropic_viscous_tensor} and
+another one using the \rs{switching}{anisotropic} model~\eqref{eq:switching_model}. The
+value of viscosity is set to $\nu = 10^{-4}$ in all cases.} 
+%
+The overall development of both \rs{}{the flute and the kink}
+instabilities is broadly similar for the two values of resistivity and
+is described  initially. Focus is 
+then placed on the \rs{development of}{detailed description of instabilities in} the
+$\eta=10^{-4}$ cases, \rs{comparing the results}{with the aim of comparing the effects} of the two
+viscosity models. \rs{These cases illustrate the development of the instabilities while showcasing the effect of the
+viscosity models.}{} Then \rs{differences apparent in}{further features of} the $\eta=10^{-3}$
+cases are summarised. \rs{without a full exploration of the (qualitatively
+similar) results.}{}
 
-\subsection{Overview of instability development}
+\subsection{\rs{Overview of instability development}{Mechanism and
+    general development of instability}}
 
@@
     \end{subfigure}
-  \mycaption{Gradients in the current density generate pressure gradients through Ohmic heating.}{All plots are from switching cases when $t=20$ through the plane $z=0$.
-Note the sign of the axial current density $j_z$ has been flipped for comparison and the Ohmic heating is given by $Q_{\eta} = \eta j^2$.
-The pressure profile of an additional test-case where $\eta=0$ is also shown.}%
+  \mycaption{Gradients in the current density generate pressure
+    gradients through Ohmic heating.}{\rs{}{Axial current density (a), Ohmic heating
+      (b) and pressure (c) as functions of the radial distance from
+      the tube axis.}{} All plots are from \rs{switching}{anisotropic}
+    cases when $t=20$ through the plane $z=0$. Note the sign of the
+    axial current density $j_z$ has been flipped for comparison and
+    the Ohmic heating is given by $Q_{\eta} = \eta j^2$. The pressure
+    profile of an additional test-case where $\eta=0$ is also
+    shown. \rs{}{Line types are indicated in the legend.}}%
   \label{fig:pressure_and_heating}
@@
 
-In all cases, the initial reaction to the twisting at the upper and lower boundaries is two torsional Alfv\'en waves which travel along the tube from the upper and lower boundaries to the opposite boundary.
-The interaction between these waves produces an oscillating pattern in the kinetic energy with a period of approximately $4$ Alfv\'en times, equal to the time taken for an Alfv\'en wave to travel the entire length of the domain (visible early in figure~\ref{fig:kink_ke-4}).
+\rs{In all cases, the initial reaction to the twisting at the upper
+and lower boundaries is two}{Initially and in all cases computed, the
+twisting at the upper and lower boundaries gives rise to a pair of}
+torsional Alfv\'en waves which \rs{}{proceed to} travel along the tube
+from the upper and lower boundaries to \rs{the}{their respective}
+opposite boundaries. The interaction between these waves produces an 
+oscillating pattern in the kinetic energy with a period of
+approximately $4$ Alfv\'en times, equal to the time taken for an
+Alfv\'en wave to \rs{travel}{traverse} the entire length of the domain
+\rs{}{as} visible early in figure~\ref{fig:kink_ke-4}.
 
-As the field continues to be twisted, currents form due to the local shear in the magnetic field which heat the plasma through Ohmic heating.
-Due to the radial form of the driver, the magnitude of the current density is greatest at the axis of the tube, then decreases radially outwards (figure~\ref{fig:current_profiles}).
-The orientation of the twisting produces a current directed in the negative $z$-direction for $r\lessapprox0.5$.
-At $r \approx 0.5$ (corresponding to the radius of peak driving velocity) the current switches direction and is in the positive $z$-direction in a shell where $0.5\lessapprox r \lessapprox 0.8$.
-This form of twisted field with an inner core of current in one direction surrounded by an oppositely-directed current shell is similar to the prescribed field in chapter~\cite{quinnEffectAnisotropicViscosity2020a}.
+As the field continues to be twisted, currents form, due to the local
+shear in the magnetic field, \rs{which}{and} heat the plasma through Ohmic
+\rs{heating}{dissipation}. Due to the radial form of the driver, the magnitude of the
+current density is greatest at the axis of the tube, then decreases
+radially outwards \rs{}{as seen in} figure~\ref{fig:current_profiles}. The orientation
+of the twisting produces a current \rs{directed}{flowing} in the negative
+$z$-direction for $r\lessapprox0.5$. At $r \approx 0.5$ (corresponding
+to the radius of peak driving velocity) the current switches \rs{direction}{orientation}
+and is in the positive $z$-direction in a shell where $0.5\lessapprox
+r \lessapprox 0.8$. This form of \rs{}{a} twisted field with an inner core of
+current in one direction surrounded by \rs{an}{a shell of}
+oppositely-directed current is similar to the \rs{prescribed field in
+chapter~}{current configuration arising due to the field prescribed in} \cite{quinnEffectAnisotropicViscosity2020a}.
 
-This current profile is reflected in the radial Ohmic heating profile (figure~\ref{fig:kink_straight_ohmic_heating_profile}) and, consequently, in the radial pressure profile (figure~\ref{fig:pressure_profiles}).
-The highly pressurised core extends to $r\approx 0.2$--$0.4$ (depending on the value of $\eta$) before increasing slightly around $r\approx 0.7$.
-The secondary bump in pressure is due to the outer shell of current.
-The pressure gradient near the axis provides the outwardly directed pressure force which competes against the binding action of the magnetic tension to (potentially) result in the fluting instability.
-The magnitude of the pressure gradient depends strongly on the value of $\eta$, with lower values producing shallower gradients which (as shall be seen) are more stable to the fluting instability.
-Indeed, when $\eta=0$, the radial pressure profile is nearly flat and the tube stable to the fluting instability.
+This current profile is reflected in the radial Ohmic heating profile
+(figure~\ref{fig:kink_straight_ohmic_heating_profile}) and,
+consequently, in the radial pressure profile
+(figure~\ref{fig:pressure_profiles}). The highly pressurised core
+extends to $r\approx 0.2$--$0.4$ (depending on the value of $\eta$)
+before increasing slightly around $r\approx 0.7$. The secondary bump
+in pressure is due to the outer shell of current. The pressure
+gradient near the axis provides the outwardly directed pressure force
+which competes against the binding action of the magnetic tension
+\rs{to (potentially) result in the}{and this provides the mechanism of}
+\rs{fluting}{flute} instability \rs{}{excitation}.  The magnitude
+of the pressure gradient depends strongly on the value of
+\rs{}{resistivity} $\eta$, with lower values producing shallower 
+gradients which (as shall be seen) are more stable to the
+\rs{fluting}{flute} instability. Indeed, when $\eta=0$, the radial
+pressure profile is nearly flat and the tube stable to the
+\rs{fluting}{flute} instability. \rs{}{IS IT POSSIBLE TO COMMENT WHY
+  THIS MECHANISM IS NOT PRESENT IN THE CONFIGURATION OF \cite{quinnEffectAnisotropicViscosity2020a}?}
 
-In all cases unstable to the fluting instability, it occurs some time between $t=20$ and $t=30$.
-During this time, the continued driving at the boundaries eventually injects enough twist that the tube also becomes unstable to the kink instability.
-This initially develops linearly alongside the fluting instability and then erupts during the kink's nonlinear phase, dominating the dynamics and disrupting the fluting instability.
-The development of the two instabilities is strongly affected by the value of $\eta$ and the viscosity model used.
+In all cases unstable to the \rs{fluting}{flute} instability, it
+occurs \rs{some time}{} between $t=20$ and $t=30$. \rs{During this
+  time, the}{The} continued driving at the boundaries eventually
+injects enough twist that the tube also becomes unstable to the kink
+instability. This initially develops linearly alongside \rs{}{or shortly
+after} the \rs{fluting}{flute} instability and then erupts during the
+\rs{kink's}{its}  nonlinear phase, dominating the dynamics and
+disrupting the   \rs{fluting}{flute} instability. The \rs{}{onset and
+the competition} of the two instabilities is strongly affected by
+the value of $\eta$ and the viscosity model used.
 
-\subsection{Development where $\eta=10^{-4}$}
+\subsection{\rs{Development where}{Instabilities at resistivity} $\eta=10^{-4}$}
 
@@
     \end{subfigure}
-\mycaption{Pressure profiles during the development of the fluting and kink instabilities.}{Shown are slices of pressure through $z=0$ where $\eta = 10^{-4}$ and the viscosity model is switching.
-Note the difference in colour scale in figure~\ref{fig:swi-4_pressure_15}.
-The development in the isotropic case is similar.}
+\mycaption{Pressure profiles during the development of the
+  \rs{fluting}{flute} and kink instabilities.}{Shown are
+  \rs{slices}{density plots} of pressure \rs{through}{at} $z=0$
+  \rs{where}{with} $\eta = 10^{-4}$ 
+  and \rs{the viscosity model is \rs{switching}{anisotropic}}{for the
+    anisotropic viscosity model}. Note the difference in colour scale
+  in figure~\ref{fig:swi-4_pressure_15}. The development in the
+  isotropic case is similar.} 
 \label{fig:kink_pressure_slices-4}%
@@
 
-Figure~\ref{fig:kink_pressure_slices-4} shows the pressure profile through $z=0$ where $\eta=10^{-4}$ and the viscosity model is switching for times $t=26$, $28$ and $30$.
-At $t=26$ the tube becomes unstable to the $m=4$ fluting instability, when the plasma begins to (slightly) bulge out diagonally from the high-pressure core (figure~\ref{fig:swi-4_pressure_13}).
-As the bulges move radially outwards into lower pressure regions they expand and accelerate, resulting in the entire pressure structure appearing clover-shaped (figure~\ref{fig:swi-4_pressure_14}).
-By $t=30$ the kink instability has disrupted the fluting instability and is developing nonlinearly (figure~\ref{fig:swi-4_pressure_15}).
-As is typical of nonlinear kink development, the tube continues to release its stored potential energy as kinetic energy and heat and the contained plasma becomes highly mixed.
-In the unseen isotropic case, the fluting instability is present but damped, and the kink instability quickly dominates the dynamics.
+\rs{}{We now describe the evolution and competition of flute and
+  kink instabilities in case of resistivity $\eta=10^{-4}$.}
+\rs{The}{Figure}~\ref{fig:kink_pressure_slices-4} shows the pressure profile
+\rs{the viscosity model is switching for times}{of the \rs{switching}{anisotropic} viscosity case 
+\eqref{eq:switching_model} at
+time moments} $t=26$, $28$ and $30$ and \rs{through}{at} $z=0$. At $t=26$
+the tube becomes unstable to \rs{the $m=4$}{} \rs{fluting}{flute}
+instability \rs{}{with azimuthal wavenumber $m=4$}, when the
+plasma begins to \rs{(slightly)}{} bulge out diagonally from the
+high-pressure core as seen in figure~\ref{fig:swi-4_pressure_13}. As  
+the bulges move radially outwards into lower pressure regions they
+expand and accelerate, resulting in the entire pressure structure
+appearing \rs{clover-shaped}{taking the shape of a four-leaf clover} (figure~\ref{fig:swi-4_pressure_14}). By
+$t=30$ the kink instability has disrupted the \rs{fluting}{flute}
+instability and is developing nonlinearly
+\rs{}{as evident in} figure~\ref{fig:swi-4_pressure_15}. As is typical of nonlinear kink
+development, the tube continues to release its stored potential energy
+\rs{as}{in the form of} kinetic energy and heat and the contained plasma becomes highly
+mixed. In the \rs{unseen}{} isotropic \rs{}{viscosity} case
+\rs{}{which will not be illustrated by a separate figure}, the
+\rs{fluting}{flute} instability is present but damped, and \rs{}{it is
+  quickly outcompeted by} the kink instability \rs{}{which} quickly dominates the dynamics.
 
@@
       \includegraphics[width=\linewidth]{field_line_plots/cropped/v-4r-4-switching_0014_cropped.png}
-      \caption{Switching}
+      \caption{\rs{Switching}{Anisotropic}}
       \label{fig:field_line_plots_swi}
     \end{subfigure}
-\mycaption{Simultaneous development of fluting and kink instabilities in the isotropic and switching cases as field lines and pressure contours.}{Field lines and contours of pressure (where $p=0.3$) are plotted at $t=28$.
-Also shown is the velocity driver as a slice.
-The fluting instability grows in both cases, though faster in the switching case.
+\mycaption{Simultaneous development of \rs{fluting}{flute} and kink
+  instabilities in the isotropic and \rs{switching}{anisotropic} cases
+  \rs{as}{illustrated by} field lines and pressure contours.}{Field
+  lines and contours of pressure (where $p=0.3$) are plotted at
+  $t=28$.
+Also shown is the velocity driver \rs{as a slice}{$u_r(\sqrt{x^2+y^2})$ at $z=2$}.
+The \rs{fluting}{flute} instability grows in both cases, though faster in the \rs{switching}{anisotropic} case.
 The initial stages of the kink instability can also be observed in the field lines of the isotropic case in subfigure~\ref{fig:field_line_plots_iso}.}
@@
 
-Figure~\ref{fig:kink_field_line_plots} shows the effect the viscosity models have on the initial stages of the fluting and kink instabilities in 3D.
-While the fluting instability is observed in both cases, it is damped in the isotropic case and grows faster in the switching case.
-In the latter case, the extended development of the fluting instability appears to disrupt the inner core of field lines and (as shall be seen) slows the growth of the kink instability.
-In the isotropic case, the fluting instability has been damped to the extent that the kink instability grows uninhibited and quickly disrupts the fluting.
+Figure~\ref{fig:kink_field_line_plots} shows the effect the viscosity
+models have on the initial stages of the \rs{fluting}{flute} and kink
+instabilities in 3D. While the \rs{fluting}{flute} instability is
+observed in both cases, it is damped in the isotropic case and grows
+faster in the \rs{switching}{anisotropic} case. In the latter case,
+the extended development of the \rs{fluting}{flute} instability
+appears to disrupt the inner core of field lines and, \rs{(as shall be
+  seen)}{as will be discussed further below,} slows the growth of the
+kink instability. In the isotropic case, the \rs{fluting}{flute}
+instability has been damped to the extent that the kink instability
+grows uninhibited and quickly disrupts the fluting.
 
@@
     \end{subfigure}
-  \mycaption{Kinetic energy as a function of time showing the development and measured growth rates of the fluting and kink instabilities.}{Both plots are from results where $\eta=10^{-4}$.}
+  \mycaption{Kinetic energy as a function of time showing the
+    development and measured growth rates \rs{}{$\gamma$ and $\sigma$}
+    of the \rs{fluting}{flute}
+    and kink instabilities, \rs{}{respectively.}}{\rs{Both plots are from results
+      where}{Resistivity is $\eta=10^{-4}$ and the second plot is a
+      enlarged version of the first. [RADO: Please chenage ``swi'' to
+      ``aniso'' in legend.  Perhaps change symbol for growth rate of
+        kink from $\sigma$ (used for visc stress tensor) to smth else
+        say $\lambda$. I'll leave you do that also in the text as figs
+  need changed first.]}}
 \label{fig:kink_str8_ke-4}%
@@
 
-Despite the fluting instability appearing in the isotropic case (figure~\ref{fig:field_line_plots_iso}) only in the switching case can the onset of both the fluting and kink instabilities be seen in the kinetic energy profile (figure~\ref{fig:kink_ke_log-4}), where the nonlinear growth rates of the two instabilities are found to be $\gamma = 0.69$ for the fluting and $\sigma = 2.55$ for the kink.
-The onset times are approximately $t=27$ for the fluting instability and $t=28$ for the kink.
-In the isotropic case, the growth rate of the kink, $\sigma = 2.97$, is larger than in the switching case, although the onset times appear similar, and the kinetic energy profile shows no evidence of the growth of the fluting instability.
-
-The faster growth of the kink compared to, say, that of chapter~\cite{quinnEffectAnisotropicViscosity2020a} is due to the relative aspect ratios of the flux tubes.
-The tube prescribed in chapter~\cite{quinnEffectAnisotropicViscosity2020a} has an aspect ratio of approximately $20$ compared to the tube studied here which has an aspect ratio of approximately $4$.
-While the total twist is similar in both tubes (after the drivers have injected twist up to $t\approx20$) the small aspect ratio results in more turns per unit length, resulting in a faster growing instability.
+Despite the \rs{fluting}{flute} instability appearing in the isotropic
+case (figure~\ref{fig:field_line_plots_iso}), only in the
+\rs{switching}{anisotropic} case can the onset of both the
+\rs{fluting}{flute} and kink instabilities be seen in the kinetic
+energy profile \rs{}{shown in} figure~\ref{fig:kink_ke_log-4}. \rs{where}{Here,} the nonlinear
+growth rates of the two instabilities are found to be $\gamma = 0.69$
+for the \rs{fluting}{flute} and $\sigma = 2.55$ for the kink. The
+onset times are approximately $t=27$ for the \rs{fluting}{flute}
+instability and \rs{$t=28$}{$t=28$ RADO: MORE LIKE $t=29.5$???} for
+the kink. In the isotropic case, the growth rate of the kink, $\sigma
+= 2.97$, is larger than in the \rs{switching}{anisotropic} case,
+although the onset times appear similar, and the kinetic energy
+profile shows no evidence of \rs{the growth of the \rs{fluting}{flute}
+instability.}{\rs{fluting}{flute} instability growth.} 
+\rs{}{}
+The faster growth of the kink compared \rs{to, say, that of
+  chapter~}{to that measured in}
+\cite{quinnEffectAnisotropicViscosity2020a} is \rs{due}{attributed} to
+the relative aspect ratios of the flux tubes. The tube prescribed in
+\rs{chapter~}{} \cite{quinnEffectAnisotropicViscosity2020a} has an aspect
+ratio of approximately $20$ compared to the tube studied here which
+has an aspect ratio of approximately $4$. While the total twist is
+similar in both tubes (after the drivers have injected twist up to
+$t\approx20$) the small aspect ratio results in more turns per unit
+length, \rs{resulting in}{leading to} a faster growing instability.
 
@@
     \end{subfigure}
-\mycaption{Stability and linear growth rate of the fluting instability.}{In~\ref{fig:suydam_condition_4}, Suydam's stability criterion and contributing terms (LHS of~\eqref{eq:suydams_criterion})  are plotted and in~\ref{fig:growth_rate_4} the predicted linear growth rate~\eqref{eq:fluting_growth_rate2} is plotted.
-Both plots are produced at $t=20$ for $\eta=10^{-4}$ and using the switching model.
+\mycaption{Stability and linear growth rate of the \rs{fluting}{flute}
+  instability.}{In \rs{}{panel} \ref{fig:suydam_condition_4}, Suydam's stability
+  criterion \rs{}{\eqref{eq:suydams_criterion}} and is contributing
+  terms \rs{(LHS of~\eqref{eq:suydams_criterion})}{}  are plotted and in
+  \rs{}{panel} \ref{fig:growth_rate_4} the predicted linear growth rate~\eqref{eq:fluting_growth_rate2} is plotted.
+Both plots are produced at $t=20$ for $\eta=10^{-4}$ and using the \rs{switching}{anisotropic} model.
 The location of the peak linear growth rate is also shown.}
@@
 
-Prior to the onset of either instability, the flux tube is found to be linearly unstable to perturbations of the form~\eqref{eq:kink_perturbation} at $t=20$ via Suydam's criterion~\eqref{eq:suydams_criterion} (figure~\ref{fig:suydam_condition_4}).
-The criterion represents a balance between destabilising pressure gradients and stabilising magnetic shear and in this case, the shear is so small and the pressure gradient so large that the tube is unstable over a wide range of radii, for $ 0.02 \lessapprox r \lessapprox 0.29$.
-The measure of linear fluting growth rate $\gamma$ is plotted as a function of $r$ at the same time (figure~\ref{fig:growth_rate_4}).
-While the magnitude of the peak linear growth rate predicts the observed rate reasonably well, the location of the peak growth matches nearly exactly the location of the resonant surface where the observed perturbation grows (figure~\ref{fig:swi-4_pressure_13}).
+Prior to the onset of either instability, the flux tube is found to be
+linearly unstable to perturbations of the
+form~\eqref{eq:kink_perturbation} at $t=20$ via Suydam's
+criterion~\eqref{eq:suydams_criterion}
+(figure~\ref{fig:suydam_condition_4}). The criterion represents a
+balance between destabilising pressure gradients and stabilising
+magnetic shear and in this case, the shear is so small and the
+pressure gradient so large that the tube is unstable over a wide range
+of radii, for $ 0.02 \lessapprox r \lessapprox 0.29$. The measure of
+linear fluting growth rate $\gamma$ is plotted as a function of $r$ at
+the same time (figure~\ref{fig:growth_rate_4}). While the magnitude of
+the peak linear growth \rs{}{[RADO: WHY DON'T WE COMPARE THE AVERAGE THEORETICAL GROWTH RATE 
+    (INSTEAD OF THE PEAK) TO THE EXPERIMENTALLY MEASURED ONE
+    INSTEAD. iF YOU AVERAGE YOU WILL GET A NUMBER QUITE CLOSE TO THE
+   0.69 FROM FIG 4B.} rate predicts the observed rate reasonably well, the location of the peak growth matches nearly exactly the location of the resonant surface where the observed perturbation grows (figure~\ref{fig:swi-4_pressure_13}).
 
@@
     \end{subfigure}
-\mycaption{Perturbations corresponding to the fluting and kink instabilities and the spatial radial distribution of the associated resonance function.}{Pressure and velocity perturbations in $z$ (corresponding to the fluting and kink instabilities, respectively) and of the resonance function $m B_{\theta}(r)/r + kB_z(r)$ as a function of $r$ using the observed fluting perturbation wavenumbers.
-All plots are from snapshots at $t=26$ where $\eta=10^{-4}$ and the viscosity model is switching.}
+\mycaption{Perturbations corresponding to the \rs{fluting}{flute} and
+  kink instabilities and the spatial radial distribution of the
+  associated resonance function.}{Pressure and velocity perturbations
+  in $z$ (corresponding to the \rs{fluting}{flute} and kink
+  instabilities, respectively) and of the resonance
+  \rs{function}{surface} $m B_{\theta}(r)/r + kB_z(r)$ as a function
+  of $r$ using the observed fluting perturbation wavenumbers. All
+  plots are \rs{from}{} snapshots at $t=26$ where $\eta=10^{-4}$ and
+  the viscosity model is \rs{switching}{anisotropic}.} 
 \label{fig:k_and_resonance}%
@@
 
-Figure~\ref{fig:pressure_pert_4} plots the observed perturbations corresponding to the fluting and kink instabilities at $t=26$.
-The fluting perturbation is observed in the pressure and is plotted as a function of $z$ following a line through the point $(r, \theta) = (0.101, 0)$.
-The kink instability is observed in the $x$-velocity (a proxy for the radial velocity) through the axis.
-Comparing the magnitudes of the perturbations at this time suggests the fluting instability is close to transitioning to its nonlinear phase while the kink instability is still very much in its linear phase.
+\rs{Figure~\ref{fig:pressure_pert_4} plots the }{The} observed
+  perturbations corresponding to the \rs{fluting}{flute} and kink
+  instabilities at $t=26$ \rs{}{are shown in
+  Figure~\ref{fig:pressure_pert_4}}. The fluting perturbation is
+  observed in the pressure and is plotted as a function of $z$
+  following a line through the point $(r, \theta) = (0.101, 0)$. The
+  kink instability is observed in the $x$-velocity (a proxy for the
+  radial velocity) through the axis. Comparing the magnitudes of the
+  perturbations at this time suggests the \rs{fluting}{flute}
+  instability is close to transitioning to its nonlinear phase while
+  the kink instability is still very much in its linear
+  phase. \rs{}{[RADO: I CAN'T QUITE FOLLOW THIS ARGUMENT - WHY IS
+      FLUTE SEEN IN PRESSURE ONLY AND KINK IN   VELOCITY ONLY?]}
 
 The value of $k$ for each perturbation is calculated as $k = 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the perturbation, measured as the difference between the two peaks closest to $z=0$ (thus minimising the influence of line-tying on the measurement).
-This gives a value of $k_{flute}=23.61$ and $k_{kink}=4.57$ for both viscosity models.
+This gives a value of $k_{\rs{flute}{\text{flute}}}=23.61$ and $k_{\rs{kink}{\text{kink}}}=4.57$ for both viscosity models.
 Hence, the observed most unstable fluting perturbation is that of the form~\eqref{eq:kink_perturbation} where $m=4$ and $k=23.61$ and the observed kink instability is that where $m=1$ and $k=4.57$.
@@
 
-Comparing the effect of the viscous models on the perturbations, in the isotropic case, the fluting perturbation is damped, while in the switching case the kink perturbation is diminished, explaining why the fluting instability appears more readily in the switching case (figure~\ref{fig:kink_ke-4}).
+Comparing the effect of the viscous models on the perturbations, in the isotropic case, the fluting perturbation is damped, while in the \rs{switching}{anisotropic} case the kink perturbation is diminished, explaining why the \rs{fluting}{flute} instability appears more readily in the \rs{switching}{anisotropic} case (figure~\ref{fig:kink_ke-4}).
 
-\subsection{Development where $\eta=10^{-3}$}
+\subsection{\rs{Development where}{Instabilities at resistivity} $\eta=10^{-3}$}
 
@@
     \end{subfigure}
-\mycaption{Pressure profiles through $z=0$ during the development of the fluting and kink instabilities in the higher resistivity switching case.}{The viscosity model is switching and $\eta = 10^{-3}$.
-In contrast to the case of $\eta=10^{-4}$, the nonlinear development of the fluting instability has time to mix the interior of the flux tube before the onset of the kink instability, the growth of which is affected by the mixed plasma.}
+\mycaption{Pressure profiles \rs{through}{at} $z=0$ during the development of the \rs{fluting}{flute} and kink instabilities in the higher resistivity \rs{switching}{anisotropic} case.}{The viscosity model is \rs{switching}{anisotropic} and $\eta = 10^{-3}$.
+In contrast to the case of $\eta=10^{-4}$, the nonlinear development of the \rs{fluting}{flute} instability has time to mix the interior of the flux tube before the onset of the kink instability, the growth of which is affected by the mixed plasma.}
 \label{fig:kink_pressure_slices-3}%
@@
 
-Figures~\ref{fig:kink_pressure_slices-3} show the prolonged development of the fluting instability and the slow nonlinear development of the kink.
-Due to the enhanced Ohmic heating when $\eta=10^{-3}$, the pressure gradient is substantially stronger than when $\eta=10^{-4}$ and the fluting instability is excited much earlier.
-Compared to the $\eta=10^{-4}$ cases, the instability occurs further from the axis, at $r\approx0.16$, and the larger pressure gradient drives the bulges further from the axis in the nonlinear phase (figure~\ref{fig:swi-3_pressure_12}).
-These bulges continue to extend outwards and mix the plasma as they develop.
-The kink instability can be observed moving the axis of the tube diagonally upwards and to the right in figure~\ref{fig:swi-3_pressure_15}.
-At this time in the $\eta=10^{-4}$ cases, the nonlinear development of the kink was further along (figure~\ref{fig:swi-4_pressure_15}).
-The development of the kink then proceeds slowly as it moves the axis of the tube through the mixed region to eventually begin the reconnection process with the outer region of field that is typical of the instability in this kind of flux tube (as was observed in chapter~\cite{quinnEffectAnisotropicViscosity2020a}).
+\rs{Figures \ref{fig:kink_pressure_slices-3} show the}{Figure
+  \ref{fig:kink_pressure_slices-3} shows a} prolonged 
+development of the \rs{fluting}{flute} instability and \rs{the}{a} slow
+nonlinear development of the kink \rs{}{instability at the higher
+  resistivity value $\eta=10^{-3}$ in the case of anisotropic viscosity}. Due to the enhanced Ohmic heating 
+\rs{when}{at} $\eta=10^{-3}$, the pressure gradient is substantially stronger
+than \rs{when}{at} $\eta=10^{-4}$ and the \rs{fluting}{flute} instability is
+excited much earlier. Compared to the $\eta=10^{-4}$ cases, the
+instability occurs further from the axis, at $r\approx0.16$, and the
+larger pressure gradient drives the bulges \rs{}{in profile} further
+from the axis \rs{in}{during} the nonlinear phase
+(figure~\ref{fig:swi-3_pressure_12}). These bulges continue to extend
+outwards and mix the plasma as they develop. The kink instability can
+be observed moving the axis of the tube diagonally upwards and to the
+right in figure~\ref{fig:swi-3_pressure_15}. At this time in the
+$\eta=10^{-4}$ cases, the nonlinear development of the kink was
+\rs{further along}{at a later stage of its development} (figure~\ref{fig:swi-4_pressure_15}). The development of
+the kink then proceeds slowly as it moves the axis of the tube through
+the mixed region to eventually begin the reconnection process with the
+outer region of field that is typical of the instability in this kind
+of flux tube (as was observed in
+\rs{chapter}{our earlier work}~\cite{quinnEffectAnisotropicViscosity2020a}).
 
@@
 \mycaption{Kinetic energy as a function of time in the cases where $\eta=10^{-3}$.}{The results from both viscosity models are shown.
-The fluting instability appears earlier than where $\eta=10^{-4}$ and the growth rate of the kink instability is decreased.}
+The \rs{fluting}{flute} instability appears earlier than where $\eta=10^{-4}$ and the growth rate of the kink instability is decreased.}
 \label{fig:kink_str8_ke-3}%
@@
 
-It is evident from the kinetic energy profile that the fluting instability develops much earlier than in the $\eta=10^{-4}$ cases and grows at an increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}).
-The kink instability grows at a rate of $\sigma \approx 0.15$, much slower than that observed in the $\eta=10^{-4}$ cases, and much lower than the fluting instability.
-One key observation is that, despite the early and disruptive growth of the fluting instability, the kink instability still generates the bulk of the kinetic energy (figure~\ref{fig:kink_ke-3}).
+It is evident from the kinetic energy profile that the \rs{fluting}{flute} instability develops much earlier than in the $\eta=10^{-4}$ cases and grows at an increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}).
+The kink instability grows at a rate of $\sigma \approx 0.15$, much slower than that observed in the $\eta=10^{-4}$ cases, and much lower than the \rs{fluting}{flute} instability.
+One key observation is that, despite the early and disruptive growth of the \rs{fluting}{flute} instability, the kink instability still generates the bulk of the kinetic energy (figure~\ref{fig:kink_ke-3}).
 
@@
 Since the kink instability occurs after the development of the fluting, its growth rate is similarly difficult to gauge.
-Nevertheless, it is clear that the fluting instability grows at a rate of the same order as that in the $\eta=10^{-4}$ cases.
+Nevertheless, it is clear that the \rs{fluting}{flute} instability grows at a rate of the same order as that in the $\eta=10^{-4}$ cases.
 It is also apparent that the kink instability grows much slower in the $\eta=10^{-3}$ cases.
@@
 \midrule
-Predicted linear $\gamma$ & 1.43 & 2.72  \\
-Observed nonlinear $\gamma$ & 0.69 & 1.06  \\
-Observed $\sigma$ & 2.55 & 0.15\\
+\rs{Predicted linear}{Theoretical linear growth rate of flute} $\gamma$ & 1.43 & 2.72  \\
+Observed nonlinear \rs{}{growth rate of flute} $\gamma$ & 0.69 & 1.06  \\
+Observed \rs{}{growth rate of kink} $\sigma$ & 2.55 & 0.15\\
 \midrule
-Radius of peak $\gamma$ & 0.125 & 0.163 \\
-Observed $r_s$ & 0.125 & 0.163 \\
+\rs{}{Theoretical} radius $r_s$ of peak \rs{$\gamma$}{flute growth rate} & 0.125 & 0.163 \\
+Observed \rs{}{radius} $r_s$ \rs{}{of peak flute growth rate} & 0.125 & 0.163 \\
 \midrule
-Observed $k_{flute}$ & 23.61 & 16.05 \\
-Observed $k_{kink}$ & 4.57 & 4.53 \\
+Observed \rs{}{axial wave number} $k_{\rs{flute}{\text{flute}}}$ & 23.61 & 16.05 \\
+Observed \rs{}{axial wave number} $k_{\rs{kink}{\text{kink}}}$ & 4.57 & 4.53 \\
 \end{tabular}
-\caption{Quantitative differences in the observed perturbations between results for both values of $\eta$. See text for details of measurements times.}
+\caption{Quantitative differences in the observed perturbations
+  between results \rs{for both values of}{between different
+    resistivity values} $\eta$. \rs{}{In all measurements the
+  anisotropic viscosity model is used except for $k_\text{kink}$ where the
+  isotropic viscosity model us used. Measurements times are listed in
+  the main text.}}
 \label{tab:kink_fluting_params}
@@
 
-Table~\ref{tab:kink_fluting_params} summarises the quantitative differences between the results for the two values of $\eta$.
-All values are calculated from simulations using the switching model with the exception of $k_{kink}$ which is measured from isotropic results due to noise in the switching case (the value of $k_{kink}$ appears similar, however).
+Table~\ref{tab:kink_fluting_params} summarises the quantitative
+differences between the results for the two values of \rs{}{the
+  resistivity} $\eta$.
+All values are calculated from simulations using the \rs{switching}{anisotropic} model with the exception of $k_{\rs{kink}{\text{kink}}}$ which is measured from isotropic results due to noise in the \rs{switching}{anisotropic} case (the value of $k_{\rs{kink}{\text{kink}}}$ appears similar, however).
 The results of the isotropic cases are qualitatively similar.
 The radius of peak $\gamma$ is calculated at time $t=20$.
-The fluting wavenumber $k$ and observed $r_s$ are measured at times just prior to the nonlinear development of the fluting instability, that is at $t=22$ when $\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$.
+The fluting wavenumber $k$ and observed $r_s$ are measured at times just prior to the nonlinear development of the \rs{fluting}{flute} instability, that is at $t=22$ when $\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$.
 The kink wavenumber is measured at $t=26$ in both cases.
@@
 
-The longitudinal wavenumber $k_{kink}$ of the observed kink perturbation remains similar in both cases since the instability is essentially governed by the twist injected by the driver which remains the same in both cases.
-In contrast, the longitudinal wavenumber $k_{flute}$ of the observed fluting perturbation is lower in the $\eta=10^{-3}$ cases.
+The longitudinal wavenumber $k_{\rs{kink}{\text{kink}}}$ of the observed kink perturbation remains similar in both cases since the instability is essentially governed by the twist injected by the driver which remains the same in both cases.
+In contrast, the longitudinal wavenumber $k_{\rs{flute}{\text{flute}}}$ of the observed fluting perturbation is lower in the $\eta=10^{-3}$ cases.
 This is due to the different resonant surface within which the perturbation grows, the location being dictated by the peak of the linear growth rate.
@@
 
-Due to the perturbations arising from numerical noise, it is likely that the $m=4$ perturbation is excited due to influences from the boundaries in the Cartesian box, for example through the interaction of reflected fast waves generated in part by the driver.
-Performing a similar experiment in a cylindrical numerical domain, or prescribing a variety of perturbations in the Cartesian domain may reveal other, faster growing modes.
-The modes may also be influenced by nonlinear coupling between the $m>1$ and $m=1$ modes, as is found in the study of kink and fluting oscillations~\cite{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017a}.
+\rs{Due to the perturbations arising from numerical noise, it}{It} is
+likely that the $m=4$ \rs{}{azimuthal} perturbation is excited due to
+influences from the boundaries in the Cartesian box, for example
+through the interaction of reflected fast waves generated in part by
+the driver. Performing a similar experiment in a cylindrical numerical
+domain, or prescribing a variety of perturbations in the Cartesian
+domain may reveal other, faster growing modes. The modes may also be
+influenced by nonlinear coupling between the $m>1$ and $m=1$ modes, as
+is found in the study of kink and \rs{fluting}{flute}
+oscillations~\cite{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017a}.
 
-This set of experiments has shown that the mixing as a result of the nonlinear fluting instability appears to slow the growth of the kink instability.
-In the linear regime it seems unlikely that the linear perturbations of either the fluting or kink are able to directly couple, given that the kink instability generally presents at the axis of a flux tube and the fluting at some resonant surface away from the axis.
-Further investigation of the nonlinear interaction between the two instabilities is required.
+\rs{This set of experiments}{Our set of numerical experiments} has
+shown that the mixing as a result of the nonlinear \rs{fluting}{flute}
+instability appears to slow the growth of the kink instability. \rs{In
+  the linear regime it seems unlikely that}{It seems unlikely that in
+  the linear regime} the \rs{linear}{} perturbations of \rs{either}{} the
+\rs{fluting}{flute} \rs{or}{and} kink are able to directly couple, given that
+the kink instability generally presents at the axis of a flux tube and
+the \rs{fluting}{flute} at some resonant surface away from the
+axis. Further investigation of the nonlinear interaction between the
+two instabilities is required.
 
-Since the main driver of the fluting instability is the pressure gradient generated through Ohmic heating, it is prudent to ask if the same pressure gradient could be generated using physical coronal values of the resistivity (of approximately $\eta=10^{-8}$~\cite{craigAnisotropicViscousDissipation2009a}) which are much smaller than those studied here.
-Additionally, the simulations presented here do not incorporate radiation or thermal conductivity, two processes which would remove energy (and thus pressure) from high-pressure regions in a coronal loop and thus could remove the required conditions for the growth of a fluting instability.
-Where $\eta=10^{-4}$, the fluting instability was quickly dominated by the kink instability and appeared to have little impact on the resultant dynamics, which mirror those of other kink instability studies (such as~\cite{hoodCoronalHeatingMagnetic2009}).
-This suggests that even lower values of resistivity would result in flux tubes without any significant fluting instability, at least for this form of driver and mechanism of pressure generation.
-Regardless, coronal loops with strong radial pressure gradients have been observed~\cite{foukalTemperatureStructurePressure1975} and such loops may be unstable to the fluting instability.
-Modelling of a prescribed fluting-unstable flux tube (as opposed to the dynamically stressed loop investigated here) would provide a useful comparison to observations, however it may be difficult to prescribe a tube which is not also susceptible to kinking.
-Linear stability analyses of this kind of flux tube (a dynamically created zero total axial current tube) focus on the kink instability~\cite{browningSolarCoronalHeating2003c} so do not provide much insight into the potential for fluting without a kink.
+Since the main driver of the \rs{fluting}{flute} instability is the
+pressure gradient generated through Ohmic heating, it is prudent to
+ask if the same pressure gradient could be generated using physical
+coronal values of the resistivity, \rs{of}{which are estimated to be}
+approximately
+$\eta=10^{-8}$~\cite{craigAnisotropicViscousDissipation2009a},
+\rs{which are}{and are thus} much smaller than those studied
+here. Additionally, the simulations presented here do not incorporate
+radiation or thermal \rs{conductivity}{conduction}, two processes which would remove
+energy (and \rs{thus}{hence} reduce pressure) from high-pressure regions in a coronal
+loop and thus could \rs{remove}{prevent meeting} the required
+conditions for the growth of a 
+\rs{fluting}{flute} instability. \rs{Where}{Indeed, at} $\eta=10^{-4}$ the
+\rs{fluting}{flute} instability was \rs{}{more} quickly \rs{dominated}{outcompeted} by the kink
+instability and appeared to have little impact on the resultant
+dynamics, which mirror those of other kink instability studies, \rs{such
+as~}{e.g.~}\cite{hoodCoronalHeatingMagnetic2009}. This suggests that even
+lower values of resistivity would result in flux tubes without any
+significant \rs{fluting}{flute} instability, at least for this form of
+driver and mechanism of pressure generation. Regardless, coronal loops
+with strong radial pressure gradients have been
+observed~\cite{foukalTemperatureStructurePressure1975}, and such loops
+may be unstable to the \rs{fluting}{flute} instability. Modelling of a
+prescribed \rs{fluting}{flute}-unstable flux tube, as opposed to the dynamically
+stressed loop investigated here, would provide a useful comparison to
+observations, however it may be difficult to prescribe a tube which is
+not also susceptible to kinking. Linear stability analyses of this
+kind of flux tube (a dynamically created zero total axial current
+tube) focus on the kink
+instability~\cite{browningSolarCoronalHeating2003c} so do not provide
+much insight into the potential for fluting without a kink.
 
-These results show that a flux tube can be unstable to the fluting instability and yet the faster growing kink instability can quickly dominate when the pressure gradient is small enough.
-However, the opposite case is also observed, where a faster growing fluting instability appears to slow the growth of the kink instability although, importantly, it does not fully disrupt the development of the kink.
-Understanding the balance between the nonlinear growth rates of the two instabilities is important in understanding whether the fluting instability may be found at all in the real solar corona, or whether a realistic growth rate is too slow compared to that of the kink instability.
+\rs{These}{While our} results show that a flux tube can be unstable to
+the \rs{fluting}{flute} instability and yet the faster growing kink
+instability can quickly dominate when the pressure gradient is small
+enough\rs{. However}{}, the opposite case is also observed\rs{,
+  where}{. A faster} growing \rs{fluting}{flute} instability appears to slow the growth of
+the kink instability although, importantly, it does not fully disrupt
+the development of the kink. Understanding the balance between the
+nonlinear growth rates of the two instabilities is important \rs{in
+understanding}{for prediction of} whether the \rs{fluting}{flute} instability may be found
+at all in the real solar corona, or whether \rs{a}{its} realistic growth rate is
+too slow compared to that of the kink instability.
 
@@
 
-This chapter details the nonlinear development of two ideal instabilities, the kink and fluting instabilities, both of which develop naturally in the course of twisting an initially straight magnetic flux tube.
-This provides a different approach to that employed in the simulations performed in chapter~\cite{quinnEffectAnisotropicViscosity2020a} in that the instabilities are not excited by any prescribed perturbations but, instead, the field is dynamically driven into an unstable state and the perturbations provided by noise in the system.
-Not only is the kink instability excited due to the twist in the field, a pressure-driven fluting instability can also be excited in unstable pressure gradients generated by Ohmic heating.
-Simulations were run over two values of resistivity, $\eta=10^{-3}$ and $10^{-4}$, and for two forms of viscosity, isotropic and switching, providing an initial and important first step into the simulation of nonlinear fluting instabilities in the solar corona.
+This \rs{chapter}{paper} details the nonlinear development of two
+ideal instabilities, the kink and \rs{}{the} \rs{fluting}{flute} instabilities,
+both of which develop naturally in the course of twisting an initially
+straight magnetic flux tube. This provides a different approach to
+that employed in the simulations performed in \rs{chapter}{our earlier
+  study}~\cite{quinnEffectAnisotropicViscosity2020a} in that the
+instabilities are not excited by any prescribed perturbations but,
+instead, the field is dynamically driven into an unstable state and
+the perturbations provided by noise in the system. Not only is the
+kink instability excited due to the twist in the field, \rs{}{but also
+and near simultaneously} a pressure-driven \rs{fluting}{flute}
+instability can also be excited in unstable pressure gradients
+generated by Ohmic heating. Simulations 
+were \rs{run}{performed} \rs{over}{with} two values of resistivity,
+$\eta=10^{-3}$ and $10^{-4}$, and for two forms of viscosity, isotropic and
+\rs{switching}{anisotropic}\rs{, providing}{. The results prove}an
+initial and important first step \rs{into the simulation of}{towards
+understanding} nonlinear \rs{fluting}{flute} instabilities in the
+solar corona.
 
-It has been shown that the fluting instability can be quickly dominated by the kink instability if the kink grows substantially faster than the fluting.
-However, if the fluting has time to develop nonlinearly, it mixes the plasma within the flux tube, generating small scale current sheets and releasing some magnetic energy.
+It has been shown that the \rs{fluting}{flute} instability can be quickly dominated by the kink instability if the kink grows substantially faster than the \rs{fluting}{flute}.
+However, if the \rs{fluting}{flute} has time to develop nonlinearly, it mixes the plasma within the flux tube, generating small scale current sheets and releasing some magnetic energy.
 The overall effect of this mixing is to slow the growth of the kink instability.
@@
 
-The form of viscosity has been found to significantly affect the growth of the fluting instability.
-Importantly, isotropic viscosity is found to damp the growth of the fluting instability to the degree that it is unable to grow appreciably before the onset of the faster growing nonlinear kink instability.
-Overall, the switching model permits greater release of kinetic energy.
-Similar to chapter~\cite{quinnEffectAnisotropicViscosity2020a}, isotropic viscous heating is found to be significantly lower than anisotropic (switching) viscous heating, by approximately two orders of magnitude.
+The form of viscosity has been found to significantly affect the
+growth of the \rs{fluting}{flute} instability. Importantly, isotropic
+viscosity is found to damp the growth of the \rs{fluting}{flute}
+instability to the degree that it is unable to grow appreciably before
+the onset of the faster growing nonlinear kink instability. Overall,
+the \rs{switching}{anisotropic} model permits greater release of
+kinetic energy. Similar to \rs{chapter}{}
+\cite{quinnEffectAnisotropicViscosity2020a}, isotropic viscous heating
+is found to be \rs{significantly lower}{lower} than anisotropic (switching)
+viscous heating, by approximately two orders of magnitude.
 
-These numerical experiments have provided evidence that the fluting instability can occur in twisted magnetic flux ropes and grow at similar rates to the kink instability.
-Further estimation of the relative growth rates in more realistic coronal loop setups is required to fully understand if the fluting instability plays a pertinent role in coronal loop physics.
+These numerical experiments have provided evidence that the \rs{fluting}{flute} instability can occur in twisted magnetic flux ropes and grow at similar rates to the kink instability.
+Further estimation of the relative growth rates in more realistic coronal loop setups is required to fully understand if the \rs{fluting}{flute} instability plays a pertinent role in coronal loop physics.
 

### 2021-09-24 paper.tex
Address Rado's comments

@@
 \newcommand{\rs}[2]{\textcolor{red}{#2}}
+\newcommand{\jq}[2]{\textcolor{blue}{#2}}
 %\newcommand{\rr}[1]{#1}
@@
 \begin{abstract}
-  \rs{}{NEEDS ABSTRACT}
+  % Context
+  The magnetic flux tubes which make up the solar corona can become unstable to a number of instabilities, including the kink instability, which forms a core part of the nanoflare theory of coronal heating.
+However, the development of the kink instability can be affected by other phenomena such as the flute instability.
+  % Aims
+  This paper aims to investigate the effect of the flute instability on the growth of the kink instability in coronal loops, particularly focussing on the effect of anisotropic plasma viscosity.
+  % Methods
+  Using the magnetohydrodynamic code, Lare3d, an initially straight flux tube is twisted via boundary motions until it reveals the kink instability and, in some cases, the flute instability.
+This is performed for multiple values of the resistivity and for anisotropic and isotropic models of viscosity.
+  % Results
+  The flute instability is found to more readily occur when viscosity is anisotropic and, where present, it damps the growth of the kink instability.
+  % Conclusions
+  \todo{conclusions please}
 \end{abstract}
@@
 studied in the coronal
-context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003c,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020a}. Given
+context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003b,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020}. Given
 its energetic nonlinear development, it is considered a potential
 mechanism for heating the solar corona through the theory of
-nanoflares~\cite{klimchukSolvingCoronalHeating2006a,browningMechanismsSolarCoronal1991}
+nanoflares~\cite{klimchukSolvingCoronalHeating2006,browningMechanismsSolarCoronal1991}
 and a key mechanism in the production of solar
@@
 the effect of anisotropic viscosity on the nonlinear
-dynamics~\cite{quinnEffectAnisotropicViscosity2020a}. In~\cite{quinnEffectAnisotropicViscosity2020a}
+dynamics~\cite{quinnEffectAnisotropicViscosity2020}. In~\cite{quinnEffectAnisotropicViscosity2020}
 and most other investigations of the kink instability
@@
 the \rs{fluting}{flute} instability, which has been theorised (for example,
-in~\cite{priestMagnetohydrodynamicsSuna}) but not yet observed in
-coronal simulations or observations, to our knowledge. \rs{}{RADO: NOT
-  YET OBSERVED? 
-  WHAT ABOUT \cite{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017a}??!!]}
+in~\cite{priestMagnetohydrodynamicsSuna}).
+\jq{}{While oscillations involving flute perturbations have been found in simulations of coronal loops~\cite{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute \em{instability} has been investigated computationally in a coronal context.}
 
@@
 ideal interchange instability but confined to a cylindrical geometry,
-the name \rs{``fluting instability''}{``flute instability''} referring to its likeness to a fluted
+the term \rs{``fluting instability''}{``flute instability''} referring to its likeness to a fluted
 column. In a twisted flux tube like a simple, unbraided coronal loop,
@@
 of the \rs{fluting}{flute} instability, the nonlinear development being of
-secondary importance to the functioning of fusion devices. More
+secondary importance in the investigation of fusion devices. More
 detailed investigations of its nonlinear development is required to
@@
 initial exploration into the nonlinear \rs{fluting}{flute} instability in the
-solar corona. \rs{Of particular interest is the effect of anisotropic
-viscosity, which is found to strongly affect the growth of the \rs{fluting}{flute}
-instability.}{}
+solar corona.
 
@@
 the local magnetic
-field~\cite{hollwegViscosityChewGoldbergerLowEquations1986a,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
-\rs{The development of the switching
-model~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}
-and implementation in Lare3d has allowed the investigation of
-the effect of anisotropic viscosity on solar phenomena.
-We find the stability of Lare3d without (the more commonly employed)
-isotropic or shock viscosity to be sufficient for at least the study
-of kink instabilities in coronal loops~\cite{quinnEffectAnisotropicViscosity2020a}.
-}{To take this into account, in \cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017},
+field~\cite{hollwegViscosityChewGoldbergerLowEquations1986,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
+\rs{}{To take this into account, in \cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017},
 we developed a phenomenological model of anisotropic viscosity that
@@
 refer to this model of viscosity as ``the switching model''. In
-\cite{quinnEffectAnisotropicViscosity2020a,Quinn2021} we implemented
+\cite{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} we implemented
 the switching model as a module for the widely-used general MHD code
@@
 which heating mechanism (viscous or Ohmic) is dominant in the solar
-corona~\cite{klimchukSolvingCoronalHeating2006a}, an important facet
+corona~\cite{klimchukSolvingCoronalHeating2006}, an important facet
 of solving the coronal heating problem. Using scaling laws, it has
@@
 scale instabilities and turbulence is relatively
-unknown~\cite{klimchukSolvingCoronalHeating2006a}. In addition to
+unknown~\cite{klimchukSolvingCoronalHeating2006}. In addition to
 directly heating the plasma, viscosity plays a part in the damping of
-instabilities and waves~\cite{rudermanSlowSurfaceWave2000a}. It is
+instabilities and waves~\cite{rudermanSlowSurfaceWave2000}. It is
 this effect we are most interested in here, and it shall be \rs{found}{reported} that
@@
 
-\rs{}{ADD A BRIEF NEW ``CONTENTS PARAGRAPH'':
-This paper is organized as follows. Section 1 ..., Section 2...}
+This paper is organised as follows.
+Section~\ref{sec-flute-intro} introduces the flute instability and relevant linear analyses, section~\ref{sec-numerical-setup} describes the governing equations, coronal loop model and details of the numerical parameters, section~\ref{sec-results} presents the overall development of the flute instability, before discussing features unique to the two values of resistivity studied, section~\ref{sec-discussion} discusses the limitations of the simulations, with suggestions for future work, and section~\ref{sec-conclusions} presents our conclusions in the wider context of coronal heating.
 
 \subsection{The \rs{fluting}{flute} instability}
+\label{sec-flute-intro}
 
@@
 the form~\eqref{eq:kink_perturbation} is given by the classical
-\rs{}{Suydam's criterion \cite{Suydam1959}}
+\rs{}{Suydam's criterion \cite{suydamStabilityLinearPinch1958}}
 \begin{equation}
@@
 \rs{In contrast to the precise form of the equilibrium state and
-  perturbation studied in~\cite{quinnEffectAnisotropicViscosity2020a},
+  perturbation studied in~\cite{quinnEffectAnisotropicViscosity2020},
   this is an experiment where a system is driven and instabilities
@@
   \eqref{eq:suydams_criterion} and \eqref{eq:fluting_growth_rate2}
-  were used in~\cite{quinnEffectAnisotropicViscosity2020a}.
+  were used in~\cite{quinnEffectAnisotropicViscosity2020}.
   In contrast, in the experiments reported in the following the system
@@
 \section{\rs{Numerical setup}{Mathematical formulation and numerical setup}}
+\label{sec-numerical-setup}
 
@@
 that used in
-\rs{our previous work~\cite{quinnEffectAnisotropicViscosity2020a}}{previous work~\cite{quinnEffectAnisotropicViscosity2020a,Quinn2021}},
+\rs{our previous work~\cite{quinnEffectAnisotropicViscosity2020}}{previous work~\cite{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}},
  the switching model, first presented
@@
 This tensor is identical to the strong field approximation of Braginskii~\cite{braginskiiTransportProcessesPlasma1965}.
-Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020a}\todo{ref KHI paper}.
+Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020}\todo{ref KHI paper}.
 }{}
@@
 more general switching model used in our earlier works 
-\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020a,Quinn2021}
+\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
 which, includes both isotropic and anisotropic contributions and can
@@
 identical to those used
-in~\cite{quinnEffectAnisotropicViscosity2020a}.}
+in~\cite{quinnEffectAnisotropicViscosity2020}.}
    {
@@
 our earlier works
-\cite{quinnEffectAnisotropicViscosity2020a,Quinn2021} and in reference
+\cite{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} and in reference
 \cite{arberStaggeredGridLagrangian2001} that describes the code Lare3d
@@
 \end{equation}
-in a cube of \rs{dimension}{size} $[-2,2]^3$. \rs{The}{Initially, the} velocity is set
+in a cube of \rs{dimension}{size} $[-2,2]^3$, with further test simulations run using an elongated domain of size $4\times4\times20$. \rs{The}{Initially, the} velocity is set
 everywhere to $\vec{u} = \vec{0}$, the density to $\rho = 1$,
@@
 internal energy to $\varepsilon = 8.67\times 10^{-4}$ (corresponding
-to a temperature of $10^6$ K). \todo{what's the plasma beta?} At the
+to a temperature of $10^6$ K, a typical coronal value). \todo{what's the plasma beta?} At the
 boundaries, the magnetic field, \rs{}{velocity,} density, and energy are fixed to their
@@
 Both drivers result in twist being added at a rate of $2\pi$ every $7.96$ Alfv\'en times.
-The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\cite{quinnEffectAnisotropicViscosity2020a,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
+The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\cite{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
 This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the \rs{fluting}{flute} instability and the helical kink instability.
@@
   a  new module for anisotropic viscosity has been
-  included as detailed in \cite{Quinn2021}.} The resolution used in the
+  included as detailed in \cite{quinnKelvinHelmholtzInstabilityCollapse2021}.} The resolution used in the
 current work is  $512$ grid points per dimension, comparable to the
@@
 \section{Results}
+\label{sec-results}
 
@@
 $\eta=10^{-3}$ and another where $\eta=10^{-4}$. As
-in~\cite{quinnEffectAnisotropicViscosity2020a}, only background
+in~\cite{quinnEffectAnisotropicViscosity2020}, only background
 resistivity is used. Each pair consists of one simulation
@@
 instabilities is broadly similar for the two values of resistivity and
-is described  initially. Focus is 
+is described  initially.
+Similar simulations were performed with a longer flux tube of length $20$ instead of the tubes shown here with length $4$, and the results were found to be qualitatively similar.
+Focus is
 then placed on the \rs{development of}{detailed description of instabilities in} the
@@
 oppositely-directed current is similar to the \rs{prescribed field in
-chapter~}{current configuration arising due to the field prescribed in} \cite{quinnEffectAnisotropicViscosity2020a}.
+chapter~}{current configuration arising due to the field prescribed in} \cite{quinnEffectAnisotropicViscosity2020}.
 
@@
 pressure profile is nearly flat and the tube stable to the
-\rs{fluting}{flute} instability. \rs{}{IS IT POSSIBLE TO COMMENT WHY
-  THIS MECHANISM IS NOT PRESENT IN THE CONFIGURATION OF \cite{quinnEffectAnisotropicViscosity2020a}?}
+\rs{fluting}{flute} instability.
 
@@
   \mycaption{Kinetic energy as a function of time showing the
-    development and measured growth rates \rs{}{$\gamma$ and $\sigma$}
+    development and measured growth rates \rs{}{$\gamma$ and $\lambda$}
     of the \rs{fluting}{flute}
@@
       where}{Resistivity is $\eta=10^{-4}$ and the second plot is a
-      enlarged version of the first. [RADO: Please chenage ``swi'' to
-      ``aniso'' in legend.  Perhaps change symbol for growth rate of
-        kink from $\sigma$ (used for visc stress tensor) to smth else
-        say $\lambda$. I'll leave you do that also in the text as figs
-  need changed first.]}}
+      enlarged version of the first.}}
 \label{fig:kink_str8_ke-4}%
@@
 growth rates of the two instabilities are found to be $\gamma = 0.69$
-for the \rs{fluting}{flute} and $\sigma = 2.55$ for the kink. The
+for the \rs{fluting}{flute} and $\lambda = 2.55$ for the kink. The
 onset times are approximately $t=27$ for the \rs{fluting}{flute}
-instability and \rs{$t=28$}{$t=28$ RADO: MORE LIKE $t=29.5$???} for
-the kink. In the isotropic case, the growth rate of the kink, $\sigma
+instability and \rs{}{$t=29.5$} for
+the kink. In the isotropic case, the growth rate of the kink, $\lambda
 = 2.97$, is larger than in the \rs{switching}{anisotropic} case,
@@
   chapter~}{to that measured in}
-\cite{quinnEffectAnisotropicViscosity2020a} is \rs{due}{attributed} to
+\cite{quinnEffectAnisotropicViscosity2020} is \rs{due}{attributed} to
 the relative aspect ratios of the flux tubes. The tube prescribed in
-\rs{chapter~}{} \cite{quinnEffectAnisotropicViscosity2020a} has an aspect
+\rs{chapter~}{} \cite{quinnEffectAnisotropicViscosity2020} has an aspect
 ratio of approximately $20$ compared to the tube studied here which
@@
   Figure~\ref{fig:pressure_pert_4}}. The fluting perturbation is
-  observed in the pressure and is plotted as a function of $z$
+  most easily observed in the pressure and is plotted as a function of $z$
   following a line through the point $(r, \theta) = (0.101, 0)$. The
-  kink instability is observed in the $x$-velocity (a proxy for the
+  kink instability is best revealed in the $x$-velocity (a proxy for the
   radial velocity) through the axis. Comparing the magnitudes of the
@@
   the kink instability is still very much in its linear
-  phase. \rs{}{[RADO: I CAN'T QUITE FOLLOW THIS ARGUMENT - WHY IS
-      FLUTE SEEN IN PRESSURE ONLY AND KINK IN   VELOCITY ONLY?]}
+  phase.
 
@@
 of flux tube (as was observed in
-\rs{chapter}{our earlier work}~\cite{quinnEffectAnisotropicViscosity2020a}).
+\rs{chapter}{our earlier work}~\cite{quinnEffectAnisotropicViscosity2020}).
 
@@
 It is evident from the kinetic energy profile that the \rs{fluting}{flute} instability develops much earlier than in the $\eta=10^{-4}$ cases and grows at an increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}).
-The kink instability grows at a rate of $\sigma \approx 0.15$, much slower than that observed in the $\eta=10^{-4}$ cases, and much lower than the \rs{fluting}{flute} instability.
+The kink instability grows at a rate of $\lambda \approx 0.15$, much slower than that observed in the $\eta=10^{-4}$ cases, and much lower than the \rs{fluting}{flute} instability.
 One key observation is that, despite the early and disruptive growth of the \rs{fluting}{flute} instability, the kink instability still generates the bulk of the kinetic energy (figure~\ref{fig:kink_ke-3}).
@@
 Observed nonlinear \rs{}{growth rate of flute} $\gamma$ & 0.69 & 1.06  \\
-Observed \rs{}{growth rate of kink} $\sigma$ & 2.55 & 0.15\\
+Observed \rs{}{growth rate of kink} $\lambda$ & 2.55 & 0.15\\
 \midrule
@@
 \section{Discussion}
+\label{sec-discussion}
 
@@
 is found in the study of kink and \rs{fluting}{flute}
-oscillations~\cite{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017a}.
+oscillations~\cite{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017}.
+
+It is prudent to ask, if the current distribution, which develops as the flux tube is twisted, is similar to that found in the initial flux tube configuration of~\cite{quinnEffectAnisotropicViscosity2020}, why do we not observe the fluting instability in~\cite{quinnEffectAnisotropicViscosity2020}?
+Although the current distribution (and thus heating and pressure distributions) in the tubes of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute instability, the tube is initially perturbed with a motion close to an unstable eigenmode of the kink instability, resulting in the instability growing from $t=0$.
+In contrast, in the tubes studied here, such a perturbation must build from numerical noise, allowing a secondary, fluting perturbation to also build and become significant enough to observe.
+
+urther detailed comparison of the models is required to fully understand this,  \todo{finish me}
 
@@
 tube) focus on the kink
-instability~\cite{browningSolarCoronalHeating2003c} so do not provide
+instability~\cite{browningSolarCoronalHeating2003b} so do not provide
 much insight into the potential for fluting without a kink.
@@
 \section{Conclusion}
+\label{sec-conclusions}
 
@@
 that employed in the simulations performed in \rs{chapter}{our earlier
-  study}~\cite{quinnEffectAnisotropicViscosity2020a} in that the
+  study}~\cite{quinnEffectAnisotropicViscosity2020} in that the
 instabilities are not excited by any prescribed perturbations but,
@@
 kinetic energy. Similar to \rs{chapter}{}
-\cite{quinnEffectAnisotropicViscosity2020a}, isotropic viscous heating
+\cite{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating
 is found to be \rs{significantly lower}{lower} than anisotropic (switching)

### 2021-10-18 paper.tex
Highlight my own comments

@@
 in~\cite{priestMagnetohydrodynamicsSuna}).
-\jq{}{While oscillations involving flute perturbations have been found in simulations of coronal loops~\cite{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute \em{instability} has been investigated computationally in a coronal context.}
+\jq{}{While oscillations involving flute perturbations have been found in simulations of coronal loops~\cite{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute instability has been investigated computationally in a coronal context.}
 
@@
 
-It is prudent to ask, if the current distribution, which develops as the flux tube is twisted, is similar to that found in the initial flux tube configuration of~\cite{quinnEffectAnisotropicViscosity2020}, why do we not observe the fluting instability in~\cite{quinnEffectAnisotropicViscosity2020}?
+\jq{}{It is prudent to ask, if the current distribution, which develops as the flux tube is twisted, is similar to that found in the initial flux tube configuration of~\cite{quinnEffectAnisotropicViscosity2020}, why do we not observe the fluting instability in~\cite{quinnEffectAnisotropicViscosity2020}?
 Although the current distribution (and thus heating and pressure distributions) in the tubes of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute instability, the tube is initially perturbed with a motion close to an unstable eigenmode of the kink instability, resulting in the instability growing from $t=0$.
-In contrast, in the tubes studied here, such a perturbation must build from numerical noise, allowing a secondary, fluting perturbation to also build and become significant enough to observe.
-
-urther detailed comparison of the models is required to fully understand this,  \todo{finish me}
+In contrast, in the tubes studied here, such a perturbation must build from numerical noise, allowing a secondary, fluting perturbation to also build and become significant enough to observe.}
 

### 2021-10-19 paper.tex
Add MNRAS template and update acknowledgements and software appendix

@@
-\documentclass[12pt]{article}
-%\usepackage[T1]{fontenc} % modern encoding
-%\usepackage[utf8]{inputenc}
-%\usepackage{libertine}
-%\usepackage[libertine]{newtxmath}
-%\usepackage[scaled=0.95]{inconsolata}
-\usepackage[margin=0.5in]{geometry}
-
-\usepackage{graphicx}  % standard package for importing graphics files
+\documentclass[fleqn,usenatbib]{mnras}
+
+\usepackage{newtxtext,newtxmath}
+\usepackage[T1]{fontenc} % modern encoding
+
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+%\usepackage{amssymb}	% Extra maths symbols
 
 %% --- user packages ---
-\usepackage{amssymb}
 \usepackage{csquotes}
 \usepackage{bm}
-\usepackage{amsmath}
 \usepackage{subcaption}
@@
 \usepackage{listings}
-
-\usepackage[
-backend=biber,
-style=numeric,
-firstinits,
-url=false,
-isbn=false,
-eprint=false
-]{biblatex}
-\renewbibmacro{in:}{}
-%\AtEveryBibitem{\clearfield{pages}} 
-\DeclareFieldFormat{date}{%
-  \thefield{year}}
-\DeclareFieldFormat{issue}{\bfseries{#1}}
-
-\addbibresource{bib.bib}
-
+%\usepackage[citecolor=blue]{hyperref}
 \usepackage{lineno}
-\usepackage[citecolor=blue]{hyperref}
-%\modulolinenumbers[5]
+
+% Package options
 
@@
 
-% For editing
-\usepackage{color}
-\newcommand{\rr}[1]{\textcolor{red}{#1}}
-\newcommand{\bb}[1]{\textcolor{blue}{#1}}
-\newcommand{\rs}[2]{\textcolor{red}{#2}}
-\newcommand{\jq}[2]{\textcolor{blue}{#2}}
-%\newcommand{\rr}[1]{#1}
-%\newcommand{\bb}[1]{#1}
-%\newcommand{\rs}[1]{#1}
-
-%\newcommand\todo[1]{\textcolor{red}{#1}}
-
-%% --- user commands ---
+%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+
+\newcommand{\rr}[1]{{#1}}
+\newcommand{\bb}[1]{{#1}}
+\newcommand{\rs}[2]{{#2}}
+\newcommand{\jq}[2]{{#2}}
 
@@
 
+\title{Flute and kink instabilities in a dynamically twisted
+    flux tube with anisotropic plasma viscosity}
+
+\author[J.~Quinn and R.~Simitev]{
+James J.~Quinn,$^{1}$\thanks{E-mail: jamiejquinn@jamiejquinn.com}
+Radostin D.~Simitev$^{2}$
+\\
+% List of institutions
+$^{1}$ Research Software Development Group, University College London, Gower Street, London WC1E 6BT, UK \\
+\href{https://orcid.org/0000-0002-0268-7032}{orcid.org/0000-0002-0268-7032} \\
+$^2$ School of Mathematics and Statistics, University of Glasgow,
+Glasgow G12 8QQ,
+UK \\ \href{https://orcid.org/0000-0002-2207-5789}{orcid.org/0000-0002-2207-5789}\\
+}
+
+\date{Accepted XXX. Received YYY; in original form ZZZ}
+
+\pubyear{2021}
+
 \begin{document}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
+
 \lstset{
@@
 
-\title{\rs{Kink and fluting instabilities in a dynamically twisted
-    flux tube}{Flute and kink instabilities in a dynamically twisted
-    flux tube with anisotropic plasma viscosity}}
-\author{\rs{}{James J.~Quinn$^{1,\ast}$, Radostin D.~Simitev$^2$}}
-\date{\small
-  $^1$ Research Software Development Group, University College London, Gower Street, London WC1E 6BT, UK.\\
-  e-mail:
-  \href{mailto:jamiejquinn@jamiejquinn.com}{jamiejquinn@jamiejquinn.com}. $^\ast$
-  Corresponding author\\
-  $^2$ School of Mathematics and Statistics, University of Glasgow,
-  Glasgow G12 8QQ,
-  UK. \\ \href{https://orcid.org/0000-0002-2207-5789}{orcid.org/0000-0002-2207-5789}\\
-\vspace{5mm}
-  Version: \today}
-\maketitle
-
 \graphicspath{{images/kink_instability_straight/}}
@@
 \begin{abstract}
-  % Context
-  The magnetic flux tubes which make up the solar corona can become unstable to a number of instabilities, including the kink instability, which forms a core part of the nanoflare theory of coronal heating.
-However, the development of the kink instability can be affected by other phenomena such as the flute instability.
-  % Aims
-  This paper aims to investigate the effect of the flute instability on the growth of the kink instability in coronal loops, particularly focussing on the effect of anisotropic plasma viscosity.
-  % Methods
-  Using the magnetohydrodynamic code, Lare3d, an initially straight flux tube is twisted via boundary motions until it reveals the kink instability and, in some cases, the flute instability.
-This is performed for multiple values of the resistivity and for anisotropic and isotropic models of viscosity.
-  % Results
-  The flute instability is found to more readily occur when viscosity is anisotropic and, where present, it damps the growth of the kink instability.
-  % Conclusions
-  \todo{conclusions please}
+Magnetic flux tubes such as those in the solar corona are subject to a
+number of instabilities. Important among them is the kink instability
+which plays a central part in the nanoflare theory of coronal heating,
+and for this reason in numerical simulations it is usually induced by
+tightly-controlled perturbations and studied in isolation. In
+contrast, we find that when disturbances are introduced in our
+magnetohydrodynamic flux tube simulations by dynamic twisting of the
+flow at the boundaries fluting modes of instability are readily
+excited. We also find that the flute instability, which has been
+theorised but rarely observed in the coronal context,  is strongly
+enhanced when plasma viscosity is assumed anisotropic.
+We proceed to investigate the co-existence and competition between
+flute and kink instabilities for a range of values of the resistivity
+and of the parameters of the anisotropic and isotropic models of viscosity.
+We conclude that while the flute instability cannot prevent the kink
+from ultimately dominating, it can significantly delay its development
+especially at strong viscous anisotropy induced by intense magnetic fields.
 \end{abstract}
+
+\begin{keywords}
+Sun: corona -- Sun: magnetic fields -- instabilities -- plasmas -- MHD
+\end{keywords}
 
@@
 such as those making up much of the solar
-corona~\cite{realeCoronalLoopsObservations2014} and has been well
+corona~\citep{realeCoronalLoopsObservations2014} and has been well
 studied in the coronal
-context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003b,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020}. Given
+context~\citep{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003b,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020}. Given
 its energetic nonlinear development, it is considered a potential
 mechanism for heating the solar corona through the theory of
-nanoflares~\cite{klimchukSolvingCoronalHeating2006,browningMechanismsSolarCoronal1991}
+nanoflares~\citep{klimchukSolvingCoronalHeating2006,browningMechanismsSolarCoronal1991}
 and a key mechanism in the production of solar
-flares~\cite{hoodKinkInstabilitySolar1979}. Previous work by the same
+flares~\citep{hoodKinkInstabilitySolar1979}. Previous work by the same
 authors has investigated a twisted magnetic flux tube already linearly
@@
 the effect of anisotropic viscosity on the nonlinear
-dynamics~\cite{quinnEffectAnisotropicViscosity2020}. In~\cite{quinnEffectAnisotropicViscosity2020}
+dynamics~\citep{quinnEffectAnisotropicViscosity2020}. In~\cite{quinnEffectAnisotropicViscosity2020}
 and most other investigations of the kink instability
@@
 in~\cite{priestMagnetohydrodynamicsSuna}).
-\jq{}{While oscillations involving flute perturbations have been found in simulations of coronal loops~\cite{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute instability has been investigated computationally in a coronal context.}
+\jq{}{While oscillations resembling flute perturbations have been found in simulations of coronal loops~\citep{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute instability has been investigated computationally in a coronal context.}
 
@@
 form of ballooning modes in
-arcades~\cite{hoodBallooningInstabilitiesSolar1986}, as the
+arcades~\citep{hoodBallooningInstabilitiesSolar1986}, as the
 instability which forms tubes of specific size in the
-photosphere~\cite{bunteInterchangeInstabilitySolar1993} and in the
+photosphere~\citep{bunteInterchangeInstabilitySolar1993} and in the
 buoyancy of flux
-tubes~\cite{schuesslerInterchangeInstabilitySmall1984}. However, the
+tubes~\citep{schuesslerInterchangeInstabilitySmall1984}. However, the
 \rs{fluting}{flute} instability specifically is more commonly studied in fusion
-contexts~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}. In
+contexts~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}. In
 fusion, the focus is generally on understanding how a particular
@@
 geometries such as that of the mirror
-machine~\cite{jungwirthTheoryFluteInstability1965} or in toroidal
+machine~\citep{jungwirthTheoryFluteInstability1965} or in toroidal
 geometries such as the
-tokomak~\cite{shafranovFluteInstabilityCurrentcarrying1968}. The
+tokomak~\citep{shafranovFluteInstabilityCurrentcarrying1968}. The
 resistive \rs{fluting}{flute} instability (also known as the resistive interchange
@@
 stabilised. As a result, this has been given significantly more
-attention~\cite{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}. While
+attention~\citep{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}. While
 this body of research is useful and applicable in solar contexts, it
@@
 the local magnetic
-field~\cite{hollwegViscosityChewGoldbergerLowEquations1986,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
+field~\citep{hollwegViscosityChewGoldbergerLowEquations1986,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
 \rs{}{To take this into account, in \cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017},
@@
 the switching model as a module for the widely-used general MHD code
-Lare3d \cite{arberStaggeredGridLagrangian2001}, and demonstrated
+Lare3d \citep{arberStaggeredGridLagrangian2001}, and demonstrated
 significant effects of anisotropic viscosity on the 
@@
 which heating mechanism (viscous or Ohmic) is dominant in the solar
-corona~\cite{klimchukSolvingCoronalHeating2006}, an important facet
+corona~\citep{klimchukSolvingCoronalHeating2006}, an important facet
 of solving the coronal heating problem. Using scaling laws, it has
@@
 viscosity) can dwarf that of Ohmic
-heating~\cite{craigAnisotropicViscousDissipation2009a,litvinenkoViscousEnergyDissipation2005}.
+heating~\citep{craigAnisotropicViscousDissipation2009a,litvinenkoViscousEnergyDissipation2005}.
 However,
@@
 scale instabilities and turbulence is relatively
-unknown~\cite{klimchukSolvingCoronalHeating2006}. In addition to
+unknown~\citep{klimchukSolvingCoronalHeating2006}. In addition to
 directly heating the plasma, viscosity plays a part in the damping of
-instabilities and waves~\cite{rudermanSlowSurfaceWave2000}. It is
+instabilities and waves~\citep{rudermanSlowSurfaceWave2000}. It is
 this effect we are most interested in here, and it shall be \rs{found}{reported} that
@@
 the form~\eqref{eq:kink_perturbation} is given by the classical
-\rs{}{Suydam's criterion \cite{suydamStabilityLinearPinch1958}}
+\rs{}{Suydam's criterion \citep{suydamStabilityLinearPinch1958}}
 \begin{equation}
@@
 \rs{dash}{prime} denotes differentiation with respect to
-$r$~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998}. This applies
+$r$~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}. This applies
 to both \rs{fluting}{flute} and kink instabilities although many
@@
 \rs{}{When} Suydam's criterion is satisfied and the flux tube is linearly stable, it may still be unstable to non-local perturbations, where the shear and pressure are small enough that interchange perturbations do not need to satisfy~\eqref{eq:resonant_surface}.
-Additionally, the inclusion of resistivity generally reduces the stabilising effect of the shear, permitting growth of a resistive interchange mode, albeit at a slower rate than that of the ideal instability~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998}.
+Additionally, the inclusion of resistivity generally reduces the stabilising effect of the shear, permitting growth of a resistive interchange mode, albeit at a slower rate than that of the ideal instability~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}.
 It will be found that the ideal linear analysis of~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998} is sufficient for understanding the \rs{fluting}{flute} instabilities investigated here since the associated flux tubes adequately fail the criterion~\eqref{eq:suydams_criterion}.
@@
 that used in
-\rs{our previous work~\cite{quinnEffectAnisotropicViscosity2020}}{previous work~\cite{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}},
+\rs{our previous work~\citep{quinnEffectAnisotropicViscosity2020}}{previous work~\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}},
  the switching model, first presented
@@
 where $\vec{b}$ is the unit vector in the direction of the magnetic field.
-This tensor is identical to the strong field approximation of Braginskii~\cite{braginskiiTransportProcessesPlasma1965}.
-Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020}\todo{ref KHI paper}.
+This tensor is identical to the strong field approximation of Braginskii~\citep{braginskiiTransportProcessesPlasma1965}.
+Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}.
 }{}
@@
 Expression \eqref{eq:switching_model} is identical to the strong field approximation of the
-general anisotropic viscosity tensor derived by Braginskii~\cite{braginskiiTransportProcessesPlasma1965}.
+general anisotropic viscosity tensor derived by Braginskii~\citep{braginskiiTransportProcessesPlasma1965}.
 Expressions \eqref{eq:isotropic_viscous_tensor} and \eqref{eq:switching_model} arise as asymptotic limits of the
 more general switching model used in our earlier works 
-\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
+\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
 which, includes both isotropic and anisotropic contributions and can
@@
 \rs{The non-dimensionalisation scheme and values align with the scheme
-used by Lare3d~\cite{arberStaggeredGridLagrangian2001} and are
+used by Lare3d~\citep{arberStaggeredGridLagrangian2001} and are
 identical to those used
@@
 our earlier works
-\cite{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} and in reference
+\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} and in reference
 \cite{arberStaggeredGridLagrangian2001} that describes the code Lare3d
@@
 \rs{}{and} the
-internal energy to $\varepsilon = 8.67\times 10^{-4}$ (corresponding
-to a temperature of $10^6$ K, a typical coronal value). \todo{what's the plasma beta?} At the
+internal energy to $\varepsilon = 8.67\times 10^{-4}$. This corresponds
+to a typical coronal temperature of $10^6$ K and a plasma beta of $1.11 \times 10^{-4}$. At the
 boundaries, the magnetic field, \rs{}{velocity,} density, and energy are fixed to their
@@
 
-\begin{figure}[t]
+\begin{figure*}
   \centering
@@
   \label{fig:pressure_and_heating}
-\end{figure}
+\end{figure*}
 
@@
 \label{fig:kink_pressure_slices-4}%
-\end{figure}
+\end{figure*}
 
@@
 linear fluting growth rate $\gamma$ is plotted as a function of $r$ at
-the same time (figure~\ref{fig:growth_rate_4}). While the magnitude of
-the peak linear growth \rs{}{[RADO: WHY DON'T WE COMPARE THE AVERAGE THEORETICAL GROWTH RATE 
-    (INSTEAD OF THE PEAK) TO THE EXPERIMENTALLY MEASURED ONE
-    INSTEAD. iF YOU AVERAGE YOU WILL GET A NUMBER QUITE CLOSE TO THE
-   0.69 FROM FIG 4B.} rate predicts the observed rate reasonably well, the location of the peak growth matches nearly exactly the location of the resonant surface where the observed perturbation grows (figure~\ref{fig:swi-4_pressure_13}).
+the same time (figure~\ref{fig:growth_rate_4}).
+The location of the peak growth matches nearly exactly the location of the resonant surface where the observed perturbation grows (figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate can be found by averaging $\gamma$ over $r$, giving a growth rate of $0.86$.
 
@@
 \label{fig:kink_pressure_slices-3}%
-\end{figure}
+\end{figure*}
 
@@
 of flux tube (as was observed in
-\rs{chapter}{our earlier work}~\cite{quinnEffectAnisotropicViscosity2020}).
+\rs{chapter}{our earlier work}~\citep{quinnEffectAnisotropicViscosity2020}).
 
@@
 
-\begin{table}[]
+\begin{table}
+\caption{Quantitative differences in the observed perturbations
+  between results \rs{for both values of}{between different
+    resistivity values} $\eta$. \rs{}{In all measurements the
+  anisotropic viscosity model is used except for $k_\text{kink}$ where the
+  isotropic viscosity model us used. Measurements times are listed in
+  the main text.}}
 \centering
@@
 \midrule
-\rs{Predicted linear}{Theoretical linear growth rate of flute} $\gamma$ & 1.43 & 2.72  \\
+\rs{Predicted linear}{Theoretical average linear growth rate of flute} $\gamma$ & 0.86 & 1.79  \\
 Observed nonlinear \rs{}{growth rate of flute} $\gamma$ & 0.69 & 1.06  \\
@@
 \end{tabular}
-\caption{Quantitative differences in the observed perturbations
-  between results \rs{for both values of}{between different
-    resistivity values} $\eta$. \rs{}{In all measurements the
-  anisotropic viscosity model is used except for $k_\text{kink}$ where the
-  isotropic viscosity model us used. Measurements times are listed in
-  the main text.}}
 \label{tab:kink_fluting_params}
@@
 is found in the study of kink and \rs{fluting}{flute}
-oscillations~\cite{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017}.
+oscillations~\citep{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017}.
 
@@
 approximately
-$\eta=10^{-8}$~\cite{craigAnisotropicViscousDissipation2009a},
+$\eta=10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a},
 \rs{which are}{and are thus} much smaller than those studied
@@
 with strong radial pressure gradients have been
-observed~\cite{foukalTemperatureStructurePressure1975}, and such loops
+observed~\citep{foukalTemperatureStructurePressure1975}, and such loops
 may be unstable to the \rs{fluting}{flute} instability. Modelling of a
@@
 tube) focus on the kink
-instability~\cite{browningSolarCoronalHeating2003b} so do not provide
+instability~\citep{browningSolarCoronalHeating2003b} so do not provide
 much insight into the potential for fluting without a kink.
@@
 
-\printbibliography
-
+\section*{Acknowledgements}
+
+Results were obtained using the ARCHIE-WeSt High Performance Computer
+(\url{www.archie-west.ac.uk}) based at the University of
+Strathclyde. JQ was funded via an EPSRC studentship: EPSRC DTG EP/N509668/1.
+
+\bibliographystyle{mnras}
+\bibliography{bib}
+
+\appendix
+
+A custom version of Lare3d~\citep{arberStaggeredGridLagrangian2001} has been developed where a new module for anisotropic viscosity has been included.
+\rs{The version including the new module}{} can be found at \url{https://github.com/jamiejquinn/Lare3d}, \rs{and also}{has been} archived at~\citep{keith_bennett_2020_4155546}.
+The version of Lare3d used in the production of the results presented here, including initial conditions, boundary conditions, control parameters and the anisotropic viscosity module, can be found at~\cite{keith_bennett_2020_4155625}.
+The data analysis and instructions for reproducing all results found in this report may be also found at \url{https://github.com/JamieJQuinn/coronal-fluting-instability-analysis} and has been archived~\citep{quinnJamieJQuinnCoronalflutinginstabilityanalysisInitial2021}.
+
+All simulations were performed on a single, multi-core machine with $40$ cores provided by Intel Xeon Gold 6138 Skylake processor running at $2$ GHz and $192$ GB of RAM, although this amount of RAM is much higher than was required; a conservative estimate of the memory used in the largest simulations is around $64$ GB.
+Most simulations completed in under $2$ days.
+
+\bsp	% typesetting comment
+\label{lastpage}
 \end{document}

### 2021-10-19 integrate_graph.py
Acknowledge David

@@ -1,0 +1,12 @@
+import statistics
+
+mm_to_val = 1.0/17.0
+values = [7, 17.5, 22, 22.5, 21.5, 17.5, 14, 11, 8, 6]
+print(statistics.mean(values)*mm_to_val)
+
+mm_to_val = 1.0/26.0
+values = [10, 20, 29, 38, 40, 53, 59, 64, 67,70,71,69,67,63,61,57,52,47,43,39,37,32,29,25,22]
+print(statistics.mean(values)*mm_to_val)
+
+
+

### 2021-10-20 paper.tex
Acknowledge David
Fix minor errors

@@
 the effect of anisotropic viscosity on the nonlinear
-dynamics~\citep{quinnEffectAnisotropicViscosity2020}. In~\cite{quinnEffectAnisotropicViscosity2020}
+dynamics~\citep{quinnEffectAnisotropicViscosity2020}. In~\citep{quinnEffectAnisotropicViscosity2020}
 and most other investigations of the kink instability
-\rs{}{e.g. \cite{hoodCoronalHeatingMagnetic2009}}, a perturbation 
+\rs{}{e.g. \citep{hoodCoronalHeatingMagnetic2009}}, a perturbation 
 is applied to an already significantly twisted flux tube. An
@@
 the \rs{fluting}{flute} instability, which has been theorised (for example,
-in~\cite{priestMagnetohydrodynamicsSuna}).
+in~\citep{priestMagnetohydrodynamicsSun2013}).
 \jq{}{While oscillations resembling flute perturbations have been found in simulations of coronal loops~\citep{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute instability has been investigated computationally in a coronal context.}
@@
 field~\citep{hollwegViscosityChewGoldbergerLowEquations1986,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
-\rs{}{To take this into account, in \cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017},
+\rs{}{To take this into account, in \citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017},
 we developed a phenomenological model of anisotropic viscosity that
@@
 refer to this model of viscosity as ``the switching model''. In
-\cite{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} we implemented
+\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} we implemented
 the switching model as a module for the widely-used general MHD code
@@
 instability \rs{can be found}{is investigated}
-in~\cite{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion}
+in~\citep{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion}
 is not satisfied, the flux tube may be unstable to perturbations of
@@
 
-While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal \rs{fluting}{flute} instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\cite{goldstonIntroductionPlasmaPhysics2020}) and is given by
+While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal \rs{fluting}{flute} instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\citep{goldstonIntroductionPlasmaPhysics2020}) and is given by
 \begin{equation}
@@
 \rs{In contrast to the precise form of the equilibrium state and
-  perturbation studied in~\cite{quinnEffectAnisotropicViscosity2020},
+  perturbation studied in~\citep{quinnEffectAnisotropicViscosity2020},
   this is an experiment where a system is driven and instabilities
@@
   \eqref{eq:suydams_criterion} and \eqref{eq:fluting_growth_rate2}
-  were used in~\cite{quinnEffectAnisotropicViscosity2020}.
+  were used in~\citep{quinnEffectAnisotropicViscosity2020}.
   In contrast, in the experiments reported in the following the system
@@
  the switching model, first presented
- in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}. While
+ in~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}. While
  this model is intended to revert to an isotropic model in the
@@
 This tensor is identical to the strong field approximation of Braginskii~\citep{braginskiiTransportProcessesPlasma1965}.
-Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}.
+Full use of the switching model can be found in~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}.
 }{}
@@
 identical to those used
-in~\cite{quinnEffectAnisotropicViscosity2020}.}
+in~\citep{quinnEffectAnisotropicViscosity2020}.}
    {
@@
 \citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} and in reference
-\cite{arberStaggeredGridLagrangian2001} that describes the code Lare3d
+\citep{arberStaggeredGridLagrangian2001} that describes the code Lare3d
 we use for numerical solution, see further below. A typical magnetic
@@
 Both drivers result in twist being added at a rate of $2\pi$ every $7.96$ Alfv\'en times.
-The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\cite{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
+The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\citep{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
 This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the \rs{fluting}{flute} instability and the helical kink instability.
@@
   a  new module for anisotropic viscosity has been
-  included as detailed in \cite{quinnKelvinHelmholtzInstabilityCollapse2021}.} The resolution used in the
+  included as detailed in \citep{quinnKelvinHelmholtzInstabilityCollapse2021}.} The resolution used in the
 current work is  $512$ grid points per dimension, comparable to the
@@
 $\eta=10^{-3}$ and another where $\eta=10^{-4}$. As
-in~\cite{quinnEffectAnisotropicViscosity2020}, only background
+in~\citep{quinnEffectAnisotropicViscosity2020}, only background
 resistivity is used. Each pair consists of one simulation
@@
 oppositely-directed current is similar to the \rs{prescribed field in
-chapter~}{current configuration arising due to the field prescribed in} \cite{quinnEffectAnisotropicViscosity2020}.
+chapter~}{current configuration arising due to the field prescribed in} \citep{quinnEffectAnisotropicViscosity2020}.
 
@@
   chapter~}{to that measured in}
-\cite{quinnEffectAnisotropicViscosity2020} is \rs{due}{attributed} to
+\citep{quinnEffectAnisotropicViscosity2020} is \rs{due}{attributed} to
 the relative aspect ratios of the flux tubes. The tube prescribed in
-\rs{chapter~}{} \cite{quinnEffectAnisotropicViscosity2020} has an aspect
+\rs{chapter~}{} \citep{quinnEffectAnisotropicViscosity2020} has an aspect
 ratio of approximately $20$ compared to the tube studied here which
@@
 
-\jq{}{It is prudent to ask, if the current distribution, which develops as the flux tube is twisted, is similar to that found in the initial flux tube configuration of~\cite{quinnEffectAnisotropicViscosity2020}, why do we not observe the fluting instability in~\cite{quinnEffectAnisotropicViscosity2020}?
+As the current distribution, which develops as the flux tube is twisted, is similar to that found in the initial flux tube configuration of~\cite{quinnEffectAnisotropicViscosity2020},the question arises why the fluting instability is not observed in the latter.
 Although the current distribution (and thus heating and pressure distributions) in the tubes of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute instability, the tube is initially perturbed with a motion close to an unstable eigenmode of the kink instability, resulting in the instability growing from $t=0$.
-In contrast, in the tubes studied here, such a perturbation must build from numerical noise, allowing a secondary, fluting perturbation to also build and become significant enough to observe.}
+In contrast, in the tubes studied here, such a perturbation must build from numerical noise, allowing a secondary, fluting perturbation to also build and become significant enough to observe.
 
@@
 dynamics, which mirror those of other kink instability studies, \rs{such
-as~}{e.g.~}\cite{hoodCoronalHeatingMagnetic2009}. This suggests that even
+as~}{e.g.~}\citep{hoodCoronalHeatingMagnetic2009}. This suggests that even
 lower values of resistivity would result in flux tubes without any
@@
 that employed in the simulations performed in \rs{chapter}{our earlier
-  study}~\cite{quinnEffectAnisotropicViscosity2020} in that the
+  study}~\citep{quinnEffectAnisotropicViscosity2020} in that the
 instabilities are not excited by any prescribed perturbations but,
@@
 kinetic energy. Similar to \rs{chapter}{}
-\cite{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating
+\citep{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating
 is found to be \rs{significantly lower}{lower} than anisotropic (switching)
@@
 
-Results were obtained using the ARCHIE-WeSt High Performance Computer
+We would like to thank David MacTaggart for his input on the thesis chapter on which this paper is based. Results were obtained using the ARCHIE-WeSt High Performance Computer
 (\url{www.archie-west.ac.uk}) based at the University of
@@
 
+\section{Associated software}
+
 A custom version of Lare3d~\citep{arberStaggeredGridLagrangian2001} has been developed where a new module for anisotropic viscosity has been included.
 \rs{The version including the new module}{} can be found at \url{https://github.com/jamiejquinn/Lare3d}, \rs{and also}{has been} archived at~\citep{keith_bennett_2020_4155546}.
-The version of Lare3d used in the production of the results presented here, including initial conditions, boundary conditions, control parameters and the anisotropic viscosity module, can be found at~\cite{keith_bennett_2020_4155625}.
-The data analysis and instructions for reproducing all results found in this report may be also found at \url{https://github.com/JamieJQuinn/coronal-fluting-instability-analysis} and has been archived~\citep{quinnJamieJQuinnCoronalflutinginstabilityanalysisInitial2021}.
+The version of Lare3d used in the production of the results presented here, including initial conditions, boundary conditions, control parameters and the anisotropic viscosity module, can be found in~\citep{keith_bennett_2020_4155625}.
+The data analysis and instructions for reproducing all results found in this report may be also found at \url{https://github.com/JamieJQuinn/coronal-fluting-instability-analysis} and has been archived~\citep{quinnJamieJQuinnCoronalflutinginstabilityanalysis2021}.
 

### 2021-12-02 paper.tex
Rename bib to paper
Remove [t] from figures
Address some minor reviewer comments and remove some \rs commands

@@
 
-\newcommand{\rr}[1]{{#1}}
-\newcommand{\bb}[1]{{#1}}
 \newcommand{\rs}[2]{{#2}}
@@
 and a key mechanism in the production of solar
-flares~\citep{hoodKinkInstabilitySolar1979}. Previous work by the same
-authors has investigated a twisted magnetic flux tube already linearly
-unstable to the helical kink instability, \rs{investigating particularly}{focussing specifically on}
+flares~\citep{hoodKinkInstabilitySolar1979}. Some of our previous work has investigated a twisted magnetic flux tube already linearly
+unstable to the helical kink instability, focussing specifically on
 the effect of anisotropic viscosity on the nonlinear
-dynamics~\citep{quinnEffectAnisotropicViscosity2020}. In~\citep{quinnEffectAnisotropicViscosity2020}
+dynamics~\citep{quinnEffectAnisotropicViscosity2020}. In~\citet{quinnEffectAnisotropicViscosity2020}
 and most other investigations of the kink instability
-\rs{}{e.g. \citep{hoodCoronalHeatingMagnetic2009}}, a perturbation 
+e.g.~\citet{hoodCoronalHeatingMagnetic2009}, a perturbation 
 is applied to an already significantly twisted flux tube. An
@@
 becomes unstable. This kind of dynamic excitation of the kink
-instability is useful in that it represents more closely \rs{the real
-development of a magnetic flux tube and associated}{actual evolution
-  of magnetic flux tubes and the associated} instabilities in 
-the solar corona. \rs{The}{In our simulations, the}
+instability is useful in that it represents more closely actual evolution of magnetic flux tubes and the associated instabilities in 
+the solar corona. In our simulations, the
 dynamic twisting of the flux tube reveals an additional instability,
-the \rs{fluting}{flute} instability, which has been theorised (for example,
-in~\citep{priestMagnetohydrodynamicsSun2013}).
-\jq{}{While oscillations resembling flute perturbations have been found in simulations of coronal loops~\citep{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute instability has been investigated computationally in a coronal context.}
-
-The \rs{fluting}{flute} instability arises in magnetised plasmas where
-the plasma pressure gradient is \rs{directed}{oriented} in the same direction as the
+the flute instability, which has been theorised (for example,
+in~\citet{priestMagnetohydrodynamicsSun2013}).
+While oscillations resembling flute perturbations have been found in simulations of coronal loops~\citep{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute instability has been investigated computationally in a coronal context.
+
+The flute instability arises in magnetised plasmas where
+the plasma pressure gradient is oriented in the same direction as the
 field line curvature, that is the pressure and magnetic tension forces
@@
 gravitational forces which gives rise to the Rayleigh-Taylor
-instability (RTI). In \rs{MHD}{magnetohydrodynamic terminology}, the RTI is a typical example of an ideal
+instability (RTI). In magnetohydrodynamic terminology, the RTI is a typical example of an ideal
 interchange instability, where magnetic field lines are minimally bent
 and are, instead, exchanged during the evolution of the
-instability. The ideal \rs{fluting}{flute} instability is another example of an
+instability. The ideal flute instability is another example of an
 ideal interchange instability but confined to a cylindrical geometry,
-the term \rs{``fluting instability''}{``flute instability''} referring to its likeness to a fluted
+the term ``flute instability'' referring to its likeness to a fluted
 column. In a twisted flux tube like a simple, unbraided coronal loop,
@@
 flux tubes studied here as a result of the driving. The appearance of
-the \rs{fluting}{flute} instability is illustrated by, for example, the pressure
+the flute instability is illustrated by, for example, the pressure
 contours in figure~\ref{fig:kink_field_line_plots}, where the
@@
 tubes~\citep{schuesslerInterchangeInstabilitySmall1984}. However, the
-\rs{fluting}{flute} instability specifically is more commonly studied in fusion
+flute instability specifically is more commonly studied in fusion
 contexts~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}. In
@@
 tokomak~\citep{shafranovFluteInstabilityCurrentcarrying1968}. The
-resistive \rs{fluting}{flute} instability (also known as the resistive interchange
-instability) can be excited even when the ideal \rs{fluting}{flute} instability is
+resistive flute instability (also known as the resistive interchange
+instability) can be excited even when the ideal flute instability is
 stabilised. As a result, this has been given significantly more
-attention~\citep{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}. While
+attention~\citet{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}. While
 this body of research is useful and applicable in solar contexts, it
 is mostly limited to the study of the stability and linear development
-of the \rs{fluting}{flute} instability, the nonlinear development being of
+of the flute instability, the nonlinear development being of
 secondary importance in the investigation of fusion devices. More
@@
 understand its importance in the context of coronal dynamics and
-coronal heating. The development of the \rs{fluting}{flute} instability and its
+coronal heating. The development of the flute instability and its
 interaction with the simultaneously growing kink instability is the
-\rs{}{main} focus of this work and the experiments described here represent an
-initial exploration into the nonlinear \rs{fluting}{flute} instability in the
+main focus of this work and the experiments described here represent an
+initial exploration into the nonlinear flute instability in the
 solar corona.
 
-\rs{}{In addition to our main goal, of particular interest here is
+In addition to our main goal, of particular interest here is
 also the effect of anisotropic plasma viscosity, which in the following is found to
-strongly influence the growth of the \rs{fluting}{flute} instability.}
+strongly influence the growth of the flute instability.
 It is well known that viscosity in magnetised plasmas (such as
-\rs{that which makes up}{those which make up} the solar corona) is
+those which make up the solar corona) is
 anisotropic and strongly dependent on the strength and direction of
@@
 field~\citep{hollwegViscosityChewGoldbergerLowEquations1986,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
-\rs{}{To take this into account, in \citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017},
-we developed a phenomenological model of anisotropic viscosity that
+To take this into account, MacTaggaret et al. developed a phenomenological model of anisotropic viscosity~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} that
 captures the main physics of viscosity in the 
@@
 in regions of very weak or zero field strength. For brevity, we will
-refer to this model of viscosity as ``the switching model''. In
-\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} we implemented
+refer to this model of viscosity as ``the switching model''. In~\citet{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} we implemented
 the switching model as a module for the widely-used general MHD code
-Lare3d \citep{arberStaggeredGridLagrangian2001}, and demonstrated
+Lare3d~\citep{arberStaggeredGridLagrangian2001}, and demonstrated
 significant effects of anisotropic viscosity on the 
 development of the nonlinear MHD kink instability and the
-Kelvin-Helmholtz instability.} \rs{The}{More generally, the} interest in
-anisotropic viscosity stems from the \rs{unanswered}{open} question of
+Kelvin-Helmholtz instability. More generally, the interest in
+anisotropic viscosity stems from the open question of
 which heating mechanism (viscous or Ohmic) is dominant in the solar
@@
 scale instabilities and turbulence is relatively
-unknown~\citep{klimchukSolvingCoronalHeating2006}. In addition to
+unknown~\citet{klimchukSolvingCoronalHeating2006}. In addition to
 directly heating the plasma, viscosity plays a part in the damping of
 instabilities and waves~\citep{rudermanSlowSurfaceWave2000}. It is
-this effect we are most interested in here, and it shall be \rs{found}{reported} that
+this effect we are most interested in here, and it shall be reported that
 the use of anisotropic viscosity permits the growth of the
-\rs{fluting}{flute} instability, which is otherwise strongly damped by
+flute instability, which is otherwise strongly damped by
 isotropic viscosity.
@@
 
-\subsection{The \rs{fluting}{flute} instability}
+\subsection{The flute instability}
 \label{sec-flute-intro}
@@
 the form~\eqref{eq:kink_perturbation} is given by the classical
-\rs{}{Suydam's criterion \citep{suydamStabilityLinearPinch1958}}
+\rs{}{Suydam's criterion~\citep{suydamStabilityLinearPinch1958}}
 \begin{equation}
@@
 instability \rs{can be found}{is investigated}
-in~\citep{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion}
+in~\citet{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion}
 is not satisfied, the flux tube may be unstable to perturbations of
@@
 
-While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal \rs{fluting}{flute} instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\citep{goldstonIntroductionPlasmaPhysics2020}) and is given by
+While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal \rs{fluting}{flute} instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\citep[][]{goldstonIntroductionPlasmaPhysics2020}) and is given by
 \begin{equation}
@@
 \rs{In contrast to the precise form of the equilibrium state and
-  perturbation studied in~\citep{quinnEffectAnisotropicViscosity2020},
+  perturbation studied in~\citet{quinnEffectAnisotropicViscosity2020},
   this is an experiment where a system is driven and instabilities
@@
   \eqref{eq:suydams_criterion} and \eqref{eq:fluting_growth_rate2}
-  were used in~\citep{quinnEffectAnisotropicViscosity2020}.
+  were used in~\citet{quinnEffectAnisotropicViscosity2020}.
   In contrast, in the experiments reported in the following the system
@@
  the switching model, first presented
- in~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}. While
+ in~\citet{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}. While
  this model is intended to revert to an isotropic model in the
@@
 This tensor is identical to the strong field approximation of Braginskii~\citep{braginskiiTransportProcessesPlasma1965}.
-Full use of the switching model can be found in~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}.
+Full use of the switching model can be found in~\citet{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}.
 }{}
+
 \rs{}{Two different models for the viscosity stress tensor $\ten{\sigma}$
@@
 Expression \eqref{eq:switching_model} is identical to the strong field approximation of the
-general anisotropic viscosity tensor derived by Braginskii~\citep{braginskiiTransportProcessesPlasma1965}.
+general anisotropic viscosity tensor derived in~\citet{braginskiiTransportProcessesPlasma1965}.
 Expressions \eqref{eq:isotropic_viscous_tensor} and \eqref{eq:switching_model} arise as asymptotic limits of the
@@
 
-\rs{The non-dimensionalisation scheme and values align with the scheme
-used by Lare3d~\citep{arberStaggeredGridLagrangian2001} and are
-identical to those used
-in~\citep{quinnEffectAnisotropicViscosity2020}.}
-   {
 The non-dimensionalisation of equations \eqref{eq:MHD} is identical to that used in
-our earlier works
-\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} and in reference
-\citep{arberStaggeredGridLagrangian2001} that describes the code Lare3d
-we use for numerical solution, see further below. A typical magnetic
+our earlier works~\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}. A typical magnetic
 field strength $B_0$, density $\rho_0$ and length scale $L_0$ are
@@
 0.29\ \text{s}$ and temperature $T_0 = 1.73 \times 10^{9}\ K$.
-   }
 
@@
 
-\begin{figure}[t]
+\begin{figure}
   \centering
@@
 Both drivers result in twist being added at a rate of $2\pi$ every $7.96$ Alfv\'en times.
-The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\citep{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
+The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\citet{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
 This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the \rs{fluting}{flute} instability and the helical kink instability.
@@
   staggered-grid, Lagrangian–Eulerian remap code for 3D MHD
-  simulations Lare3D of \cite{arberStaggeredGridLagrangian2001} where
+  simulations Lare3D of~\cite{arberStaggeredGridLagrangian2001} where
   a  new module for anisotropic viscosity has been
-  included as detailed in \citep{quinnKelvinHelmholtzInstabilityCollapse2021}.} The resolution used in the
+  included as detailed in~\citet{quinnKelvinHelmholtzInstabilityCollapse2021}.} The resolution used in the
 current work is  $512$ grid points per dimension, comparable to the
@@
 $\eta=10^{-3}$ and another where $\eta=10^{-4}$. As
-in~\citep{quinnEffectAnisotropicViscosity2020}, only background
+in~\citet{quinnEffectAnisotropicViscosity2020}, only background
 resistivity is used. Each pair consists of one simulation
@@
 current in one direction surrounded by \rs{an}{a shell of}
-oppositely-directed current is similar to the \rs{prescribed field in
-chapter~}{current configuration arising due to the field prescribed in} \citep{quinnEffectAnisotropicViscosity2020}.
+oppositely-directed current is similar to the current configuration arising due to the field prescribed in~\citet{quinnEffectAnisotropicViscosity2020}.
 
@@
 instability.}{\rs{fluting}{flute} instability growth.}
-\rs{}{}
-The faster growth of the kink compared \rs{to, say, that of
-  chapter~}{to that measured in}
-\citep{quinnEffectAnisotropicViscosity2020} is \rs{due}{attributed} to
+
+The faster growth of the kink compared to that measured in~
+\citet{quinnEffectAnisotropicViscosity2020} is \rs{due}{attributed} to
 the relative aspect ratios of the flux tubes. The tube prescribed in
-\rs{chapter~}{} \citep{quinnEffectAnisotropicViscosity2020} has an aspect
+\rs{chapter~}{}~\citep{quinnEffectAnisotropicViscosity2020} has an aspect
 ratio of approximately $20$ compared to the tube studied here which
@@
 \bibliographystyle{mnras}
-\bibliography{bib}
+\bibliography{paper}
 
@@
 \rs{The version including the new module}{} can be found at \url{https://github.com/jamiejquinn/Lare3d}, \rs{and also}{has been} archived at~\citep{keith_bennett_2020_4155546}.
-The version of Lare3d used in the production of the results presented here, including initial conditions, boundary conditions, control parameters and the anisotropic viscosity module, can be found in~\citep{keith_bennett_2020_4155625}.
+The version of Lare3d used in the production of the results presented here, including initial conditions, boundary conditions, control parameters and the anisotropic viscosity module, can be found in~\citet{keith_bennett_2020_4155625}.
 The data analysis and instructions for reproducing all results found in this report may be also found at \url{https://github.com/JamieJQuinn/coronal-fluting-instability-analysis} and has been archived~\citep{quinnJamieJQuinnCoronalflutinginstabilityanalysis2021}.

### 2021-12-02 paper.tex
Change fluting to flute everywhere

@@
 The helical kink instability occurs for perturbations where $m=1, k\ne0$ and is the only instability of this form which is a body instability, that is it moves the entire body of the flux tube.
-Perturbations where $m>1$ are termed \rs{fluting}{flute} or interchange instabilities.
+Perturbations where $m>1$ are termed flute or interchange instabilities.
 
 When the magnetic field is sheared, as in a twisted magnetic flux
-tube, an interchange instability (such as the \rs{fluting}{flute}
+tube, an interchange instability (such as the flute
 instability) is confined to a surface where the peaks and troughs
@@
 $r$~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}. This applies
-to both \rs{fluting}{flute} and kink instabilities although many
+to both flute and kink instabilities although many
 additional effects such as line-tying are not incorporated into the
@@
 Additionally, the inclusion of resistivity generally reduces the stabilising effect of the shear, permitting growth of a resistive interchange mode, albeit at a slower rate than that of the ideal instability~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}.
-It will be found that the ideal linear analysis of~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998} is sufficient for understanding the \rs{fluting}{flute} instabilities investigated here since the associated flux tubes adequately fail the criterion~\eqref{eq:suydams_criterion}.
-
-While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal \rs{fluting}{flute} instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\citep[][]{goldstonIntroductionPlasmaPhysics2020}) and is given by
+It will be found that the ideal linear analysis of~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998} is sufficient for understanding the flute instabilities investigated here since the associated flux tubes adequately fail the criterion~\eqref{eq:suydams_criterion}.
+
+While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal flute instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\citep[][]{goldstonIntroductionPlasmaPhysics2020}) and is given by
 \begin{equation}
@@
 The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\citet{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
-This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the \rs{fluting}{flute} instability and the helical kink instability.
+This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the flute instability and the helical kink instability.
 
@@
 \rs{to (potentially) result in the}{and this provides the mechanism of}
-\rs{fluting}{flute} instability \rs{}{excitation}.  The magnitude
+flute instability \rs{}{excitation}.  The magnitude
 of the pressure gradient depends strongly on the value of
@@
 gradients which (as shall be seen) are more stable to the
-\rs{fluting}{flute} instability. Indeed, when $\eta=0$, the radial
+flute instability. Indeed, when $\eta=0$, the radial
 pressure profile is nearly flat and the tube stable to the
-\rs{fluting}{flute} instability.
-
-In all cases unstable to the \rs{fluting}{flute} instability, it
+flute instability.
+
+In all cases unstable to the flute instability, it
 occurs \rs{some time}{} between $t=20$ and $t=30$. \rs{During this
@@
 instability. This initially develops linearly alongside \rs{}{or shortly
-after} the \rs{fluting}{flute} instability and then erupts during the
+after} the flute instability and then erupts during the
 \rs{kink's}{its}  nonlinear phase, dominating the dynamics and
-disrupting the   \rs{fluting}{flute} instability. The \rs{}{onset and
+disrupting the   flute instability. The \rs{}{onset and
 the competition} of the two instabilities is strongly affected by
@@
 \mycaption{Pressure profiles during the development of the
-  \rs{fluting}{flute} and kink instabilities.}{Shown are
+  flute and kink instabilities.}{Shown are
   \rs{slices}{density plots} of pressure \rs{through}{at} $z=0$
@@
 time moments} $t=26$, $28$ and $30$ and \rs{through}{at} $z=0$. At $t=26$
-the tube becomes unstable to \rs{the $m=4$}{} \rs{fluting}{flute}
+the tube becomes unstable to \rs{the $m=4$}{} flute
 instability \rs{}{with azimuthal wavenumber $m=4$}, when the
@@
 appearing \rs{clover-shaped}{taking the shape of a four-leaf clover} (figure~\ref{fig:swi-4_pressure_14}). By
-$t=30$ the kink instability has disrupted the \rs{fluting}{flute}
+$t=30$ the kink instability has disrupted the flute
 instability and is developing nonlinearly
@@
 \rs{}{which will not be illustrated by a separate figure}, the
-\rs{fluting}{flute} instability is present but damped, and \rs{}{it is
+flute instability is present but damped, and \rs{}{it is
   quickly outcompeted by} the kink instability \rs{}{which} quickly dominates the dynamics.
@@
     \end{subfigure}
-\mycaption{Simultaneous development of \rs{fluting}{flute} and kink
+\mycaption{Simultaneous development of flute and kink
   instabilities in the isotropic and \rs{switching}{anisotropic} cases
@@
 Also shown is the velocity driver \rs{as a slice}{$u_r(\sqrt{x^2+y^2})$ at $z=2$}.
-The \rs{fluting}{flute} instability grows in both cases, though faster in the \rs{switching}{anisotropic} case.
+The flute instability grows in both cases, though faster in the \rs{switching}{anisotropic} case.
 The initial stages of the kink instability can also be observed in the field lines of the isotropic case in subfigure~\ref{fig:field_line_plots_iso}.}
@@
 Figure~\ref{fig:kink_field_line_plots} shows the effect the viscosity
-models have on the initial stages of the \rs{fluting}{flute} and kink
-instabilities in 3D. While the \rs{fluting}{flute} instability is
+models have on the initial stages of the flute and kink
+instabilities in 3D. While the flute instability is
 observed in both cases, it is damped in the isotropic case and grows
 faster in the \rs{switching}{anisotropic} case. In the latter case,
-the extended development of the \rs{fluting}{flute} instability
+the extended development of the flute instability
 appears to disrupt the inner core of field lines and, \rs{(as shall be
   seen)}{as will be discussed further below,} slows the growth of the
-kink instability. In the isotropic case, the \rs{fluting}{flute}
+kink instability. In the isotropic case, the flute
 instability has been damped to the extent that the kink instability
@@
     development and measured growth rates \rs{}{$\gamma$ and $\lambda$}
-    of the \rs{fluting}{flute}
+    of the flute
     and kink instabilities, \rs{}{respectively.}}{\rs{Both plots are from results
@@
 
-Despite the \rs{fluting}{flute} instability appearing in the isotropic
+Despite the flute instability appearing in the isotropic
 case (figure~\ref{fig:field_line_plots_iso}), only in the
 \rs{switching}{anisotropic} case can the onset of both the
-\rs{fluting}{flute} and kink instabilities be seen in the kinetic
+flute and kink instabilities be seen in the kinetic
 energy profile \rs{}{shown in} figure~\ref{fig:kink_ke_log-4}. \rs{where}{Here,} the nonlinear
 growth rates of the two instabilities are found to be $\gamma = 0.69$
-for the \rs{fluting}{flute} and $\lambda = 2.55$ for the kink. The
-onset times are approximately $t=27$ for the \rs{fluting}{flute}
+for the flute and $\lambda = 2.55$ for the kink. The
+onset times are approximately $t=27$ for the flute
 instability and \rs{}{$t=29.5$} for
@@
 although the onset times appear similar, and the kinetic energy
-profile shows no evidence of \rs{the growth of the \rs{fluting}{flute}
-instability.}{\rs{fluting}{flute} instability growth.}
+profile shows no evidence of \rs{the growth of the flute
+instability.}{flute instability growth.}
 
@@
     \end{subfigure}
-\mycaption{Stability and linear growth rate of the \rs{fluting}{flute}
+\mycaption{Stability and linear growth rate of the flute
   instability.}{In \rs{}{panel} \ref{fig:suydam_condition_4}, Suydam's stability
@@
     \end{subfigure}
-\mycaption{Perturbations corresponding to the \rs{fluting}{flute} and
+\mycaption{Perturbations corresponding to the flute and
   kink instabilities and the spatial radial distribution of the
   associated resonance function.}{Pressure and velocity perturbations
-  in $z$ (corresponding to the \rs{fluting}{flute} and kink
+  in $z$ (corresponding to the flute and kink
   instabilities, respectively) and of the resonance
@@
 \rs{Figure~\ref{fig:pressure_pert_4} plots the }{The} observed
-  perturbations corresponding to the \rs{fluting}{flute} and kink
+  perturbations corresponding to the flute and kink
   instabilities at $t=26$ \rs{}{are shown in
@@
   radial velocity) through the axis. Comparing the magnitudes of the
-  perturbations at this time suggests the \rs{fluting}{flute}
+  perturbations at this time suggests the flute
   instability is close to transitioning to its nonlinear phase while
@@
 
-Comparing the effect of the viscous models on the perturbations, in the isotropic case, the fluting perturbation is damped, while in the \rs{switching}{anisotropic} case the kink perturbation is diminished, explaining why the \rs{fluting}{flute} instability appears more readily in the \rs{switching}{anisotropic} case (figure~\ref{fig:kink_ke-4}).
+Comparing the effect of the viscous models on the perturbations, in the isotropic case, the fluting perturbation is damped, while in the \rs{switching}{anisotropic} case the kink perturbation is diminished, explaining why the flute instability appears more readily in the \rs{switching}{anisotropic} case (figure~\ref{fig:kink_ke-4}).
 
@@
     \end{subfigure}
-\mycaption{Pressure profiles \rs{through}{at} $z=0$ during the development of the \rs{fluting}{flute} and kink instabilities in the higher resistivity \rs{switching}{anisotropic} case.}{The viscosity model is \rs{switching}{anisotropic} and $\eta = 10^{-3}$.
-In contrast to the case of $\eta=10^{-4}$, the nonlinear development of the \rs{fluting}{flute} instability has time to mix the interior of the flux tube before the onset of the kink instability, the growth of which is affected by the mixed plasma.}
+\mycaption{Pressure profiles \rs{through}{at} $z=0$ during the development of the flute and kink instabilities in the higher resistivity \rs{switching}{anisotropic} case.}{The viscosity model is \rs{switching}{anisotropic} and $\eta = 10^{-3}$.
+In contrast to the case of $\eta=10^{-4}$, the nonlinear development of the flute instability has time to mix the interior of the flux tube before the onset of the kink instability, the growth of which is affected by the mixed plasma.}
 \label{fig:kink_pressure_slices-3}%
@@
   \ref{fig:kink_pressure_slices-3} shows a} prolonged 
-development of the \rs{fluting}{flute} instability and \rs{the}{a} slow
+development of the flute instability and \rs{the}{a} slow
 nonlinear development of the kink \rs{}{instability at the higher
@@
 \rs{when}{at} $\eta=10^{-3}$, the pressure gradient is substantially stronger
-than \rs{when}{at} $\eta=10^{-4}$ and the \rs{fluting}{flute} instability is
+than \rs{when}{at} $\eta=10^{-4}$ and the flute instability is
 excited much earlier. Compared to the $\eta=10^{-4}$ cases, the
@@
 \mycaption{Kinetic energy as a function of time in the cases where $\eta=10^{-3}$.}{The results from both viscosity models are shown.
-The \rs{fluting}{flute} instability appears earlier than where $\eta=10^{-4}$ and the growth rate of the kink instability is decreased.}
+The flute instability appears earlier than where $\eta=10^{-4}$ and the growth rate of the kink instability is decreased.}
 \label{fig:kink_str8_ke-3}%
@@
 
-It is evident from the kinetic energy profile that the \rs{fluting}{flute} instability develops much earlier than in the $\eta=10^{-4}$ cases and grows at an increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}).
-The kink instability grows at a rate of $\lambda \approx 0.15$, much slower than that observed in the $\eta=10^{-4}$ cases, and much lower than the \rs{fluting}{flute} instability.
-One key observation is that, despite the early and disruptive growth of the \rs{fluting}{flute} instability, the kink instability still generates the bulk of the kinetic energy (figure~\ref{fig:kink_ke-3}).
+It is evident from the kinetic energy profile that the flute instability develops much earlier than in the $\eta=10^{-4}$ cases and grows at an increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}).
+The kink instability grows at a rate of $\lambda \approx 0.15$, much slower than that observed in the $\eta=10^{-4}$ cases, and much lower than the flute instability.
+One key observation is that, despite the early and disruptive growth of the flute instability, the kink instability still generates the bulk of the kinetic energy (figure~\ref{fig:kink_ke-3}).
 
@@
 Since the kink instability occurs after the development of the fluting, its growth rate is similarly difficult to gauge.
-Nevertheless, it is clear that the \rs{fluting}{flute} instability grows at a rate of the same order as that in the $\eta=10^{-4}$ cases.
+Nevertheless, it is clear that the flute instability grows at a rate of the same order as that in the $\eta=10^{-4}$ cases.
 It is also apparent that the kink instability grows much slower in the $\eta=10^{-3}$ cases.
@@
 The radius of peak $\gamma$ is calculated at time $t=20$.
-The fluting wavenumber $k$ and observed $r_s$ are measured at times just prior to the nonlinear development of the \rs{fluting}{flute} instability, that is at $t=22$ when $\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$.
+The fluting wavenumber $k$ and observed $r_s$ are measured at times just prior to the nonlinear development of the flute instability, that is at $t=22$ when $\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$.
 The kink wavenumber is measured at $t=26$ in both cases.
@@
 influenced by nonlinear coupling between the $m>1$ and $m=1$ modes, as
-is found in the study of kink and \rs{fluting}{flute}
+is found in the study of kink and flute
 oscillations~\citep{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017}.
@@
 \rs{This set of experiments}{Our set of numerical experiments} has
-shown that the mixing as a result of the nonlinear \rs{fluting}{flute}
+shown that the mixing as a result of the nonlinear flute
 instability appears to slow the growth of the kink instability. \rs{In
@@
   the linear regime} the \rs{linear}{} perturbations of \rs{either}{} the
-\rs{fluting}{flute} \rs{or}{and} kink are able to directly couple, given that
+flute \rs{or}{and} kink are able to directly couple, given that
 the kink instability generally presents at the axis of a flux tube and
-the \rs{fluting}{flute} at some resonant surface away from the
+the flute at some resonant surface away from the
 axis. Further investigation of the nonlinear interaction between the
@@
 
-Since the main driver of the \rs{fluting}{flute} instability is the
+Since the main driver of the flute instability is the
 pressure gradient generated through Ohmic heating, it is prudent to
@@
 conditions for the growth of a 
-\rs{fluting}{flute} instability. \rs{Where}{Indeed, at} $\eta=10^{-4}$ the
-\rs{fluting}{flute} instability was \rs{}{more} quickly \rs{dominated}{outcompeted} by the kink
+flute instability. \rs{Where}{Indeed, at} $\eta=10^{-4}$ the
+flute instability was \rs{}{more} quickly \rs{dominated}{outcompeted} by the kink
 instability and appeared to have little impact on the resultant
@@
 lower values of resistivity would result in flux tubes without any
-significant \rs{fluting}{flute} instability, at least for this form of
+significant flute instability, at least for this form of
 driver and mechanism of pressure generation. Regardless, coronal loops
@@
 observed~\citep{foukalTemperatureStructurePressure1975}, and such loops
-may be unstable to the \rs{fluting}{flute} instability. Modelling of a
-prescribed \rs{fluting}{flute}-unstable flux tube, as opposed to the dynamically
+may be unstable to the flute instability. Modelling of a
+prescribed flute-unstable flux tube, as opposed to the dynamically
 stressed loop investigated here, would provide a useful comparison to
@@
 \rs{These}{While our} results show that a flux tube can be unstable to
-the \rs{fluting}{flute} instability and yet the faster growing kink
+the flute instability and yet the faster growing kink
 instability can quickly dominate when the pressure gradient is small
 enough\rs{. However}{}, the opposite case is also observed\rs{,
-  where}{. A faster} growing \rs{fluting}{flute} instability appears to slow the growth of
+  where}{. A faster} growing flute instability appears to slow the growth of
 the kink instability although, importantly, it does not fully disrupt
@@
 nonlinear growth rates of the two instabilities is important \rs{in
-understanding}{for prediction of} whether the \rs{fluting}{flute} instability may be found
+understanding}{for prediction of} whether the flute instability may be found
 at all in the real solar corona, or whether \rs{a}{its} realistic growth rate is
@@
 This \rs{chapter}{paper} details the nonlinear development of two
-ideal instabilities, the kink and \rs{}{the} \rs{fluting}{flute} instabilities,
+ideal instabilities, the kink and \rs{}{the} flute instabilities,
 both of which develop naturally in the course of twisting an initially
@@
 kink instability excited due to the twist in the field, \rs{}{but also
-and near simultaneously} a pressure-driven \rs{fluting}{flute}
+and near simultaneously} a pressure-driven flute
 instability can also be excited in unstable pressure gradients
@@
 initial and important first step \rs{into the simulation of}{towards
-understanding} nonlinear \rs{fluting}{flute} instabilities in the
+understanding} nonlinear flute instabilities in the
 solar corona.
 
-It has been shown that the \rs{fluting}{flute} instability can be quickly dominated by the kink instability if the kink grows substantially faster than the \rs{fluting}{flute}.
-However, if the \rs{fluting}{flute} has time to develop nonlinearly, it mixes the plasma within the flux tube, generating small scale current sheets and releasing some magnetic energy.
+It has been shown that the flute instability can be quickly dominated by the kink instability if the kink grows substantially faster than the flute.
+However, if the flute has time to develop nonlinearly, it mixes the plasma within the flux tube, generating small scale current sheets and releasing some magnetic energy.
 The overall effect of this mixing is to slow the growth of the kink instability.
@@
 The form of viscosity has been found to significantly affect the
-growth of the \rs{fluting}{flute} instability. Importantly, isotropic
-viscosity is found to damp the growth of the \rs{fluting}{flute}
+growth of the flute instability. Importantly, isotropic
+viscosity is found to damp the growth of the flute
 instability to the degree that it is unable to grow appreciably before
@@
 
-These numerical experiments have provided evidence that the \rs{fluting}{flute} instability can occur in twisted magnetic flux ropes and grow at similar rates to the kink instability.
-Further estimation of the relative growth rates in more realistic coronal loop setups is required to fully understand if the \rs{fluting}{flute} instability plays a pertinent role in coronal loop physics.
+These numerical experiments have provided evidence that the flute instability can occur in twisted magnetic flux ropes and grow at similar rates to the kink instability.
+Further estimation of the relative growth rates in more realistic coronal loop setups is required to fully understand if the flute instability plays a pertinent role in coronal loop physics.
 

### 2021-12-02 paper.tex
Remove more \rs

@@
 perpendicular to the direction of the field, \rs{}{known as the
-  ``resonance surface''}. \rs{which in}{In} an axisymmetric twisted
-flux tube \rs{}{the resonance surface} is located at a radius $r$
+  ``resonance surface''}. In an axisymmetric twisted
+flux tube the resonance surface is located at a radius $r$
 given by
@@
 the form~\eqref{eq:kink_perturbation} is given by the classical
-\rs{}{Suydam's criterion~\citep{suydamStabilityLinearPinch1958}}
+Suydam's criterion~\citep{suydamStabilityLinearPinch1958}
 \begin{equation}
@@
 B_{\theta}$ is the safety factor for a flux tube of length $L$ and a
-\rs{dash}{prime} denotes differentiation with respect to
+prime denotes differentiation with respect to
 $r$~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}. This applies
@@
 corresponding linear analysis. The effect of line-tying on the kink
-instability \rs{can be found}{is investigated}
+instability is investigated
 in~\citet{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion}
@@
 by~\eqref{eq:resonant_surface}. 
-\rs{}{When} Suydam's criterion is satisfied and the flux tube is linearly stable, it may still be unstable to non-local perturbations, where the shear and pressure are small enough that interchange perturbations do not need to satisfy~\eqref{eq:resonant_surface}.
+When Suydam's criterion is satisfied and the flux tube is linearly stable, it may still be unstable to non-local perturbations, where the shear and pressure are small enough that interchange perturbations do not need to satisfy~\eqref{eq:resonant_surface}.
 Additionally, the inclusion of resistivity generally reduces the stabilising effect of the shear, permitting growth of a resistive interchange mode, albeit at a slower rate than that of the ideal instability~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}.
@@
 
-Throughout this \rs{chapter}{paper}, the twisted flux tube generated by the drivers has a pressure profile which is approximately axisymmetric, and independent of $z$ away from the boundaries at $z=\pm2$, and has a negative gradient, hence $|\nabla p|$ may be written as $-d p/ dr$.
+Throughout this paper, the twisted flux tube generated by the drivers has a pressure profile which is approximately axisymmetric, and independent of $z$ away from the boundaries at $z=\pm2$, and has a negative gradient, hence $|\nabla p|$ may be written as $-d p/ dr$.
 Similarly, away from the boundaries, the magnetic field has a negligible $r$ component and little dependence on $\theta$ and $z$, allowing the field to be approximated as $\vec{B} = (0, B_{\theta}(r), B_z(r))^{\text{T}}$, in cylindrical coordinates $(r, \theta, z)$.
@@
   \label{eq:fluting_growth_rate2}
-\gamma_{\rs{{ideal}}{\text{ideal}}}^2 = \frac{-2p'}{\rho R_c}.
-\end{equation}
-This \rs{growth rate remains applicable}{approximation for the growth rate continues to hold} while the flux tube remains relatively axisymmetric, that is while the kink instability remains in its linear phase.
+\gamma_{\text{ideal}}^2 = \frac{-2p'}{\rho R_c}.
+\end{equation}
+This approximation for the growth rate continues to hold while the flux tube remains relatively axisymmetric, that is while the kink instability remains in its linear phase.
 
@@
 
-\section{\rs{Numerical setup}{Mathematical formulation and numerical setup}}
+\section{Mathematical formulation and numerical setup}
 \label{sec-numerical-setup}
 
-\rs{Lare3d numerically solves}{We consider} the
-\rs{MHD}{magnetohydrodynamic} equations for the density $\rho$, plasma
+We consider the
+magnetohydrodynamic equations for the density $\rho$, plasma
 velocity $\vec{u}$, pressure $p$, magnetic field $\vec{B}$ and
@@
 where $\eta$ is the non-dimensionalised resistivity,
-$\rs{\jmath}{\vec{\jmath}} = \nabla \times \vec{B}$ is the current
+$\vec{\jmath} = \nabla \times \vec{B}$ is the current
 density and \rs{$\ten{\sigma}$ is the viscous stress tensor (described
@@
 \end{equation}
-\rs{where}{with} the specific heat ratio is given by $\gamma = 5/3$.
+with the specific heat ratio is given by $\gamma = 5/3$.
 
@@
   \label{eq:isotropic_viscous_tensor}
-  \ten{\sigma}_{\rs{{iso}}{\text{iso}}} = \nu \ten{W},
+  \ten{\sigma}_{\text{iso}} = \nu \ten{W},
 \end{equation}
@@
 is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$
-identity matrix. We use an identical model of anisotropic viscosity \rs{as}{to}
+identity matrix. We use an identical model of anisotropic viscosity to
 that used in
-\rs{our previous work~\citep{quinnEffectAnisotropicViscosity2020}}{previous work~\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}},
+previous work~\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021},
  the switching model, first presented
@@
  anisotropic component, since there are no null points present in the
- \rs{simulations}{simulations reported here} at any point. To this
+ simulations reported here at any point. To this
  end, we set the switching parameter (which controls the degree of
  viscous anisotropy) to $a_0 = 150$ in Lare3d's control, a value
- sufficiently large \rs{}{so} that the anisotropic viscous stress tensor is given by
+ sufficiently large so that the anisotropic viscous stress tensor is given by
 \begin{equation}
@@
   \label{eq:isotropic_viscous_tensor}
-\rs{}{\ten{\sigma} = }\ten{\sigma}_{\rs{{iso}}{\text{iso}}} = \nu \ten{W},
+\ten{\sigma = }\ten{\sigma}_{\text{iso}} = \nu \ten{W},
 \end{equation}
@@
 is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$
-identity \rs{}{tensor. The second model, which is the one of actual interest, is the} anisotropic viscosity stress
+identity tensor. The second model, which is the one of actual interest, is the anisotropic viscosity stress
 tensor given by
@@
 \end{equation}
-in a cube of \rs{dimension}{size} $[-2,2]^3$, with further test simulations run using an elongated domain of size $4\times4\times20$. \rs{The}{Initially, the} velocity is set
+in a cube of size $[-2,2]^3$, with further test simulations run using an elongated domain of size $4\times4\times20$. Initially, the velocity is set
 everywhere to $\vec{u} = \vec{0}$, the density to $\rho = 1$,
-\rs{}{and} the
+and the
 internal energy to $\varepsilon = 8.67\times 10^{-4}$. This corresponds
 to a typical coronal temperature of $10^6$ K and a plasma beta of $1.11 \times 10^{-4}$. At the
-boundaries, the magnetic field, \rs{}{velocity,} density, and energy are fixed to their
+boundaries, the magnetic field, velocity, density, and energy are fixed to their
 initial values \rs{}{and their derivatives normal to the
-boundaries are set to zero} \rs{and the velocity to zero}{} except
-\rs{the boundaries}{where twisting velocity ``driver''}, described
+boundaries are set to zero}  except
+where twisting velocity ``driver'', described
 below, is prescribed.
@@
   \mycaption{Radial velocity profile $u_r(r)$ and acceleration profile
-    $u_t(t)$ of the driver \rs{}{\eqref{eq:null_twisting_profile}} for
+    $u_t(t)$ of the driver \eqref{eq:null_twisting_profile} for
     parameters $u_0 = 0.15$, $r_d = 5$ and $t_r = 2$.}{} 
@@
 This form of driver allows the system to be accelerated slowly enough that the production of disruptive shocks and fast waves is minimal.
-It is unavoidable that some waves are produced during the boundary acceleration, however these usefully provide \rs{one}{a} source of noise which eventually forms a perturbation.
+It is unavoidable that some waves are produced during the boundary acceleration, however these usefully provide a source of noise which eventually forms a perturbation.
 \rs{}{
@@
 using isotropic viscosity~\eqref{eq:isotropic_viscous_tensor} and
-another one using the \rs{switching}{anisotropic} model~\eqref{eq:switching_model}. The
+another one using the anisotropic model~\eqref{eq:switching_model}. The
 value of viscosity is set to $\nu = 10^{-4}$ in all cases.} 
 %
-The overall development of both \rs{}{the flute and the kink}
+The overall development of both the flute and the kink
 instabilities is broadly similar for the two values of resistivity and
@@
 Focus is
-then placed on the \rs{development of}{detailed description of instabilities in} the
-$\eta=10^{-4}$ cases, \rs{comparing the results}{with the aim of comparing the effects} of the two
+then placed on the detailed description of instabilities in the
+$\eta=10^{-4}$ cases, with the aim of comparing the effects of the two
 viscosity models. \rs{These cases illustrate the development of the instabilities while showcasing the effect of the
-viscosity models.}{} Then \rs{differences apparent in}{further features of} the $\eta=10^{-3}$
+viscosity models.}{} Then further features of the $\eta=10^{-3}$
 cases are summarised. \rs{without a full exploration of the (qualitatively
@@
       (b) and pressure (c) as functions of the radial distance from
-      the tube axis.}{} All plots are from \rs{switching}{anisotropic}
+      the tube axis.}{} All plots are from anisotropic
     cases when $t=20$ through the plane $z=0$. Note the sign of the
@@
     profile of an additional test-case where $\eta=0$ is also
-    shown. \rs{}{Line types are indicated in the legend.}}%
+    shown. Line types are indicated in the legend.}%
   \label{fig:pressure_and_heating}
@@
 twisting at the upper and lower boundaries gives rise to a pair of}
-torsional Alfv\'en waves which \rs{}{proceed to} travel along the tube
-from the upper and lower boundaries to \rs{the}{their respective}
+torsional Alfv\'en waves which proceed to travel along the tube
+from the upper and lower boundaries to their respective
 opposite boundaries. The interaction between these waves produces an 
@@
 approximately $4$ Alfv\'en times, equal to the time taken for an
-Alfv\'en wave to \rs{travel}{traverse} the entire length of the domain
-\rs{}{as} visible early in figure~\ref{fig:kink_ke-4}.
+Alfv\'en wave to traverse the entire length of the domain
+as visible early in figure~\ref{fig:kink_ke-4}.
 
 As the field continues to be twisted, currents form, due to the local
-shear in the magnetic field, \rs{which}{and} heat the plasma through Ohmic
-\rs{heating}{dissipation}. Due to the radial form of the driver, the magnitude of the
+shear in the magnetic field, and heat the plasma through Ohmic
+dissipation. Due to the radial form of the driver, the magnitude of the
 current density is greatest at the axis of the tube, then decreases
-radially outwards \rs{}{as seen in} figure~\ref{fig:current_profiles}. The orientation
-of the twisting produces a current \rs{directed}{flowing} in the negative
+radially outwards as seen in figure~\ref{fig:current_profiles}. The orientation
+of the twisting produces a current flowing in the negative
 $z$-direction for $r\lessapprox0.5$. At $r \approx 0.5$ (corresponding
-to the radius of peak driving velocity) the current switches \rs{direction}{orientation}
+to the radius of peak driving velocity) the current switches orientation
 and is in the positive $z$-direction in a shell where $0.5\lessapprox
-r \lessapprox 0.8$. This form of \rs{}{a} twisted field with an inner core of
-current in one direction surrounded by \rs{an}{a shell of}
+r \lessapprox 0.8$. This form of a twisted field with an inner core of
+current in one direction surrounded by a shell of
 oppositely-directed current is similar to the current configuration arising due to the field prescribed in~\citet{quinnEffectAnisotropicViscosity2020}.
@@
 which competes against the binding action of the magnetic tension
-\rs{to (potentially) result in the}{and this provides the mechanism of}
-flute instability \rs{}{excitation}.  The magnitude
+and this provides the mechanism of
+flute instability excitation.  The magnitude
 of the pressure gradient depends strongly on the value of
-\rs{}{resistivity} $\eta$, with lower values producing shallower 
+resistivity $\eta$, with lower values producing shallower 
 gradients which (as shall be seen) are more stable to the
@@
 In all cases unstable to the flute instability, it
-occurs \rs{some time}{} between $t=20$ and $t=30$. \rs{During this
+occurs  between $t=20$ and $t=30$. \rs{During this
   time, the}{The} continued driving at the boundaries eventually
@@
 after} the flute instability and then erupts during the
-\rs{kink's}{its}  nonlinear phase, dominating the dynamics and
+its  nonlinear phase, dominating the dynamics and
 disrupting the   flute instability. The \rs{}{onset and
@@
 
-\subsection{\rs{Development where}{Instabilities at resistivity} $\eta=10^{-4}$}
+\subsection{Instabilities at resistivity $\eta=10^{-4}$}
 
@@
   flute and kink instabilities.}{Shown are
-  \rs{slices}{density plots} of pressure \rs{through}{at} $z=0$
-  \rs{where}{with} $\eta = 10^{-4}$ 
-  and \rs{the viscosity model is \rs{switching}{anisotropic}}{for the
-    anisotropic viscosity model}. Note the difference in colour scale
+  density plots of pressure at $z=0$
+  with $\eta = 10^{-4}$ 
+  and for the anisotropic viscosity model}. Note the difference in colour scale
   in figure~\ref{fig:swi-4_pressure_15}. The development in the
-  isotropic case is similar.} 
+  isotropic case is similar. 
 \label{fig:kink_pressure_slices-4}%
@@
   kink instabilities in case of resistivity $\eta=10^{-4}$.}
-\rs{The}{Figure}~\ref{fig:kink_pressure_slices-4} shows the pressure profile
+Figure~\ref{fig:kink_pressure_slices-4} shows the pressure profile
 \rs{the viscosity model is switching for times}{of the \rs{switching}{anisotropic} viscosity case 
 \eqref{eq:switching_model} at
-time moments} $t=26$, $28$ and $30$ and \rs{through}{at} $z=0$. At $t=26$
-the tube becomes unstable to \rs{the $m=4$}{} flute
-instability \rs{}{with azimuthal wavenumber $m=4$}, when the
-plasma begins to \rs{(slightly)}{} bulge out diagonally from the
+time moments} $t=26$, $28$ and $30$ and at $z=0$. At $t=26$
+the tube becomes unstable to  flute
+instability with azimuthal wavenumber $m=4$, when the
+plasma begins to  bulge out diagonally from the
 high-pressure core as seen in figure~\ref{fig:swi-4_pressure_13}. As  
@@
 expand and accelerate, resulting in the entire pressure structure
-appearing \rs{clover-shaped}{taking the shape of a four-leaf clover} (figure~\ref{fig:swi-4_pressure_14}). By
+appearing taking the shape of a four-leaf clover (figure~\ref{fig:swi-4_pressure_14}). By
 $t=30$ the kink instability has disrupted the flute
 instability and is developing nonlinearly
-\rs{}{as evident in} figure~\ref{fig:swi-4_pressure_15}. As is typical of nonlinear kink
+as evident in figure~\ref{fig:swi-4_pressure_15}. As is typical of nonlinear kink
 development, the tube continues to release its stored potential energy
-\rs{as}{in the form of} kinetic energy and heat and the contained plasma becomes highly
-mixed. In the \rs{unseen}{} isotropic \rs{}{viscosity} case
-\rs{}{which will not be illustrated by a separate figure}, the
+in the form of kinetic energy and heat and the contained plasma becomes highly
+mixed. In the  isotropic viscosity case
+which will not be illustrated by a separate figure, the
 flute instability is present but damped, and \rs{}{it is
-  quickly outcompeted by} the kink instability \rs{}{which} quickly dominates the dynamics.
+  quickly outcompeted by} the kink instability which quickly dominates the dynamics.
 
@@
       \includegraphics[width=\linewidth]{field_line_plots/cropped/v-4r-4-switching_0014_cropped.png}
-      \caption{\rs{Switching}{Anisotropic}}
+      \caption{Anisotropic}
       \label{fig:field_line_plots_swi}
@@
 \mycaption{Simultaneous development of flute and kink
-  instabilities in the isotropic and \rs{switching}{anisotropic} cases
-  \rs{as}{illustrated by} field lines and pressure contours.}{Field
+  instabilities in the isotropic and anisotropic cases
+  illustrated by field lines and pressure contours.}{Field
   lines and contours of pressure (where $p=0.3$) are plotted at
@@
 Also shown is the velocity driver \rs{as a slice}{$u_r(\sqrt{x^2+y^2})$ at $z=2$}.
-The flute instability grows in both cases, though faster in the \rs{switching}{anisotropic} case.
+The flute instability grows in both cases, though faster in the anisotropic case.
 The initial stages of the kink instability can also be observed in the field lines of the isotropic case in subfigure~\ref{fig:field_line_plots_iso}.}
@@
 observed in both cases, it is damped in the isotropic case and grows
-faster in the \rs{switching}{anisotropic} case. In the latter case,
+faster in the anisotropic case. In the latter case,
 the extended development of the flute instability
@@
   \mycaption{Kinetic energy as a function of time showing the
-    development and measured growth rates \rs{}{$\gamma$ and $\lambda$}
+    development and measured growth rates $\gamma$ and $\lambda$
     of the flute
-    and kink instabilities, \rs{}{respectively.}}{\rs{Both plots are from results
+    and kink instabilities, respectively.}{\rs{Both plots are from results
       where}{Resistivity is $\eta=10^{-4}$ and the second plot is a
@@
 case (figure~\ref{fig:field_line_plots_iso}), only in the
-\rs{switching}{anisotropic} case can the onset of both the
+anisotropic case can the onset of both the
 flute and kink instabilities be seen in the kinetic
-energy profile \rs{}{shown in} figure~\ref{fig:kink_ke_log-4}. \rs{where}{Here,} the nonlinear
+energy profile shown in figure~\ref{fig:kink_ke_log-4}. Here, the nonlinear
 growth rates of the two instabilities are found to be $\gamma = 0.69$
@@
 onset times are approximately $t=27$ for the flute
-instability and \rs{}{$t=29.5$} for
+instability and $t=29.5$ for
 the kink. In the isotropic case, the growth rate of the kink, $\lambda
-= 2.97$, is larger than in the \rs{switching}{anisotropic} case,
+= 2.97$, is larger than in the anisotropic case,
 although the onset times appear similar, and the kinetic energy
@@
 The faster growth of the kink compared to that measured in~
-\citet{quinnEffectAnisotropicViscosity2020} is \rs{due}{attributed} to
+\citet{quinnEffectAnisotropicViscosity2020} is attributed to
 the relative aspect ratios of the flux tubes. The tube prescribed in
-\rs{chapter~}{}~\citep{quinnEffectAnisotropicViscosity2020} has an aspect
+~\citep{quinnEffectAnisotropicViscosity2020} has an aspect
 ratio of approximately $20$ compared to the tube studied here which
@@
 $t\approx20$) the small aspect ratio results in more turns per unit
-length, \rs{resulting in}{leading to} a faster growing instability.
+length, leading to a faster growing instability.
 
@@
 \mycaption{Stability and linear growth rate of the flute
-  instability.}{In \rs{}{panel} \ref{fig:suydam_condition_4}, Suydam's stability
-  criterion \rs{}{\eqref{eq:suydams_criterion}} and is contributing
-  terms \rs{(LHS of~\eqref{eq:suydams_criterion})}{}  are plotted and in
-  \rs{}{panel} \ref{fig:growth_rate_4} the predicted linear growth rate~\eqref{eq:fluting_growth_rate2} is plotted.
-Both plots are produced at $t=20$ for $\eta=10^{-4}$ and using the \rs{switching}{anisotropic} model.
+  instability.}{In panel \ref{fig:suydam_condition_4}, Suydam's stability
+  criterion \eqref{eq:suydams_criterion} and is contributing
+  terms   are plotted and in
+  panel \ref{fig:growth_rate_4} the predicted linear growth rate~\eqref{eq:fluting_growth_rate2} is plotted.
+Both plots are produced at $t=20$ for $\eta=10^{-4}$ and using the anisotropic model.
 The location of the peak linear growth rate is also shown.}
@@
   instabilities, respectively) and of the resonance
-  \rs{function}{surface} $m B_{\theta}(r)/r + kB_z(r)$ as a function
+  surface $m B_{\theta}(r)/r + kB_z(r)$ as a function
   of $r$ using the observed fluting perturbation wavenumbers. All
-  plots are \rs{from}{} snapshots at $t=26$ where $\eta=10^{-4}$ and
-  the viscosity model is \rs{switching}{anisotropic}.} 
+  plots are  snapshots at $t=26$ where $\eta=10^{-4}$ and
+  the viscosity model is anisotropic.} 
 \label{fig:k_and_resonance}%
@@
 
-\rs{Figure~\ref{fig:pressure_pert_4} plots the }{The} observed
+The observed
   perturbations corresponding to the flute and kink
@@
 The value of $k$ for each perturbation is calculated as $k = 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the perturbation, measured as the difference between the two peaks closest to $z=0$ (thus minimising the influence of line-tying on the measurement).
-This gives a value of $k_{\rs{flute}{\text{flute}}}=23.61$ and $k_{\rs{kink}{\text{kink}}}=4.57$ for both viscosity models.
+This gives a value of $k_{\text{flute}}=23.61$ and $k_{\text{kink}}=4.57$ for both viscosity models.
 Hence, the observed most unstable fluting perturbation is that of the form~\eqref{eq:kink_perturbation} where $m=4$ and $k=23.61$ and the observed kink instability is that where $m=1$ and $k=4.57$.
@@
 
-Comparing the effect of the viscous models on the perturbations, in the isotropic case, the fluting perturbation is damped, while in the \rs{switching}{anisotropic} case the kink perturbation is diminished, explaining why the flute instability appears more readily in the \rs{switching}{anisotropic} case (figure~\ref{fig:kink_ke-4}).
-
-\subsection{\rs{Development where}{Instabilities at resistivity} $\eta=10^{-3}$}
+Comparing the effect of the viscous models on the perturbations, in the isotropic case, the fluting perturbation is damped, while in the anisotropic case the kink perturbation is diminished, explaining why the flute instability appears more readily in the anisotropic case (figure~\ref{fig:kink_ke-4}).
+
+\subsection{Instabilities at resistivity $\eta=10^{-3}$}
 
@@
     \end{subfigure}
-\mycaption{Pressure profiles \rs{through}{at} $z=0$ during the development of the flute and kink instabilities in the higher resistivity \rs{switching}{anisotropic} case.}{The viscosity model is \rs{switching}{anisotropic} and $\eta = 10^{-3}$.
+\mycaption{Pressure profiles at $z=0$ during the development of the flute and kink instabilities in the higher resistivity anisotropic case.}{The viscosity model is anisotropic and $\eta = 10^{-3}$.
 In contrast to the case of $\eta=10^{-4}$, the nonlinear development of the flute instability has time to mix the interior of the flux tube before the onset of the kink instability, the growth of which is affected by the mixed plasma.}
@@
   \ref{fig:kink_pressure_slices-3} shows a} prolonged 
-development of the flute instability and \rs{the}{a} slow
+development of the flute instability and a slow
 nonlinear development of the kink \rs{}{instability at the higher
   resistivity value $\eta=10^{-3}$ in the case of anisotropic viscosity}. Due to the enhanced Ohmic heating 
-\rs{when}{at} $\eta=10^{-3}$, the pressure gradient is substantially stronger
-than \rs{when}{at} $\eta=10^{-4}$ and the flute instability is
+at $\eta=10^{-3}$, the pressure gradient is substantially stronger
+than at $\eta=10^{-4}$ and the flute instability is
 excited much earlier. Compared to the $\eta=10^{-4}$ cases, the
 instability occurs further from the axis, at $r\approx0.16$, and the
-larger pressure gradient drives the bulges \rs{}{in profile} further
-from the axis \rs{in}{during} the nonlinear phase
+larger pressure gradient drives the bulges in profile further
+from the axis during the nonlinear phase
 (figure~\ref{fig:swi-3_pressure_12}). These bulges continue to extend
@@
 $\eta=10^{-4}$ cases, the nonlinear development of the kink was
-\rs{further along}{at a later stage of its development} (figure~\ref{fig:swi-4_pressure_15}). The development of
+at a later stage of its development (figure~\ref{fig:swi-4_pressure_15}). The development of
 the kink then proceeds slowly as it moves the axis of the tube through
@@
 of flux tube (as was observed in
-\rs{chapter}{our earlier work}~\citep{quinnEffectAnisotropicViscosity2020}).
+our earlier work~\citep{quinnEffectAnisotropicViscosity2020}).
 
@@
 \midrule
-\rs{Predicted linear}{Theoretical average linear growth rate of flute} $\gamma$ & 0.86 & 1.79  \\
-Observed nonlinear \rs{}{growth rate of flute} $\gamma$ & 0.69 & 1.06  \\
-Observed \rs{}{growth rate of kink} $\lambda$ & 2.55 & 0.15\\
+Theoretical average linear growth rate of flute $\gamma$ & 0.86 & 1.79  \\
+Observed nonlinear growth rate of flute $\gamma$ & 0.69 & 1.06  \\
+Observed growth rate of kink $\lambda$ & 2.55 & 0.15\\
 \midrule
-\rs{}{Theoretical} radius $r_s$ of peak \rs{$\gamma$}{flute growth rate} & 0.125 & 0.163 \\
-Observed \rs{}{radius} $r_s$ \rs{}{of peak flute growth rate} & 0.125 & 0.163 \\
+Theoretical radius $r_s$ of peak flute growth rate & 0.125 & 0.163 \\
+Observed radius $r_s$ of peak flute growth rate & 0.125 & 0.163 \\
 \midrule
-Observed \rs{}{axial wave number} $k_{\rs{flute}{\text{flute}}}$ & 23.61 & 16.05 \\
-Observed \rs{}{axial wave number} $k_{\rs{kink}{\text{kink}}}$ & 4.57 & 4.53 \\
+Observed axial wave number $k_{\text{flute}}$ & 23.61 & 16.05 \\
+Observed axial wave number $k_{\text{kink}}$ & 4.57 & 4.53 \\
 \end{tabular}
@@
   resistivity} $\eta$.
-All values are calculated from simulations using the \rs{switching}{anisotropic} model with the exception of $k_{\rs{kink}{\text{kink}}}$ which is measured from isotropic results due to noise in the \rs{switching}{anisotropic} case (the value of $k_{\rs{kink}{\text{kink}}}$ appears similar, however).
+All values are calculated from simulations using the anisotropic model with the exception of $k_{\text{kink}}$ which is measured from isotropic results due to noise in the anisotropic case (the value of $k_{\text{kink}}$ appears similar, however).
 The results of the isotropic cases are qualitatively similar.
@@
 
-The longitudinal wavenumber $k_{\rs{kink}{\text{kink}}}$ of the observed kink perturbation remains similar in both cases since the instability is essentially governed by the twist injected by the driver which remains the same in both cases.
-In contrast, the longitudinal wavenumber $k_{\rs{flute}{\text{flute}}}$ of the observed fluting perturbation is lower in the $\eta=10^{-3}$ cases.
+The longitudinal wavenumber $k_{\text{kink}}$ of the observed kink perturbation remains similar in both cases since the instability is essentially governed by the twist injected by the driver which remains the same in both cases.
+In contrast, the longitudinal wavenumber $k_{\text{flute}}$ of the observed fluting perturbation is lower in the $\eta=10^{-3}$ cases.
 This is due to the different resonant surface within which the perturbation grows, the location being dictated by the peak of the linear growth rate.
@@
 
-\rs{Due to the perturbations arising from numerical noise, it}{It} is
-likely that the $m=4$ \rs{}{azimuthal} perturbation is excited due to
+It is
+likely that the $m=4$ azimuthal perturbation is excited due to
 influences from the boundaries in the Cartesian box, for example
@@
 
-\rs{This set of experiments}{Our set of numerical experiments} has
+Our set of numerical experiments has
 shown that the mixing as a result of the nonlinear flute
@@
   the linear regime it seems unlikely that}{It seems unlikely that in
-  the linear regime} the \rs{linear}{} perturbations of \rs{either}{} the
-flute \rs{or}{and} kink are able to directly couple, given that
+  the linear regime} the  perturbations of  the
+flute and kink are able to directly couple, given that
 the kink instability generally presents at the axis of a flux tube and
@@
 ask if the same pressure gradient could be generated using physical
-coronal values of the resistivity, \rs{of}{which are estimated to be}
+coronal values of the resistivity, which are estimated to be
 approximately
 $\eta=10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a},
-\rs{which are}{and are thus} much smaller than those studied
+and are thus much smaller than those studied
 here. Additionally, the simulations presented here do not incorporate
-radiation or thermal \rs{conductivity}{conduction}, two processes which would remove
-energy (and \rs{thus}{hence} reduce pressure) from high-pressure regions in a coronal
-loop and thus could \rs{remove}{prevent meeting} the required
+radiation or thermal conduction, two processes which would remove
+energy (and hence reduce pressure) from high-pressure regions in a coronal
+loop and thus could prevent meeting the required
 conditions for the growth of a 
-flute instability. \rs{Where}{Indeed, at} $\eta=10^{-4}$ the
-flute instability was \rs{}{more} quickly \rs{dominated}{outcompeted} by the kink
+flute instability. Indeed, at $\eta=10^{-4}$ the
+flute instability was more quickly outcompeted by the kink
 instability and appeared to have little impact on the resultant
@@
 
-\rs{These}{While our} results show that a flux tube can be unstable to
+While our results show that a flux tube can be unstable to
 the flute instability and yet the faster growing kink
 instability can quickly dominate when the pressure gradient is small
-enough\rs{. However}{}, the opposite case is also observed\rs{,
+enough, the opposite case is also observed\rs{,
   where}{. A faster} growing flute instability appears to slow the growth of
@@
 understanding}{for prediction of} whether the flute instability may be found
-at all in the real solar corona, or whether \rs{a}{its} realistic growth rate is
+at all in the real solar corona, or whether its realistic growth rate is
 too slow compared to that of the kink instability.
@@
 
-This \rs{chapter}{paper} details the nonlinear development of two
-ideal instabilities, the kink and \rs{}{the} flute instabilities,
+This paper details the nonlinear development of two
+ideal instabilities, the kink and the flute instabilities,
 both of which develop naturally in the course of twisting an initially
@@
 generated by Ohmic heating. Simulations 
-were \rs{run}{performed} \rs{over}{with} two values of resistivity,
+were performed with two values of resistivity,
 $\eta=10^{-3}$ and $10^{-4}$, and for two forms of viscosity, isotropic and
@@
 the onset of the faster growing nonlinear kink instability. Overall,
-the \rs{switching}{anisotropic} model permits greater release of
-kinetic energy. Similar to \rs{chapter}{}
+the anisotropic model permits greater release of
+kinetic energy. Similar to 
 \citep{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating
-is found to be \rs{significantly lower}{lower} than anisotropic (switching)
+is found to be lower than anisotropic (switching)
 viscous heating, by approximately two orders of magnitude.
@@
 A custom version of Lare3d~\citep{arberStaggeredGridLagrangian2001} has been developed where a new module for anisotropic viscosity has been included.
-\rs{The version including the new module}{} can be found at \url{https://github.com/jamiejquinn/Lare3d}, \rs{and also}{has been} archived at~\citep{keith_bennett_2020_4155546}.
+The version including the new module can be found at \url{https://github.com/jamiejquinn/Lare3d}, and has been archived at~\citep{keith_bennett_2020_4155546}.
 The version of Lare3d used in the production of the results presented here, including initial conditions, boundary conditions, control parameters and the anisotropic viscosity module, can be found in~\citet{keith_bennett_2020_4155625}.

### 2021-12-02 paper.tex
Remove all \rs commands

@@
 \end{equation}
-where $m$ and $k$ are the wavenumbers \rs{in the $\theta$ and $z$
-  directions, respectively}{in the azimuthal and axial directions,
+where $m$ and $k$ are the wavenumbers in the azimuthal and axial directions,
   $\theta$ and $z$, respectively and $r$ is the radial coordinate in
-  cylindrical polars}. 
+  cylindrical polars. 
 The helical kink instability occurs for perturbations where $m=1, k\ne0$ and is the only instability of this form which is a body instability, that is it moves the entire body of the flux tube.
@@
 the surface where the perturbation wavevector $(0, m/r, k)$ is
-perpendicular to the direction of the field, \rs{}{known as the
-  ``resonance surface''}. In an axisymmetric twisted
+perpendicular to the direction of the field, known as the
+  ``resonance surface''. In an axisymmetric twisted
 flux tube the resonance surface is located at a radius $r$
@@
 
-Throughout this paper, the twisted flux tube generated by the drivers has a pressure profile which is approximately axisymmetric, and independent of $z$ away from the boundaries at $z=\pm2$, and has a negative gradient, hence $|\nabla p|$ may be written as $-d p/ dr$.
-Similarly, away from the boundaries, the magnetic field has a negligible $r$ component and little dependence on $\theta$ and $z$, allowing the field to be approximated as $\vec{B} = (0, B_{\theta}(r), B_z(r))^{\text{T}}$, in cylindrical coordinates $(r, \theta, z)$.
-For a twisted field of this form, the radius of curvature is given by
-\begin{equation}
-  \label{eq:radius_of_curvature}
-  R_c = \frac{1}{|(\vec{b}\cdot\nabla) \vec{b}|} = \frac{r}{b_{\theta}^2},
-\end{equation}
-where $\vec{b} = \vec{B}/|\vec{B}|$ is the unit vector in the direction of the magnetic field and $b_{\theta}$ is the component of $\vec{b}$ in the azimuthal direction.
-These approximations allows the growth rate to be written as
-\begin{equation}
-  \label{eq:fluting_growth_rate2}
-\gamma_{\text{ideal}}^2 = \frac{-2p'}{\rho R_c}.
-\end{equation}
-This approximation for the growth rate continues to hold while the flux tube remains relatively axisymmetric, that is while the kink instability remains in its linear phase.
-
-\rs{In contrast to the precise form of the equilibrium state and
-  perturbation studied in~\citet{quinnEffectAnisotropicViscosity2020},
-  this is an experiment where a system is driven and instabilities
-  occur organically as a result of noise providing a random
-  perturbation. As a result of the driving, the flux tube is not in
-  static equilibrium. Consequently, the stability criterion and linear
-  growth rate presented previously are useful only as a guide and for
-  approximate comparison.}{The stability criterion
-  \eqref{eq:suydams_criterion} and the linear
-  growth rate approximation \eqref{eq:fluting_growth_rate2} are useful
-  only as a guide and for 
-  approximate analysis of the numerical simulations presented in this
-  work.  The precise form of the equilibrium state and the
-  perturbations needed for the validity of
-  \eqref{eq:suydams_criterion} and \eqref{eq:fluting_growth_rate2}
-  were used in~\citet{quinnEffectAnisotropicViscosity2020}.
-  In contrast, in the experiments reported in the following the system
-  is driven and instabilities occur spontaneously due to random
-  perturbation. As a result of the driving, the flux tube is also not
-  in static equilibrium initially. }
+Throughout this paper, the twisted flux tube generated by the drivers has
+a pressure profile which is approximately axisymmetric, and independent of $z$
+away from the boundaries at $z=\pm2$, and has a negative gradient, hence
+$|\nabla p|$ may be written as $-d p/ dr$. Similarly, away from the boundaries,
+the magnetic field has a negligible $r$ component and little dependence on
+$\theta$ and $z$, allowing the field to be approximated as $\vec{B} = (0,
+B_{\theta}(r), B_z(r))^{\text{T}}$, in cylindrical coordinates $(r, \theta,
+z)$. For a twisted field of this form, the radius of curvature is given by
+\begin{equation} \label{eq:radius_of_curvature} R_c
+= \frac{1}{|(\vec{b}\cdot\nabla) \vec{b}|} = \frac{r}{b_{\theta}^2},
+\end{equation} where $\vec{b} = \vec{B}/|\vec{B}|$ is the unit vector in the
+direction of the magnetic field and $b_{\theta}$ is the component of $\vec{b}$
+in the azimuthal direction. These approximations allows the growth rate to be
+written as \begin{equation} \label{eq:fluting_growth_rate2}
+\gamma_{\text{ideal}}^2 = \frac{-2p'}{\rho R_c}. \end{equation} This
+approximation for the growth rate continues to hold while the flux tube remains
+relatively axisymmetric, that is while the kink instability remains in its
+linear phase.
+
+The stability criterion \eqref{eq:suydams_criterion} and the linear growth rate
+approximation \eqref{eq:fluting_growth_rate2} are useful only as a guide and
+for approximate analysis of the numerical simulations presented in this work.
+The precise form of the equilibrium state and the perturbations needed for the
+validity of \eqref{eq:suydams_criterion} and \eqref{eq:fluting_growth_rate2}
+were used in~\citet{quinnEffectAnisotropicViscosity2020}. In contrast, in the
+experiments reported in the following the system is driven and instabilities
+occur spontaneously due to random perturbation. As a result of the driving, the
+flux tube is also not in static equilibrium initially.
 
@@
 velocity $\vec{u}$, pressure $p$, magnetic field $\vec{B}$ and
-internal energy $\varepsilon$, \rs{}{in their non-dimensionalised
-  visco-resistive form}
+internal energy $\varepsilon$, in their non-dimensionalised
+  visco-resistive form
+
 \begin{subequations}
@@
 \end{subequations}
+
 where $\eta$ is the non-dimensionalised resistivity,
 $\vec{\jmath} = \nabla \times \vec{B}$ is the current
-density and \rs{$\ten{\sigma}$ is the viscous stress tensor (described
-  below). The}{the} terms ${Q}_{\nu} = \ten{\sigma} : \vec{\nabla}\vec{u}$
+density and the terms ${Q}_{\nu} = \ten{\sigma} : \vec{\nabla}\vec{u}$
   and ${Q}_{\eta} = \eta | \vec{\jmath} |^2$ are viscous heating and
@@
   of the equation of state for an ideal gas
+
 \begin{equation}
@@
 
-\rs{The isotropic (or Newtonian) viscosity stress tensor is given by
-\begin{equation}
-  \label{eq:isotropic_viscous_tensor}
-  \ten{\sigma}_{\text{iso}} = \nu \ten{W},
-\end{equation}
-where $\nu$ is the viscous transport parameter, generally referred to as the viscosity,
-\begin{equation}
-  \label{eq:rate_of_strain}
-  \ten{W} = \nabla\vec{u} + (\nabla\vec{u})^T - \tfrac{2}{3}(\nabla \cdot \vec{u})\ten{I},
-\end{equation}
-is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$
-identity matrix. We use an identical model of anisotropic viscosity to
-that used in
-previous work~\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021},
- the switching model, first presented
- in~\citet{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}. While
- this model is intended to revert to an isotropic model in the
- vicinity of magnetic null points, we effectively only make use of the
- anisotropic component, since there are no null points present in the
- simulations reported here at any point. To this
- end, we set the switching parameter (which controls the degree of
- viscous anisotropy) to $a_0 = 150$ in Lare3d's control, a value
- sufficiently large so that the anisotropic viscous stress tensor is given by
-\begin{equation}
-  \label{eq:switching_model}
-\ten{\sigma}_{\text{swi}} = \nu \left[\frac{3}{2}(\ten{W}\vec{b}\cdot\vec{b}) \left( \vec{b} \otimes \vec{b} - \frac{1}{3}\ten{I} \right)\right],
-\end{equation}
-where $\vec{b}$ is the unit vector in the direction of the magnetic field.
-This tensor is identical to the strong field approximation of Braginskii~\citep{braginskiiTransportProcessesPlasma1965}.
-Full use of the switching model can be found in~\citet{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}.
-}{}
-
-\rs{}{Two different models for the viscosity stress tensor $\ten{\sigma}$
+Two different models for the viscosity stress tensor $\ten{\sigma}$
 will be compared and contrasted in this study. The first model is the
-conventional} isotropic (or Newtonian) viscosity stress tensor \rs{}{used in
-the vast majority of the existing literature, so that,} 
+conventional isotropic (or Newtonian) viscosity stress tensor used in
+the vast majority of the existing literature, so that, 
 \begin{equation}
@@
   \label{eq:switching_model}
-\rs{}{\ten{\sigma} = \ten{\sigma}_\text{aniso}} = \nu \left[\frac{3}{2}(\ten{W}\vec{b}\cdot\vec{b}) \left( \vec{b} \otimes \vec{b} - \frac{1}{3}\ten{I} \right)\right],
+\ten{\sigma} = \ten{\sigma}_\text{aniso} = \nu \left[\frac{3}{2}(\ten{W}\vec{b}\cdot\vec{b}) \left( \vec{b} \otimes \vec{b} - \frac{1}{3}\ten{I} \right)\right],
 \end{equation}
@@
 field.
-\rs{}{
+
 Expression \eqref{eq:switching_model} is identical to the strong field approximation of the
@@
 present study where the variations in the magnetic field are not
-significantly large.}
+significantly large.
 
@@
 
-\rs{}{The following initial and boundary conditions are used to form a
-magnetic flux tube and excite instabilities by dynamic twisting.} 
+The following initial and boundary conditions are used to form a
+magnetic flux tube and excite instabilities by dynamic twisting. 
 The magnetic field is prescribed as initially straight and uniform,
@@
 boundaries, the magnetic field, velocity, density, and energy are fixed to their
-initial values \rs{}{and their derivatives normal to the
-boundaries are set to zero}  except
+initial values and their derivatives normal to the
+boundaries are set to zero  except
 where twisting velocity ``driver'', described
 below, is prescribed.
-\rs{The spatial
-derivatives of these variables are also set to zero at the
-boundaries.}{} \rs{The resolution is $512$ grid points per dimension,
-comparable to the highest resolution kink instability studies
-of~\cite{hoodCoronalHeatingMagnetic2009} or medium resolution studies
-of~\cite{barefordShockHeatingNumerical2015}.}{}
 
@@
 It is unavoidable that some waves are produced during the boundary acceleration, however these usefully provide a source of noise which eventually forms a perturbation.
-\rs{}{
-The driver} velocity is set to $u_0 = 0.15$, the normalising factor is $u_{r0} = 2.08$, and setting $r_d = 5$ corresponds to a driver constrained to $r<1$ and with a peak velocity at $r\approx 0.38$.
+
+The driver velocity is set to $u_0 = 0.15$, the normalising factor is $u_{r0} = 2.08$, and setting $r_d = 5$ corresponds to a driver constrained to $r<1$ and with a peak velocity at $r\approx 0.38$.
 The ramping time is set to $t_r = 2$, resulting in an acceleration from $0$ to $u_0$ over approximately $5$ Alfv\'en times.
@@
 
-\rs{}{The problem formulated above is solved numerically using the
+The problem formulated above is solved numerically using the
   staggered-grid, Lagrangian–Eulerian remap code for 3D MHD
@@
   a  new module for anisotropic viscosity has been
-  included as detailed in~\citet{quinnKelvinHelmholtzInstabilityCollapse2021}.} The resolution used in the
+  included as detailed in~\citet{quinnKelvinHelmholtzInstabilityCollapse2021}. The resolution used in the
 current work is  $512$ grid points per dimension, comparable to the
@@
 
-\rs{Two pairs of simulations were performed,}{We focus the attention
+We focus the attention
 on two selected pairs of  
@@
 another one using the anisotropic model~\eqref{eq:switching_model}. The
-value of viscosity is set to $\nu = 10^{-4}$ in all cases.} 
+value of viscosity is set to $\nu = 10^{-4}$ in all cases. 
 %
@@
 $\eta=10^{-4}$ cases, with the aim of comparing the effects of the two
-viscosity models. \rs{These cases illustrate the development of the instabilities while showcasing the effect of the
-viscosity models.}{} Then further features of the $\eta=10^{-3}$
-cases are summarised. \rs{without a full exploration of the (qualitatively
-similar) results.}{}
-
-\subsection{\rs{Overview of instability development}{Mechanism and
-    general development of instability}}
+viscosity models. Then further features of the $\eta=10^{-3}$
+cases are summarised.
+
+\subsection{Mechanism and
+    general development of instability}
 
@@
     \end{subfigure}
-  \mycaption{Gradients in the current density generate pressure
-    gradients through Ohmic heating.}{\rs{}{Axial current density (a), Ohmic heating
-      (b) and pressure (c) as functions of the radial distance from
-      the tube axis.}{} All plots are from anisotropic
-    cases when $t=20$ through the plane $z=0$. Note the sign of the
-    axial current density $j_z$ has been flipped for comparison and
-    the Ohmic heating is given by $Q_{\eta} = \eta j^2$. The pressure
-    profile of an additional test-case where $\eta=0$ is also
-    shown. Line types are indicated in the legend.}%
+  \mycaption{
+  Gradients in the current density generate pressure gradients through Ohmic
+  heating.}{Axial current density (a), Ohmic heating (b) and pressure (c) as
+  functions of the radial distance from the tube axis. All plots are from
+  anisotropic cases when $t=20$ through the plane $z=0$. Note the sign of the
+  axial current density $j_z$ has been flipped for comparison and the Ohmic
+  heating is given by $Q_{\eta} = \eta j^2$. The pressure profile of an
+  additional test-case where $\eta=0$ is also shown. Line types are indicated
+  in the legend.}%
   \label{fig:pressure_and_heating}
@@
 
-\rs{In all cases, the initial reaction to the twisting at the upper
-and lower boundaries is two}{Initially and in all cases computed, the
-twisting at the upper and lower boundaries gives rise to a pair of}
+Initially and in all cases computed, the
+twisting at the upper and lower boundaries gives rise to a pair of
 torsional Alfv\'en waves which proceed to travel along the tube
@@
 In all cases unstable to the flute instability, it
-occurs  between $t=20$ and $t=30$. \rs{During this
-  time, the}{The} continued driving at the boundaries eventually
+occurs  between $t=20$ and $t=30$. The continued driving at the boundaries eventually
 injects enough twist that the tube also becomes unstable to the kink
-instability. This initially develops linearly alongside \rs{}{or shortly
-after} the flute instability and then erupts during the
+instability. This initially develops linearly alongside or shortly
+after the flute instability and then erupts during the
 its  nonlinear phase, dominating the dynamics and
-disrupting the   flute instability. The \rs{}{onset and
-the competition} of the two instabilities is strongly affected by
+disrupting the   flute instability. The onset and
+the competition of the two instabilities is strongly affected by
 the value of $\eta$ and the viscosity model used.
@@
 
-\rs{}{We now describe the evolution and competition of flute and
-  kink instabilities in case of resistivity $\eta=10^{-4}$.}
+We now describe the evolution and competition of flute and
+  kink instabilities in case of resistivity $\eta=10^{-4}$.
 Figure~\ref{fig:kink_pressure_slices-4} shows the pressure profile
-\rs{the viscosity model is switching for times}{of the \rs{switching}{anisotropic} viscosity case 
+of the anisotropic viscosity case 
 \eqref{eq:switching_model} at
-time moments} $t=26$, $28$ and $30$ and at $z=0$. At $t=26$
+time moments $t=26$, $28$ and $30$ and at $z=0$. At $t=26$
 the tube becomes unstable to  flute
@@
 which will not be illustrated by a separate figure, the
-flute instability is present but damped, and \rs{}{it is
-  quickly outcompeted by} the kink instability which quickly dominates the dynamics.
+flute instability is present but damped, and it is
+  quickly outcompeted by the kink instability which quickly dominates the dynamics.
 
@@
   $t=28$.
-Also shown is the velocity driver \rs{as a slice}{$u_r(\sqrt{x^2+y^2})$ at $z=2$}.
+Also shown is the velocity driver $u_r(\sqrt{x^2+y^2})$ at $z=2$.
 The flute instability grows in both cases, though faster in the anisotropic case.
@@
 
-Figure~\ref{fig:kink_field_line_plots} shows the effect the viscosity
-models have on the initial stages of the flute and kink
-instabilities in 3D. While the flute instability is
-observed in both cases, it is damped in the isotropic case and grows
-faster in the anisotropic case. In the latter case,
-the extended development of the flute instability
-appears to disrupt the inner core of field lines and, \rs{(as shall be
-  seen)}{as will be discussed further below,} slows the growth of the
-kink instability. In the isotropic case, the flute
-instability has been damped to the extent that the kink instability
-grows uninhibited and quickly disrupts the fluting.
+Figure~\ref{fig:kink_field_line_plots} shows the effect the viscosity models
+have on the initial stages of the flute and kink instabilities in 3D. While the
+flute instability is observed in both cases, it is damped in the isotropic case
+and grows faster in the anisotropic case. In the latter case, the extended
+development of the flute instability appears to disrupt the inner core of field
+lines and, as will be discussed further below, slows the growth of the kink
+instability. In the isotropic case, the flute instability has been damped to
+the extent that the kink instability grows uninhibited and quickly disrupts the
+fluting.
 
@@
     \end{subfigure}
-  \mycaption{Kinetic energy as a function of time showing the
-    development and measured growth rates $\gamma$ and $\lambda$
-    of the flute
-    and kink instabilities, respectively.}{\rs{Both plots are from results
-      where}{Resistivity is $\eta=10^{-4}$ and the second plot is a
-      enlarged version of the first.}}
+  \mycaption{Kinetic energy as a function of time showing the development and
+  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
+  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and the second
+  plot is a enlarged version of the first.}
 \label{fig:kink_str8_ke-4}%
@@
 although the onset times appear similar, and the kinetic energy
-profile shows no evidence of \rs{the growth of the flute
-instability.}{flute instability growth.}
+profile shows no evidence of flute instability growth.
 
@@
   perturbations corresponding to the flute and kink
-  instabilities at $t=26$ \rs{}{are shown in
-  Figure~\ref{fig:pressure_pert_4}}. The fluting perturbation is
+  instabilities at $t=26$ are shown in
+  Figure~\ref{fig:pressure_pert_4}. The fluting perturbation is
   most easily observed in the pressure and is plotted as a function of $z$
@@
 
-\rs{Figures \ref{fig:kink_pressure_slices-3} show the}{Figure
-  \ref{fig:kink_pressure_slices-3} shows a} prolonged 
+Figure
+  \ref{fig:kink_pressure_slices-3} shows a prolonged 
 development of the flute instability and a slow
-nonlinear development of the kink \rs{}{instability at the higher
-  resistivity value $\eta=10^{-3}$ in the case of anisotropic viscosity}. Due to the enhanced Ohmic heating 
+nonlinear development of the kink instability at the higher
+  resistivity value $\eta=10^{-3}$ in the case of anisotropic viscosity. Due to the enhanced Ohmic heating 
 at $\eta=10^{-3}$, the pressure gradient is substantially stronger
@@
 \caption{Quantitative differences in the observed perturbations
-  between results \rs{for both values of}{between different
-    resistivity values} $\eta$. \rs{}{In all measurements the
+  between results between different
+    resistivity values $\eta$. In all measurements the
   anisotropic viscosity model is used except for $k_\text{kink}$ where the
   isotropic viscosity model us used. Measurements times are listed in
-  the main text.}}
+  the main text.}
 \centering
@@
 Table~\ref{tab:kink_fluting_params} summarises the quantitative
-differences between the results for the two values of \rs{}{the
-  resistivity} $\eta$.
+differences between the results for the two values of the
+  resistivity $\eta$.
 All values are calculated from simulations using the anisotropic model with the exception of $k_{\text{kink}}$ which is measured from isotropic results due to noise in the anisotropic case (the value of $k_{\text{kink}}$ appears similar, however).
@@
 shown that the mixing as a result of the nonlinear flute
-instability appears to slow the growth of the kink instability. \rs{In
-  the linear regime it seems unlikely that}{It seems unlikely that in
-  the linear regime} the  perturbations of  the
+instability appears to slow the growth of the kink instability. It seems unlikely that in
+ the linear regime the perturbations of the
 flute and kink are able to directly couple, given that
@@
 instability and appeared to have little impact on the resultant
-dynamics, which mirror those of other kink instability studies, \rs{such
-as~}{e.g.~}\citep{hoodCoronalHeatingMagnetic2009}. This suggests that even
+dynamics, which mirror those of other kink instability studies, e.g.~\citep{hoodCoronalHeatingMagnetic2009}. This suggests that even
 lower values of resistivity would result in flux tubes without any
@@
 instability can quickly dominate when the pressure gradient is small
-enough, the opposite case is also observed\rs{,
-  where}{. A faster} growing flute instability appears to slow the growth of
+enough, the opposite case is also observed. A faster growing flute instability appears to slow the growth of
 the kink instability although, importantly, it does not fully disrupt
 the development of the kink. Understanding the balance between the
-nonlinear growth rates of the two instabilities is important \rs{in
-understanding}{for prediction of} whether the flute instability may be found
+nonlinear growth rates of the two instabilities is important for prediction of whether the flute instability may be found
 at all in the real solar corona, or whether its realistic growth rate is
@@
 straight magnetic flux tube. This provides a different approach to
-that employed in the simulations performed in \rs{chapter}{our earlier
-  study}~\citep{quinnEffectAnisotropicViscosity2020} in that the
+that employed in the simulations performed in our earlier
+  study~\citep{quinnEffectAnisotropicViscosity2020} in that the
 instabilities are not excited by any prescribed perturbations but,
@@
 the perturbations provided by noise in the system. Not only is the
-kink instability excited due to the twist in the field, \rs{}{but also
-and near simultaneously} a pressure-driven flute
+kink instability excited due to the twist in the field, but nearly simultaneously a pressure-driven flute
 instability can also be excited in unstable pressure gradients
@@
 $\eta=10^{-3}$ and $10^{-4}$, and for two forms of viscosity, isotropic and
-\rs{switching}{anisotropic}\rs{, providing}{. The results prove}an
-initial and important first step \rs{into the simulation of}{towards
-understanding} nonlinear flute instabilities in the
+anisotropic. The results prove an
+initial and important first step towards
+understanding nonlinear flute instabilities in the
 solar corona.

### 2021-12-02 paper.tex
Reformat paragraphs

@@
 \begin{abstract}
-Magnetic flux tubes such as those in the solar corona are subject to a
-number of instabilities. Important among them is the kink instability
-which plays a central part in the nanoflare theory of coronal heating,
-and for this reason in numerical simulations it is usually induced by
-tightly-controlled perturbations and studied in isolation. In
-contrast, we find that when disturbances are introduced in our
-magnetohydrodynamic flux tube simulations by dynamic twisting of the
-flow at the boundaries fluting modes of instability are readily
-excited. We also find that the flute instability, which has been
-theorised but rarely observed in the coronal context,  is strongly
-enhanced when plasma viscosity is assumed anisotropic.
-We proceed to investigate the co-existence and competition between
-flute and kink instabilities for a range of values of the resistivity
-and of the parameters of the anisotropic and isotropic models of viscosity.
-We conclude that while the flute instability cannot prevent the kink
-from ultimately dominating, it can significantly delay its development
-especially at strong viscous anisotropy induced by intense magnetic fields.
+Magnetic flux tubes such as those in the solar corona are subject to a number
+of instabilities. Important among them is the kink instability which plays
+a central part in the nanoflare theory of coronal heating, and for this reason
+in numerical simulations it is usually induced by tightly-controlled
+perturbations and studied in isolation. In contrast, we find that when
+disturbances are introduced in our magnetohydrodynamic flux tube simulations by
+dynamic twisting of the flow at the boundaries fluting modes of instability are
+readily excited. We also find that the flute instability, which has been
+theorised but rarely observed in the coronal context,  is strongly enhanced
+when plasma viscosity is assumed anisotropic. We proceed to investigate the
+co-existence and competition between flute and kink instabilities for a range
+of values of the resistivity and of the parameters of the anisotropic and
+isotropic models of viscosity. We conclude that while the flute instability
+cannot prevent the kink from ultimately dominating, it can significantly delay
+its development especially at strong viscous anisotropy induced by intense
+magnetic fields.
 \end{abstract}
@@
 
-The helical kink instability is a form of ideal magnetohydrodynamic
-(MHD) instability which occurs in highly twisted magnetic flux tubes
-such as those making up much of the solar
-corona~\citep{realeCoronalLoopsObservations2014} and has been well
-studied in the coronal
-context~\citep{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003b,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020}. Given
-its energetic nonlinear development, it is considered a potential
+The helical kink instability is a form of ideal magnetohydrodynamic (MHD)
+instability which occurs in highly twisted magnetic flux tubes such as those
+making up much of the solar corona~\citep{realeCoronalLoopsObservations2014}
+and has been well studied in the coronal
+context~\citep{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003b,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020}.
+Given its energetic nonlinear development, it is considered a potential
 mechanism for heating the solar corona through the theory of
@@
 and a key mechanism in the production of solar
-flares~\citep{hoodKinkInstabilitySolar1979}. Some of our previous work has investigated a twisted magnetic flux tube already linearly
-unstable to the helical kink instability, focussing specifically on
-the effect of anisotropic viscosity on the nonlinear
-dynamics~\citep{quinnEffectAnisotropicViscosity2020}. In~\citet{quinnEffectAnisotropicViscosity2020}
-and most other investigations of the kink instability
-e.g.~\citet{hoodCoronalHeatingMagnetic2009}, a perturbation 
-is applied to an already significantly twisted flux tube. An
-alternative way to excite the instability (and the way employed here)
-is to start with an initially straight field and apply twisting
-motions at the boundaries to form a twisted flux tube which eventually
-becomes unstable. This kind of dynamic excitation of the kink
-instability is useful in that it represents more closely actual evolution of magnetic flux tubes and the associated instabilities in 
-the solar corona. In our simulations, the
-dynamic twisting of the flux tube reveals an additional instability,
-the flute instability, which has been theorised (for example,
-in~\citet{priestMagnetohydrodynamicsSun2013}).
-While oscillations resembling flute perturbations have been found in simulations of coronal loops~\citep{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute instability has been investigated computationally in a coronal context.
-
-The flute instability arises in magnetised plasmas where
-the plasma pressure gradient is oriented in the same direction as the
-field line curvature, that is the pressure and magnetic tension forces
-compete. This is similar to the competition between pressure and
-gravitational forces which gives rise to the Rayleigh-Taylor
-instability (RTI). In magnetohydrodynamic terminology, the RTI is a typical example of an ideal
-interchange instability, where magnetic field lines are minimally bent
-and are, instead, exchanged during the evolution of the
-instability. The ideal flute instability is another example of an
-ideal interchange instability but confined to a cylindrical geometry,
-the term ``flute instability'' referring to its likeness to a fluted
-column. In a twisted flux tube like a simple, unbraided coronal loop,
-the magnetic curvature is always directed towards the axis so the tube
-may be unstable to fluting when the pressure decreases outwards from a
-high-pressure core. Such a pressure distribution is generated in the
-flux tubes studied here as a result of the driving. The appearance of
-the flute instability is illustrated by, for example, the pressure
-contours in figure~\ref{fig:kink_field_line_plots}, where the
-perturbations follow the pitch of the twisted field.
-
-In other solar contexts, interchange instabilities can be found in the
-form of ballooning modes in
-arcades~\citep{hoodBallooningInstabilitiesSolar1986}, as the
-instability which forms tubes of specific size in the
-photosphere~\citep{bunteInterchangeInstabilitySolar1993} and in the
-buoyancy of flux
-tubes~\citep{schuesslerInterchangeInstabilitySmall1984}. However, the
+flares~\citep{hoodKinkInstabilitySolar1979}. Some of our previous work has
+investigated a twisted magnetic flux tube already linearly unstable to the
+helical kink instability, focussing specifically on the effect of anisotropic
+viscosity on the nonlinear
+dynamics~\citep{quinnEffectAnisotropicViscosity2020}.
+In~\citet{quinnEffectAnisotropicViscosity2020} and most other investigations of
+the kink instability e.g.~\citet{hoodCoronalHeatingMagnetic2009},
+a perturbation is applied to an already significantly twisted flux tube. An
+alternative way to excite the instability (and the way employed here) is to
+start with an initially straight field and apply twisting motions at the
+boundaries to form a twisted flux tube which eventually becomes unstable. This
+kind of dynamic excitation of the kink instability is useful in that it
+represents more closely actual evolution of magnetic flux tubes and the
+associated instabilities in the solar corona. In our simulations, the dynamic
+twisting of the flux tube reveals an additional instability, the flute
+instability, which has been theorised (for example,
+in~\citet{priestMagnetohydrodynamicsSun2013}). While oscillations resembling
+flute perturbations have been found in simulations of coronal
+loops~\citep{terradasEffectMagneticTwist2018}, to our knowledge, this is the
+first time the flute instability has been investigated computationally in
+a coronal context.
+
+The flute instability arises in magnetised plasmas where the plasma pressure
+gradient is oriented in the same direction as the field line curvature, that is
+the pressure and magnetic tension forces compete. This is similar to the
+competition between pressure and gravitational forces which gives rise to the
+Rayleigh-Taylor instability (RTI). In magnetohydrodynamic terminology, the RTI
+is a typical example of an ideal interchange instability, where magnetic field
+lines are minimally bent and are, instead, exchanged during the evolution of
+the instability. The ideal flute instability is another example of an ideal
+interchange instability but confined to a cylindrical geometry, the term
+``flute instability'' referring to its likeness to a fluted column. In
+a twisted flux tube like a simple, unbraided coronal loop, the magnetic
+curvature is always directed towards the axis so the tube may be unstable to
+fluting when the pressure decreases outwards from a high-pressure core. Such
+a pressure distribution is generated in the flux tubes studied here as a result
+of the driving. The appearance of the flute instability is illustrated by, for
+example, the pressure contours in figure~\ref{fig:kink_field_line_plots}, where
+the perturbations follow the pitch of the twisted field.
+
+In other solar contexts, interchange instabilities can be found in the form of
+ballooning modes in arcades~\citep{hoodBallooningInstabilitiesSolar1986}, as
+the instability which forms tubes of specific size in the
+photosphere~\citep{bunteInterchangeInstabilitySolar1993} and in the buoyancy of
+flux tubes~\citep{schuesslerInterchangeInstabilitySmall1984}. However, the
 flute instability specifically is more commonly studied in fusion
-contexts~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}. In
-fusion, the focus is generally on understanding how a particular
-plasma device may be stabilised to the instability in particular
-geometries such as that of the mirror
-machine~\citep{jungwirthTheoryFluteInstability1965} or in toroidal
-geometries such as the
-tokomak~\citep{shafranovFluteInstabilityCurrentcarrying1968}. The
-resistive flute instability (also known as the resistive interchange
-instability) can be excited even when the ideal flute instability is
-stabilised. As a result, this has been given significantly more
-attention~\citet{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}. While
-this body of research is useful and applicable in solar contexts, it
-is mostly limited to the study of the stability and linear development
-of the flute instability, the nonlinear development being of
-secondary importance in the investigation of fusion devices. More
-detailed investigations of its nonlinear development is required to
-understand its importance in the context of coronal dynamics and
-coronal heating. The development of the flute instability and its
-interaction with the simultaneously growing kink instability is the
-main focus of this work and the experiments described here represent an
-initial exploration into the nonlinear flute instability in the
+contexts~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998,zhengAdvancedTokamakStability2015,wessonHydromagneticStabilityTokamaks1978}.
+In fusion, the focus is generally on understanding how a particular plasma
+device may be stabilised to the instability in particular geometries such as
+that of the mirror machine~\citep{jungwirthTheoryFluteInstability1965} or in
+toroidal geometries such as the
+tokomak~\citep{shafranovFluteInstabilityCurrentcarrying1968}. The resistive
+flute instability (also known as the resistive interchange instability) can be
+excited even when the ideal flute instability is stabilised. As a result, this
+has been given significantly more
+attention~\citet{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}.
+While this body of research is useful and applicable in solar contexts, it is
+mostly limited to the study of the stability and linear development of the
+flute instability, the nonlinear development being of secondary importance in
+the investigation of fusion devices. More detailed investigations of its
+nonlinear development is required to understand its importance in the context
+of coronal dynamics and coronal heating. The development of the flute
+instability and its interaction with the simultaneously growing kink
+instability is the main focus of this work and the experiments described here
+represent an initial exploration into the nonlinear flute instability in the
 solar corona.
 
-In addition to our main goal, of particular interest here is
-also the effect of anisotropic plasma viscosity, which in the following is found to
-strongly influence the growth of the flute instability.
-It is well known that viscosity in magnetised plasmas (such as
-those which make up the solar corona) is
-anisotropic and strongly dependent on the strength and direction of
-the local magnetic
+In addition to our main goal, of particular interest here is also the effect of
+anisotropic plasma viscosity, which in the following is found to strongly
+influence the growth of the flute instability. It is well known that viscosity
+in magnetised plasmas (such as those which make up the solar corona) is
+anisotropic and strongly dependent on the strength and direction of the local
+magnetic
 field~\citep{hollwegViscosityChewGoldbergerLowEquations1986,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
-To take this into account, MacTaggaret et al. developed a phenomenological model of anisotropic viscosity~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} that
-captures the main physics of viscosity in the 
-solar corona as outlined in the analysis of
-\cite{braginskiiTransportProcessesPlasma1965}, namely parallel
-viscosity in regions of strong field  strength and isotropic viscosity
-in regions of very weak or zero field strength. For brevity, we will
-refer to this model of viscosity as ``the switching model''. In~\citet{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021} we implemented
-the switching model as a module for the widely-used general MHD code
-Lare3d~\citep{arberStaggeredGridLagrangian2001}, and demonstrated
-significant effects of anisotropic viscosity on the 
-development of the nonlinear MHD kink instability and the
-Kelvin-Helmholtz instability. More generally, the interest in
-anisotropic viscosity stems from the open question of
-which heating mechanism (viscous or Ohmic) is dominant in the solar
-corona~\citep{klimchukSolvingCoronalHeating2006}, an important facet
-of solving the coronal heating problem. Using scaling laws, it has
-been suggested that viscous heating (generated through anisotropic
-viscosity) can dwarf that of Ohmic
+To take this into account, MacTaggaret et al. developed a phenomenological
+model of anisotropic
+viscosity~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} that
+captures the main physics of viscosity in the solar corona as outlined in the
+analysis of \cite{braginskiiTransportProcessesPlasma1965}, namely parallel
+viscosity in regions of strong field  strength and isotropic viscosity in
+regions of very weak or zero field strength. For brevity, we will refer to this
+model of viscosity as ``the switching model''.
+In~\citet{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
+we implemented the switching model as a module for the widely-used general MHD
+code Lare3d~\citep{arberStaggeredGridLagrangian2001}, and demonstrated
+significant effects of anisotropic viscosity on the development of the
+nonlinear MHD kink instability and the Kelvin-Helmholtz instability. More
+generally, the interest in anisotropic viscosity stems from the open question
+of which heating mechanism (viscous or Ohmic) is dominant in the solar
+corona~\citep{klimchukSolvingCoronalHeating2006}, an important facet of solving
+the coronal heating problem. Using scaling laws, it has been suggested that
+viscous heating (generated through anisotropic viscosity) can dwarf that of
+Ohmic
 heating~\citep{craigAnisotropicViscousDissipation2009a,litvinenkoViscousEnergyDissipation2005}.
-However,
-due to computational and observational limitations, this cannot be
-directly tested, and so the influence of other factors such as small
-scale instabilities and turbulence is relatively
-unknown~\citet{klimchukSolvingCoronalHeating2006}. In addition to
-directly heating the plasma, viscosity plays a part in the damping of
-instabilities and waves~\citep{rudermanSlowSurfaceWave2000}. It is
-this effect we are most interested in here, and it shall be reported that
-the use of anisotropic viscosity permits the growth of the
-flute instability, which is otherwise strongly damped by
-isotropic viscosity.
-
-This paper is organised as follows.
-Section~\ref{sec-flute-intro} introduces the flute instability and relevant linear analyses, section~\ref{sec-numerical-setup} describes the governing equations, coronal loop model and details of the numerical parameters, section~\ref{sec-results} presents the overall development of the flute instability, before discussing features unique to the two values of resistivity studied, section~\ref{sec-discussion} discusses the limitations of the simulations, with suggestions for future work, and section~\ref{sec-conclusions} presents our conclusions in the wider context of coronal heating.
+However, due to computational and observational limitations, this cannot be
+directly tested, and so the influence of other factors such as small scale
+instabilities and turbulence is relatively
+unknown~\citet{klimchukSolvingCoronalHeating2006}. In addition to directly
+heating the plasma, viscosity plays a part in the damping of instabilities and
+waves~\citep{rudermanSlowSurfaceWave2000}. It is this effect we are most
+interested in here, and it shall be reported that the use of anisotropic
+viscosity permits the growth of the flute instability, which is otherwise
+strongly damped by isotropic viscosity.
+
+This paper is organised as follows. Section~\ref{sec-flute-intro} introduces
+the flute instability and relevant linear analyses,
+section~\ref{sec-numerical-setup} describes the governing equations, coronal
+loop model and details of the numerical parameters, section~\ref{sec-results}
+presents the overall development of the flute instability, before discussing
+features unique to the two values of resistivity studied,
+section~\ref{sec-discussion} discusses the limitations of the simulations, with
+suggestions for future work, and section~\ref{sec-conclusions} presents our
+conclusions in the wider context of coronal heating.
 
@@
 where $m$ and $k$ are the wavenumbers in the azimuthal and axial directions,
-  $\theta$ and $z$, respectively and $r$ is the radial coordinate in
-  cylindrical polars. 
-The helical kink instability occurs for perturbations where $m=1, k\ne0$ and is the only instability of this form which is a body instability, that is it moves the entire body of the flux tube.
-Perturbations where $m>1$ are termed flute or interchange instabilities.
-
-When the magnetic field is sheared, as in a twisted magnetic flux
-tube, an interchange instability (such as the flute
-instability) is confined to a surface where the peaks and troughs
-follow the shear of the field. That is, the instability is confined to
-the surface where the perturbation wavevector $(0, m/r, k)$ is
-perpendicular to the direction of the field, known as the
-  ``resonance surface''. In an axisymmetric twisted
-flux tube the resonance surface is located at a radius $r$
-given by
+$\theta$ and $z$, respectively and $r$ is the radial coordinate in cylindrical
+polars. The helical kink instability occurs for perturbations where $m=1,
+k\ne0$ and is the only instability of this form which is a body instability,
+that is it moves the entire body of the flux tube. Perturbations where $m>1$
+are termed flute or interchange instabilities.
+
+When the magnetic field is sheared, as in a twisted magnetic flux tube, an
+interchange instability (such as the flute instability) is confined to
+a surface where the peaks and troughs follow the shear of the field. That is,
+the instability is confined to the surface where the perturbation wavevector
+$(0, m/r, k)$ is perpendicular to the direction of the field, known as the
+``resonance surface''. In an axisymmetric twisted flux tube the resonance
+surface is located at a radius $r$ given by
 \begin{equation}
@@
 
-The stability of an infinite cylindrical flux tube to perturbations of
-the form~\eqref{eq:kink_perturbation} is given by the classical
-Suydam's criterion~\citep{suydamStabilityLinearPinch1958}
+The stability of an infinite cylindrical flux tube to perturbations of the
+form~\eqref{eq:kink_perturbation} is given by the classical Suydam's
+criterion~\citep{suydamStabilityLinearPinch1958}
 \begin{equation}
@@
 \end{equation}
-where $S = r q'/q$ is a measure of the shear, $q = 2\pi r B_z / L
-B_{\theta}$ is the safety factor for a flux tube of length $L$ and a
-prime denotes differentiation with respect to
-$r$~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}. This applies
-to both flute and kink instabilities although many
-additional effects such as line-tying are not incorporated into the
-corresponding linear analysis. The effect of line-tying on the kink
-instability is investigated
-in~\citet{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion}
-is not satisfied, the flux tube may be unstable to perturbations of
-the form~\eqref{eq:kink_perturbation}. When $m>1$, the perturbations
-remain local to resonant surfaces given
-by~\eqref{eq:resonant_surface}. 
-When Suydam's criterion is satisfied and the flux tube is linearly stable, it may still be unstable to non-local perturbations, where the shear and pressure are small enough that interchange perturbations do not need to satisfy~\eqref{eq:resonant_surface}.
-Additionally, the inclusion of resistivity generally reduces the stabilising effect of the shear, permitting growth of a resistive interchange mode, albeit at a slower rate than that of the ideal instability~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}.
-It will be found that the ideal linear analysis of~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998} is sufficient for understanding the flute instabilities investigated here since the associated flux tubes adequately fail the criterion~\eqref{eq:suydams_criterion}.
-
-While Suydam's condition gives an indication of the stability of a flux tube to a given perturbation, the linear growth rate of the ideal flute instability $\gamma$ can be found via a stability analysis analogous to that of the Rayleigh-Taylor instability (see~\citep[][]{goldstonIntroductionPlasmaPhysics2020}) and is given by
+where $S = r q'/q$ is a measure of the shear, $q = 2\pi r B_z / L B_{\theta}$
+is the safety factor for a flux tube of length $L$ and a prime denotes
+differentiation with respect to
+$r$~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}. This applies to both
+flute and kink instabilities although many additional effects such as
+line-tying are not incorporated into the corresponding linear analysis. The
+effect of line-tying on the kink instability is investigated
+in~\citet{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion} is
+not satisfied, the flux tube may be unstable to perturbations of the
+form~\eqref{eq:kink_perturbation}. When $m>1$, the perturbations remain local
+to resonant surfaces given by~\eqref{eq:resonant_surface}. When Suydam's
+criterion is satisfied and the flux tube is linearly stable, it may still be
+unstable to non-local perturbations, where the shear and pressure are small
+enough that interchange perturbations do not need to
+satisfy~\eqref{eq:resonant_surface}. Additionally, the inclusion of resistivity
+generally reduces the stabilising effect of the shear, permitting growth of
+a resistive interchange mode, albeit at a slower rate than that of the ideal
+instability~\citep{mikhailovskiiInstabilitiesConfinedPlasma1998}. It will be
+found that the ideal linear analysis
+of~\cite{mikhailovskiiInstabilitiesConfinedPlasma1998} is sufficient for
+understanding the flute instabilities investigated here since the associated
+flux tubes adequately fail the criterion~\eqref{eq:suydams_criterion}.
+
+While Suydam's condition gives an indication of the stability of a flux tube to
+a given perturbation, the linear growth rate of the ideal flute instability
+$\gamma$ can be found via a stability analysis analogous to that of the
+Rayleigh-Taylor instability
+(see~\citep[][]{goldstonIntroductionPlasmaPhysics2020}) and is given by
 \begin{equation}
@@
 \end{equation}
-where $R_c$ is the radius of curvature of the magnetic field.
-This equation only applies when the pressure gradient and radius of curvature vector are in the same direction, that is the plasma is constrained by a concave magnetic field such that the pressure forces and magnetic tension forces are in competition.
-In a cylindrical, twisted flux tube, the field is always concave towards the central axis of the tube, so any inwardly directed pressure gradient is potentially unstable to fluting.
+where $R_c$ is the radius of curvature of the magnetic field. This equation
+only applies when the pressure gradient and radius of curvature vector are in
+the same direction, that is the plasma is constrained by a concave magnetic
+field such that the pressure forces and magnetic tension forces are in
+competition. In a cylindrical, twisted flux tube, the field is always concave
+towards the central axis of the tube, so any inwardly directed pressure
+gradient is potentially unstable to fluting.
 
@@
 in the azimuthal direction. These approximations allows the growth rate to be
-written as \begin{equation} \label{eq:fluting_growth_rate2}
-\gamma_{\text{ideal}}^2 = \frac{-2p'}{\rho R_c}. \end{equation} This
-approximation for the growth rate continues to hold while the flux tube remains
-relatively axisymmetric, that is while the kink instability remains in its
-linear phase.
+written as
+\begin{equation}
+\label{eq:fluting_growth_rate2}
+\gamma_{\text{ideal}}^2 = \frac{-2p'}{\rho R_c}.
+\end{equation}
+This approximation for the growth rate continues to hold while the flux tube
+remains relatively axisymmetric, that is while the kink instability remains in
+its linear phase.
 
@@
 
-We consider the
-magnetohydrodynamic equations for the density $\rho$, plasma
-velocity $\vec{u}$, pressure $p$, magnetic field $\vec{B}$ and
-internal energy $\varepsilon$, in their non-dimensionalised
-  visco-resistive form
-
+We consider the magnetohydrodynamic equations for the density $\rho$, plasma
+velocity $\vec{u}$, pressure $p$, magnetic field $\vec{B}$ and internal energy
+$\varepsilon$, in their non-dimensionalised visco-resistive form
 \begin{subequations}
@@
 \end{subequations}
-
-where $\eta$ is the non-dimensionalised resistivity,
-$\vec{\jmath} = \nabla \times \vec{B}$ is the current
-density and the terms ${Q}_{\nu} = \ten{\sigma} : \vec{\nabla}\vec{u}$
-  and ${Q}_{\eta} = \eta | \vec{\jmath} |^2$ are viscous heating and
-  Ohmic heating, respectively. The system is closed by the inclusion
+where $\eta$ is the non-dimensionalised resistivity, $\vec{\jmath} = \nabla
+\times \vec{B}$ is the current density and the terms ${Q}_{\nu} = \ten{\sigma}
+: \vec{\nabla}\vec{u}$ and ${Q}_{\eta} = \eta | \vec{\jmath} |^2$ are viscous
+heating and Ohmic heating, respectively. The system is closed by the inclusion
 of the equation of state for an ideal gas 
-
 \begin{equation}
@@
 
-Two different models for the viscosity stress tensor $\ten{\sigma}$
-will be compared and contrasted in this study. The first model is the
-conventional isotropic (or Newtonian) viscosity stress tensor used in
-the vast majority of the existing literature, so that, 
+Two different models for the viscosity stress tensor $\ten{\sigma}$ will be
+compared and contrasted in this study. The first model is the conventional
+isotropic (or Newtonian) viscosity stress tensor used in the vast majority of
+the existing literature, so that, 
 \begin{equation}
@@
 \end{equation}
-where $\nu$ is the viscous transport parameter, generally referred to as the viscosity,
+where $\nu$ is the viscous transport parameter, generally referred to as the
+viscosity,
 \begin{equation}
@@
 \end{equation}
-is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$
-identity tensor. The second model, which is the one of actual interest, is the anisotropic viscosity stress
-tensor given by
+is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$ identity
+tensor. The second model, which is the one of actual interest, is the
+anisotropic viscosity stress tensor given by
 \begin{equation}
@@
 
-Expression \eqref{eq:switching_model} is identical to the strong field approximation of the
-general anisotropic viscosity tensor derived in~\citet{braginskiiTransportProcessesPlasma1965}.
-Expressions \eqref{eq:isotropic_viscous_tensor} and \eqref{eq:switching_model} arise as asymptotic limits of the
-more general switching model used in our earlier works 
+Expression \eqref{eq:switching_model} is identical to the strong field
+approximation of the general anisotropic viscosity tensor derived
+in~\citet{braginskiiTransportProcessesPlasma1965}. Expressions
+\eqref{eq:isotropic_viscous_tensor} and \eqref{eq:switching_model} arise as
+asymptotic limits of the more general switching model used in our earlier works
 \citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
-which, includes both isotropic and anisotropic contributions and can
-switch gradually between them depending on the strength of the
-magnetic field at a given spacio-temporal location. For example, in
-the vicinity of a null point where the magnetic field becomes weak the
-isotropic viscosity contribution becomes dominant in the switching
-model. Switching between the two limit cases is not relevant in the
-present study where the variations in the magnetic field are not
-significantly large.
-
-The non-dimensionalisation of equations \eqref{eq:MHD} is identical to that used in
-our earlier works~\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}. A typical magnetic
-field strength $B_0$, density $\rho_0$ and length scale $L_0$ are
-chosen and the other variables non-dimensionalised
-appropriately. Velocity and time are non-dimensionalised using the
-Alfv\'en speed $u_A = B_0 / \sqrt{\rho_0 \mu_0}$ and Alfv\'en crossing 
-time $t_A = L_0/u_A$, respectively. Temperature is non-dimensionalised
-via $T_0 = u_A^2 \bar{m} / k_B$, where $k_B$ is the Boltzmann constant
-and $\bar{m}$ is the average mass of ions, here taken to be $\bar{m} =
-1.2m_p$ (a mass typical for the solar corona) where $m_p$ is the
-proton mass. Dimensional quantities can be recovered by multiplying
-the non-dimensional variables by their respective reference value
-(e.g. $\vec{B}_{\dim} = B_0 \vec{B}$). The reference values used here
-are $B_0 = 5 \times 10^{-3}$ T, $L_0 = 1$ Mm and $\rho_0 = 1.67 \times
-10^{-12} \ \text{kg m}^{-3}$, giving reference values for the Alfv\'en
-speed $u_A = 3.45\ \text{Mm s}^{-1}$, Alfv\'en time $t_A =
+which, includes both isotropic and anisotropic contributions and can switch
+gradually between them depending on the strength of the magnetic field at
+a given spacio-temporal location. For example, in the vicinity of a null point
+where the magnetic field becomes weak the isotropic viscosity contribution
+becomes dominant in the switching model. Switching between the two limit cases
+is not relevant in the present study where the variations in the magnetic field
+are not significantly large.
+
+The non-dimensionalisation of equations \eqref{eq:MHD} is identical to that
+used in our earlier
+works~\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}.
+A typical magnetic field strength $B_0$, density $\rho_0$ and length scale
+$L_0$ are chosen and the other variables non-dimensionalised appropriately.
+Velocity and time are non-dimensionalised using the Alfv\'en speed $u_A = B_0
+/ \sqrt{\rho_0 \mu_0}$ and Alfv\'en crossing time $t_A = L_0/u_A$,
+respectively. Temperature is non-dimensionalised via $T_0 = u_A^2 \bar{m}
+/ k_B$, where $k_B$ is the Boltzmann constant and $\bar{m}$ is the average mass
+of ions, here taken to be $\bar{m} = 1.2m_p$ (a mass typical for the solar
+corona) where $m_p$ is the proton mass. Dimensional quantities can be recovered
+by multiplying the non-dimensional variables by their respective reference
+value (e.g. $\vec{B}_{\dim} = B_0 \vec{B}$). The reference values used here are
+$B_0 = 5 \times 10^{-3}$ T, $L_0 = 1$ Mm and $\rho_0 = 1.67 \times 10^{-12}
+\ \text{kg m}^{-3}$, giving reference values for the Alfv\'en speed $u_A
+= 3.45\ \text{Mm s}^{-1}$, Alfv\'en time $t_A =
 0.29\ \text{s}$ and temperature $T_0 = 1.73 \times 10^{9}\ K$.
 
-The following initial and boundary conditions are used to form a
-magnetic flux tube and excite instabilities by dynamic twisting. 
-The magnetic field is prescribed as initially straight and uniform,
+The following initial and boundary conditions are used to form a magnetic flux
+tube and excite instabilities by dynamic twisting. The magnetic field is
+prescribed as initially straight and uniform,
 \begin{equation}
@@
 \end{equation}
-in a cube of size $[-2,2]^3$, with further test simulations run using an elongated domain of size $4\times4\times20$. Initially, the velocity is set
-everywhere to $\vec{u} = \vec{0}$, the density to $\rho = 1$,
-and the
-internal energy to $\varepsilon = 8.67\times 10^{-4}$. This corresponds
-to a typical coronal temperature of $10^6$ K and a plasma beta of $1.11 \times 10^{-4}$. At the
-boundaries, the magnetic field, velocity, density, and energy are fixed to their
-initial values and their derivatives normal to the
-boundaries are set to zero  except
-where twisting velocity ``driver'', described
-below, is prescribed.
+in a cube of size $[-2,2]^3$, with further test simulations run using an
+elongated domain of size $4\times4\times20$. Initially, the velocity is set
+everywhere to $\vec{u} = \vec{0}$, the density to $\rho = 1$, and the internal
+energy to $\varepsilon = 8.67\times 10^{-4}$. This corresponds to a typical
+coronal temperature of $10^6$ K and a plasma beta of $1.11 \times 10^{-4}$. At
+the boundaries, the magnetic field, velocity, density, and energy are fixed to
+their initial values and their derivatives normal to the boundaries are set to
+zero  except where twisting velocity ``driver'', described below, is
+prescribed.
 
@@
 
-The flux rope is formed by prescribing a slowly accelerating, rotating flow at the upper $z$-boundary as
+The flux rope is formed by prescribing a slowly accelerating, rotating flow at
+the upper $z$-boundary as
 \begin{equation}
@@
 \end{equation}
-where $u_r(r)$ describes the radial profile of the twisting motion in terms of the radius $r^2 = x^2 + y^2$,
+where $u_r(r)$ describes the radial profile of the twisting motion in terms of
+the radius $r^2 = x^2 + y^2$,
 \begin{equation}
@@
 \end{equation}
-where $r_d$ controls the radial extent of the driver, $u_{r0}$ is a normalising factor, and $u_t(t)$ describes the imposed acceleration of the twisting motion,
+where $r_d$ controls the radial extent of the driver, $u_{r0}$ is a normalising
+factor, and $u_t(t)$ describes the imposed acceleration of the twisting motion,
 \begin{equation}
@@
 \end{equation}
-where the parameter $t_r$ controls the time taken to reach the final driver velocity $u_0$.
-The functions $u_r(r)$ and $u_t(t)$ are plotted in figure~\ref{fig:kink_driver}.
-At the lower boundary, the flow is in the opposite direction.
-This form of driver allows the system to be accelerated slowly enough that the production of disruptive shocks and fast waves is minimal.
-It is unavoidable that some waves are produced during the boundary acceleration, however these usefully provide a source of noise which eventually forms a perturbation.
-
-The driver velocity is set to $u_0 = 0.15$, the normalising factor is $u_{r0} = 2.08$, and setting $r_d = 5$ corresponds to a driver constrained to $r<1$ and with a peak velocity at $r\approx 0.38$.
-The ramping time is set to $t_r = 2$, resulting in an acceleration from $0$ to $u_0$ over approximately $5$ Alfv\'en times.
-These driver parameters correspond to a peak rotational period of $T_R = 15.92$, the length of time taken for one full turn to be injected by a single driver.
-Both drivers result in twist being added at a rate of $2\pi$ every $7.96$ Alfv\'en times.
-The twist profile across the entire flux tube develops in such a way that by $t\approx 20$, it is qualitatively similar to those studied in~\citet{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015} however the length of the flux tubes differs significantly.
-This configuration produces a $z$-directed tube of increasingly twisted magnetic field that eventually becomes unstable to both the flute instability and the helical kink instability.
-
-The problem formulated above is solved numerically using the
-  staggered-grid, Lagrangian–Eulerian remap code for 3D MHD
-  simulations Lare3D of~\cite{arberStaggeredGridLagrangian2001} where
-  a  new module for anisotropic viscosity has been
-  included as detailed in~\citet{quinnKelvinHelmholtzInstabilityCollapse2021}. The resolution used in the
-current work is  $512$ grid points per dimension, comparable to the
-highest resolution kink instability studies
-of~\cite{hoodCoronalHeatingMagnetic2009} or medium resolution studies
-of~\cite{barefordShockHeatingNumerical2015}.
+where the parameter $t_r$ controls the time taken to reach the final driver
+velocity $u_0$. The functions $u_r(r)$ and $u_t(t)$ are plotted in
+figure~\ref{fig:kink_driver}. At the lower boundary, the flow is in the
+opposite direction. This form of driver allows the system to be accelerated
+slowly enough that the production of disruptive shocks and fast waves is
+minimal. It is unavoidable that some waves are produced during the boundary
+acceleration, however these usefully provide a source of noise which eventually
+forms a perturbation.
+
+The driver velocity is set to $u_0 = 0.15$, the normalising factor is $u_{r0}
+= 2.08$, and setting $r_d = 5$ corresponds to a driver constrained to $r<1$ and
+with a peak velocity at $r\approx 0.38$. The ramping time is set to $t_r = 2$,
+resulting in an acceleration from $0$ to $u_0$ over approximately $5$ Alfv\'en
+times. These driver parameters correspond to a peak rotational period of $T_R
+= 15.92$, the length of time taken for one full turn to be injected by a single
+driver. Both drivers result in twist being added at a rate of $2\pi$ every
+$7.96$ Alfv\'en times. The twist profile across the entire flux tube develops
+in such a way that by $t\approx 20$, it is qualitatively similar to those
+studied
+in~\citet{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015}
+however the length of the flux tubes differs significantly. This configuration
+produces a $z$-directed tube of increasingly twisted magnetic field that
+eventually becomes unstable to both the flute instability and the helical kink
+instability.
+
+The problem formulated above is solved numerically using the staggered-grid,
+Lagrangian–Eulerian remap code for 3D MHD simulations Lare3D
+of~\cite{arberStaggeredGridLagrangian2001} where a  new module for anisotropic
+viscosity has been included as detailed
+in~\citet{quinnKelvinHelmholtzInstabilityCollapse2021}. The resolution used in
+the current work is  $512$ grid points per dimension, comparable to the highest
+resolution kink instability studies of~\cite{hoodCoronalHeatingMagnetic2009} or
+medium resolution studies of~\cite{barefordShockHeatingNumerical2015}.
 
@@
 
-We focus the attention
-on two selected pairs of  
-simulations, one pair where the background resistivity is set to
-$\eta=10^{-3}$ and another where $\eta=10^{-4}$. As
-in~\citet{quinnEffectAnisotropicViscosity2020}, only background
-resistivity is used. Each pair consists of one simulation
-using isotropic viscosity~\eqref{eq:isotropic_viscous_tensor} and
-another one using the anisotropic model~\eqref{eq:switching_model}. The
-value of viscosity is set to $\nu = 10^{-4}$ in all cases. 
-%
-The overall development of both the flute and the kink
-instabilities is broadly similar for the two values of resistivity and
-is described  initially.
-Similar simulations were performed with a longer flux tube of length $20$ instead of the tubes shown here with length $4$, and the results were found to be qualitatively similar.
-Focus is
-then placed on the detailed description of instabilities in the
-$\eta=10^{-4}$ cases, with the aim of comparing the effects of the two
-viscosity models. Then further features of the $\eta=10^{-3}$
-cases are summarised.
+We focus the attention on two selected pairs of  simulations, one pair where
+the background resistivity is set to $\eta=10^{-3}$ and another where
+$\eta=10^{-4}$. As in~\citet{quinnEffectAnisotropicViscosity2020}, only
+background resistivity is used. Each pair consists of one simulation using
+isotropic viscosity~\eqref{eq:isotropic_viscous_tensor} and another one using
+the anisotropic model~\eqref{eq:switching_model}. The value of viscosity is set
+to $\nu = 10^{-4}$ in all cases.
+
+The overall development of both the flute and the kink instabilities is broadly
+similar for the two values of resistivity and is described  initially. Similar
+simulations were performed with a longer flux tube of length $20$ instead of
+the tubes shown here with length $4$, and the results were found to be
+qualitatively similar. Focus is then placed on the detailed description of
+instabilities in the $\eta=10^{-4}$ cases, with the aim of comparing the
+effects of the two viscosity models. Then further features of the
+$\eta=10^{-3}$ cases are summarised.
 
@@
     \end{subfigure}
-  \mycaption{
-  Gradients in the current density generate pressure gradients through Ohmic
-  heating.}{Axial current density (a), Ohmic heating (b) and pressure (c) as
-  functions of the radial distance from the tube axis. All plots are from
-  anisotropic cases when $t=20$ through the plane $z=0$. Note the sign of the
-  axial current density $j_z$ has been flipped for comparison and the Ohmic
-  heating is given by $Q_{\eta} = \eta j^2$. The pressure profile of an
-  additional test-case where $\eta=0$ is also shown. Line types are indicated
-  in the legend.}%
+  \mycaption{ Gradients in the current density generate pressure gradients
+  through Ohmic heating.}{Axial current density (a), Ohmic heating (b) and
+  pressure (c) as functions of the radial distance from the tube axis. All
+  plots are from anisotropic cases when $t=20$ through the plane $z=0$. Note
+  the sign of the axial current density $j_z$ has been flipped for comparison
+  and the Ohmic heating is given by $Q_{\eta} = \eta j^2$. The pressure profile
+  of an additional test-case where $\eta=0$ is also shown. Line types are
+  indicated in the legend.}
   \label{fig:pressure_and_heating}
@@
 
-Initially and in all cases computed, the
-twisting at the upper and lower boundaries gives rise to a pair of
-torsional Alfv\'en waves which proceed to travel along the tube
-from the upper and lower boundaries to their respective
+Initially and in all cases computed, the twisting at the upper and lower
+boundaries gives rise to a pair of torsional Alfv\'en waves which proceed to
+travel along the tube from the upper and lower boundaries to their respective
 opposite boundaries. The interaction between these waves produces an
-oscillating pattern in the kinetic energy with a period of
-approximately $4$ Alfv\'en times, equal to the time taken for an
-Alfv\'en wave to traverse the entire length of the domain
-as visible early in figure~\ref{fig:kink_ke-4}.
-
-As the field continues to be twisted, currents form, due to the local
-shear in the magnetic field, and heat the plasma through Ohmic
-dissipation. Due to the radial form of the driver, the magnitude of the
-current density is greatest at the axis of the tube, then decreases
-radially outwards as seen in figure~\ref{fig:current_profiles}. The orientation
-of the twisting produces a current flowing in the negative
-$z$-direction for $r\lessapprox0.5$. At $r \approx 0.5$ (corresponding
-to the radius of peak driving velocity) the current switches orientation
-and is in the positive $z$-direction in a shell where $0.5\lessapprox
-r \lessapprox 0.8$. This form of a twisted field with an inner core of
-current in one direction surrounded by a shell of
-oppositely-directed current is similar to the current configuration arising due to the field prescribed in~\citet{quinnEffectAnisotropicViscosity2020}.
+oscillating pattern in the kinetic energy with a period of approximately $4$
+Alfv\'en times, equal to the time taken for an Alfv\'en wave to traverse the
+entire length of the domain as visible early in figure~\ref{fig:kink_ke-4}.
+
+As the field continues to be twisted, currents form, due to the local shear in
+the magnetic field, and heat the plasma through Ohmic dissipation. Due to the
+radial form of the driver, the magnitude of the current density is greatest at
+the axis of the tube, then decreases radially outwards as seen in
+figure~\ref{fig:current_profiles}. The orientation of the twisting produces
+a current flowing in the negative $z$-direction for $r\lessapprox0.5$. At $r
+\approx 0.5$ (corresponding to the radius of peak driving velocity) the current
+switches orientation and is in the positive $z$-direction in a shell where
+$0.5\lessapprox r \lessapprox 0.8$. This form of a twisted field with an inner
+core of current in one direction surrounded by a shell of oppositely-directed
+current is similar to the current configuration arising due to the field
+prescribed in~\citet{quinnEffectAnisotropicViscosity2020}.
 
 This current profile is reflected in the radial Ohmic heating profile
-(figure~\ref{fig:kink_straight_ohmic_heating_profile}) and,
-consequently, in the radial pressure profile
-(figure~\ref{fig:pressure_profiles}). The highly pressurised core
-extends to $r\approx 0.2$--$0.4$ (depending on the value of $\eta$)
-before increasing slightly around $r\approx 0.7$. The secondary bump
-in pressure is due to the outer shell of current. The pressure
-gradient near the axis provides the outwardly directed pressure force
-which competes against the binding action of the magnetic tension
-and this provides the mechanism of
-flute instability excitation.  The magnitude
-of the pressure gradient depends strongly on the value of
-resistivity $\eta$, with lower values producing shallower 
-gradients which (as shall be seen) are more stable to the
-flute instability. Indeed, when $\eta=0$, the radial
-pressure profile is nearly flat and the tube stable to the
-flute instability.
-
-In all cases unstable to the flute instability, it
-occurs  between $t=20$ and $t=30$. The continued driving at the boundaries eventually
-injects enough twist that the tube also becomes unstable to the kink
-instability. This initially develops linearly alongside or shortly
-after the flute instability and then erupts during the
-its  nonlinear phase, dominating the dynamics and
-disrupting the   flute instability. The onset and
-the competition of the two instabilities is strongly affected by
-the value of $\eta$ and the viscosity model used.
+(figure~\ref{fig:kink_straight_ohmic_heating_profile}) and, consequently, in
+the radial pressure profile (figure~\ref{fig:pressure_profiles}). The highly
+pressurised core extends to $r\approx 0.2$--$0.4$ (depending on the value of
+$\eta$) before increasing slightly around $r\approx 0.7$. The secondary bump in
+pressure is due to the outer shell of current. The pressure gradient near the
+axis provides the outwardly directed pressure force which competes against the
+binding action of the magnetic tension and this provides the mechanism of flute
+instability excitation.  The magnitude of the pressure gradient depends
+strongly on the value of resistivity $\eta$, with lower values producing
+shallower gradients which (as shall be seen) are more stable to the flute
+instability. Indeed, when $\eta=0$, the radial pressure profile is nearly flat
+and the tube stable to the flute instability.
+
+In all cases unstable to the flute instability, it occurs  between $t=20$ and
+$t=30$. The continued driving at the boundaries eventually injects enough twist
+that the tube also becomes unstable to the kink instability. This initially
+develops linearly alongside or shortly after the flute instability and then
+erupts during the its  nonlinear phase, dominating the dynamics and disrupting
+the   flute instability. The onset and the competition of the two instabilities
+is strongly affected by the value of $\eta$ and the viscosity model used.
 
@@
     \end{subfigure}
-\mycaption{Pressure profiles during the development of the
-  flute and kink instabilities.}{Shown are
-  density plots of pressure at $z=0$
-  with $\eta = 10^{-4}$ 
-  and for the anisotropic viscosity model}. Note the difference in colour scale
-  in figure~\ref{fig:swi-4_pressure_15}. The development in the
-  isotropic case is similar. 
+\mycaption{Pressure profiles during the development of the flute and kink
+instabilities.}{Shown are density plots of pressure at $z=0$ with $\eta
+= 10^{-4}$ and for the anisotropic viscosity model. Note the difference in
+colour scale in figure~\ref{fig:swi-4_pressure_15}. The development in the
+isotropic case is similar.}
 \label{fig:kink_pressure_slices-4}%
@@
 
-We now describe the evolution and competition of flute and
-  kink instabilities in case of resistivity $\eta=10^{-4}$.
-Figure~\ref{fig:kink_pressure_slices-4} shows the pressure profile
-of the anisotropic viscosity case 
-\eqref{eq:switching_model} at
-time moments $t=26$, $28$ and $30$ and at $z=0$. At $t=26$
-the tube becomes unstable to  flute
-instability with azimuthal wavenumber $m=4$, when the
-plasma begins to  bulge out diagonally from the
-high-pressure core as seen in figure~\ref{fig:swi-4_pressure_13}. As  
-the bulges move radially outwards into lower pressure regions they
-expand and accelerate, resulting in the entire pressure structure
-appearing taking the shape of a four-leaf clover (figure~\ref{fig:swi-4_pressure_14}). By
-$t=30$ the kink instability has disrupted the flute
-instability and is developing nonlinearly
-as evident in figure~\ref{fig:swi-4_pressure_15}. As is typical of nonlinear kink
-development, the tube continues to release its stored potential energy
-in the form of kinetic energy and heat and the contained plasma becomes highly
-mixed. In the  isotropic viscosity case
-which will not be illustrated by a separate figure, the
-flute instability is present but damped, and it is
-  quickly outcompeted by the kink instability which quickly dominates the dynamics.
+We now describe the evolution and competition of flute and kink instabilities
+in case of resistivity $\eta=10^{-4}$. Figure~\ref{fig:kink_pressure_slices-4}
+shows the pressure profile of the anisotropic viscosity case
+\eqref{eq:switching_model} at time moments $t=26$, $28$ and $30$ and at $z=0$.
+At $t=26$ the tube becomes unstable to  flute instability with azimuthal
+wavenumber $m=4$, when the plasma begins to  bulge out diagonally from the
+high-pressure core as seen in figure~\ref{fig:swi-4_pressure_13}. As  the
+bulges move radially outwards into lower pressure regions they expand and
+accelerate, resulting in the entire pressure structure appearing taking the
+shape of a four-leaf clover (figure~\ref{fig:swi-4_pressure_14}). By $t=30$ the
+kink instability has disrupted the flute instability and is developing
+nonlinearly as evident in figure~\ref{fig:swi-4_pressure_15}. As is typical of
+nonlinear kink development, the tube continues to release its stored potential
+energy in the form of kinetic energy and heat and the contained plasma becomes
+highly mixed. In the  isotropic viscosity case which will not be illustrated by
+a separate figure, the flute instability is present but damped, and it is
+quickly outcompeted by the kink instability which quickly dominates the
+dynamics.
 
@@
     \end{subfigure}
-\mycaption{Simultaneous development of flute and kink
-  instabilities in the isotropic and anisotropic cases
-  illustrated by field lines and pressure contours.}{Field
-  lines and contours of pressure (where $p=0.3$) are plotted at
-  $t=28$.
-Also shown is the velocity driver $u_r(\sqrt{x^2+y^2})$ at $z=2$.
-The flute instability grows in both cases, though faster in the anisotropic case.
-The initial stages of the kink instability can also be observed in the field lines of the isotropic case in subfigure~\ref{fig:field_line_plots_iso}.}
+\mycaption{Simultaneous development of flute and kink instabilities in the
+isotropic and anisotropic cases illustrated by field lines and pressure
+contours.}{Field lines and contours of pressure (where $p=0.3$) are plotted at
+$t=28$. Also shown is the velocity driver $u_r(\sqrt{x^2+y^2})$ at $z=2$. The
+flute instability grows in both cases, though faster in the anisotropic case.
+The initial stages of the kink instability can also be observed in the field
+lines of the isotropic case in subfigure~\ref{fig:field_line_plots_iso}.}
 \label{fig:kink_field_line_plots}%
@@
 
-Despite the flute instability appearing in the isotropic
-case (figure~\ref{fig:field_line_plots_iso}), only in the
-anisotropic case can the onset of both the
-flute and kink instabilities be seen in the kinetic
-energy profile shown in figure~\ref{fig:kink_ke_log-4}. Here, the nonlinear
-growth rates of the two instabilities are found to be $\gamma = 0.69$
-for the flute and $\lambda = 2.55$ for the kink. The
-onset times are approximately $t=27$ for the flute
-instability and $t=29.5$ for
-the kink. In the isotropic case, the growth rate of the kink, $\lambda
-= 2.97$, is larger than in the anisotropic case,
-although the onset times appear similar, and the kinetic energy
-profile shows no evidence of flute instability growth.
-
-The faster growth of the kink compared to that measured in~
-\citet{quinnEffectAnisotropicViscosity2020} is attributed to
-the relative aspect ratios of the flux tubes. The tube prescribed in
-~\citep{quinnEffectAnisotropicViscosity2020} has an aspect
-ratio of approximately $20$ compared to the tube studied here which
-has an aspect ratio of approximately $4$. While the total twist is
-similar in both tubes (after the drivers have injected twist up to
-$t\approx20$) the small aspect ratio results in more turns per unit
-length, leading to a faster growing instability.
+Despite the flute instability appearing in the isotropic case
+(figure~\ref{fig:field_line_plots_iso}), only in the anisotropic case can the
+onset of both the flute and kink instabilities be seen in the kinetic energy
+profile shown in figure~\ref{fig:kink_ke_log-4}. Here, the nonlinear growth
+rates of the two instabilities are found to be $\gamma = 0.69$ for the flute
+and $\lambda = 2.55$ for the kink. The onset times are approximately $t=27$ for
+the flute instability and $t=29.5$ for the kink. In the isotropic case, the
+growth rate of the kink, $\lambda = 2.97$, is larger than in the anisotropic
+case, although the onset times appear similar, and the kinetic energy profile
+shows no evidence of flute instability growth.
+
+The faster growth of the kink compared to that measured in~\citet{quinnEffectAnisotropicViscosity2020} is attributed to the relative
+aspect ratios of the flux tubes. The tube prescribed in~\citep{quinnEffectAnisotropicViscosity2020} has an aspect ratio of
+approximately $20$ compared to the tube studied here which has an aspect ratio
+of approximately $4$. While the total twist is similar in both tubes (after the
+drivers have injected twist up to $t\approx20$) the small aspect ratio results
+in more turns per unit length, leading to a faster growing instability.
 
@@
     \end{subfigure}
-\mycaption{Stability and linear growth rate of the flute
-  instability.}{In panel \ref{fig:suydam_condition_4}, Suydam's stability
-  criterion \eqref{eq:suydams_criterion} and is contributing
-  terms   are plotted and in
-  panel \ref{fig:growth_rate_4} the predicted linear growth rate~\eqref{eq:fluting_growth_rate2} is plotted.
-Both plots are produced at $t=20$ for $\eta=10^{-4}$ and using the anisotropic model.
-The location of the peak linear growth rate is also shown.}
+\mycaption{Stability and linear growth rate of the flute instability.}{In panel
+\ref{fig:suydam_condition_4}, Suydam's stability criterion
+\eqref{eq:suydams_criterion} and is contributing terms   are plotted and in
+panel \ref{fig:growth_rate_4} the predicted linear growth
+rate~\eqref{eq:fluting_growth_rate2} is plotted. Both plots are produced at
+$t=20$ for $\eta=10^{-4}$ and using the anisotropic model. The location of the
+peak linear growth rate is also shown.}
 \label{fig:stability_and_growth}%
@@
 
-Prior to the onset of either instability, the flux tube is found to be
-linearly unstable to perturbations of the
-form~\eqref{eq:kink_perturbation} at $t=20$ via Suydam's
-criterion~\eqref{eq:suydams_criterion}
-(figure~\ref{fig:suydam_condition_4}). The criterion represents a
-balance between destabilising pressure gradients and stabilising
-magnetic shear and in this case, the shear is so small and the
-pressure gradient so large that the tube is unstable over a wide range
-of radii, for $ 0.02 \lessapprox r \lessapprox 0.29$. The measure of
-linear fluting growth rate $\gamma$ is plotted as a function of $r$ at
-the same time (figure~\ref{fig:growth_rate_4}).
-The location of the peak growth matches nearly exactly the location of the resonant surface where the observed perturbation grows (figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate can be found by averaging $\gamma$ over $r$, giving a growth rate of $0.86$.
+Prior to the onset of either instability, the flux tube is found to be linearly
+unstable to perturbations of the form~\eqref{eq:kink_perturbation} at $t=20$
+via Suydam's criterion~\eqref{eq:suydams_criterion}
+(figure~\ref{fig:suydam_condition_4}). The criterion represents a balance
+between destabilising pressure gradients and stabilising magnetic shear and in
+this case, the shear is so small and the pressure gradient so large that the
+tube is unstable over a wide range of radii, for $ 0.02 \lessapprox
+r \lessapprox 0.29$. The measure of linear fluting growth rate $\gamma$ is
+plotted as a function of $r$ at the same time (figure~\ref{fig:growth_rate_4}).
+The location of the peak growth matches nearly exactly the location of the
+resonant surface where the observed perturbation grows
+(figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate
+can be found by averaging $\gamma$ over $r$, giving a growth rate of $0.86$.
 
@@
     \end{subfigure}
-\mycaption{Perturbations corresponding to the flute and
-  kink instabilities and the spatial radial distribution of the
-  associated resonance function.}{Pressure and velocity perturbations
-  in $z$ (corresponding to the flute and kink
-  instabilities, respectively) and of the resonance
-  surface $m B_{\theta}(r)/r + kB_z(r)$ as a function
-  of $r$ using the observed fluting perturbation wavenumbers. All
-  plots are  snapshots at $t=26$ where $\eta=10^{-4}$ and
-  the viscosity model is anisotropic.} 
+\mycaption{Perturbations corresponding to the flute and kink instabilities and
+the spatial radial distribution of the associated resonance function.}{Pressure
+and velocity perturbations in $z$ (corresponding to the flute and kink
+instabilities, respectively) and of the resonance surface $m B_{\theta}(r)/r
++ kB_z(r)$ as a function of $r$ using the observed fluting perturbation
+wavenumbers. All plots are  snapshots at $t=26$ where $\eta=10^{-4}$ and the
+viscosity model is anisotropic.} 
 \label{fig:k_and_resonance}%
@@
 
-The observed
-  perturbations corresponding to the flute and kink
-  instabilities at $t=26$ are shown in
-  Figure~\ref{fig:pressure_pert_4}. The fluting perturbation is
-  most easily observed in the pressure and is plotted as a function of $z$
-  following a line through the point $(r, \theta) = (0.101, 0)$. The
-  kink instability is best revealed in the $x$-velocity (a proxy for the
-  radial velocity) through the axis. Comparing the magnitudes of the
-  perturbations at this time suggests the flute
-  instability is close to transitioning to its nonlinear phase while
-  the kink instability is still very much in its linear
+The observed perturbations corresponding to the flute and kink instabilities at
+$t=26$ are shown in Figure~\ref{fig:pressure_pert_4}. The fluting perturbation
+is most easily observed in the pressure and is plotted as a function of $z$
+following a line through the point $(r, \theta) = (0.101, 0)$. The kink
+instability is best revealed in the $x$-velocity (a proxy for the radial
+velocity) through the axis. Comparing the magnitudes of the perturbations at
+this time suggests the flute instability is close to transitioning to its
+nonlinear phase while the kink instability is still very much in its linear
 phase.
 
-The value of $k$ for each perturbation is calculated as $k = 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the perturbation, measured as the difference between the two peaks closest to $z=0$ (thus minimising the influence of line-tying on the measurement).
-This gives a value of $k_{\text{flute}}=23.61$ and $k_{\text{kink}}=4.57$ for both viscosity models.
-Hence, the observed most unstable fluting perturbation is that of the form~\eqref{eq:kink_perturbation} where $m=4$ and $k=23.61$ and the observed kink instability is that where $m=1$ and $k=4.57$.
-Using these values, it is observed that the fluting perturbation exactly resonates with the field, that is $m B_{\theta}(r)/r + kB_z(r) = 0$, at $r=0.125$ (figure~\ref{fig:resonant_surface_4}).
-This is precisely the predicted radius of peak linear growth (figure~\ref{fig:growth_rate_4}).
-At this time the perturbation is close to resonance, that is $m B_{\theta}(r)/r + kB_z(r) \approx 0$, over a range of radii from $r=0.125$ to $0.2$.
-
-Comparing the effect of the viscous models on the perturbations, in the isotropic case, the fluting perturbation is damped, while in the anisotropic case the kink perturbation is diminished, explaining why the flute instability appears more readily in the anisotropic case (figure~\ref{fig:kink_ke-4}).
+The value of $k$ for each perturbation is calculated as $k
+= 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the
+perturbation, measured as the difference between the two peaks closest to $z=0$
+(thus minimising the influence of line-tying on the measurement). This gives
+a value of $k_{\text{flute}}=23.61$ and $k_{\text{kink}}=4.57$ for both
+viscosity models. Hence, the observed most unstable fluting perturbation is
+that of the form~\eqref{eq:kink_perturbation} where $m=4$ and $k=23.61$ and the
+observed kink instability is that where $m=1$ and $k=4.57$. Using these values,
+it is observed that the fluting perturbation exactly resonates with the field,
+that is $m B_{\theta}(r)/r + kB_z(r) = 0$, at $r=0.125$
+(figure~\ref{fig:resonant_surface_4}). This is precisely the predicted radius
+of peak linear growth (figure~\ref{fig:growth_rate_4}). At this time the
+perturbation is close to resonance, that is $m B_{\theta}(r)/r + kB_z(r)
+\approx 0$, over a range of radii from $r=0.125$ to $0.2$.
+
+Comparing the effect of the viscous models on the perturbations, in the
+isotropic case, the fluting perturbation is damped, while in the anisotropic
+case the kink perturbation is diminished, explaining why the flute instability
+appears more readily in the anisotropic case (figure~\ref{fig:kink_ke-4}).
 
@@
     \end{subfigure}
-\mycaption{Pressure profiles at $z=0$ during the development of the flute and kink instabilities in the higher resistivity anisotropic case.}{The viscosity model is anisotropic and $\eta = 10^{-3}$.
-In contrast to the case of $\eta=10^{-4}$, the nonlinear development of the flute instability has time to mix the interior of the flux tube before the onset of the kink instability, the growth of which is affected by the mixed plasma.}
+\mycaption{Pressure profiles at $z=0$ during the development of the flute and
+kink instabilities in the higher resistivity anisotropic case.}{The viscosity
+model is anisotropic and $\eta = 10^{-3}$. In contrast to the case of
+$\eta=10^{-4}$, the nonlinear development of the flute instability has time to
+mix the interior of the flux tube before the onset of the kink instability, the
+growth of which is affected by the mixed plasma.}
 \label{fig:kink_pressure_slices-3}%
@@
 
-Figure
-  \ref{fig:kink_pressure_slices-3} shows a prolonged 
-development of the flute instability and a slow
-nonlinear development of the kink instability at the higher
-  resistivity value $\eta=10^{-3}$ in the case of anisotropic viscosity. Due to the enhanced Ohmic heating 
-at $\eta=10^{-3}$, the pressure gradient is substantially stronger
-than at $\eta=10^{-4}$ and the flute instability is
-excited much earlier. Compared to the $\eta=10^{-4}$ cases, the
-instability occurs further from the axis, at $r\approx0.16$, and the
-larger pressure gradient drives the bulges in profile further
-from the axis during the nonlinear phase
-(figure~\ref{fig:swi-3_pressure_12}). These bulges continue to extend
-outwards and mix the plasma as they develop. The kink instability can
-be observed moving the axis of the tube diagonally upwards and to the
-right in figure~\ref{fig:swi-3_pressure_15}. At this time in the
-$\eta=10^{-4}$ cases, the nonlinear development of the kink was
-at a later stage of its development (figure~\ref{fig:swi-4_pressure_15}). The development of
-the kink then proceeds slowly as it moves the axis of the tube through
-the mixed region to eventually begin the reconnection process with the
-outer region of field that is typical of the instability in this kind
-of flux tube (as was observed in
-our earlier work~\citep{quinnEffectAnisotropicViscosity2020}).
+Figure \ref{fig:kink_pressure_slices-3} shows a prolonged development of the
+flute instability and a slow nonlinear development of the kink instability at
+the higher resistivity value $\eta=10^{-3}$ in the case of anisotropic
+viscosity. Due to the enhanced Ohmic heating at $\eta=10^{-3}$, the pressure
+gradient is substantially stronger than at $\eta=10^{-4}$ and the flute
+instability is excited much earlier. Compared to the $\eta=10^{-4}$ cases, the
+instability occurs further from the axis, at $r\approx0.16$, and the larger
+pressure gradient drives the bulges in profile further from the axis during the
+nonlinear phase (figure~\ref{fig:swi-3_pressure_12}). These bulges continue to
+extend outwards and mix the plasma as they develop. The kink instability can be
+observed moving the axis of the tube diagonally upwards and to the right in
+figure~\ref{fig:swi-3_pressure_15}. At this time in the $\eta=10^{-4}$ cases,
+the nonlinear development of the kink was at a later stage of its development
+(figure~\ref{fig:swi-4_pressure_15}). The development of the kink then proceeds
+slowly as it moves the axis of the tube through the mixed region to eventually
+begin the reconnection process with the outer region of field that is typical
+of the instability in this kind of flux tube (as was observed in our earlier
+work~\citep{quinnEffectAnisotropicViscosity2020}).
 
@@
     \end{subfigure}
-\mycaption{Kinetic energy as a function of time in the cases where $\eta=10^{-3}$.}{The results from both viscosity models are shown.
-The flute instability appears earlier than where $\eta=10^{-4}$ and the growth rate of the kink instability is decreased.}
+\mycaption{Kinetic energy as a function of time in the cases where
+$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
+instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
+the kink instability is decreased.}
 \label{fig:kink_str8_ke-3}%
@@
 
-It is evident from the kinetic energy profile that the flute instability develops much earlier than in the $\eta=10^{-4}$ cases and grows at an increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}).
-The kink instability grows at a rate of $\lambda \approx 0.15$, much slower than that observed in the $\eta=10^{-4}$ cases, and much lower than the flute instability.
-One key observation is that, despite the early and disruptive growth of the flute instability, the kink instability still generates the bulk of the kinetic energy (figure~\ref{fig:kink_ke-3}).
-
-Due to the influence of the drivers on the kinetic energy, the fluting growth rate is difficult to estimate from the kinetic energy profile as accurately as in the $\eta=10^{-4}$ cases.
-Since the kink instability occurs after the development of the fluting, its growth rate is similarly difficult to gauge.
-Nevertheless, it is clear that the flute instability grows at a rate of the same order as that in the $\eta=10^{-4}$ cases.
-It is also apparent that the kink instability grows much slower in the $\eta=10^{-3}$ cases.
+It is evident from the kinetic energy profile that the flute instability
+develops much earlier than in the $\eta=10^{-4}$ cases and grows at an
+increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}). The kink
+instability grows at a rate of $\lambda \approx 0.15$, much slower than that
+observed in the $\eta=10^{-4}$ cases, and much lower than the flute
+instability. One key observation is that, despite the early and disruptive
+growth of the flute instability, the kink instability still generates the bulk
+of the kinetic energy (figure~\ref{fig:kink_ke-3}).
+
+Due to the influence of the drivers on the kinetic energy, the fluting growth
+rate is difficult to estimate from the kinetic energy profile as accurately as
+in the $\eta=10^{-4}$ cases. Since the kink instability occurs after the
+development of the fluting, its growth rate is similarly difficult to gauge.
+Nevertheless, it is clear that the flute instability grows at a rate of the
+same order as that in the $\eta=10^{-4}$ cases. It is also apparent that the
+kink instability grows much slower in the $\eta=10^{-3}$ cases.
 
 \begin{table}
-\caption{Quantitative differences in the observed perturbations
-  between results between different
-    resistivity values $\eta$. In all measurements the
+\caption{Quantitative differences in the observed perturbations between results
+between different resistivity values $\eta$. In all measurements the
 anisotropic viscosity model is used except for $k_\text{kink}$ where the
-  isotropic viscosity model us used. Measurements times are listed in
-  the main text.}
+isotropic viscosity model us used. Measurements times are listed in the main
+text.}
 \centering
@@
 
-Table~\ref{tab:kink_fluting_params} summarises the quantitative
-differences between the results for the two values of the
-  resistivity $\eta$.
-All values are calculated from simulations using the anisotropic model with the exception of $k_{\text{kink}}$ which is measured from isotropic results due to noise in the anisotropic case (the value of $k_{\text{kink}}$ appears similar, however).
-The results of the isotropic cases are qualitatively similar.
-The radius of peak $\gamma$ is calculated at time $t=20$.
-The fluting wavenumber $k$ and observed $r_s$ are measured at times just prior to the nonlinear development of the flute instability, that is at $t=22$ when $\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$.
-The kink wavenumber is measured at $t=26$ in both cases.
+Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
+between the results for the two values of the resistivity $\eta$. All values
+are calculated from simulations using the anisotropic model with the exception
+of $k_{\text{kink}}$ which is measured from isotropic results due to noise in
+the anisotropic case (the value of $k_{\text{kink}}$ appears similar, however).
+The results of the isotropic cases are qualitatively similar. The radius of
+peak $\gamma$ is calculated at time $t=20$. The fluting wavenumber $k$ and
+observed $r_s$ are measured at times just prior to the nonlinear development of
+the flute instability, that is at $t=22$ when $\eta=10^{-3}$ and $t=26$ when
+$\eta = 10^{-4}$. The kink wavenumber is measured at $t=26$ in both cases.
 These times allow fair comparison between measurements.
 
-The longitudinal wavenumber $k_{\text{kink}}$ of the observed kink perturbation remains similar in both cases since the instability is essentially governed by the twist injected by the driver which remains the same in both cases.
-In contrast, the longitudinal wavenumber $k_{\text{flute}}$ of the observed fluting perturbation is lower in the $\eta=10^{-3}$ cases.
-This is due to the different resonant surface within which the perturbation grows, the location being dictated by the peak of the linear growth rate.
-Note that the location of this peak again matches well the location of the observed resonant surface, as in the $\eta=10^{-4}$ cases.
-Similar to the $\eta=10^{-4}$ cases, the peak growth rate predicted by the linear analysis is the same order of magnitude as the observed growth rate.
+The longitudinal wavenumber $k_{\text{kink}}$ of the observed kink perturbation
+remains similar in both cases since the instability is essentially governed by
+the twist injected by the driver which remains the same in both cases. In
+contrast, the longitudinal wavenumber $k_{\text{flute}}$ of the observed
+fluting perturbation is lower in the $\eta=10^{-3}$ cases. This is due to the
+different resonant surface within which the perturbation grows, the location
+being dictated by the peak of the linear growth rate. Note that the location of
+this peak again matches well the location of the observed resonant surface, as
+in the $\eta=10^{-4}$ cases. Similar to the $\eta=10^{-4}$ cases, the peak
+growth rate predicted by the linear analysis is the same order of magnitude as
+the observed growth rate.
 
@@
 
-It is
-likely that the $m=4$ azimuthal perturbation is excited due to
-influences from the boundaries in the Cartesian box, for example
-through the interaction of reflected fast waves generated in part by
-the driver. Performing a similar experiment in a cylindrical numerical
-domain, or prescribing a variety of perturbations in the Cartesian
-domain may reveal other, faster growing modes. The modes may also be
-influenced by nonlinear coupling between the $m>1$ and $m=1$ modes, as
-is found in the study of kink and flute
+It is likely that the $m=4$ azimuthal perturbation is excited due to influences
+from the boundaries in the Cartesian box, for example through the interaction
+of reflected fast waves generated in part by the driver. Performing a similar
+experiment in a cylindrical numerical domain, or prescribing a variety of
+perturbations in the Cartesian domain may reveal other, faster growing modes.
+The modes may also be influenced by nonlinear coupling between the $m>1$ and
+$m=1$ modes, as is found in the study of kink and flute
 oscillations~\citep{terradasEffectMagneticTwist2018,rudermanNonlinearGenerationFluting2017}.
 
-As the current distribution, which develops as the flux tube is twisted, is similar to that found in the initial flux tube configuration of~\cite{quinnEffectAnisotropicViscosity2020},the question arises why the fluting instability is not observed in the latter.
-Although the current distribution (and thus heating and pressure distributions) in the tubes of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute instability, the tube is initially perturbed with a motion close to an unstable eigenmode of the kink instability, resulting in the instability growing from $t=0$.
-In contrast, in the tubes studied here, such a perturbation must build from numerical noise, allowing a secondary, fluting perturbation to also build and become significant enough to observe.
-
-Our set of numerical experiments has
-shown that the mixing as a result of the nonlinear flute
-instability appears to slow the growth of the kink instability. It seems unlikely that in
- the linear regime the perturbations of the
-flute and kink are able to directly couple, given that
-the kink instability generally presents at the axis of a flux tube and
-the flute at some resonant surface away from the
-axis. Further investigation of the nonlinear interaction between the
+As the current distribution, which develops as the flux tube is twisted, is
+similar to that found in the initial flux tube configuration
+of~\cite{quinnEffectAnisotropicViscosity2020},the question arises why the
+fluting instability is not observed in the latter. Although the current
+distribution (and thus heating and pressure distributions) in the tubes
+of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute
+instability, the tube is initially perturbed with a motion close to an unstable
+eigenmode of the kink instability, resulting in the instability growing from
+$t=0$. In contrast, in the tubes studied here, such a perturbation must build
+from numerical noise, allowing a secondary, fluting perturbation to also build
+and become significant enough to observe.
+
+Our set of numerical experiments has shown that the mixing as a result of the
+nonlinear flute instability appears to slow the growth of the kink instability.
+It seems unlikely that in the linear regime the perturbations of the flute and
+kink are able to directly couple, given that the kink instability generally
+presents at the axis of a flux tube and the flute at some resonant surface away
+from the axis. Further investigation of the nonlinear interaction between the
 two instabilities is required.
 
-Since the main driver of the flute instability is the
-pressure gradient generated through Ohmic heating, it is prudent to
-ask if the same pressure gradient could be generated using physical
-coronal values of the resistivity, which are estimated to be
-approximately
-$\eta=10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a},
-and are thus much smaller than those studied
-here. Additionally, the simulations presented here do not incorporate
-radiation or thermal conduction, two processes which would remove
-energy (and hence reduce pressure) from high-pressure regions in a coronal
-loop and thus could prevent meeting the required
-conditions for the growth of a 
-flute instability. Indeed, at $\eta=10^{-4}$ the
-flute instability was more quickly outcompeted by the kink
-instability and appeared to have little impact on the resultant
-dynamics, which mirror those of other kink instability studies, e.g.~\citep{hoodCoronalHeatingMagnetic2009}. This suggests that even
-lower values of resistivity would result in flux tubes without any
-significant flute instability, at least for this form of
-driver and mechanism of pressure generation. Regardless, coronal loops
-with strong radial pressure gradients have been
-observed~\citep{foukalTemperatureStructurePressure1975}, and such loops
-may be unstable to the flute instability. Modelling of a
-prescribed flute-unstable flux tube, as opposed to the dynamically
-stressed loop investigated here, would provide a useful comparison to
-observations, however it may be difficult to prescribe a tube which is
-not also susceptible to kinking. Linear stability analyses of this
-kind of flux tube (a dynamically created zero total axial current
-tube) focus on the kink
-instability~\citep{browningSolarCoronalHeating2003b} so do not provide
-much insight into the potential for fluting without a kink.
-
-While our results show that a flux tube can be unstable to
-the flute instability and yet the faster growing kink
-instability can quickly dominate when the pressure gradient is small
-enough, the opposite case is also observed. A faster growing flute instability appears to slow the growth of
-the kink instability although, importantly, it does not fully disrupt
-the development of the kink. Understanding the balance between the
-nonlinear growth rates of the two instabilities is important for prediction of whether the flute instability may be found
-at all in the real solar corona, or whether its realistic growth rate is
-too slow compared to that of the kink instability.
+Since the main driver of the flute instability is the pressure gradient
+generated through Ohmic heating, it is prudent to ask if the same pressure
+gradient could be generated using physical coronal values of the resistivity,
+which are estimated to be approximately
+$\eta=10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a}, and are thus
+much smaller than those studied here. Additionally, the simulations presented
+here do not incorporate radiation or thermal conduction, two processes which
+would remove energy (and hence reduce pressure) from high-pressure regions in
+a coronal loop and thus could prevent meeting the required conditions for the
+growth of a flute instability. Indeed, at $\eta=10^{-4}$ the flute instability
+was more quickly outcompeted by the kink instability and appeared to have
+little impact on the resultant dynamics, which mirror those of other kink
+instability studies, e.g.~\citep{hoodCoronalHeatingMagnetic2009}. This suggests
+that even lower values of resistivity would result in flux tubes without any
+significant flute instability, at least for this form of driver and mechanism
+of pressure generation. Regardless, coronal loops with strong radial pressure
+gradients have been observed~\citep{foukalTemperatureStructurePressure1975},
+and such loops may be unstable to the flute instability. Modelling of
+a prescribed flute-unstable flux tube, as opposed to the dynamically stressed
+loop investigated here, would provide a useful comparison to observations,
+however it may be difficult to prescribe a tube which is not also susceptible
+to kinking. Linear stability analyses of this kind of flux tube (a dynamically
+created zero total axial current tube) focus on the kink
+instability~\citep{browningSolarCoronalHeating2003b} so do not provide much
+insight into the potential for fluting without a kink.
+
+While our results show that a flux tube can be unstable to the flute
+instability and yet the faster growing kink instability can quickly dominate
+when the pressure gradient is small enough, the opposite case is also observed.
+A faster growing flute instability appears to slow the growth of the kink
+instability although, importantly, it does not fully disrupt the development of
+the kink. Understanding the balance between the nonlinear growth rates of the
+two instabilities is important for prediction of whether the flute instability
+may be found at all in the real solar corona, or whether its realistic growth
+rate is too slow compared to that of the kink instability.
 
@@
 
-This paper details the nonlinear development of two
-ideal instabilities, the kink and the flute instabilities,
-both of which develop naturally in the course of twisting an initially
-straight magnetic flux tube. This provides a different approach to
-that employed in the simulations performed in our earlier
-  study~\citep{quinnEffectAnisotropicViscosity2020} in that the
-instabilities are not excited by any prescribed perturbations but,
-instead, the field is dynamically driven into an unstable state and
-the perturbations provided by noise in the system. Not only is the
-kink instability excited due to the twist in the field, but nearly simultaneously a pressure-driven flute
-instability can also be excited in unstable pressure gradients
-generated by Ohmic heating. Simulations 
-were performed with two values of resistivity,
-$\eta=10^{-3}$ and $10^{-4}$, and for two forms of viscosity, isotropic and
-anisotropic. The results prove an
-initial and important first step towards
-understanding nonlinear flute instabilities in the
-solar corona.
-
-It has been shown that the flute instability can be quickly dominated by the kink instability if the kink grows substantially faster than the flute.
-However, if the flute has time to develop nonlinearly, it mixes the plasma within the flux tube, generating small scale current sheets and releasing some magnetic energy.
-The overall effect of this mixing is to slow the growth of the kink instability.
-The slowed growth of the kink does not appear to significantly impact the kinetic energy released during its evolution, only the time over which it is released.
-
-The form of viscosity has been found to significantly affect the
-growth of the flute instability. Importantly, isotropic
-viscosity is found to damp the growth of the flute
-instability to the degree that it is unable to grow appreciably before
-the onset of the faster growing nonlinear kink instability. Overall,
-the anisotropic model permits greater release of
-kinetic energy. Similar to 
-\citep{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating
-is found to be lower than anisotropic (switching)
-viscous heating, by approximately two orders of magnitude.
-
-These numerical experiments have provided evidence that the flute instability can occur in twisted magnetic flux ropes and grow at similar rates to the kink instability.
-Further estimation of the relative growth rates in more realistic coronal loop setups is required to fully understand if the flute instability plays a pertinent role in coronal loop physics.
+This paper details the nonlinear development of two ideal instabilities, the
+kink and the flute instabilities, both of which develop naturally in the course
+of twisting an initially straight magnetic flux tube. This provides a different
+approach to that employed in the simulations performed in our earlier
+study~\citep{quinnEffectAnisotropicViscosity2020} in that the instabilities are
+not excited by any prescribed perturbations but, instead, the field is
+dynamically driven into an unstable state and the perturbations provided by
+noise in the system. Not only is the kink instability excited due to the twist
+in the field, but nearly simultaneously a pressure-driven flute instability can
+also be excited in unstable pressure gradients generated by Ohmic heating.
+Simulations were performed with two values of resistivity, $\eta=10^{-3}$ and
+$10^{-4}$, and for two forms of viscosity, isotropic and anisotropic. The
+results prove an initial and important first step towards understanding
+nonlinear flute instabilities in the solar corona.
+
+It has been shown that the flute instability can be quickly dominated by the
+kink instability if the kink grows substantially faster than the flute.
+However, if the flute has time to develop nonlinearly, it mixes the plasma
+within the flux tube, generating small scale current sheets and releasing some
+magnetic energy. The overall effect of this mixing is to slow the growth of the
+kink instability. The slowed growth of the kink does not appear to
+significantly impact the kinetic energy released during its evolution, only the
+time over which it is released.
+
+The form of viscosity has been found to significantly affect the growth of the
+flute instability. Importantly, isotropic viscosity is found to damp the growth
+of the flute instability to the degree that it is unable to grow appreciably
+before the onset of the faster growing nonlinear kink instability. Overall, the
+anisotropic model permits greater release of kinetic energy. Similar to
+\citep{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating is found
+to be lower than anisotropic (switching) viscous heating, by approximately two
+orders of magnitude.
+
+These numerical experiments have provided evidence that the flute instability
+can occur in twisted magnetic flux ropes and grow at similar rates to the kink
+instability. Further estimation of the relative growth rates in more realistic
+coronal loop setups is required to fully understand if the flute instability
+plays a pertinent role in coronal loop physics.
 
@@
 
-We would like to thank David MacTaggart for his input on the thesis chapter on which this paper is based. Results were obtained using the ARCHIE-WeSt High Performance Computer
-(\url{www.archie-west.ac.uk}) based at the University of
+We would like to thank David MacTaggart for his input on the thesis chapter on
+which this paper is based. Results were obtained using the ARCHIE-WeSt High
+Performance Computer (\url{www.archie-west.ac.uk}) based at the University of
 Strathclyde. JQ was funded via an EPSRC studentship: EPSRC DTG EP/N509668/1.
@@
 
-A custom version of Lare3d~\citep{arberStaggeredGridLagrangian2001} has been developed where a new module for anisotropic viscosity has been included.
-The version including the new module can be found at \url{https://github.com/jamiejquinn/Lare3d}, and has been archived at~\citep{keith_bennett_2020_4155546}.
-The version of Lare3d used in the production of the results presented here, including initial conditions, boundary conditions, control parameters and the anisotropic viscosity module, can be found in~\citet{keith_bennett_2020_4155625}.
-The data analysis and instructions for reproducing all results found in this report may be also found at \url{https://github.com/JamieJQuinn/coronal-fluting-instability-analysis} and has been archived~\citep{quinnJamieJQuinnCoronalflutinginstabilityanalysis2021}.
-
-All simulations were performed on a single, multi-core machine with $40$ cores provided by Intel Xeon Gold 6138 Skylake processor running at $2$ GHz and $192$ GB of RAM, although this amount of RAM is much higher than was required; a conservative estimate of the memory used in the largest simulations is around $64$ GB.
-Most simulations completed in under $2$ days.
+A custom version of Lare3d~\citep{arberStaggeredGridLagrangian2001} has been
+developed where a new module for anisotropic viscosity has been included. The
+version including the new module can be found at
+\url{https://github.com/jamiejquinn/Lare3d}, and has been archived
+at~\citep{keith_bennett_2020_4155546}. The version of Lare3d used in the
+production of the results presented here, including initial conditions,
+boundary conditions, control parameters and the anisotropic viscosity module,
+can be found in~\citet{keith_bennett_2020_4155625}. The data analysis and
+instructions for reproducing all results found in this report may be also found
+at \url{https://github.com/JamieJQuinn/coronal-fluting-instability-analysis}
+and has been
+archived~\citep{quinnJamieJQuinnCoronalflutinginstabilityanalysis2021}.
+
+All simulations were performed on a single, multi-core machine with $40$ cores
+provided by Intel Xeon Gold 6138 Skylake processor running at $2$ GHz and $192$
+GB of RAM, although this amount of RAM is much higher than was required;
+a conservative estimate of the memory used in the largest simulations is around
+$64$ GB. Most simulations completed in under $2$ days.
 

### 2021-12-02 paper.tex
Fix all citations in text

@@
 captures the main physics of viscosity in the solar corona as outlined in the
-analysis of \cite{braginskiiTransportProcessesPlasma1965}, namely parallel
+analysis of~\cite{braginskiiTransportProcessesPlasma1965}, namely parallel
 viscosity in regions of strong field  strength and isotropic viscosity in
@@
 \eqref{eq:isotropic_viscous_tensor} and \eqref{eq:switching_model} arise as
-asymptotic limits of the more general switching model used in our earlier works
-\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
+asymptotic limits of the more general switching model used in our earlier works~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
 which, includes both isotropic and anisotropic contributions and can switch
@@
 The faster growth of the kink compared to that measured in~\citet{quinnEffectAnisotropicViscosity2020} is attributed to the relative
-aspect ratios of the flux tubes. The tube prescribed in~\citep{quinnEffectAnisotropicViscosity2020} has an aspect ratio of
+aspect ratios of the flux tubes. The tube prescribed in~\citet{quinnEffectAnisotropicViscosity2020} has an aspect ratio of
 approximately $20$ compared to the tube studied here which has an aspect ratio
@@
 little impact on the resultant dynamics, which mirror those of other kink
-instability studies, e.g.~\citep{hoodCoronalHeatingMagnetic2009}. This suggests
+instability studies~\citep{hoodCoronalHeatingMagnetic2009}. This suggests
 that even lower values of resistivity would result in flux tubes without any
@@
 before the onset of the faster growing nonlinear kink instability. Overall, the
-anisotropic model permits greater release of kinetic energy. Similar to
-\citep{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating is found
+anisotropic model permits greater release of kinetic energy. Similar to~\citet{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating is found
 to be lower than anisotropic (switching) viscous heating, by approximately two

### 2021-12-02 paper.tex
Fix reviewers language comments

@@
 
-In addition to our main goal, of particular interest here is also the effect of
+In addition to our main goal, of particular interest here is the effect of
 anisotropic plasma viscosity, which in the following is found to strongly
@@
 direction of the magnetic field and $b_{\theta}$ is the component of $\vec{b}$
-in the azimuthal direction. These approximations allows the growth rate to be
+in the azimuthal direction. These approximations allow the growth rate to be
 written as
@@
 develops linearly alongside or shortly after the flute instability and then
-erupts during the its  nonlinear phase, dominating the dynamics and disrupting
+erupts during its nonlinear phase, dominating the dynamics and disrupting
 the   flute instability. The onset and the competition of the two instabilities
@@
 \eqref{eq:switching_model} at time moments $t=26$, $28$ and $30$ and at $z=0$.
-At $t=26$ the tube becomes unstable to  flute instability with azimuthal
+At $t=26$ the tube becomes unstable to the flute instability with azimuthal
 wavenumber $m=4$, when the plasma begins to  bulge out diagonally from the
@@
 lines and, as will be discussed further below, slows the growth of the kink
-instability. In the isotropic case, the flute instability has been damped to
+instability. In the isotropic case the flute instability has been damped to
 the extent that the kink instability grows uninhibited and quickly disrupts the
@@
 of the instability in this kind of flux tube (as was observed in our earlier
-work~\citep{quinnEffectAnisotropicViscosity2020}).
+work~\citep[][]{quinnEffectAnisotropicViscosity2020}).
 

### 2021-12-11 paper.tex
TEST Rado
Add revision command to highlight responses to reviewers

@@
 \newcommand{\jq}[2]{{#2}}
+
+\newcommand{\rev}{{\color{red} #1}}
 
@@
 and a key mechanism in the production of solar
-flares~\citep{hoodKinkInstabilitySolar1979}. Some of our previous work has
+flares~\citep{hoodKinkInstabilitySolar1979}. \rev{Some of our previous work} has
 investigated a twisted magnetic flux tube already linearly unstable to the

### 2021-12-27 paper.tex
Add paragraph in introduction motivating changing resistivity

@@
 
+\rev{It will be shown in our results that the flute instability is driven by
+a pressure gradient generated through Ohmic heating, so the value of
+resistivity is an important parameter in the development of the instability. In
+addition to exploring the effect of viscosity model on the flute instability,
+we also explore the effect of varying resistivity. Ideally, our simulations
+would be performed using a realistic coronal resistivity of approximately
+$10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a} however due to the
+dissipative nature of numerical schemes (particularly when using shock
+capturing techniques) this is computationally infeasible. In order to provide
+some sense of the scaling expected with resistivity, to allow us to speculate
+about the expected results at coronal values, we perform our simulations at
+two, computationally accessible values of resistivity, $10^{-3}$ and $10^{-4}$.
+This is not intended to replace a full parameter study so we will speculate
+whether our results generalise to lower values of resistivity but will not
+attempt to quantify any scaling laws or suggest concrete trends.}
+
 This paper is organised as follows. Section~\ref{sec-flute-intro} introduces

### 2021-12-27 paper.tex
Remove space
Add comment on recommending use of noise in instability study
Add more discussion on ansiotropy in discussion

@@
 
+\rev{We have found evidence of the flute instability using both models of
+viscosity, however isotropic viscosity damps the initial growth such that it
+does not develop beyond its linear phase before the faster growing kink
+instability disrupts the flux tube and halts the development of the flute. Due
+to the enhanced growth of the flute instability in the anisotropic case, the
+tube becomes more readily mixed and the growth rate of the kink instability is
+smaller. Beyond the effect on the growth of the two observed instabilities, the
+two viscosity models greatly affect both the viscous heating and Ohmic heating
+rates. Anisotropic viscosity is naturally less dissipative than isotropic
+viscosity and results in viscous heating approximately two orders of magnitude
+less than that associated with isotropic viscosity. This is somewhat offset by
+the anisotropic viscosity model permitting greater kinetic energy release and
+enhanced mixing, which in turn enhances Ohmic dissipation of heat through the
+generation of small, strong current sheets. The overall effect is that more
+heat is released when the viscosity is anisotropic. This is similarly observed
+in previous work~\citep{quinnEffectAnisotropicViscosity2020}.}
+
 It is likely that the $m=4$ azimuthal perturbation is excited due to influences
@@
 from numerical noise, allowing a secondary, fluting perturbation to also build
-and become significant enough to observe.
+and become significant enough to observe. \rev{As an explorative alternative to
+prescriptive perturbations, we recommend the use of numerical noise in the
+study of coronal instabilities.}
 
@@
 
-The form of viscosity has been found to significantly affect the growth of the
-flute instability. Importantly, isotropic viscosity is found to damp the growth
-of the flute instability to the degree that it is unable to grow appreciably
-before the onset of the faster growing nonlinear kink instability. Overall, the
-anisotropic model permits greater release of kinetic energy. Similar to~\citet{quinnEffectAnisotropicViscosity2020}, isotropic viscous heating is found
-to be lower than anisotropic (switching) viscous heating, by approximately two
-orders of magnitude.
-
 These numerical experiments have provided evidence that the flute instability

### 2021-12-27 paper.tex
Soften mixing statement and reword viscous heat generation phrase

@@
 rates. Anisotropic viscosity is naturally less dissipative than isotropic
-viscosity and results in viscous heating approximately two orders of magnitude
-less than that associated with isotropic viscosity. This is somewhat offset by
-the anisotropic viscosity model permitting greater kinetic energy release and
+viscosity and generates approximately two orders of magnitude less total
+viscous heat than isotropic viscosity. This is somewhat offset by the
+anisotropic viscosity model permitting greater kinetic energy release and
 enhanced mixing, which in turn enhances Ohmic dissipation of heat through the
@@
 
-Our set of numerical experiments has shown that the mixing as a result of the
-nonlinear flute instability appears to slow the growth of the kink instability.
+Our set of numerical experiments has suggested that the mixing as a result of the
+nonlinear flute instability slows the growth of the kink instability.
 It seems unlikely that in the linear regime the perturbations of the flute and

### 2021-12-27 paper.tex
Justify conclusion that mixing leads to slower kink growth

@@
 
-Our set of numerical experiments has suggested that the mixing as a result of the
-nonlinear flute instability slows the growth of the kink instability.
-It seems unlikely that in the linear regime the perturbations of the flute and
-kink are able to directly couple, given that the kink instability generally
-presents at the axis of a flux tube and the flute at some resonant surface away
-from the axis. Further investigation of the nonlinear interaction between the
-two instabilities is required.
+\rev{The growth rate of the kink instability is, counter-intuitively, lower in
+the weakly dissipative anisotropic cases, compared to the strongly dissipative
+isotropic cases, i.e. one would expect the kink instability to grow more
+quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
+the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
+this behaviour, where the kink instability grows (marginally) faster in the
+anisotropic cases. We conjecture it is the presence of the flute modes which
+negatively affects the growth of the kink instability. It seems unlikely that
+in the linear regime the perturbations of the flute and kink are able to
+directly couple, given that the kink instability generally presents at the axis
+of a flux tube and the flute at some resonant surface away from the axis.
+Instead of a linear coupling, we believe that the linear kink instability is
+affected by the more complex magnetic field configuration that arises due to
+the mixing caused by the nonlinear development of the flute modes (for example,
+compare figures~\ref{fig:field_line_plots_iso}
+and~\ref{fig:field_line_plots_swi}).}
 

### 2021-12-27 paper.tex
Clarify aims in discussion

@@
 
+\rev{Our aim in performing the reported numerical experiments was to explore
+the flute instability in a dynamically twisted coronal flux tube, specifically
+focussing on the effect of anisotropic viscosity on the development of the
+instability. In addition we wish to understand the effect the instability has
+on the proceeding kink instability, the effect on the overall heating generated
+through viscous and Ohmic dissipation, and the effect that varying resistivity
+has on the development of the flute.}
+
 \rev{We have found evidence of the flute instability using both models of

### 2021-12-27 paper.tex
Rework conclusion

@@
 does not develop beyond its linear phase before the faster growing kink
-instability disrupts the flux tube and halts the development of the flute. Due
-to the enhanced growth of the flute instability in the anisotropic case, the
-tube becomes more readily mixed and the growth rate of the kink instability is
-smaller. Beyond the effect on the growth of the two observed instabilities, the
-two viscosity models greatly affect both the viscous heating and Ohmic heating
+instability disrupts the flux tube and halts the development of the flute.
+Given that most numerical studies of the kink instability employ isotropic or
+shock viscosity, this is likely why the flute instability has not been
+previously reported.
+
+The growth rate of the kink instability is, counter-intuitively, lower in the
+weakly dissipative anisotropic cases, compared to the strongly dissipative
+isotropic cases, i.e. one would expect the kink instability to grow more
+quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
+the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
+this behaviour, where the kink instability grows (marginally) faster in the
+anisotropic cases. We conjecture it is the presence of the flute modes which
+negatively affects the growth of the kink instability. It seems unlikely that
+in the linear regime the perturbations of the flute and kink are able to
+directly couple, given that the kink instability generally presents at the axis
+of a flux tube and the flute at some resonant surface away from the axis.
+Instead of a linear coupling, we believe that the linear kink instability is
+disturbed by the more complex magnetic field configuration that arises due to
+the mixing caused by the nonlinear development of the flute modes. The
+complexity in the field can be seen by comparing
+figures~\ref{fig:field_line_plots_iso} and~\ref{fig:field_line_plots_swi}).
+
+Beyond the effect on the growth of the two observed instabilities, the two
+viscosity models greatly affect both the viscous heating and Ohmic heating
 rates. Anisotropic viscosity is naturally less dissipative than isotropic
 viscosity and generates approximately two orders of magnitude less total
-viscous heat than isotropic viscosity. This is somewhat offset by the
-anisotropic viscosity model permitting greater kinetic energy release and
-enhanced mixing, which in turn enhances Ohmic dissipation of heat through the
-generation of small, strong current sheets. The overall effect is that more
-heat is released when the viscosity is anisotropic. This is similarly observed
-in previous work~\citep{quinnEffectAnisotropicViscosity2020}.}
+viscous heat than isotropic viscosity. This is somewhat offset by anisotropic
+viscosity permitting greater kinetic energy release and enhanced mixing, which
+in turn enhances Ohmic dissipation of heat through the generation of small,
+strong current sheets. The overall effect is that more heat is generated when
+the viscosity is anisotropic, similar to what has been observed in previous
+work~\citep{quinnEffectAnisotropicViscosity2020}. In the context of
+coronal heating, this is encouraging: the use of a less dissipative viscosity
+model actually results in greater overall heating. How this result generalises
+to more realistic coronal resistivities, and whether this result holds true for
+other coronal instabilities, should be the subject of further investigation.}
+
+\rev{Since the flute instability only develops nonlinearly when using anisotropic viscosity, it is difficult to distinguish the effect of the instability from that of the viscosity itself on the viscous or Ohmic heating.
+TODO}
 
@@
 study of coronal instabilities.}
-
-\rev{The growth rate of the kink instability is, counter-intuitively, lower in
-the weakly dissipative anisotropic cases, compared to the strongly dissipative
-isotropic cases, i.e. one would expect the kink instability to grow more
-quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
-the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
-this behaviour, where the kink instability grows (marginally) faster in the
-anisotropic cases. We conjecture it is the presence of the flute modes which
-negatively affects the growth of the kink instability. It seems unlikely that
-in the linear regime the perturbations of the flute and kink are able to
-directly couple, given that the kink instability generally presents at the axis
-of a flux tube and the flute at some resonant surface away from the axis.
-Instead of a linear coupling, we believe that the linear kink instability is
-affected by the more complex magnetic field configuration that arises due to
-the mixing caused by the nonlinear development of the flute modes (for example,
-compare figures~\ref{fig:field_line_plots_iso}
-and~\ref{fig:field_line_plots_swi}).}
 

### 2022-01-11 paper.tex
?
few minor edits, mainly testing my git

@@
 
-\usepackage{newtxtext,newtxmath}
-\usepackage[T1]{fontenc} % modern encoding
+%\usepackage{newtxtext,newtxmath}
+%\usepackage[T1]{fontenc} % modern encoding
 
@@
 \usepackage{amsmath}	% Advanced maths commands
-%\usepackage{amssymb}	% Extra maths symbols
+\usepackage{amssymb}	% Extra maths symbols
 
@@
 
-\newcommand{\rev}{{\color{red} #1}}
+\newcommand{\rev}[1]{{\color{red} #1}}
 
@@
 and a key mechanism in the production of solar
-flares~\citep{hoodKinkInstabilitySolar1979}. \rev{Some of our previous work} has
-investigated a twisted magnetic flux tube already linearly unstable to the
+flares~\citep{hoodKinkInstabilitySolar1979}. \rev{In our previous work
+we have} investigated a twisted magnetic flux tube already linearly unstable to the
 helical kink instability, focussing specifically on the effect of anisotropic
@@
 dynamics~\citep{quinnEffectAnisotropicViscosity2020}.
-In~\citet{quinnEffectAnisotropicViscosity2020} and most other investigations of
-the kink instability e.g.~\citet{hoodCoronalHeatingMagnetic2009},
+\rev{There and in} most other investigations of
+the kink instability e.g.~\rev{\citep{hoodCoronalHeatingMagnetic2009}},
 a perturbation is applied to an already significantly twisted flux tube. An
@@
 kind of dynamic excitation of the kink instability is useful in that it
-represents more closely actual evolution of magnetic flux tubes and the
+represents more closely the actual evolution of magnetic flux tubes and the
 associated instabilities in the solar corona. In our simulations, the dynamic
 twisting of the flux tube reveals an additional instability, the flute
-instability, which has been theorised (for example,
-in~\citet{priestMagnetohydrodynamicsSun2013}). While oscillations resembling
+instability, which has been theorised, for example
+in~\rev{\citep{priestMagnetohydrodynamicsSun2013}}. While oscillations resembling
 flute perturbations have been found in simulations of coronal

### 2022-01-17 paper.tex
Text edits for main Q1,2,3

@@
 \usepackage{lineno}
+\usepackage[normalem]{ulem}
 
@@
 
-\newcommand{\rev}[1]{{\color{red} #1}}
+\newcommand{\rev}[1]{{\color{red} {#1}}}
+\newcommand{\newold}[2]{{#1}{}}
+\newcommand{\revcite}[1]{{\color{red} \underline{#1}}}
 
@@
 in numerical simulations it is usually induced by tightly-controlled
-perturbations and studied in isolation. In contrast, we find that when
-disturbances are introduced in our magnetohydrodynamic flux tube simulations by
-dynamic twisting of the flow at the boundaries fluting modes of instability are
-readily excited. We also find that the flute instability, which has been
+perturbations and studied in isolation. In contrast, we find that
+fluting modes of instability are readily excited when disturbances are
+introduced in our magnetohydrodynamic flux tube simulations by dynamic
+twisting of the flow at the boundaries. We also find that the flute instability, which has been 
 theorised but rarely observed in the coronal context,  is strongly enhanced
@@
 and a key mechanism in the production of solar
-flares~\citep{hoodKinkInstabilitySolar1979}. \rev{In our previous work
-we have} investigated a twisted magnetic flux tube already linearly unstable to the
+flares~\citep{hoodKinkInstabilitySolar1979}. \rev{Our previous work}
+investigated a twisted magnetic flux tube already linearly unstable to
+the 
 helical kink instability, focussing specifically on the effect of anisotropic
@@
 \rev{There and in} most other investigations of
-the kink instability e.g.~\rev{\citep{hoodCoronalHeatingMagnetic2009}},
+the kink instability e.g.~\revcite{\citep{hoodCoronalHeatingMagnetic2009}},
 a perturbation is applied to an already significantly twisted flux tube. An
@@
 boundaries to form a twisted flux tube which eventually becomes unstable. This
-kind of dynamic excitation of the kink instability is useful in that it
+kind of dynamic excitation of the kink instability \rev{}
+%is useful in that it
 represents more closely the actual evolution of magnetic flux tubes and the
@@
 instability, which has been theorised, for example
-in~\rev{\citep{priestMagnetohydrodynamicsSun2013}}. While oscillations resembling
+in~\revcite{\citep{priestMagnetohydrodynamicsSun2013}}. While oscillations resembling
 flute perturbations have been found in simulations of coronal
@@
 the instability which forms tubes of specific size in the
-photosphere~\citep{bunteInterchangeInstabilitySolar1993} and in the buoyancy of
+photosphere~\citep{bunteInterchangeInstabilitySolar1993}, and in the buoyancy of
 flux tubes~\citep{schuesslerInterchangeInstabilitySmall1984}. However, the
@@
 toroidal geometries such as the
-tokomak~\citep{shafranovFluteInstabilityCurrentcarrying1968}. The resistive
+tokamak~\citep{shafranovFluteInstabilityCurrentcarrying1968}. The resistive
 flute instability (also known as the resistive interchange instability) can be
@@
 has been given significantly more
-attention~\citet{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}.
+attention~\revcite{\citep{johnsonResistiveInterchangesNegativeV1967,correa-restrepoResistiveBallooningModes1983}}.
 While this body of research is useful and applicable in solar contexts, it is
@@
 field~\citep{hollwegViscosityChewGoldbergerLowEquations1986,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}.
-To take this into account, MacTaggaret et al. developed a phenomenological
-model of anisotropic
-viscosity~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} that
-captures the main physics of viscosity in the solar corona as outlined in the
+To take this into account,
+\revcite{\citet{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}}
+developed a phenomenological model of anisotropic  viscosity
+%\rev{\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}}
+that captures the main physics of viscosity in the solar corona as outlined in the
 analysis of~\cite{braginskiiTransportProcessesPlasma1965}, namely parallel
@@
 model of viscosity as ``the switching model''.
-In~\citet{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
+In \revcite{\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}}
 we implemented the switching model as a module for the widely-used general MHD
@@
 instabilities and turbulence is relatively
-unknown~\citet{klimchukSolvingCoronalHeating2006}. In addition to directly
+unknown~\revcite{\citep{klimchukSolvingCoronalHeating2006}}. In addition to directly
 heating the plasma, viscosity plays a part in the damping of instabilities and
@@
 
-\rev{It will be shown in our results that the flute instability is driven by
-a pressure gradient generated through Ohmic heating, so the value of
-resistivity is an important parameter in the development of the instability. In
-addition to exploring the effect of viscosity model on the flute instability,
-we also explore the effect of varying resistivity. Ideally, our simulations
-would be performed using a realistic coronal resistivity of approximately
-$10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a} however due to the
-dissipative nature of numerical schemes (particularly when using shock
-capturing techniques) this is computationally infeasible. In order to provide
-some sense of the scaling expected with resistivity, to allow us to speculate
-about the expected results at coronal values, we perform our simulations at
-two, computationally accessible values of resistivity, $10^{-3}$ and $10^{-4}$.
-This is not intended to replace a full parameter study so we will speculate
-whether our results generalise to lower values of resistivity but will not
-attempt to quantify any scaling laws or suggest concrete trends.}
-
-This paper is organised as follows. Section~\ref{sec-flute-intro} introduces
-the flute instability and relevant linear analyses,
-section~\ref{sec-numerical-setup} describes the governing equations, coronal
-loop model and details of the numerical parameters, section~\ref{sec-results}
-presents the overall development of the flute instability, before discussing
-features unique to the two values of resistivity studied,
-section~\ref{sec-discussion} discusses the limitations of the simulations, with
+\rev{The value of plasma resistivity strongly affects the development of
+the flute instability because the instability is due to pressure
+gradients generated through Ohmic heating as will be shown further below.
+Ideally, our simulations would be performed using a realistic coronal
+resistivity values of approximately
+$10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a}, however, due
+to the dissipative nature of numerical schemes (particularly when using shock
+capturing techniques) this is computationally infeasible.
+To overcome this limitation and to attempt to extrapolate results
+towards more realistic values, we perform and compare simulations at 
+two, computationally accessible, resistivity values, $10^{-3}$ and
+$10^{-4}$. This comparison runs as an additional theme of the paper,
+even if not quite a primary aim.}
+% To overcome this limitation, we perform and compare simulations at
+% two, computationally accessible, values of resistivity, $10^{-3}$ and
+% $10^{-4}$, and this comparison runs as an additional theme of the paper.
+% While this does not constitute a detailed parameter study of
+% resistivity (which is expensive) it allows us to speculate as to how
+% results might extrapolate to more realistic values.}
+%
+% \rev{It will be shown in our results that the flute instability is driven by
+% a pressure gradient generated through Ohmic heating, so the value of
+% resistivity is an important parameter in the development of the instability. In
+% addition to exploring the effect of viscosity model on the flute instability,
+% we also explore the effect of varying resistivity. Ideally, our simulations
+% would be performed using a realistic coronal resistivity of approximately
+% $10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a} however due to the
+% dissipative nature of numerical schemes (particularly when using shock
+% capturing techniques) this is computationally infeasible. In order to provide
+% some sense of the scaling expected with resistivity, to allow us to speculate
+% about the expected results at coronal values, we perform our simulations at
+% two, computationally accessible values of resistivity, $10^{-3}$ and $10^{-4}$.
+% This is not intended to replace a full parameter study so we will speculate
+% whether our results generalise to lower values of resistivity but will not
+% attempt to quantify any scaling laws or suggest concrete trends.}
+
+Our article is organised as follows. Section~\ref{sec-flute-intro} introduces
+the flute instability and \rev{recalls relevant background on its linear stability analysis}.
+Section~\ref{sec-numerical-setup} describes the governing equations,
+the coronal loop model and the numerical parameters used. Section~\ref{sec-results}
+presents the overall development of the flute instability before
+\rev{proceeding to compare simulations in the cases of various viscous
+anisotropy and various resistivity values. Here results are
+organised by resistivity values as this allows to contrast isotropic
+and anisotropic viscosity cases more directly.}
+Section~\ref{sec-discussion} discusses the limitations of the simulations, with
 suggestions for future work, and section~\ref{sec-conclusions} presents our
@@
 
-\subsection{The flute instability}
+\section{The flute instability}
 \label{sec-flute-intro}
@@
 k\ne0$ and is the only instability of this form which is a body instability,
-that is it moves the entire body of the flux tube. Perturbations where $m>1$
+i.e.{} it moves the entire body of the flux tube. Perturbations where $m>1$
 are termed flute or interchange instabilities.
@@
 effect of line-tying on the kink instability is investigated
-in~\citet{hoodKinkInstabilitySolar1979}. Where~\eqref{eq:suydams_criterion} is
+in \revcite{\citep{hoodKinkInstabilitySolar1979}}. Where~\eqref{eq:suydams_criterion} is
 not satisfied, the flux tube may be unstable to perturbations of the
@@
 Rayleigh-Taylor instability
-(see~\citep[][]{goldstonIntroductionPlasmaPhysics2020}) and is given by
+see~\citep[][]{goldstonIntroductionPlasmaPhysics2020}, and is given by
 \begin{equation}
@@
 validity of \eqref{eq:suydams_criterion} and \eqref{eq:fluting_growth_rate2}
-were used in~\citet{quinnEffectAnisotropicViscosity2020}. In contrast, in the
+were used in~\revcite{\citep{quinnEffectAnisotropicViscosity2020}}. In contrast, in the
 experiments reported in the following the system is driven and instabilities
-occur spontaneously due to random perturbation. As a result of the driving, the
+occur spontaneously due to random perturbations. As a result of the driving, the
 flux tube is also not in static equilibrium initially.
@@
 approximation of the general anisotropic viscosity tensor derived
-in~\citet{braginskiiTransportProcessesPlasma1965}. Expressions
+by \revcite{\citet{braginskiiTransportProcessesPlasma1965}}. Expressions
 \eqref{eq:isotropic_viscous_tensor} and \eqref{eq:switching_model} arise as
@@
 studied
-in~\citet{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015}
+in~\citep{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015}
 however the length of the flux tubes differs significantly. This configuration
@@
 viscosity has been included as detailed
-in~\citet{quinnKelvinHelmholtzInstabilityCollapse2021}. The resolution used in
+in~\citep{quinnKelvinHelmholtzInstabilityCollapse2021}. The resolution used in
 the current work is  $512$ grid points per dimension, comparable to the highest
@@
 the background resistivity is set to $\eta=10^{-3}$ and another where
-$\eta=10^{-4}$. As in~\citet{quinnEffectAnisotropicViscosity2020}, only
+$\eta=10^{-4}$. As in~\citep{quinnEffectAnisotropicViscosity2020}, only
 background resistivity is used. Each pair consists of one simulation using
@@
 current is similar to the current configuration arising due to the field
-prescribed in~\citet{quinnEffectAnisotropicViscosity2020}.
+prescribed in~\citep{quinnEffectAnisotropicViscosity2020}.
 
@@
 bulges move radially outwards into lower pressure regions they expand and
-accelerate, resulting in the entire pressure structure appearing taking the
+accelerate, resulting in the entire pressure structure \rev{\newold{}{appearing}} taking the
 shape of a four-leaf clover (figure~\ref{fig:swi-4_pressure_14}). By $t=30$ the
@@
 
-The faster growth of the kink compared to that measured in~\citet{quinnEffectAnisotropicViscosity2020} is attributed to the relative
-aspect ratios of the flux tubes. The tube prescribed in~\citet{quinnEffectAnisotropicViscosity2020} has an aspect ratio of
+The faster growth of the kink compared to that measured in~\citep{quinnEffectAnisotropicViscosity2020} is attributed to the relative
+aspect ratios of the flux tubes. The tube prescribed in~\citep{quinnEffectAnisotropicViscosity2020} has an aspect ratio of
 approximately $20$ compared to the tube studied here which has an aspect ratio
@@
 \caption{Quantitative differences in the observed perturbations between results
-between different resistivity values $\eta$. In all measurements the
+\rev{with} different resistivity values $\eta$. In all measurements the
 anisotropic viscosity model is used except for $k_\text{kink}$ where the
@@
 this behaviour, where the kink instability grows (marginally) faster in the
-anisotropic cases. We conjecture it is the presence of the flute modes which
-negatively affects the growth of the kink instability. It seems unlikely that
+anisotropic cases. We speculate that it is the presence of the flute modes which
+negatively affects the growth of the kink instability.} {It seems unlikely that
 in the linear regime the perturbations of the flute and kink are able to
 directly couple, given that the kink instability generally presents at the axis
-of a flux tube and the flute at some resonant surface away from the axis.
-Instead of a linear coupling, we believe that the linear kink instability is
+of a flux tube and the flute at some resonant surface away from the
+axis.} \rev{Instead of a linear coupling, we believe that the linear kink instability is
 disturbed by the more complex magnetic field configuration that arises due to
@@
 complexity in the field can be seen by comparing
-figures~\ref{fig:field_line_plots_iso} and~\ref{fig:field_line_plots_swi}).
+figures~\ref{fig:field_line_plots_iso} and~\ref{fig:field_line_plots_swi}.
 

### 2022-01-19 paper.tex
RQ1: Draft of enlarged Table 1

@@
 
-\begin{table}
-\caption{Quantitative differences in the observed perturbations between results
+\begin{table*}
+\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
 \rev{with} different resistivity values $\eta$. In all measurements the
@@
 isotropic viscosity model us used. Measurements times are listed in the main
-text.}
+text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
+\rev{with} different \rev{viscosity models and} resistivity values
+$\eta$. Measurements times are listed in the main text.} 
 \centering
-\begin{tabular}{ccc}
+\begin{tabular}{ccccc}
+&\multicolumn{2}{c}{\rev{Anisotropic}}& \multicolumn{2}{c}{\rev{Isotropic}} \\
 &
 $\eta=10^{-4}$ &
-$\eta=10^{-3}$ \\
+$\eta=10^{-3}$ &
+\rev{$\eta=10^{-4}$} &
+\rev{$\eta=10^{-3}$} \\
 \midrule
-Theoretical average linear growth rate of flute $\gamma$ & 0.86 & 1.79  \\
-Observed nonlinear growth rate of flute $\gamma$ & 0.69 & 1.06  \\
-Observed growth rate of kink $\lambda$ & 2.55 & 0.15\\
+Theoretical average linear growth rate of flute $\gamma$ & 0.86 & 1.79
+& \rev{??} & \rev{??} \\
+Observed nonlinear growth rate of flute $\gamma$ & 0.69 & 1.06  &
+\rev{--} & \rev{1.06}\\
+Observed growth rate of kink $\lambda$ & 2.55 & 0.15 & \rev{2.97} & \rev{0.15}\\
 \midrule
-Theoretical radius $r_s$ of peak flute growth rate & 0.125 & 0.163 \\
-Observed radius $r_s$ of peak flute growth rate & 0.125 & 0.163 \\
+Theoretical radius $r_s$ of peak flute growth rate & 0.125 & 0.163 &
+\rev{--} & \rev{??}\\
+Observed radius $r_s$ of peak flute growth rate & 0.125 & 0.163 & \rev{--} & \rev{??}\\
 \midrule
-Observed axial wave number $k_{\text{flute}}$ & 23.61 & 16.05 \\
-Observed axial wave number $k_{\text{kink}}$ & 4.57 & 4.53 \\
+Observed axial wave number $k_{\text{flute}}$ & 23.61 & 16.05 & \rev{--} & \rev{??} \\
+Observed axial wave number $k_{\text{kink}}$ & \rev{??} & \rev{??} & 4.57 & 4.53\\
 \end{tabular}
 \label{tab:kink_fluting_params}
-\end{table}
+\end{table*}
 
@@
 
+\rev{Perturbing a magnetic flux tube by dynamic twisting of the flow
+at the cylinder bases leads to excitation of the flute instability in
+addition to the well studied kink instability.}
+
 \rev{Our aim in performing the reported numerical experiments was to explore
@@
 the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
-this behaviour, where the kink instability grows (marginally) faster in the
+this behaviour, where the kink instability grows \newold{}{(marginally)} faster in the
 anisotropic cases. We speculate that it is the presence of the flute modes which
@@
 of a flux tube and the flute at some resonant surface away from the
-axis.} \rev{Instead of a linear coupling, we believe that the linear kink instability is
+axis.} \rev{We believe that, instead of a linear coupling, the linear kink instability is
 disturbed by the more complex magnetic field configuration that arises due to

### 2022-01-19 paper.tex
OPTIONAL LANGUAGE EDITS: Fixed all of them, including narative and parenthetical ctations

@@
 \rev{There and in} most other investigations of
-the kink instability e.g.~\revcite{\citep{hoodCoronalHeatingMagnetic2009}},
+the kink instability e.g.~that of \revcite{\citet{hoodCoronalHeatingMagnetic2009}},
 a perturbation is applied to an already significantly twisted flux tube. An
@@
 instability, which has been theorised, for example
-in~\revcite{\citep{priestMagnetohydrodynamicsSun2013}}. While oscillations resembling
+by~\revcite{\citet{priestMagnetohydrodynamicsSun2013}}. While oscillations resembling
 flute perturbations have been found in simulations of coronal
@@
 
-In addition to our main goal, of particular interest here is the effect of
+In addition to our main goal, of particular interest here is
+\rev{\sout{also}} the effect of
 anisotropic plasma viscosity, which in the following is found to strongly
@@
 model of viscosity as ``the switching model''.
-In \revcite{\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}}
+In \revcite{\citet{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}}, 
 we implemented the switching model as a module for the widely-used general MHD
@@
 effect of line-tying on the kink instability is investigated
-in \revcite{\citep{hoodKinkInstabilitySolar1979}}. Where~\eqref{eq:suydams_criterion} is
+by \revcite{\citet{hoodKinkInstabilitySolar1979}}. Where~\eqref{eq:suydams_criterion} is
 not satisfied, the flux tube may be unstable to perturbations of the
@@
 $\gamma$ can be found via a stability analysis analogous to that of the
-Rayleigh-Taylor instability
-see~\citep[][]{goldstonIntroductionPlasmaPhysics2020}, and is given by
+Rayleigh-Taylor instability~\citep[][]{goldstonIntroductionPlasmaPhysics2020}, and is given by
 \begin{equation}
@@
 direction of the magnetic field and $b_{\theta}$ is the component of $\vec{b}$
-in the azimuthal direction. These approximations allow the growth rate to be
+in the azimuthal direction. \rev{These approximations allow} the growth rate to be
 written as
@@
 validity of \eqref{eq:suydams_criterion} and \eqref{eq:fluting_growth_rate2}
-were used in~\revcite{\citep{quinnEffectAnisotropicViscosity2020}}. In contrast, in the
+were used by~\revcite{\citet{quinnEffectAnisotropicViscosity2020}}. In contrast, in the
 experiments reported in the following the system is driven and instabilities
@@
 asymptotic limits of the more general switching model used in our earlier works~\citep{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}
-which, includes both isotropic and anisotropic contributions and can switch
+which includes both isotropic and anisotropic contributions and can switch
 gradually between them depending on the strength of the magnetic field at
@@
 The non-dimensionalisation of equations \eqref{eq:MHD} is identical to that
-used in our earlier
-works~\citep{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}.
+used in the earlier
+works by \revcite{\citet{quinnEffectAnisotropicViscosity2020,quinnKelvinHelmholtzInstabilityCollapse2021}}
+\rev{\sout{and in reference (Arber... , see further below}}.
 A typical magnetic field strength $B_0$, density $\rho_0$ and length scale
@@
 studied
-in~\citep{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009,barefordShockHeatingNumerical2015}
+by~\revcite{\citet{quinnEffectAnisotropicViscosity2020,hoodCoronalHeatingMagnetic2009}}, and \revcite{\citet{barefordShockHeatingNumerical2015}},
 however the length of the flux tubes differs significantly. This configuration
@@
 viscosity has been included as detailed
-in~\citep{quinnKelvinHelmholtzInstabilityCollapse2021}. The resolution used in
+by~\revcite{\citet{quinnKelvinHelmholtzInstabilityCollapse2021}}. The resolution used in
 the current work is  $512$ grid points per dimension, comparable to the highest
@@
 the background resistivity is set to $\eta=10^{-3}$ and another where
-$\eta=10^{-4}$. As in~\citep{quinnEffectAnisotropicViscosity2020}, only
+$\eta=10^{-4}$. As in the work of ~\revcite{\citet{quinnEffectAnisotropicViscosity2020}}, only
 background resistivity is used. Each pair consists of one simulation using
@@
 current is similar to the current configuration arising due to the field
-prescribed in~\citep{quinnEffectAnisotropicViscosity2020}.
+prescribed by~\revcite{\citet{quinnEffectAnisotropicViscosity2020}}.
 
@@
 develops linearly alongside or shortly after the flute instability and then
-erupts during its nonlinear phase, dominating the dynamics and disrupting
+\rev{erupts during its nonlinear phase}, dominating the dynamics and disrupting
 the   flute instability. The onset and the competition of the two instabilities
@@
 \eqref{eq:switching_model} at time moments $t=26$, $28$ and $30$ and at $z=0$.
-At $t=26$ the tube becomes unstable to the flute instability with azimuthal
+At $t=26$ the tube becomes unstable \rev{to the flute instability} with azimuthal
 wavenumber $m=4$, when the plasma begins to  bulge out diagonally from the
@@
 
-The faster growth of the kink compared to that measured in~\citep{quinnEffectAnisotropicViscosity2020} is attributed to the relative
-aspect ratios of the flux tubes. The tube prescribed in~\citep{quinnEffectAnisotropicViscosity2020} has an aspect ratio of
+The faster growth of the kink compared to that measured by~\revcite{\citet{quinnEffectAnisotropicViscosity2020}} is attributed to the relative
+aspect ratios of the flux tubes. The tube prescribed by~\revcite{\citet{quinnEffectAnisotropicViscosity2020}} has an aspect ratio of
 approximately $20$ compared to the tube studied here which has an aspect ratio
@@
 
-Comparing the effect of the viscous models on the perturbations, in the
-isotropic case, the fluting perturbation is damped, while in the anisotropic
+Comparing the effect of the viscous models on the perturbations, \rev{in the
+isotropic case the fluting perturbation is damped}, while in the anisotropic
 case the kink perturbation is diminished, explaining why the flute instability
@@
 begin the reconnection process with the outer region of field that is typical
-of the instability in this kind of flux tube (as was observed in our earlier
-work~\citep[][]{quinnEffectAnisotropicViscosity2020}).
+of the instability in this kind of flux tube as was observed by \revcite{\citet{quinnEffectAnisotropicViscosity2020}}.
 
@@
 shock viscosity, this is likely why the flute instability has not been
-previously reported.
-
-The growth rate of the kink instability is, counter-intuitively, lower in the
+previously reported.}
+
+\rev{The growth rate of the kink instability is, counter-intuitively, lower in the
 weakly dissipative anisotropic cases, compared to the strongly dissipative
@@
 quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
-the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
+the simulations reported by~\citet{quinnEffectAnisotropicViscosity2020} display
 this behaviour, where the kink instability grows \newold{}{(marginally)} faster in the
@@
 of twisting an initially straight magnetic flux tube. This provides a different
-approach to that employed in the simulations performed in our earlier
-study~\citep{quinnEffectAnisotropicViscosity2020} in that the instabilities are
+approach to that employed in the simulations performed in the earlier
+study by ~\revcite{\citet{quinnEffectAnisotropicViscosity2020}} in that the instabilities are
 not excited by any prescribed perturbations but, instead, the field is
@@
 \url{https://github.com/jamiejquinn/Lare3d}, and has been archived
-at~\citep{keith_bennett_2020_4155546}. The version of Lare3d used in the
+by~\revcite{\citet{keith_bennett_2020_4155546}}. The version of Lare3d used in the
 production of the results presented here, including initial conditions,
 boundary conditions, control parameters and the anisotropic viscosity module,
-can be found in~\citet{keith_bennett_2020_4155625}. The data analysis and
+can be found in the repository of ~\revcite{\citet{keith_bennett_2020_4155625}}. The data analysis and
 instructions for reproducing all results found in this report may be also found

### 2022-01-20 paper.tex
Minor R4; figures rearranged
figure to Figure: MNRAS style guideline

@@
 of the driving. The appearance of the flute instability is illustrated by, for
-example, the pressure contours in figure~\ref{fig:kink_field_line_plots}, where
+example, the pressure contours in Figure~\ref{fig:kink_field_line_plots}, where
 the perturbations follow the pitch of the twisted field.
@@
 velocity $u_0$. The functions $u_r(r)$ and $u_t(t)$ are plotted in
-figure~\ref{fig:kink_driver}. At the lower boundary, the flow is in the
+Figure~\ref{fig:kink_driver}. At the lower boundary, the flow is in the
 opposite direction. This form of driver allows the system to be accelerated
@@
 
+\begin{figure}
+  \centering
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
+      \caption{Kinetic Energy}
+      \label{fig:kink_ke-4}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.49\textwidth}
+      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
+      \caption{Growth rate estimation}
+      \label{fig:kink_ke_log-4}
+    \end{subfigure}
+  \mycaption{Kinetic energy as a function of time showing the development and
+  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
+  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and the second
+  plot is a enlarged version of the first.}
+\label{fig:kink_str8_ke-4}%
+\end{figure}
+
 \section{Results}
@@
 Alfv\'en times, equal to the time taken for an Alfv\'en wave to traverse the
-entire length of the domain as visible early in figure~\ref{fig:kink_ke-4}.
+entire length of the domain as visible early in Figure~\ref{fig:kink_ke-4}.
 
@@
 the axis of the tube, then decreases radially outwards as seen in
-figure~\ref{fig:current_profiles}. The orientation of the twisting produces
+Figure~\ref{fig:current_profiles}. The orientation of the twisting produces
 a current flowing in the negative $z$-direction for $r\lessapprox0.5$. At $r
@@
 This current profile is reflected in the radial Ohmic heating profile
-(figure~\ref{fig:kink_straight_ohmic_heating_profile}) and, consequently, in
-the radial pressure profile (figure~\ref{fig:pressure_profiles}). The highly
+(Figure~\ref{fig:kink_straight_ohmic_heating_profile}) and, consequently, in
+the radial pressure profile (Figure~\ref{fig:pressure_profiles}). The highly
 pressurised core extends to $r\approx 0.2$--$0.4$ (depending on the value of
@@
 = 10^{-4}$ and for the anisotropic viscosity model. Note the difference in
-colour scale in figure~\ref{fig:swi-4_pressure_15}. The development in the
+colour scale in Figure~\ref{fig:swi-4_pressure_15}. The development in the
 isotropic case is similar.}
@@
 wavenumber $m=4$, when the plasma begins to  bulge out diagonally from the
-high-pressure core as seen in figure~\ref{fig:swi-4_pressure_13}. As  the
+high-pressure core as seen in Figure~\ref{fig:swi-4_pressure_13}. As  the
 bulges move radially outwards into lower pressure regions they expand and
 accelerate, resulting in the entire pressure structure \rev{\newold{}{appearing}} taking the
-shape of a four-leaf clover (figure~\ref{fig:swi-4_pressure_14}). By $t=30$ the
+shape of a four-leaf clover (Figure~\ref{fig:swi-4_pressure_14}). By $t=30$ the
 kink instability has disrupted the flute instability and is developing
-nonlinearly as evident in figure~\ref{fig:swi-4_pressure_15}. As is typical of
+nonlinearly as evident in Figure~\ref{fig:swi-4_pressure_15}. As is typical of
 nonlinear kink development, the tube continues to release its stored potential
@@
 
-\begin{figure}
-  \centering
-    \begin{subfigure}{0.49\textwidth}
-      \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
-      \caption{Kinetic Energy}
-      \label{fig:kink_ke-4}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.49\textwidth}
-      \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
-      \caption{Growth rate estimation}
-      \label{fig:kink_ke_log-4}
-    \end{subfigure}
-  \mycaption{Kinetic energy as a function of time showing the development and
-  measured growth rates $\gamma$ and $\lambda$ of the flute and kink
-  instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and the second
-  plot is a enlarged version of the first.}
-\label{fig:kink_str8_ke-4}%
-\end{figure}
+% \begin{figure}
+%   \centering
+%     \begin{subfigure}{0.49\textwidth}
+%       \includegraphics[width=\linewidth]{kinetic_energy-4.pdf}
+%       \caption{Kinetic Energy}
+%       \label{fig:kink_ke-4}
+%     \end{subfigure}
+%     \hfill
+%     \begin{subfigure}{0.49\textwidth}
+%       \includegraphics[width=\linewidth]{kinetic_energy_log-4.pdf}
+%       \caption{Growth rate estimation}
+%       \label{fig:kink_ke_log-4}
+%     \end{subfigure}
+%   \mycaption{Kinetic energy as a function of time showing the development and
+%   measured growth rates $\gamma$ and $\lambda$ of the flute and kink
+%   instabilities, respectively.}{Resistivity is $\eta=10^{-4}$ and the second
+%   plot is a enlarged version of the first.}
+% \label{fig:kink_str8_ke-4}%
+% \end{figure}
 
 Despite the flute instability appearing in the isotropic case
-(figure~\ref{fig:field_line_plots_iso}), only in the anisotropic case can the
+(Figure~\ref{fig:field_line_plots_iso}), only in the anisotropic case can the
 onset of both the flute and kink instabilities be seen in the kinetic energy
-profile shown in figure~\ref{fig:kink_ke_log-4}. Here, the nonlinear growth
+profile shown in Figure~\ref{fig:kink_ke_log-4}. Here, the nonlinear growth
 rates of the two instabilities are found to be $\gamma = 0.69$ for the flute
@@
 via Suydam's criterion~\eqref{eq:suydams_criterion}
-(figure~\ref{fig:suydam_condition_4}). The criterion represents a balance
+(Figure~\ref{fig:suydam_condition_4}). The criterion represents a balance
 between destabilising pressure gradients and stabilising magnetic shear and in
@@
 r \lessapprox 0.29$. The measure of linear fluting growth rate $\gamma$ is
-plotted as a function of $r$ at the same time (figure~\ref{fig:growth_rate_4}).
+plotted as a function of $r$ at the same time (Figure~\ref{fig:growth_rate_4}).
 The location of the peak growth matches nearly exactly the location of the
 resonant surface where the observed perturbation grows
-(figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate
+(Figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate
 can be found by averaging $\gamma$ over $r$, giving a growth rate of $0.86$.
@@
 that is $m B_{\theta}(r)/r + kB_z(r) = 0$, at $r=0.125$
-(figure~\ref{fig:resonant_surface_4}). This is precisely the predicted radius
-of peak linear growth (figure~\ref{fig:growth_rate_4}). At this time the
+(Figure~\ref{fig:resonant_surface_4}). This is precisely the predicted radius
+of peak linear growth (Figure~\ref{fig:growth_rate_4}). At this time the
 perturbation is close to resonance, that is $m B_{\theta}(r)/r + kB_z(r)
@@
 case the kink perturbation is diminished, explaining why the flute instability
-appears more readily in the anisotropic case (figure~\ref{fig:kink_ke-4}).
+appears more readily in the anisotropic case (Figure~\ref{fig:kink_ke-4}).
 
@@
 pressure gradient drives the bulges in profile further from the axis during the
-nonlinear phase (figure~\ref{fig:swi-3_pressure_12}). These bulges continue to
+nonlinear phase (Figure~\ref{fig:swi-3_pressure_12}). These bulges continue to
 extend outwards and mix the plasma as they develop. The kink instability can be
 observed moving the axis of the tube diagonally upwards and to the right in
-figure~\ref{fig:swi-3_pressure_15}. At this time in the $\eta=10^{-4}$ cases,
+Figure~\ref{fig:swi-3_pressure_15}. At this time in the $\eta=10^{-4}$ cases,
 the nonlinear development of the kink was at a later stage of its development
-(figure~\ref{fig:swi-4_pressure_15}). The development of the kink then proceeds
+(Figure~\ref{fig:swi-4_pressure_15}). The development of the kink then proceeds
 slowly as it moves the axis of the tube through the mixed region to eventually
@@
 develops much earlier than in the $\eta=10^{-4}$ cases and grows at an
-increased rate of $\gamma = 1.06$ (figure~\ref{fig:kink_ke_log-3}). The kink
+increased rate of $\gamma = 1.06$ (Figure~\ref{fig:kink_ke_log-3}). The kink
 instability grows at a rate of $\lambda \approx 0.15$, much slower than that
@@
 growth of the flute instability, the kink instability still generates the bulk
-of the kinetic energy (figure~\ref{fig:kink_ke-3}).
+of the kinetic energy (Figure~\ref{fig:kink_ke-3}).
 

### 2022-01-20 paper.tex
Minor Query R6: pressure change to gas pressure throughout results

@@
       \includegraphics[width=\linewidth]{pressure_profiles.pdf}
-      \caption{Pressure}
+      \caption{\rev{Gas pressure}}
       \label{fig:pressure_profiles}
     \end{subfigure}
-  \mycaption{ Gradients in the current density generate pressure gradients
+  \mycaption{Gradients in the current density generate \rev{gas} pressure gradients
   through Ohmic heating.}{Axial current density (a), Ohmic heating (b) and
@@
   the sign of the axial current density $j_z$ has been flipped for comparison
-  and the Ohmic heating is given by $Q_{\eta} = \eta j^2$. The pressure profile
-  of an additional test-case where $\eta=0$ is also shown. Line types are
-  indicated in the legend.}
+  and the Ohmic heating is given by $Q_{\eta} = \eta j^2$. The
+  \rev{gas} pressure profile of an additional test-case where $\eta=0$
+  is also shown. Line types are   indicated in the legend.}
   \label{fig:pressure_and_heating}
@@
 (Figure~\ref{fig:kink_straight_ohmic_heating_profile}) and, consequently, in
-the radial pressure profile (Figure~\ref{fig:pressure_profiles}). The highly
+the radial \rev{gas} pressure profile (Figure~\ref{fig:pressure_profiles}). The highly
 pressurised core extends to $r\approx 0.2$--$0.4$ (depending on the value of
 $\eta$) before increasing slightly around $r\approx 0.7$. The secondary bump in
-pressure is due to the outer shell of current. The pressure gradient near the
-axis provides the outwardly directed pressure force which competes against the
+\rev{gas} pressure is due to the outer shell of current. The \rev{gas}
+pressure gradient near the
+axis provides the outwardly directed \rev{gas} pressure force which competes against the
 binding action of the magnetic tension and this provides the mechanism of flute
-instability excitation.  The magnitude of the pressure gradient depends
+instability excitation.  The magnitude of the \rev{gas} pressure gradient depends
 strongly on the value of resistivity $\eta$, with lower values producing
 shallower gradients which (as shall be seen) are more stable to the flute
-instability. Indeed, when $\eta=0$, the radial pressure profile is nearly flat
+instability. Indeed, when $\eta=0$, the radial \rev{gas} pressure profile is nearly flat
 and the tube stable to the flute instability.
@@
     \end{subfigure}
-\mycaption{Pressure profiles during the development of the flute and kink
-instabilities.}{Shown are density plots of pressure at $z=0$ with $\eta
+\mycaption{\rev{Gas pressure} profiles during the development of the flute and kink
+instabilities.}{Shown are density plots of \rev{gas} pressure at $z=0$ with $\eta
 = 10^{-4}$ and for the anisotropic viscosity model. Note the difference in
@@
 in case of resistivity $\eta=10^{-4}$. Figure~\ref{fig:kink_pressure_slices-4}
-shows the pressure profile of the anisotropic viscosity case
+shows the \rev{gas} pressure profile of the anisotropic viscosity case
 \eqref{eq:switching_model} at time moments $t=26$, $28$ and $30$ and at $z=0$.
@@
 high-pressure core as seen in Figure~\ref{fig:swi-4_pressure_13}. As  the
-bulges move radially outwards into lower pressure regions they expand and
-accelerate, resulting in the entire pressure structure \rev{\newold{}{appearing}} taking the
+bulges move radially outwards into lower \rev{gas} pressure regions they expand and
+accelerate, resulting in the entire \rev{gas} pressure structure \rev{\newold{}{appearing}} taking the
 shape of a four-leaf clover (Figure~\ref{fig:swi-4_pressure_14}). By $t=30$ the
@@
 \mycaption{Simultaneous development of flute and kink instabilities in the
-isotropic and anisotropic cases illustrated by field lines and pressure
-contours.}{Field lines and contours of pressure (where $p=0.3$) are plotted at
+isotropic and anisotropic cases illustrated by field lines and
+\rev{gas} pressure
+contours.}{Field lines and contours of \rev{gas} pressure (where $p=0.3$) are plotted at
 $t=28$. Also shown is the velocity driver $u_r(\sqrt{x^2+y^2})$ at $z=2$. The
@@
 \mycaption{Perturbations corresponding to the flute and kink instabilities and
-the spatial radial distribution of the associated resonance function.}{Pressure
+the spatial radial distribution of the associated resonance
+function.}{\rev{Gas pressure}
 and velocity perturbations in $z$ (corresponding to the flute and kink
@@
     \end{subfigure}
-\mycaption{Pressure profiles at $z=0$ during the development of the flute and
+\mycaption{\rev{Gas pressure} profiles at $z=0$ during the development of the flute and
 kink instabilities in the higher resistivity anisotropic case.}{The viscosity
@@
 the higher resistivity value $\eta=10^{-3}$ in the case of anisotropic
-viscosity. Due to the enhanced Ohmic heating at $\eta=10^{-3}$, the pressure
+viscosity. Due to the enhanced Ohmic heating at $\eta=10^{-3}$, the \rev{gas} pressure
 gradient is substantially stronger than at $\eta=10^{-4}$ and the flute
@@
 instability occurs further from the axis, at $r\approx0.16$, and the larger
-pressure gradient drives the bulges in profile further from the axis during the
+\rev{gas} pressure gradient drives the bulges in profile further from the axis during the
 nonlinear phase (Figure~\ref{fig:swi-3_pressure_12}). These bulges continue to
@@
 fluting instability is not observed in the latter. Although the current
-distribution (and thus heating and pressure distributions) in the tubes
+distribution (and thus heating and \rev{gas} pressure distributions) in the tubes
 of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute
@@
 
-Since the main driver of the flute instability is the pressure gradient
-generated through Ohmic heating, it is prudent to ask if the same pressure
+Since the main driver of the flute instability is the \rev{gas} pressure gradient
+generated through Ohmic heating, it is prudent to ask if the same
+\rev{gas} pressure
 gradient could be generated using physical coronal values of the resistivity,
@@
 here do not incorporate radiation or thermal conduction, two processes which
-would remove energy (and hence reduce pressure) from high-pressure regions in
+would remove energy (and hence reduce \rev{gas} pressure) from high-pressure regions in
 a coronal loop and thus could prevent meeting the required conditions for the
@@
 significant flute instability, at least for this form of driver and mechanism
-of pressure generation. Regardless, coronal loops with strong radial pressure
+of \rev{gas} pressure generation. Regardless, coronal loops with
+strong radial \rev{gas} pressure
 gradients have been observed~\citep{foukalTemperatureStructurePressure1975},
@@
 instability and yet the faster growing kink instability can quickly dominate
-when the pressure gradient is small enough, the opposite case is also observed.
+when the \rev{gas} pressure gradient is small enough, the opposite case is also observed.
 A faster growing flute instability appears to slow the growth of the kink

### 2022-01-20 paper.tex
Minor Query R8: groth is damped

@@
 interested in here, and it shall be reported that the use of anisotropic
-viscosity permits the growth of the flute instability, which is otherwise
+viscosity permits the \rev{growth} of the flute instability, which is otherwise
 strongly damped by isotropic viscosity.
@@
 highly mixed. In the  isotropic viscosity case which will not be illustrated by
-a separate figure, the flute instability is present but damped, and it is
-quickly outcompeted by the kink instability which quickly dominates the
-dynamics.
+a separate figure, the flute instability is present but \rev{its
+ growth is damped relative to the anisotropic case}, and it is 
+outcompeted by the kink instability which quickly dominates the dynamics.
 
@@
 have on the initial stages of the flute and kink instabilities in 3D. While the
-flute instability is observed in both cases, it is damped in the isotropic case
-and grows faster in the anisotropic case. In the latter case, the extended
+flute instability is observed in both cases,
+\rev{its growth is  damped} in the isotropic case and grows faster in
+the anisotropic case. 
+In the latter case, the extended
 development of the flute instability appears to disrupt the inner core of field
 lines and, as will be discussed further below, slows the growth of the kink
-instability. In the isotropic case the flute instability has been damped to
-the extent that the kink instability grows uninhibited and quickly disrupts the
+instability. In the isotropic case the
+\rev{growth of the flute instability is damped relative to the anisotropic case}
+to the extent that the kink instability grows uninhibited and quickly disrupts the
 fluting.

### 2022-01-21 paper.tex
Minor Query R9: Added [Using equation 6 ...] to text.

@@
 tube is unstable over a wide range of radii, for $ 0.02 \lessapprox
-r \lessapprox 0.29$. The measure of linear fluting growth rate $\gamma$ is
-plotted as a function of $r$ at the same time (Figure~\ref{fig:growth_rate_4}).
+r \lessapprox 0.29$. \rev{Using
+  equation~\eqref{eq:fluting_growth_rate2}, the} linear
+fluting growth rate $\gamma$ is plotted as a function of $r$ at the
+same time 
+(Figure~\ref{fig:growth_rate_4}).
+
 The location of the peak growth matches nearly exactly the location of the

### 2022-01-21 paper.tex
Minor Query R11: carefully mentioned peak linear growth rate r_s

--- 2022-01-20 paper.tex
@@
 $t=20$ for $\eta=10^{-4}$ and using the anisotropic model. The location of the
-peak linear growth rate is also shown.}
+\rev{peak linear growth rate $r_s$} is also shown.}
 \label{fig:stability_and_growth}%
@@
 unstable to perturbations of the form~\eqref{eq:kink_perturbation} at $t=20$
-via Suydam's criterion~\eqref{eq:suydams_criterion}
-(Figure~\ref{fig:suydam_condition_4}). The criterion represents a balance
-between destabilising pressure gradients and stabilising magnetic shear and in
-this case, the shear is so small and the pressure gradient so large that the
-tube is unstable over a wide range of radii, for $ 0.02 \lessapprox
-r \lessapprox 0.29$. The measure of linear fluting growth rate $\gamma$ is
-plotted as a function of $r$ at the same time (Figure~\ref{fig:growth_rate_4}).
-The location of the peak growth matches nearly exactly the location of the
-resonant surface where the observed perturbation grows
+via Suydam's criterion~\eqref{eq:suydams_criterion} as shown in
+Figure~\ref{fig:suydam_condition_4}. The criterion represents a
+balance between destabilising pressure gradients and stabilising
+magnetic shear and in this case, the shear is so small and the
+pressure gradient so large that the tube is unstable over a wide range
+of radii, for $ 0.02 \lessapprox r \lessapprox 0.29$.
+\rev{Using equation~\eqref{eq:fluting_growth_rate2}, the} linear
+fluting  growth rate $\gamma$ is plotted as a function of $r$ at
+$t=20$ in Figure~\ref{fig:growth_rate_4}. \rev{At any fixed moment,
+the radial dependence of the flute instability growth rate, $\gamma(r)$, is a concave
+function and peaks at a certain radius that we denote by $r_s$ in
+Figure~\ref{fig:growth_rate_4} and Table \ref{tab:kink_fluting_params}
+where we compare theoretical and numerical estimates.}
+
+The location of the peak \rev{fluting growth rate $r_s$} matches
+nearly exactly the location of the resonant surface where the observed perturbation grows
 (Figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate
@@
 (Figure~\ref{fig:resonant_surface_4}). This is precisely the predicted radius
-of peak linear growth (Figure~\ref{fig:growth_rate_4}). At this time the
-perturbation is close to resonance, that is $m B_{\theta}(r)/r + kB_z(r)
-\approx 0$, over a range of radii from $r=0.125$ to $0.2$.
+of peak linear \rev{flute growth $r_s$} seen in
+Figure~\ref{fig:growth_rate_4}. At this time the perturbation is close
+to resonance, that is $m B_{\theta}(r)/r + kB_z(r)\approx 0$, over a
+range of radii from $r=0.125$ to $0.2$.
 
@@
 The results of the isotropic cases are qualitatively similar. The radius of
-peak $\gamma$ is calculated at time $t=20$. The fluting wavenumber $k$ and
+peak \rev{linear flute growth rate $r_s$} is calculated at time $t=20$. The fluting wavenumber $k$ and
 observed $r_s$ are measured at times just prior to the nonlinear development of
@@
 different resonant surface within which the perturbation grows, the location
-being dictated by the peak of the linear growth rate. Note that the location of
+being dictated by the peak of the linear \ref{flute growth rate $r_s$}. Note that the location of
 this peak again matches well the location of the observed resonant surface, as
-in the $\eta=10^{-4}$ cases. Similar to the $\eta=10^{-4}$ cases, the peak
-growth rate predicted by the linear analysis is the same order of magnitude as
+in the $\eta=10^{-4}$ cases. Similar to the $\eta=10^{-4}$ cases, the \rev{peak
+growth rate $r_s$} predicted by the linear analysis is the same order of magnitude as
 the observed growth rate.

### 2022-01-21 paper.tex
Minor Query R11: carefully mentioned peak linear growth rate r_s

@@
 different resonant surface within which the perturbation grows, the location
-being dictated by the peak of the linear \ref{flute growth rate $r_s$}. Note that the location of
+being dictated by the peak of the linear \rev{flute growth rate $r_s$}. Note that the location of
 this peak again matches well the location of the observed resonant surface, as

### 2022-01-21 paper.tex
Minor Query R12: Fig7a - perturbations vs profiles

@@
       \includegraphics[width=\linewidth]{perturbations_4.pdf}
-      \caption{Perturbations}
+      \caption{\rev{Selected flow and pressure profiles.}}
       \label{fig:pressure_pert_4}
@@
       \includegraphics[width=\linewidth]{resonant_surface_4.pdf}
-      \caption{Resonance function}
+      \caption{Resonance function.}
       \label{fig:resonant_surface_4}
     \end{subfigure}
-\mycaption{Perturbations corresponding to the flute and kink instabilities and
-the spatial radial distribution of the associated resonance
-function.}{\rev{Gas pressure}
-and velocity perturbations in $z$ (corresponding to the flute and kink
-instabilities, respectively) and of the resonance surface $m B_{\theta}(r)/r
+  \mycaption{\rev{\newold{Selected flow and pressure profiles and the 
+resonance function defined by equation
+\eqref{eq:resonant_surface}.}{Perturbations corresponding to the flute
+        and kink instabilities and the spatial radial distribution of the associated resonance
+function.}}}{\rev{(a) Gas pressure} and velocity \rev{profiles in $z$}
+    \rev{at the fixed point $(r, \theta) = (0.101, 0)$} \rev{assuming the form of the most
+      unstable modes}. (b) The resonance surface $m B_{\theta}(r)/r
 + kB_z(r)$ as a function of $r$ using the observed fluting perturbation
@@
 
-The observed perturbations corresponding to the flute and kink instabilities at
-$t=26$ are shown in Figure~\ref{fig:pressure_pert_4}. The fluting perturbation
-is most easily observed in the pressure and is plotted as a function of $z$
-following a line through the point $(r, \theta) = (0.101, 0)$. The kink
+The \rev{flow and pressure profiles in the axial direction $z$} at
+$t=26$ are shown in Figure~\ref{fig:pressure_pert_4} \rev{and at this
+moment they assume the form of a superposition of the unstable modes
+with the largest amplitude. In particular, the} fluting perturbation
+  is most easily observed in the pressure \rev{profile and} \rev{\newold{}{ plotted
+  as a function of $z$ following a line through the point $(r, \theta) = (0.101, 0)$.}} \rev{the} kink
 instability is best revealed in the $x$-velocity (a proxy for the radial
-velocity) through the axis. Comparing the magnitudes of the perturbations at
+velocity) through the axis. Comparing the magnitudes of the \rev{profiles} at
 this time suggests the flute instability is close to transitioning to its

### 2022-01-21 paper.tex
Minor Query R13: the two peaks of what?

@@
 
-The value of $k$ for each perturbation is calculated as $k
+The value of $k$ for each \rev{instability mode} is calculated as $k
 = 2\pi/\tilde{\lambda}$ where $\tilde{\lambda}$ is the wavelength of the
 perturbation, measured as the difference between the two peaks closest to $z=0$
-(thus minimising the influence of line-tying on the measurement). This gives
+(thus minimising the influence of line-tying on the
+measurement). \rev{In particular, the two peaks closest to $z=0$ of
+  the pressure profile are used to calculate the wavenumber of
+  the flute mode $k_{\text{flute}}$ and those of the radial velocity
+  profile are used to calculate the wavenumber of
+  the kink mode $k_{\text{kink}}$, respectively.} This gives
 a value of $k_{\text{flute}}=23.61$ and $k_{\text{kink}}=4.57$ for both

### 2022-01-25 paper.tex
Minor Query R16: cited Torok and Kliem

@@
 and has been well studied in the coronal
-context~\citep{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003b,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020}.
+context
+\citep{hoodKinkInstabilitySolar1979,
+  hoodCoronalHeatingMagnetic2009,
+  browningSolarCoronalHeating2003b,
+  Torok2003, Torok2004, Torok2005,
+  barefordShockHeatingNumerical2015,
+  quinnEffectAnisotropicViscosity2020}.
 Given its energetic nonlinear development, it is considered a potential
